### 2022-08-31 doc/paper.tex
Final name I think.

\documentclass[a4paper]{elsarticle}
% vim: tw=0 wm=0

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}

\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}

\usepackage{blindtext}

\usepackage{numprint}
\npdecimalsign{.}
\npthousandsep{}

\usepackage[draft,nomargin,inline]{fixme}
\fxsetface{inline}{\itshape}
\fxsetface{env}{\itshape}
%\fxuselayouts{margin}
%\fxuselayouts{inline}
\fxusetheme{color}

\usepackage{url}
\newcommand{\keywords}[1]{\par\aDSvspace\baselineskip
	\noindent\keywordname\enspace\ignorespaces#1}

\usepackage{tikz}
\usetikzlibrary{positioning}
\definecolor{canaryyellow}{rgb}{1.0, 0.94, 0.0}
\definecolor{brightgreen}{rgb}{0.4, 1.0, 0.0}
\definecolor{jazzberryjam}{rgb}{0.65, 0.04, 0.37}

%defining of command

\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}
\newcommand\str[1]{\texttt{#1}}
\newcommand\pL[1][]{\ensuremath{p^{\mathrm{L}#1}}}
\newcommand\pR[1][]{\ensuremath{p^{\mathrm{R}#1}}}
\newcommand\qL{\ensuremath{q^\mathrm{L}}}
\newcommand\qR{\ensuremath{q^\mathrm{R}}}
\newcommand\pLH{\ensuremath{\hat{p}^\mathrm{L}}}
\newcommand\pRH{\ensuremath{\hat{p}^\mathrm{R}}}
\newcommand{\Vext}{\ensuremath{V_\mathrm{{ext}}}}
\newcommand\UB{\ensuremath{\mathrm{UB}}}
\newcommand\Sigmand{\ensuremath{\Sigma^\mathrm{nd}}}
\newcommand{\mdmwnpp}{MDMWNPP\xspace}

\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}
\setlength{\leftmarginii}{1.8ex}
\raggedbottom
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}

% scaling factor for tables
\newcommand\tabscale{0.8}
\newtheorem{Theorem}{Theorem}
\newtheorem{Lemma}{Lemma}

\begin{document}

	%\setlength{\parindent}{0pt}  % disallow indentations
	%\numberwithin{table}{1}
	%\mainmatter  % start of an individual contribution

	% first the title is needed
	\title{RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}

\author[1]{Aleksandar Kartelj}
\author[2]{Marko Djukanovi\'c}
	\address[1]{$kartelj@matf.bg.ac.rs$, \\  Faculty of Mathematics, University of Belgrade, Serbia}
    \address[2]{$ marko.djukanovic@pmf.unibl.org$,\\   Faculty of Natural Sciences and Mathematics, University of Banja Luka, Bosnia and Herzegovina}
	\begin{abstract}

	\end{abstract}
	\maketitle

\section{Introduction}\label{sec:introduction}

\subsection{Contributions of this work}

The main contributions of this work can be summarized as follows:

\begin{enumerate}
	\item The proposed method outperforms all state-of-the-art methods for ground-truth problems from literature, considered in the SRBench benchmark.

	\item It shows high robustness, which is proved by testing methods under different levels of Gaussian white noise.

	\item The method is very efficient, taking in average around xyz seconds to reach exact solution -- when exact solution is found.

	\item The new set of unbiased instances is introduced -- randomly generated formula of various sizes. All the other methods were tested against this new test-bed. The proposed RILS-ROLS method showed to be dominant here as well. 
\end{enumerate}

\section{Problem definition and search space}
\label{sec:search-space}

\section{Literature review}\label{sec:lit-rev}

\section{Proposed iterated local search method}\label{sec:rils}

\section{Experimental evaluation}\label{sec:experiments}

\subsection{Parameter tuning}
SAMO JEDAN PARAMETAR!!!

\subsection{Comparison with other methods}

\subsection{Statistical evaluation}

\section{Conclusions and future work}\label{sec:conclusions}

 \newpage
 \appendix

 \section{Complete results for a single random seed}\label{sec:appendix-1}

 \section{Overview of RILS-ROLS python package}\label{sec:appendix-2}

 \section{Analysis within SRBench}

\newpage
%\section*{References}
\bibliographystyle{abbrv}	
%\bibliography{bib}

\end{document}

### 2022-08-31 rils_rols/node.py

@@ -1,0 +1,579 @@
+from abc import abstractmethod
+import copy
+from math import acos, asin, atan, ceil, cos, exp, floor, log, sin, sqrt, tan
+
+class Node:
+    tmp = -1
+    node_value_cache = {}
+    cache_hits = 0
+    cache_tries = 1
+
+    VERY_SMALL = 0.0001
+
+    @classmethod
+    def reset_node_value_cache(cls):
+        cls.node_value_cache = {}
+        cls.cache_hits = 0
+        cls.cache_tries = 1    
+
+    def __init__(self):
+        self.arity = 0
+        self.left = None
+        self.right = None
+        self.symmetric = True
+
+    @abstractmethod
+    def evaluate_inner(self,X, a=None, b=None):
+        pass
+
+    def evaluate(self, X):
+        if self.arity==0:
+            return self.evaluate_inner(X, None, None)
+        elif self.arity == 1:
+            leftVal = self.left.evaluate(X)
+            return self.evaluate_inner(X,leftVal, None)
+        elif self.arity==2:
+            leftVal = self.left.evaluate(X)
+            rightVal = self.right.evaluate(X)
+            return self.evaluate_inner(X,leftVal,rightVal)
+        else:
+            raise Exception("Arity > 2 is not allowed.")
+
+    def evaluate_all(self, X, cache):
+        key = str(self)
+        Node.cache_tries+=1
+        yp = []
+        if cache and key in Node.node_value_cache:
+            Node.cache_hits+=1
+            yp = Node.node_value_cache[key]
+        else:
+            if self.arity==2:
+                left_yp = self.left.evaluate_all(X, cache)
+                right_yp = self.right.evaluate_all(X, cache)
+                for i in range(len(X)):
+                    ypi = self.evaluate_inner(X[i], left_yp[i], right_yp[i])
+                    yp.append(ypi)
+            elif self.arity==1:
+                left_yp = self.left.evaluate_all(X, cache)
+                for i in range(len(X)):
+                    ypi = self.evaluate_inner(X[i], left_yp[i], None)
+                    yp.append(ypi)
+            elif self.arity==0:
+                for i in range(len(X)):
+                    ypi = self.evaluate_inner(X[i],None, None)
+                    yp.append(ypi)
+            if cache:
+                Node.node_value_cache[key]=yp
+                if len(Node.node_value_cache)==5000:
+                    Node.node_value_cache.clear()
+        return yp
+
+    def expand_fast(self):
[…]

### 2022-08-31 rils_rols/rils_rols.py

@@ -1,0 +1,419 @@
+import copy
+import time
+import math
+from random import Random
+from sklearn.base import BaseEstimator
+import copy
+from sympy import *
+from .node import Node, NodeConstant, NodeVariable, NodePlus, NodeMinus, NodeMultiply, NodeDivide, NodeSqr, NodeSqrt, NodeLn, NodeExp, NodeSin, NodeCos, NodeArcCos, NodeArcSin
+
+import warnings
+
+from .solution import Solution
+warnings.filterwarnings("ignore")
+
+class RILSRegressor(BaseEstimator):
+
+    def __init__(self, max_fit_calls=100000, max_seconds=100, complexity_penalty=0.001, error_tolerance=0.000001,random_state=0):
+        self.max_seconds = max_seconds
+        self.max_fit_calls = max_fit_calls
+        self.complexity_penalty = complexity_penalty
+        self.random_state = random_state
+        self.error_tolerance = error_tolerance
+
+
+    def __reset(self):
+        self.model = None
+        self.varNames = None
+        self.ls_it = 0
+        self.main_it = 0
+        self.last_improved_it = 0
+        self.time_start = 0
+        self.time_elapsed = 0
+        self.rg = Random(self.random_state)
+        Solution.clearStats()
+        Node.reset_node_value_cache()
+
+    def __setup_nodes(self, variableCount):
+        self.allowed_nodes=[NodeConstant(-1), NodeConstant(0), NodeConstant(0.5), NodeConstant(1), NodeConstant(2), NodeConstant(math.pi)]
+        for i in range(variableCount):
+            self.allowed_nodes.append(NodeVariable(i))
+        self.allowed_nodes+=[NodePlus(), NodeMinus(), NodeMultiply(), NodeDivide(), NodeSqr(), NodeSqrt(),NodeLn(), NodeExp(),NodeSin(), NodeCos(), NodeArcSin(), NodeArcCos()]
+
+    def fit(self, X, y):
+        x_all = copy.deepcopy(X)
+        y_all = copy.deepcopy(y)
+        # take 1% of points or at least 100 points initially 
+        n = int(0.01*len(x_all))
+        if n<100:
+            n=100
+        print("Taking "+str(n)+" points initially.")
+        X = x_all[:n]
+        y = y_all[:n]
+        size_increased_main_it = 0
+
+        self.__reset()
+        self.start = time.time()
+        if len(X) == 0:
+            raise Exception("Input feature data set (X) cannot be empty.")
[…]

### 2022-08-31 rils_rols/solution.py

@@ -1,0 +1,289 @@
+import copy
+from math import e, inf
+import math
+
+from .node import NodeAbs, NodeArcCos, NodeArcSin, NodeArcTan, NodeCeil, NodeConstant, NodeCos, NodeExp, NodeFloor, NodeLn, NodeMax, NodeMin, NodeMultiply, NodePlus, NodePow, NodeSgn, NodeSin, NodeTan, NodeVariable
+from .utils import R2, RMSE
+from sympy import *
+from sympy.core.numbers import ImaginaryUnit
+from sympy.core.symbol import Symbol
+import numpy as np
+import statsmodels.api as sma
+
+
+class Solution:
+
+    math_error_count = 0
+    fit_calls = 0
+    fit_fails = 0
+
+    @classmethod
+    def clearStats(cls):
+        cls.math_error_count=0
+        cls.fit_fails = 0
+        cls.fit_calls=0
+
+    def __init__(self, factors, complexity_penalty):
+        self.factors =  copy.deepcopy(factors)
+        self.complexity_penalty = complexity_penalty
+
+    def __str__(self) -> str:
+        return "+".join([str(x) for x in self.factors])
+
+    def evaluate_all(self,X, cache):
+        yp = np.zeros(len(X))
+        for fact in self.factors:
+            fyp = fact.evaluate_all(X, cache)
+            for i in range(len(fyp)):
+                yp[i]+=fyp[i]
+        return yp
+
+    def fitness(self, X, y, cache=True):
+        try:
+            Solution.fit_calls+=1
+            yp = self.evaluate_all(X, cache) 
+            return (1-R2(y, yp), RMSE(y, yp), self.size())
+        except Exception as e:
+            #print(e)
+            Solution.math_error_count+=1
+            Solution.fit_fails+=1
+            return (inf, inf, inf)
+
+    def size(self):
+        totSize = len(self.factors) 
+        for fact in self.factors:
+            totSize+=fact.size()
+        return totSize
+        
+
+    def fit_constants_OLS(self, X, y):
+        new_factors = []
+        for fact in self.factors:
+            if fact.contains_type(type(NodeVariable(0))):
+                new_factors.append(copy.deepcopy(fact))
+        Xnew = np.zeros((len(X), len(new_factors)))
+        try:
+            for i in range(len(new_factors)):
+                fiX = new_factors[i].evaluate_all(X, True)
+                for j in range(len(fiX)):
+                    if math.isnan(fiX[j]):
[…]

### 2022-08-31 rils_rols/utils.py

@@ -1,0 +1,73 @@
+from math import nan, sqrt
+from statistics import mean
+from numpy.random import RandomState
+
+# described in Apendix 4 of paper Contemporary Symbolic Regression Methods and their Relative Performance
+def noisefy(y, noise_level, random_state):
+    yRMSE = 0
+    for i in range(len(y)):
+        yRMSE+=(y[i]*y[i])
+    yRMSE=sqrt(yRMSE/len(y))
+    yRMSE_noise_SD = noise_level*yRMSE
+    rg = RandomState(random_state)
+    noise = rg.normal(0, yRMSE_noise_SD, len(y))
+    y_n = []
+    for i in range(len(y)):
+        y_n.append(y[i]+noise[i])
+    return y_n
+
+def RMSE(yt, yp):
+    if len(yp)!=len(yt):
+        raise Exception("Vectors of predicted and true y values should be of same size.")
+    try:
+        rmse = 0.0
+        for i in range(len(yp)):
+            err = yp[i]-yt[i]
+            err*=err
+            if err == nan:
+                return nan
+            rmse+=err
+        rmse = sqrt(rmse/len(yp))
+        return rmse
+    except OverflowError:
+       return nan
+
+def percentile_abs_error(yt, yp, percentile):
+    if len(yp)!=len(yt):
+        raise Exception("Vectors of predicted and true y values should be of same size.")
+    try:
+        errors = []
+        for i in range(len(yp)):
+            err = yp[i]-yt[i]
+            if err<0:
+                err*=-1
+            if err == nan:
+                return nan
+            errors.append(err)
+        errors.sort()
+        idx = int(percentile*(len(yp)-1)/100)
+        return errors[idx]
+    except OverflowError:
+        return nan
+
+def R2(yt, yp):
+    if len(yp)!=len(yt):
+        raise Exception("Vectors of predicted and true y values should be of same size.")
+    try:
+        yt_mean = mean(yt)
+        ss_res = 0
+        ss_tot = 0
+        for i in range(len(yp)):
+            err = yp[i]-yt[i]
+            err*=err
+            if err == nan:
+                return nan
+            ss_res+=err
+            var_err = yt_mean-yt[i]
+            var_err*=var_err
+            ss_tot+=var_err
+        if ss_tot<0.000000000001:
+            ss_tot=1
+        return 1-ss_res/ss_tot
+    except OverflowError:
+        return nan

### 2022-08-31 setup.py

@@ -1,0 +1,12 @@
+from setuptools import setup
+
+setup(name='rils',
+    version='0.0',
+    description='Symbolic Regression Tool Based On The Iterated Local Search',
+    author='Aleksandar Kartelj, Marko Đjukanović',
+    author_email='aleksandar.kartelj@gmail.com',
+    url='https://github.com/kartelj/rils',
+    packages = ['rils-rols'],
+    package_dir = {'rils':'rils_rols'}, 
+    install_requires=['joblib', "sklearn", "sympy", "chardet", "certifi", "idna"],
+)

### 2022-08-31 test.py

@@ -1,0 +1,48 @@
+from datetime import datetime
+from random import Random
+import rils
+import utils
+from os import listdir
+from os.path import isfile, join
+
+
+instances_dir = "toyInstances" 
+random_state = 12345
+train_perc = 0.75
+
+instance_files = [f for f in listdir(instances_dir) if isfile(join(instances_dir, f))]
+
+out_path = "out_{0}.txt".format(datetime.now().strftime("%Y_%m_%d_%H_%M_%S"))
+with open(out_path, "w") as f:
+    f.write("Tests started\n")
+
+for fpath in instance_files:
+    print("Running instance "+fpath)
+    with open(instances_dir+"/"+ fpath) as f:
+        lines = f.readlines()
+        train_cnt = int(len(lines)*train_perc)
+        rg = Random(random_state)
+        rg.shuffle(lines)
+        X_train = []
+        y_train= []    
+        X_test = []
+        y_test = []
+        for i in range(len(lines)):
+            line = lines[i]       
+            tokens = line.split(sep="\t")
+            newX = [float(t) for t in tokens[:len(tokens)-1]]
+            newY = float(tokens[len(tokens)-1])
+            if i<train_cnt:
+                X_train.append(newX)
+                y_train.append(newY)
+            else:
+                X_test.append(newX)
+                y_test.append(newY)
+
+    vnl = rils.RILS(random_state = random_state)
+    vnl.fit(X_train, y_train)
+    reportString = vnl.fit_report_string(X_train, y_train)
+    yp = vnl.predict(X_test)
+    print("%s\tRMSE=%.3f\tR2=%.3f"%(vnl, utils.RMSE(y_test, yp), utils.R2(y_test, yp)))
+    with open(out_path, "a") as f:
+        f.write(fpath+"\tTestRMSE="+str(round(utils.RMSE(y_test, yp),3))+"\tTestR2="+str(round(utils.R2(y_test, yp),3))+"\t"+reportString+"\n")

### 2022-08-31 testPMLB_blackbox.py

@@ -1,0 +1,65 @@
+from datetime import datetime
+from pmlb import regression_dataset_names
+from pmlb import fetch_data
+from sklearn.model_selection import train_test_split
+from sklearn import linear_model
+from sklearn.preprocessing import StandardScaler
+import utils
+from sklearn import svm
+from rils import RILS
+
+#print(regression_dataset_names)
+
+pmlb_cache = "../pmlb/datasets"
+time = 100
+seed = 12345
+test_perc = 0.25
+outPath = "out_{0}.txt".format(datetime.now().strftime("%Y_%m_%d_%H_%M_%S"))
+size_penalty = None
+scale_x = True
+scale_y = False
+
+#regression_dataset_names = ["feynman_I_29_16"]
+for dataset in regression_dataset_names:
+    X, y = fetch_data(dataset, return_X_y=True,  local_cache_dir=pmlb_cache)
+
+    X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=test_perc, random_state=seed)
+
+    # scale and normalize the data
+    if scale_x:
+        print('scaling X')
+        sc_X = StandardScaler() 
+        X_train_scaled = sc_X.fit_transform(X_train)
+        X_test_scaled = sc_X.transform(X_test)
+    else:
+        X_train_scaled = X_train
+        X_test_scaled = X_test
+
+    if scale_y:
+        print('scaling y')
+        sc_y = StandardScaler()
+        y_train_scaled = sc_y.fit_transform(y_train.reshape(-1,1)).flatten()
+    else:
+        y_train_scaled = y_train
+
+    ridge = linear_model.Ridge(alpha=.5)
+    ridge.fit(X_train_scaled, y_train)
+    ridgeScore = round(ridge.score(X_test_scaled, y_test),3)
+    print(dataset+"\tRidgeR2="+str(ridgeScore))
+
+    svr = svm.SVR(C=1.0, epsilon=0.2)
+    svr.fit(X_train_scaled, y_train)
+    svrScore = round(svr.score(X_test_scaled, y_test),3)
+    print(dataset+"\tSvrR2="+str(svrScore))
+
+    ilsr = RILS(100000,time, complexity_penalty=size_penalty, random_state = seed)
+    ilsr.fit(X_train_scaled, y_train_scaled)
[…]

### 2022-08-31 testPMLB_ground_truth.py

@@ -1,0 +1,77 @@
+from tabnanny import check
+from pmlb import fetch_data
+from sklearn.model_selection import train_test_split
+from rils_rols.rils_rols import RILSRegressor
+from rils_rols.utils import noisefy, R2, RMSE
+from os import listdir, stat
+import sys
+from sklearn.utils.estimator_checks import check_estimator
+import numpy as np
+
+#check_estimator(RILSRegressor())
+
+if len(sys.argv)!=8:
+    print("Usage: <working part or -1> <parts >=1> <random seed> <max time (s)> <max fit calls> <size penalty> <noise level>")
+    print("Passed parameters were:")
+    print(sys.argv[1:])
+    sys.exit(1)
+
+part = int(sys.argv[1])
+parts = int(sys.argv[2])
+
+seed = int(sys.argv[3])
+max_seconds = int(sys.argv[4])
+max_fit_calls = int(sys.argv[5])
+complexity_penalty = float(sys.argv[6])
+noise_level = float(sys.argv[7])
+test_size = 0.25
+label="target"
+
+pmlb_cache = "../pmlb/datasets"
+excluded_feynman = ["feynman_I_26_2", "feynman_I_30_5", "feynman_test_10"] # this are using arcsin or arcos
+ground_truth_regr_datasets = list(filter(lambda x: (x.startswith("feynman") or x.startswith("strogatz")) and not x in excluded_feynman, listdir(pmlb_cache)))
+
+tmp_dict = {}
+for dataset in ground_truth_regr_datasets:
+    size = stat(pmlb_cache+"/"+dataset+"/"+dataset+".tsv.gz").st_size
+    tmp_dict[dataset]=size
+
+ground_truth_regr_datasets.clear()
+for dataset in sorted(tmp_dict.items(), key=lambda x: x[1]):
+    ground_truth_regr_datasets.append(dataset[0])
+
+out_path = "out_sp"+str(complexity_penalty)+"_nl"+str(noise_level)+".txt"
+for i in range(len(ground_truth_regr_datasets)):
+    if i%parts!=part:
+        continue
+    dataset = ground_truth_regr_datasets[i]
+    #true_model = get_sym_model(dataset)
+    print("Doing "+dataset)
+   
+    input_data = fetch_data(dataset,  local_cache_dir=pmlb_cache)
+        
+    feature_names = [x for x in input_data.columns.values if x != label]
+    feature_names = np.array(feature_names)
+
[…]

### 2022-09-11 doc/paper.tex
Start woring on Intro

@@
 
+	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade to study it intensively.
+SR can be seen as a generalization of the well known  concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}.
+All regression models in principle have the same task: given a set of a $n$-dimensional input data and the output data, the aim is to find a  function consisting of $n$ (input) variables that fits to the output data w.r.t.
+some in advance known measure.
+When aiming a model to be a linear combination of input variables, it represents the problem of linear regression.
+However, when there are some nonlinear relations between variables, which are relevant, linear regression models are not enough.
+This is the point where symbolic regression comes into the play.
+Unlike linear regression, it allows the search over the space of all possible mathematical formulas in order to find the best fitting ones able to  predict the output variable from the input variables.
+The base of constructing the explicit formula are the basis operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.
+\fxnote{Marko: proceed}
+	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef
+
 \subsection{Contributions of this work}
@@
 \bibliographystyle{abbrv}	
-%\bibliography{bib}
+\bibliography{bib}
 

### 2022-09-11 doc/paper.tex
Update: into

@@
 SR can be seen as a generalization of the well known  concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}.
-All regression models in principle have the same task: given a set of a $n$-dimensional input data and the output data, the aim is to find a  function consisting of $n$ (input) variables that fits to the output data w.r.t.
+All regression models in principle have the same task: given a set of a $n$-dimensional input data and the output data, the aim is to find a  mathematical expression (function) consisting of $n$ (input) variables that fits to the output data w.r.t.
 some in advance known measure.
@@
 The base of constructing the explicit formula are the basis operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.
-\fxnote{Marko: proceed}
 	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef
+
+	 Concrete examples of application of SR include having a less black--box tool, as it may say much more how SR model achieve predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others.
+Moreover, in that way we may grasp why the variables are related in the obtained way.
+As an example, appearance of an exponential function may associate  to  some physical phenomenon such as intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}.
+Additionally, the SR models, if they are correct, may have    posses  larger extrapolation power than other mathematical models, and especially than neural network--based methods.
+SR models may maximize obtaining physically more reasonable equations that could serve to establish a physical theory behind as the final goal.
+Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}.
+\fxnote{TODO}
+
+	 There are many different ways to tackle the SR achieving right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming.
+\fxnote{TODO}
 

### 2022-09-12 doc/paper.tex
Intro: working

@@
 Additionally, the SR models, if they are correct, may have    posses  larger extrapolation power than other mathematical models, and especially than neural network--based methods.
-SR models may maximize obtaining physically more reasonable equations that could serve to establish a physical theory behind as the final goal.
+SR models may maximize obtaining physically more reasonable equations that could serve as insight towards  establishing  physical theory behind as the final goal.
 Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}.
-\fxnote{TODO}
+In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities is presented there.
+Applications of SR to discovering physical laws from distorted video is studied in~\cite{udrescu2021symbolic} by means of a unsupervised learning method.
+Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}, tackled by  a machine learning method.
+Application of SR to model the mutations effects on protein  stability, in the domain of fundamental and applied biology,  is shown in~\cite{louis2021reviewing}.
+One of the recent work studies of  auto-discovering conserved quantities using trajectory data from unknown dynamical systems, where SR is solved by a machine learning algorithm, see~\cite{liu2021machine}.
+Last but not least, we mention the paper~\cite{liang2019phillips} discovers  the application of  SR to model analytic representations of the exciton binding energy.
+The use of SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic}.
 
-	 There are many different ways to tackle the SR achieving right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming.
+	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming.
 \fxnote{TODO}

### 2022-09-12 doc/paper.tex
working...

@@
 Last but not least, we mention the paper~\cite{liang2019phillips} discovers  the application of  SR to model analytic representations of the exciton binding energy.
-The use of SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic}.
+The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic}.
 
-	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming.
-\fxnote{TODO}
+	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming (GP).
+Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
+A differential evolution algorithm was proposed by Cerny et al.~\cite{cerny2008using}.
+Application of local--based heuristics on solving SR is discovered in~\cite{kommenda2018local}.
 
+	 Machine learning--based methodologies to solve SR are presented in~\cite{}...
+
+	Short descriptions of the SR methods used in our experiments are given in Table~\ref{} \fxnote{TODO}
 \subsection{Contributions of this work}

### 2022-09-12 doc/paper.tex
Intro: working...

@@
 
-	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming (GP).
+	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming (GP) and various approximate methods such as meta-heuristics.
 Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
 A differential evolution algorithm was proposed by Cerny et al.~\cite{cerny2008using}.
-Application of local--based heuristics on solving SR is discovered in~\cite{kommenda2018local}.
+Age-fitness Pareto Optimization approach is proposed by Smidt and Lipson~\cite{schmidt2010age}.
+	 Application of local--based heuristics on solving SR is discusses by Commenda in his Ph.D.
+thesis~\cite{kommenda2018local}.
+A  GP-based approach, the gene-pool optimal mixing evolutionary algorithm (GOMEA) is studied by Virgolin et al.~\cite{virgolin2021improving}.
+Another evolutionary algorithm, the interaction-transformation EA (ITEA) has been proposed by de Franca et al.~\cite{de2021interaction}.
+Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
 

### 2022-09-13 doc/paper.tex
Intor:working

@@
 some in advance known measure.
+This computationally intensive task is in general NP--hard~\cite{virgolin2022symbolic}.
 When aiming a model to be a linear combination of input variables, it represents the problem of linear regression.
@@
 Last but not least, we mention the paper~\cite{liang2019phillips} discovers  the application of  SR to model analytic representations of the exciton binding energy.
-The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic}.
+The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
 
-	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming (GP) and various approximate methods such as meta-heuristics.
+	 There are many different ways to tackle the SR by achieving the right analytic expressions, most of them are related to machine learning techniques or to the technique of genetic programming (GP) and various approximate methods, such as meta-heuristics.
 Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
@@
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
+Kommenda et al.~\cite{kommenda2020parameter} proposed a method called OPERON algorithm, which uses nonlinear least squares for parameter
+	 identification of SR models further integrated into a local search mechanism in
+	 tree-based GP.
+The C++ implementation of OPERON is discussed in~\cite{burlacu2020operon}.
+The metod that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
+It is also worth to mention the GP--based Eureqa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
+This solver is nowadays known as the gold standard for symbolic regression.
 
-	 Machine learning--based methodologies to solve SR are presented in~\cite{}...
+	 Machine learning--based methods to solve SR are based on Bayesian symbolic regression (BSR)~\cite{jin2019bayesian} which belongs to the family of Markov Chain Monte Carlo algorithms.
+Deep Symbolic Regression (DSR), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
+This mechanism of search is further considered in~\cite{landajuela2021improving}.
+A fast neural network approach, called OccamNet,  is proposed in~\cite{costa2020fast}.
 
-	Short descriptions of the SR methods used in our experiments are given in Table~\ref{} \fxnote{TODO}
+	There are also powerful hybrid techniques to solve SR; among them, we emphasize the EPLEX solver from~\cite{la2019probabilistic,mundhenk2021symbolic}...
+
+	Short overview of the GP--based methods to solve SR are given in Table~\ref{} \fxnote{TODO}
+
+		Short overview of the machine--learning based method to solve SR are given in Table~\ref{} \fxnote{TODO}
 \subsection{Contributions of this work}

### 2022-09-14 doc/paper.tex
Intro: work

@@
 The C++ implementation of OPERON is discussed in~\cite{burlacu2020operon}.
-The metod that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+The metod that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+A GP approach that uses the idea of semantic back-propagation (SBP-GP) is proposed in~\cite{virgolin2019linear}.
 Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
 It is also worth to mention the GP--based Eureqa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
-This solver is nowadays known as the gold standard for symbolic regression.
+This solver is nowadays accepted for the gold standard of symbolic regression.
 
@@
 A fast neural network approach, called OccamNet,  is proposed in~\cite{costa2020fast}.
+A deep reinforcement learning approach enhanced with genetic programming is given in~\cite{mundhenk2021symbolic}.
 
-	There are also powerful hybrid techniques to solve SR; among them, we emphasize the EPLEX solver from~\cite{la2019probabilistic,mundhenk2021symbolic}...
+	Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the EPLEX solver from~\cite{la2019probabilistic,la2016epsilon} and AI Feynman algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method that  combines neural network
+	fitting.
+The later one is one of the most efficient method for physically inspired models.
+We also mention the Fast Function Extraction (FFX) algorithm developed by McConaghy~\cite{mcconaghy2011ffx}, which is a non-evolutionary technique in combination with a machine learning technique --- pathwise regularized learning -- which is in charge to quickly prune a huge set of candidate basis functions down to compact models.
 
-	Short overview of the GP--based methods to solve SR are given in Table~\ref{} \fxnote{TODO}
+	Short overview of the GP--based methods to solve SR are given in Table~\ref{tab:gp-based} \fxnote{TODO}
+
+	 \begin{table}[!ht]
+		\centering
+		\begin{tabular}{l l l} \\ \hline
+			Algorithm          &   paper/year &   Short details   \\ \hline
+			Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
+			APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
+			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection                \\ 
+		     \fxnote{TODO}  &      & 
+		\end{tabular}
+		\caption{Overview of SR methods.}
+		\label{tab:gp-based}
+	\end{table}
 
 		Short overview of the machine--learning based method to solve SR are given in Table~\ref{} \fxnote{TODO}
+
+		\fxnote{TODO: about benchmarking in the literature...}
 \subsection{Contributions of this work}

### 2022-09-14 doc/paper.tex
working...

@@
 \newcommand\ToDo[1]{\textcolor{red}{#1}}
-
+ \usepackage{tabularx}
 \usepackage{xspace}
@@
 
-	 Machine learning--based methods to solve SR are based on Bayesian symbolic regression (BSR)~\cite{jin2019bayesian} which belongs to the family of Markov Chain Monte Carlo algorithms.
+	 Machine learning--based method   based on Bayesian symbolic regression (BSR) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms.
 Deep Symbolic Regression (DSR), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
-This mechanism of search is further considered in~\cite{landajuela2021improving}.
+This mechanism of search is further investigated in~\cite{landajuela2021improving}.
 A fast neural network approach, called OccamNet,  is proposed in~\cite{costa2020fast}.
@@
 
-	 \begin{table}[!ht]
+	 \begin{table}[htb]
 		\centering
-		\begin{tabular}{l l l} \\ \hline
+		\begin{tabularx}{350pt}{l  l  X}  
 			Algorithm          &   paper/year &   Short details   \\ \hline
+	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
+	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
 			Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
@@
 			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection                \\ 
+	       Local optimization     & \cite{kommenda2018local}   & Constants Optimization in GP by Nonlinear Least Square \\
 	       \fxnote{TODO}             &      & 
-		\end{tabular}
-		\caption{Overview of SR methods.}
+		\end{tabularx}
+		\caption{Overview of methods to solve SR.}
 		\label{tab:gp-based}

### 2022-09-15 doc/paper.tex
Intro: working

@@
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
-Kommenda et al.~\cite{kommenda2020parameter} proposed a method called OPERON algorithm, which uses nonlinear least squares for parameter
-	 identification of SR models further integrated into a local search mechanism in
+A Variable neighborhood search GP--based approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}.
+	 Kommenda et al.~\cite{kommenda2020parameter} proposed a method called OPERON algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in
 	 tree-based GP.
 The C++ implementation of OPERON is discussed in~\cite{burlacu2020operon}.
-The metod that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+The method that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
 A GP approach that uses the idea of semantic back-propagation (SBP-GP) is proposed in~\cite{virgolin2019linear}.
 Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
-It is also worth to mention the GP--based Eureqa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
+It is also worth to mention the GP--based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
 This solver is nowadays accepted for the gold standard of symbolic regression.
@@
 
-	 \begin{table}[htb]
+	 \begin{table}[!ht]
 		\centering
-		\begin{tabularx}{350pt}{l  l  X}  
+		\scalebox{0.7}{
+		\begin{tabularx}{450pt}{l  l  X}  
 			Algorithm          &   paper/year &   Short details   \\ \hline
@@
 	       Local optimization     & \cite{kommenda2018local}   & Constants Optimization in GP by Nonlinear Least Square \\
-	       \fxnote{TODO}             &      & 
-		\end{tabularx}
+	       GOMEA  & \cite{virgolin2021improving} (2021)    & A model-based
+	       EA framework called Gene-pool optimal mixing evolutionary algorithm \\
+	       ITEA & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
+	       SA & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
+
+	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
+	       Taylor GP &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations \\
+	       SBP-GP &  \cite{virgolin2019linear} (2019)  & the idea of semantic back-propagation \\
+	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
+	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
+	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\ 
+	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\
+         DRLA & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming
+
+	\end{tabularx} }
 		\caption{Overview of methods to solve SR.}
@@
 	\end{table}
-
-		Short overview of the machine--learning based method to solve SR are given in Table~\ref{} \fxnote{TODO}
 

### 2022-09-15 doc/paper.tex
Intro: working...

--- 2022-09-14 doc/paper.tex
@@
 Age-fitness Pareto Optimization approach is proposed by Smidt and Lipson~\cite{schmidt2010age}.
-	 Application of local--based heuristics on solving SR is discusses by Commenda in his Ph.D.
+Application of artificial bee colony programming to solve SR is proposed by Karaboga et al.~\cite{karaboga2012artificial}.
+	 Influence of local--based heuristics on solving SR is reported by Commenda in his Ph.D.
 thesis~\cite{kommenda2018local}.
@@
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
-Kommenda et al.~\cite{kommenda2020parameter} proposed a method called OPERON algorithm, which uses nonlinear least squares for parameter
-	 identification of SR models further integrated into a local search mechanism in
+A Variable neighborhood programming approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
+	 Kommenda et al.~\cite{kommenda2020parameter} proposed a method called OPERON algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in
 	 tree-based GP.
 The C++ implementation of OPERON is discussed in~\cite{burlacu2020operon}.
-The metod that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+The method that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
 A GP approach that uses the idea of semantic back-propagation (SBP-GP) is proposed in~\cite{virgolin2019linear}.
 Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
-It is also worth to mention the GP--based Eureqa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
+It is also worth to mention the GP--based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
 This solver is nowadays accepted for the gold standard of symbolic regression.
@@
 The later one is one of the most efficient method for physically inspired models.
-We also mention the Fast Function Extraction (FFX) algorithm developed by McConaghy~\cite{mcconaghy2011ffx}, which is a non-evolutionary technique in combination with a machine learning technique --- pathwise regularized learning -- which is in charge to quickly prune a huge set of candidate basis functions down to compact models.
+We also mention the Fast Function Extraction (FFX) algorithm developed by McConaghy~\cite{mcconaghy2011ffx},  a non-evolutionary method in combination with a machine learning technique---path-wise regularized learning--- which   quickly prune a huge set of candidate basis functions down to compact models.
 
-	Short overview of the GP--based methods to solve SR are given in Table~\ref{tab:gp-based} \fxnote{TODO}
+	A short chronological overview of the most important  literature methods to solve SR are given in Table~\ref{tab:gp-based}.
 
-	 \begin{table}[htb]
+	 \begin{table}[!ht]
 		\centering
-		\begin{tabularx}{350pt}{l  l  X}  
-			Algorithm          &   paper/year &   Short details   \\ \hline
+		\scalebox{0.7}{
+		\begin{tabularx}{450pt}{l  l  X}  
+			Algorithm          &   Paper/year &   Short details   \\ \hline
 	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
@@
         	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
+        	FFX  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
+             ABCP &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
 			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
-	       Local optimization     & \cite{kommenda2018local}   & Constants Optimization in GP by Nonlinear Least Square \\
-	       \fxnote{TODO}             &      & 
-		\end{tabularx}
+	       Local optimization     & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
+	       SBP-GP &  \cite{virgolin2019linear} (2019)  & the idea of semantic back-propagation \\
+	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
+	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
+	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
+	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
+	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\
+
+	       AI Feynman  & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
+	             GOMEA  & \cite{virgolin2021improving} (2021)    & A model-based
+	       EA framework called Gene-pool optimal mixing evolutionary algorithm \\
+	       ITEA & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
+	       SA & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
+
+         DRLA & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming \\
+            Taylor GP &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations  \\ \hline
+
+	\end{tabularx} }
 		\caption{Overview of methods to solve SR.}
@@
 
-		Short overview of the machine--learning based method to solve SR are given in Table~\ref{} \fxnote{TODO}
-
 	 \fxnote{TODO: about benchmarking in the literature...}
+	 Concerning 
 \subsection{Contributions of this work}

### 2022-09-15 doc/paper.tex
exptension...

@@
 
-	 \fxnote{TODO: about benchmarking in the literature...}
-	 Concerning 
+	The progress in the SR field suffered from a lack of uniform, robust, and transparent
+	benchmarking standards over the last two decade. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
+	open-source, reproducible benchmarking platform for SR, called SRBench.
+The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression by 130 SR datasets for which model forms are known, see more in the aforementioned paper.\fxnote{TODO: Describe results of experimental evaluation}
 \subsection{Contributions of this work}

### 2022-09-16 doc/paper.tex
Intro: drafted

@@
 	       Local optimization     & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
-	       SBP-GP &  \cite{virgolin2019linear} (2019)  & the idea of semantic back-propagation \\
+	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
 	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
@@
 	open-source, reproducible benchmarking platform for SR, called SRBench.
-The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression by 130 SR datasets for which model forms are known, see more in the aforementioned paper.\fxnote{TODO: Describe results of experimental evaluation}
-\subsection{Contributions of this work}
+The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression, by 130 SR datasets for which model forms are known; see more in the aforementioned paper.
+In the extensive experimental evaluation  where 14
+	symbolic regression methods and 7 machine learning methods are compared on the  set of 252 diverse
+    regression problems.
+The general conclusions derived from there are: ($i$) when comes to real-world problem, the best performing algorithms are those which combine genetic algorithm with parameter estimation; ($ii$) when come to the instances with the presence of noise, the GP--based and deep learning techniques are performing similarly.
 
-The main contributions of this work can be summarized as follows:
+    In this work we present yet another GP--based approach to solve SR, which utilizes the popular iterated local search meta-heuristic~\cite{lourencco2003iterated,lourencco2019iterated}; in the remaining text, we label the metod by \textsc{Rils-Rols}.
+The main code of the efficient local search is utilization of the ordinary least square method~\cite{leng2007ordinary} that is in charge for an efficient finding suitable coefficients of linearised formulas.
+\fxnote{TODO: maybe expand the core of the algorithm...
+}
+
+The main contributions of this work may be summarized as follows:
 
@@
 All the other methods were tested against this new test-bed.
-The proposed RILS-ROLS method showed to be dominant here as well.
+The proposed \textsc{Rils-Rols} method showed to be dominant here as well.
 \end{enumerate}

### 2022-09-16 doc/paper.tex
Chapter 2: working

@@
 \newcommand\tabscale{0.8}
-\newtheorem{Theorem}{Theorem}
+\newtheorem{definition}{Definition}
 \newtheorem{Lemma}{Lemma}
@@
 	\begin{abstract}
-
+		  \fxnote{TODO}
 	\end{abstract}
@@
 The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
+Yet another application to wind speed forecasting is given in~\cite{abdellaoui2021symbolic}.
 
@@
 \label{sec:search-space}
+In this section we formally define the SR problem, followed by defining the search space framework of the problem.
 
-\section{Literature review}\label{sec:lit-rev}
+\begin{definition}
+  Given is a dataset $D = \{(x_i, y_i)\}_{i=1}^n$, where $\textbf{x} \in \mathbb{R}^d$ represents input variables (features), and $y$ target variable.
+Suppose that there exists an analytical model of the form $f(\textbf{x})= g^*(\textbf{x}, \theta^*) + \epsilon $ that is a generator of all observations in $D$.
+   The goal of SR is to learn a mapping $\tilde{f}(\textbf{x})=  \tilde{g}(\textbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the presented  white noise using given input data.
+
+\end{definition}
+
+Koza~\cite{koza1994genetic} introduced the problem of SR as a specific application of genetic programming.
+GP deals with the object called programs, which need to be optimized.
+In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants.
+\fxnote{TODO: dati primjer sintaksnog drveta} In essence, syntax trees are part of search space of SR.
+That is, each sample $\tilde{f}$ is a point in the search space, represented by respective syntax tree.
+How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error-based measure (such as $MSE$, or $R^2$).
+
+%\section{Literature review}\label{sec:lit-rev}
 

### 2022-09-16 doc/paper.tex
Update...

@@
 			Algorithm          &   Paper/year &   Short details   \\ \hline
+			GP         &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
 	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
@@
 That is, each sample $\tilde{f}$ is a point in the search space, represented by respective syntax tree.
-How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error-based measure (such as $MSE$, or $R^2$).
+How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).
 
@@
 \section{Proposed iterated local search method}\label{sec:rils}
+
+   \subsection{Iterated local search framework}
+
+   \subsection{Ordinary least square method}
+
+   \subsection{The proposed Rils-Rols}
 

### 2022-09-16 doc/paper.tex
Chapter 2: working

@@
-\documentclass[a4paper]{elsarticle}
+\documentclass[a4paper,12pt]{elsarticle}
 % vim: tw=0 wm=0
@@
 %\usepackage{changes}
-
+\usepackage{tikz}
+\usepackage{fullpage}
+\usepackage{calc}
+\usetikzlibrary{positioning,shadows,arrows,trees,shapes,fit}
 \usepackage{blindtext}
@@
 		\scalebox{0.7}{
-		\begin{tabularx}{450pt}{l  l  X}  
+		\begin{tabularx}{550pt}{l  l  X}  
 			Algorithm          &   Paper/year &   Short details   \\ \hline
@@
 GP deals with the object called programs, which need to be optimized.
-In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants.
-\fxnote{TODO: dati primjer sintaksnog drveta} In essence, syntax trees are part of search space of SR.
-That is, each sample $\tilde{f}$ is a point in the search space, represented by respective syntax tree.
+In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants; as an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example} In essence, syntax trees are elements of the search space of SR.
+That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree.
 How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).
+\fxnote{TODO: proceed...}
+
+\begin{figure}[!ht]
+	\centering
+\begin{tikzpicture}
+	[font=\small, edge from parent, 
+	every node/.style={top color=white, bottom color=blue!25, 
+		rectangle,rounded corners, minimum size=6mm, draw=blue!75,
+		very thick, drop shadow, align=center},
+	edge from parent/.style={draw=blue!50,thick},
+	level 1/.style={sibling distance=3cm},
+	level 2/.style={sibling distance=1.2cm}, 
+	level 3/.style={sibling distance=1cm}, 
+	level distance=2cm,
+	]
+	\node (A) {$\times$} 
+	child { node (B) {$\sin$}
+		%child { node {x} 
+			%edge from parent node[left=.5em,draw=none] {} }
+		child { node {$x$}}
+	}
+	child {node (C) {$\times$}
+		%child { node {x}
+		%	child { node {C1a}}
+		%}
+		child { node {$x$}}
+		child { node {$/$}
+			child { node {$x$}}
+			child { node {$y$} %edge from parent node[right=.5em,draw=none] {$\frac{a}{b}$}
+			}
+		}
+	};
+%	child { node {+} 
+	%	child { node {2}}
+	%	child { node {$x$}}
+	%};
+
+\end{tikzpicture}
+
+\caption{Syntax tree representation for the expression $\sin x \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
+\label{fig:syntax-tree-example}
+\end{figure}
 

### 2022-09-16 doc/paper.tex
Update

@@
 
-    In this work we present yet another GP--based approach to solve SR, which utilizes the popular iterated local search meta-heuristic~\cite{lourencco2003iterated,lourencco2019iterated}; in the remaining text, we label the metod by \textsc{Rils-Rols}.
-The main code of the efficient local search is utilization of the ordinary least square method~\cite{leng2007ordinary} that is in charge for an efficient finding suitable coefficients of linearised formulas.
+    In this work we present yet another GP--based approach to solve SR, which utilizes the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated}; in the remaining text, we label the metod by \textsc{Rils-Rols}.
+The main code of the efficient local search is utilization of the ordinary least square method (OLS)~\cite{leng2007ordinary} that is in charge for an efficient finding suitable coefficients of linearised formulas.
 \fxnote{TODO: maybe expand the core of the algorithm...
@@
   Given is a dataset $D = \{(x_i, y_i)\}_{i=1}^n$, where $\textbf{x} \in \mathbb{R}^d$ represents input variables (features), and $y$ target variable.
-Suppose that there exists an analytical model of the form $f(\textbf{x})= g^*(\textbf{x}, \theta^*) + \epsilon $ that is a generator of all observations in $D$.
+Suppose that there exists an analytical model of the form $f(\textbf{x})= g^*(\textbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.
    The goal of SR is to learn a mapping $\tilde{f}(\textbf{x})=  \tilde{g}(\textbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the presented  white noise using given input data.
@@
 How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).
+Interestingly, the search space of SR consists of its discrete and continuous part.
+More precisely, the model we are seeking for might be obtained as a composition of some functions from a (finite) set of mathematical functions.
+It is common to use the set of the following elementary mathematical functions in the experiments: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, and $a^x$.
+It is allowed to link functions will all four operators: $+$, $-$, $\times$, and $/$.
+After fixing functions that build models, the set of coefficients that  fits to this model must be provided.
+For the most physical models, these coefficients may receive any real value, that is they are continuous in its nature.
+
 \fxnote{TODO: proceed...}
@@
 
-   \subsection{Iterated local search framework}
+   \subsection{Iterated local search}
+   \fxnote{TODO: Marko}
 

### 2022-09-17 doc/paper.tex
ILS: explained

@@
 It is allowed to link functions will all four operators: $+$, $-$, $\times$, and $/$.
-After fixing functions that build models, the set of coefficients that  fits to this model must be provided.
+After fixing functions that build models, the set of optimal coefficients that  fits to this model must be provided.
 For the most physical models, these coefficients may receive any real value, that is they are continuous in its nature.
 
-\fxnote{TODO: proceed...}
+\fxnote{TODO: needs for extension...}
 
@@
    \subsection{Iterated local search}
-   \fxnote{TODO: Marko}
+    Iterated local search (ILS)~\cite{lourencco2003iterated} is an efficient meta-heuristics, whose essential idea is given as follow.
+Iteratively generate a sequence of solutions generated by the (embedded) heuristic, such as local search or  randomized greedy heuristics,  leading
+    towards better solutions than if one uses repeated random trials of that heuristic.
+This simple idea appeared in the literature by Baxter~\cite{baxter1981local} in early 1980s, and, since then, had been many time re-invented by many researches under different names; some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
+    Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases,  combinations of these~\cite{applegate2003chained}.
+
+   In the literate, one of the mostly applied ILS versions in the literature is pseudo-coded in Algorithm~\ref{alg:ils}.
+Note that we also used the core of this version in our \textsc{Risl-Rols} algorithm.
+\fxnote{Provjeriti da li je ovo tačno -- popraviti algoritam ako nije sa onim što je korišten...}
+
+   \begin{algorithm}
+  		\begin{algorithmic}[1] 
+  			 \State \textbf{Input}: a COP problem; an LS procedure  
+  	 		\State \textbf{Output}: an approximate (feasible) solution 
+  	 		\State $s \gets$ Generate an initial solution
+  	 		\State  $s \gets LS(s)$
+   	 		\While{\emph{Stopping criteria is not met}}
+   	    		 \State  $s' \gets$ Perturbation($s$)
+   	    		 \State  $s' \gets$ LS($s'$)
+   	    		 \State  $ s \gets$ AcceptanceCriterion($s, s'$)
+   	 		\EndWhile
+   		\end{algorithmic}
+    	\caption{An ILS framework from the literature.}
+    	   	     \label{alg:ils}
+    \end{algorithm}
+
+An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure.
+At each iteration, ILS applies three steps.
+First, the current incumbent solution is perturbed, that is mutated.
+The perturbed solution is then improved by LS procedure.
+The outcome is thereafter compared to the incumbent solution and possibly replaced for the new one, with accordance to the chosen acceptance criterion.
 

### 2022-09-17 doc/paper.tex
update

@@
 First, the current incumbent solution is perturbed, that is mutated.
-The perturbed solution is then improved by LS procedure.
-The outcome is thereafter compared to the incumbent solution and possibly replaced for the new one, with accordance to the chosen acceptance criterion.
+Secondly, the perturbed solution is then improved by LS procedure.
+Thirdly, the LS outcome is thereafter compared to the incumbent solution and possibly replaced as the new one, with accordance to the chosen acceptance criterion.
 

### 2022-09-18 doc/paper.tex
Work on Section 3.2

@@
 \section{Proposed iterated local search method}\label{sec:rils}
+   Before we give details on our \textsc{Rils-Rols} method fro solving SR, we explain the basics of the two main techniques incorporated into our algorithm.
+These are ILS meta-heuristic and OLS methods, respectively.
 
@@
   		\begin{algorithmic}[1] 
-  			 \State \textbf{Input}: a COP problem; an LS procedure  
+  			 \State \textbf{Input}: a COP problem; a LS procedure  of the problem 
   	 		\State \textbf{Output}: an approximate (feasible) solution 
@@
    	 		\While{\emph{Stopping criteria is not met}}
-   	    		 \State  $s' \gets$ Perturbation($s$)
-   	    		 \State  $s' \gets$ LS($s'$)
-   	    		 \State  $ s \gets$ AcceptanceCriterion($s, s'$)
+   	    		 \State  $s' \gets$ \texttt{Perturbation}($s$)
+   	    		 \State  $s' \gets$ \texttt{LS}($s'$)
+   	    		 \State  $ s \gets$ \texttt{AcceptanceCriterion}($s, s'$)
    	 		\EndWhile
    		\end{algorithmic}
-    	\caption{An ILS framework from the literature.}
+    	\caption{An ILS framework from   literature.}
     	   	     \label{alg:ils}
@@
 At each iteration, ILS applies three steps.
-First, the current incumbent solution is perturbed, that is mutated.
+First, the current incumbent solution is perturbed, that is mutated in a way the knowledge of the current best solution is (partially) used at the next iterations.
 Secondly, the perturbed solution is then improved by LS procedure.
@@
  \subsection{Ordinary least square method}
+   Ordinary least square method (OLS) is a linear regression technique.
+It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model).
+More precisely, given data $({X}, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_n)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized.
+This sum is also know by the term the sum of squared error (SSE).
+There are many methods to minimize SSE; one of the analytical methods is the calculus method that takes into account   partial derivation w.r.t.
+$k$ of the cost function $ \sum_{i} |\tilde{y}_i - y_i|^2 $, getting
 
+   $$  \frac{\partial}{\partial k} \sum_{i} |\tilde{y}_i - y_i|^2 = \frac{\partial}{\partial k} \sum ( kx_i+b  - y_i)^2 =  \sum -2x_i(kx_i + b - y_i)  =  \sum -2x_i (\tilde{y}_i - y_i ) . $$
+
+   Taking into account   partial derivation w.r.t.  $b$, we have 
+    $$  \frac{\partial}{\partial b} \sum_{i} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum ( kx_i+b  - y_i)^2 = \sum -2  (\tilde{y}_i - y_i). $$
+
+    Thus, we get the system of equation: 
+    \begin{align*}
+    	  &\sum -2x_i (\tilde{y}_i - y_i )  = 0 \\
+    	  &\sum -2  (\tilde{y}_i - y_i ) = 0.
+    \end{align*}
+     The above system can be transformed to 
+     \begin{align*}
+     	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
+     	 & \sum y_i  = k \sum x_i + b \cdot n 
+     \end{align*}
+     which is a system of two equations with two variables ($k$ and $b$) that is  solved efficiently.
    \subsection{The proposed Rils-Rols}
-
+    \fxnote{TODO}
 \section{Experimental evaluation}\label{sec:experiments}

### 2022-09-26 doc/paper.tex
update in concept

@@
 some in advance known measure.
-This computationally intensive task is in general NP--hard~\cite{virgolin2022symbolic}.
+This computationally intensive task is in general  provenly NP--hard~\cite{virgolin2022symbolic}.
 When aiming a model to be a linear combination of input variables, it represents the problem of linear regression.
@@
 
-   In the literate, one of the mostly applied ILS versions in the literature is pseudo-coded in Algorithm~\ref{alg:ils}.
+   In the literate, one of the mostly applied ILS versions is pseudo-coded in Algorithm~\ref{alg:ils}.
 Note that we also used the core of this version in our \textsc{Risl-Rols} algorithm.

### 2022-10-07 formula_gen.py
Finished testing.

@@ -1,0 +1,140 @@
+from msilib.schema import Error
+import sys
+import copy
+import math
+from rils_rols.node import Node, NodePlus, NodeVariable, NodeMinus, NodeMultiply, NodeDivide, NodeSqr, NodeSqrt, NodeLn, NodeExp, NodeSin, NodeCos, NodeConstant
+import random
+from sympy import symbols, simplify, lambdify, I
+import os
+import warnings
+
+warnings.filterwarnings("error")
+
+def random_tree(size, allowed_nodes, rg, parent=None):
+    if size<1:
+        raise Exception("Random tree cannot have size smaller than 1.")
+    if size==1:
+        allowed_terms = list(filter(lambda x: x.arity==0 , allowed_nodes)) 
+        node = copy.deepcopy(allowed_terms[rg.randrange(len(allowed_terms))])
+        return node
+    elif size == 2:
+        interm = list(filter(lambda x: x.arity==1, allowed_nodes))
+        node = copy.deepcopy(interm[rg.randrange(len(interm))])
+        node.left = random_tree(size-1, allowed_nodes, rg, node)
+        return node
+    else:
+        min_arity = 1
+        if parent is not None and parent.arity==1:
+            min_arity = 2 # this is to avoid unary compositions like f(g(h...)), although f(g(..)) can happen because of above elif, but no more than 2 unary compositions will happen in non-simplified form
+        interm = list(filter(lambda x: x.arity>=min_arity, allowed_nodes))
+        node = copy.deepcopy(interm[rg.randrange(len(interm))])
+        if node.arity == 1:
+            node.left = random_tree(size-1, allowed_nodes, rg, node)
+        else:
+            if rg.randint(0,1)==0:
+                left_size = math.floor(size/2)
+                right_size = size - left_size - 1
+            else:
+                right_size = math.floor(size/2)
+                left_size = size - right_size - 1
+            node.left = random_tree(left_size, allowed_nodes, rg, node)
+            node.right = random_tree(right_size, allowed_nodes, rg, node)
+        return node
+
+def contains_all_vars(expr : Node, var_cnt):
+    for i in range(var_cnt):
+        if not expr.contains(NodeVariable(i)):
+            return False
+    return True
+
[…]

### 2022-10-07 random_12345_truth/random_03_01_0010000_02.f

@@ -1,0 +1,1 @@
+x0 + 1

### 2022-10-07 random_12345_truth/random_03_01_0010000_03.f

@@ -1,0 +1,1 @@
+0.31830988618379*x0

### 2022-10-07 random_12345_truth/random_04_01_0010000_00.f

@@ -1,0 +1,1 @@
+log(x0) + 1

### 2022-10-07 random_12345_truth/random_04_01_0010000_02.f

@@ -1,0 +1,1 @@
+3.1415926535898*exp(x0)

### 2022-10-07 random_12345_truth/random_04_01_0010000_03.f

@@ -1,0 +1,1 @@
+sin(x0) + 2

### 2022-10-07 random_12345_truth/random_04_02_0010000_00.f

@@ -1,0 +1,1 @@
+log(x0 + x1)

### 2022-10-07 random_12345_truth/random_04_02_0010000_01.f

@@ -1,0 +1,1 @@
+sin(x0 + x1)

### 2022-10-07 random_12345_truth/random_05_01_0010000_04.f

@@ -1,0 +1,1 @@
+exp(-sin(x0))

### 2022-10-07 random_12345_truth/random_05_02_0010000_03.f

@@ -1,0 +1,1 @@
+log(x0*cos(x1))

### 2022-10-07 random_12345_truth/random_06_01_0010000_01.f

@@ -1,0 +1,1 @@
+exp(0.87356852683023*sqrt(x0))

### 2022-10-07 random_12345_truth/random_06_01_0010000_03.f

@@ -1,0 +1,1 @@
+exp(2 - 2*x0)

### 2022-10-07 random_12345_truth/random_06_02_0010000_04.f

@@ -1,0 +1,1 @@
+x0**2 + x1 - 1

### 2022-10-07 random_12345_truth/random_06_03_0010000_03.f

@@ -1,0 +1,1 @@
+(x0 + x1)*cos(x2)

### 2022-10-07 random_12345_truth/random_07_01_0010000_01.f

@@ -1,0 +1,1 @@
+sqrt(x0 + cos(2) + 1)

### 2022-10-07 random_12345_truth/random_07_03_0010000_01.f

@@ -1,0 +1,1 @@
+x0 + x1 - x2 - 1

### 2022-10-07 random_12345_truth/random_07_03_0010000_03.f

@@ -1,0 +1,1 @@
+x0*x2 - 3.1415926535898*x1

### 2022-10-07 random_12345_truth/random_07_04_0010000_01.f

@@ -1,0 +1,1 @@
+x0*x1*x3/x2

### 2022-10-07 random_12345_truth/random_08_01_0010000_00.f

@@ -1,0 +1,1 @@
+log(2 - x0) + 10

### 2022-10-07 random_12345_truth/random_08_02_0010000_00.f

@@ -1,0 +1,1 @@
+(x0 + log(x0))*(x1 + 10)

### 2022-10-07 random_12345_truth/random_08_02_0010000_02.f

@@ -1,0 +1,1 @@
+log(-x1 + exp(cos(x0)))

### 2022-10-07 random_12345_truth/random_08_03_0010000_00.f

@@ -1,0 +1,1 @@
+cos(x0*x2 + 3.1415926535898*x1)

### 2022-10-07 random_12345_truth/random_08_03_0010000_04.f

@@ -1,0 +1,1 @@
+log(2*x0 + x1*x2)

### 2022-10-07 random_12345_truth/random_08_04_0010000_01.f

@@ -1,0 +1,1 @@
+x2*x3*exp(x1)/x0

### 2022-10-07 random_12345_truth/random_09_02_0010000_00.f

@@ -1,0 +1,1 @@
+x1**2*exp(x0 + 10)/100

### 2022-10-07 random_12345_truth/random_09_02_0010000_04.f

@@ -1,0 +1,1 @@
+cos(1) + 2*exp(-x1)

### 2022-10-07 random_12345_truth/random_09_03_0010000_01.f

@@ -1,0 +1,1 @@
+-log(x1) + cos(x0*x2)

### 2022-10-07 random_12345_truth/random_09_03_0010000_02.f

@@ -1,0 +1,1 @@
+cos((x2 - 3.1415926535898)*sin(x0*x1))

### 2022-10-07 random_12345_truth/random_09_04_0010000_00.f

@@ -1,0 +1,1 @@
+log(x1*x3*exp(x2)/x0)

### 2022-10-07 random_12345_truth/random_09_04_0010000_02.f

@@ -1,0 +1,1 @@
+sin(x0*x2) + cos(x1 + x3)

### 2022-10-07 random_12345_truth/random_10_01_0010000_02.f

@@ -1,0 +1,1 @@
+sin(exp(10 - x0)*sin(1))

### 2022-10-07 random_12345_truth/random_10_01_0010000_03.f

@@ -1,0 +1,1 @@
+-1.00000000000001*exp(x0) + 9.8696044010894/x0**2

### 2022-10-07 random_12345_truth/random_10_02_0010000_01.f

@@ -1,0 +1,1 @@
+cos(x1*sin(x0) + log(2*x1))

### 2022-10-07 random_12345_truth/random_10_03_0010000_02.f

@@ -1,0 +1,1 @@
+log(sqrt(x0)*x1/cos(x2))

### 2022-10-07 random_12345_truth/random_10_03_0010000_03.f

@@ -1,0 +1,1 @@
+exp(x0*sqrt(x1 + x2)*log(x0))

### 2022-10-07 random_12345_truth/random_10_03_0010000_04.f

@@ -1,0 +1,1 @@
+cos(x0/x2**2 + x1 + cos(10))

### 2022-10-07 random_12345_truth/random_10_04_0010000_01.f

@@ -1,0 +1,1 @@
+sin((x1 + log(x0))*log(x2*x3))

### 2022-10-07 random_12345_truth/random_10_04_0010000_02.f

@@ -1,0 +1,1 @@
+sin(x0 - x3 + log(x1) + sin(x2))

### 2022-10-07 random_12345_truth/random_10_04_0010000_03.f

@@ -1,0 +1,1 @@
+sin(x1*x2)*cos(x0 + log(x3))

### 2022-10-07 random_12345_truth/random_10_04_0010000_04.f

@@ -1,0 +1,1 @@
+log(cos(x0*x2)*cos(x1*x3))

### 2022-10-07 random_12345_truth/random_11_01_0010000_03.f

@@ -1,0 +1,1 @@
+sin(2*sin(1)/(cos(x0) + 1))

### 2022-10-07 random_12345_truth/random_11_01_0010000_04.f

@@ -1,0 +1,1 @@
+(log(10) + 9.8696044010894)*exp(sqrt(x0) + 2)

### 2022-10-07 random_12345_truth/random_11_02_0010000_01.f

@@ -1,0 +1,1 @@
+sin(cos(x0*x1**2) - 2 + exp(-1))

### 2022-10-07 random_12345_truth/random_11_02_0010000_03.f

@@ -1,0 +1,1 @@
+log(sqrt(x0) + 10) + sin(x1) + exp(-1)

### 2022-10-07 random_12345_truth/random_11_03_0010000_00.f

@@ -1,0 +1,1 @@
+x0**2*log(x2) + log(100*x1)

### 2022-10-07 random_12345_truth/random_11_03_0010000_04.f

@@ -1,0 +1,1 @@
+sin(x1 + sin(x0) - sin(x2) + cos(2))

### 2022-10-07 random_12345_truth/random_11_04_0010000_00.f

@@ -1,0 +1,1 @@
+cos(x3*sin(x1)*cos(x0 + x2**2))

### 2022-10-07 random_12345_truth/random_11_04_0010000_04.f

@@ -1,0 +1,1 @@
+exp(sin(x1*cos(x2))*sin(x0 + x3))

### 2022-10-07 random_12345_truth/random_12_01_0010000_01.f

@@ -1,0 +1,1 @@
+-cos(143205691646535.0*x0) + exp(2)*cosh(pi)

### 2022-10-07 random_12345_truth/random_12_02_0010000_02.f

@@ -1,0 +1,1 @@
+(cos(x1) - 31.415926535898)/(x0**2*sin(x1))

### 2022-10-07 random_12345_truth/random_12_02_0010000_03.f

@@ -1,0 +1,1 @@
+exp(sqrt(x1) + sin(1))/(2*x0)

### 2022-10-07 random_12345_truth/random_12_02_0010000_04.f

@@ -1,0 +1,1 @@
+-sqrt(x0) + x1**4 - 1.77245385090552 + sin(1)

### 2022-10-07 random_12345_truth/random_12_03_0010000_01.f

@@ -1,0 +1,1 @@
+x0**2 - x1**2 - 6.98296267768627e-15*x2

### 2022-10-07 random_12345_truth/random_12_04_0010000_00.f

@@ -1,0 +1,1 @@
+x0*x2*sqrt(x3) + exp(x3*sin(x1))

### 2022-10-07 random_12345_truth/random_12_04_0010000_02.f

@@ -1,0 +1,1 @@
+x3*exp((x0 + x2**2)**2)*log(x1)

### 2022-10-07 random_12345_truth/random_13_01_0010000_02.f

@@ -1,0 +1,1 @@
+(0.31830988618379*x0 - 1.77245385090552)*exp(1 - exp(2))

### 2022-10-07 random_12345_truth/random_13_02_0010000_02.f

@@ -1,0 +1,1 @@
+(x0 - exp(x1) - exp(2) + 1)**2

### 2022-10-07 random_12345_truth/random_13_02_0010000_04.f

@@ -1,0 +1,1 @@
+exp(exp(exp(-1)*cos(x0)) + sin(x1 + sin(1)))

### 2022-10-07 random_12345_truth/random_13_03_0010000_00.f

@@ -1,0 +1,1 @@
+-x2 + sin(x0) + sqrt(cos(x1)) - 10 + log(10)

### 2022-10-07 random_12345_truth/random_13_03_0010000_04.f

@@ -1,0 +1,1 @@
+6.98296267768627e-15*x0**4/(x2**2*(x1 - 2))

### 2022-10-07 random_12345_truth/random_13_04_0010000_01.f

@@ -1,0 +1,1 @@
+cos(x1**10 + exp(x3)/(x0 + x2))

### 2022-10-07 random_12345_truth/random_14_01_0010000_03.f

@@ -1,0 +1,1 @@
+log(sqrt(x0) + log(10))*sin(0.31830988618379*sqrt(x0))

### 2022-10-07 random_12345_truth/random_14_01_0010000_04.f

@@ -1,0 +1,1 @@
+cos(log(x0) + sqrt(2)) + sqrt(sin(2) + 19333.689074366)

### 2022-10-07 random_12345_truth/random_14_02_0010000_04.f

@@ -1,0 +1,1 @@
+cos(sin(cos(x0) + cos(x1))*cos(exp(x1) + exp(2)))

### 2022-10-07 random_12345_truth/random_14_03_0010000_00.f

@@ -1,0 +1,1 @@
+x0*x1 + x0 + exp(x2**2/cos(1))

### 2022-10-07 random_12345_truth/random_14_03_0010000_02.f

@@ -1,0 +1,1 @@
+(log(sin(x0)) + sqrt(sin(x2)))*log(sin(x1)/100)

### 2022-10-07 random_12345_truth/random_14_04_0010000_00.f

@@ -1,0 +1,1 @@
+10*(x2 - x3 - exp(x0))/x1

### 2022-10-07 random_12345_truth/random_14_04_0010000_01.f

@@ -1,0 +1,1 @@
+exp(-x0 + x1**2 + exp(x2) + cos(x3**2))

### 2022-10-07 random_12345_truth/random_14_04_0010000_02.f

@@ -1,0 +1,1 @@
+-x2*x3 + cos(x0)*cos(exp(10)) + cos(exp(x1))

### 2022-10-07 random_12345_truth/random_15_01_0010000_00.f

@@ -1,0 +1,1 @@
+-sin(cos(exp(x0)) - sin(1.77245385090552 + log(10)) + 9)

### 2022-10-07 random_12345_truth/random_15_01_0010000_03.f

@@ -1,0 +1,1 @@
+1.64872127070013*sqrt(-x0*log(x0**2))*sqrt(sin(1))

### 2022-10-07 random_12345_truth/random_15_03_0010000_03.f

@@ -1,0 +1,1 @@
+exp(sqrt(x2)*cos(100))/cos(x1 + log(x0))

### 2022-10-07 random_12345_truth/random_15_04_0010000_00.f

@@ -1,0 +1,1 @@
+cos(x2*x3/cos(x0) + exp(sin(x1))*log(4))

### 2022-10-07 random_12345_truth/random_15_04_0010000_01.f

@@ -1,0 +1,1 @@
+x1*exp(-100*x0)/(x3*cos(x2**2))

### 2022-10-07 random_12345_truth/random_15_05_0010000_00.f

@@ -1,0 +1,1 @@
+cos(x0 + 10*x3 + x4 + (-x1 + x2)*sin(1))

### 2022-10-07 testPMLB_ground_truth.py

@@ -28,6 +28,7 @@ test_size = 0.25
 label="target"
 
 pmlb_cache = "../../pmlb/datasets"
+'''
 excluded_feynman = ["feynman_I_26_2", "feynman_I_30_5", "feynman_test_10"] # this are using arcsin or arcos
 ground_truth_regr_datasets = list(filter(lambda x: (x.startswith("feynman") or x.startswith("strogatz")) and not x in excluded_feynman, listdir(pmlb_cache)))
 
@@ -39,8 +40,9 @@ for dataset in ground_truth_regr_datasets:
 ground_truth_regr_datasets.clear()
 for dataset in sorted(tmp_dict.items(), key=lambda x: x[1]):
     ground_truth_regr_datasets.append(dataset[0])
+'''
 
-#ground_truth_regr_datasets = ["strogatz_vdp2"]
+#ground_truth_regr_datasets = ["feynman_I_15_3t"]
 ground_truth_regr_datasets = ['strogatz_vdp2','feynman_I_39_1','feynman_III_12_43','feynman_I_34_27','strogatz_glider1','feynman_I_12_1','feynman_I_12_5','feynman_I_25_13','feynman_I_29_4','feynman_II_8_31','feynman_I_14_4','feynman_II_34_2','feynman_I_43_31','feynman_II_27_18','feynman_I_14_3','feynman_II_3_24','feynman_II_34_29a','feynman_II_34_2a','feynman_III_7_38','feynman_I_18_12','feynman_II_4_23','feynman_III_15_27','feynman_II_38_14','feynman_II_37_1','feynman_I_47_23','feynman_II_38_3','feynman_II_34_11','feynman_I_43_16','feynman_I_18_14','feynman_III_21_20','feynman_I_34_8','feynman_I_39_22','feynman_I_12_4','feynman_II_10_9','feynman_I_39_11','feynman_III_15_14','feynman_I_34_1','strogatz_glider2','feynman_III_13_18','feynman_II_34_29b','feynman_II_15_5','feynman_I_43_43','feynman_I_27_6','feynman_I_38_12','feynman_I_11_19','feynman_I_12_11','feynman_III_17_37','feynman_II_27_16','feynman_I_32_5','strogatz_barmag2','feynman_III_19_51','strogatz_predprey2','feynman_II_11_3','feynman_II_15_4','strogatz_lv2','feynman_I_24_6','feynman_III_15_12','feynman_test_19','feynman_II_8_7','feynman_II_6_1
[…]

### 2022-10-07 doc/paper.tex

@@
     Iterated local search (ILS)~\cite{lourencco2003iterated} is an efficient meta-heuristics, whose essential idea is given as follow.
-Iteratively generate a sequence of solutions generated by the (embedded) heuristic, such as local search or  randomized greedy heuristics,  leading
+Iteratively generate a sequence of solutions produced by the (embedded) heuristic, such as local search or  randomized greedy heuristics,  leading
     towards better solutions than if one uses repeated random trials of that heuristic.
@@
 Secondly, the perturbed solution is then improved by LS procedure.
-Thirdly, the LS outcome is thereafter compared to the incumbent solution and possibly replaced as the new one, with accordance to the chosen acceptance criterion.
+Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion.
+Usually, this basic variant of ILS incorporates a mechanism of tabu list, that avoids the search getting back to already visited local search within a number of iterations.
 
@@
 
+ \\
+
 \newpage

### 2022-10-10 doc/paper.tex
Some results are in tex.

@@
 
+\begin{table}[!htb]
+	\caption{Comparison without noise}\label{tab:comp_noise0}
+	\centering
+		\begin{tabular}{l|rrr|rrr} \hline
+			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
+			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+			RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
+			AIFeynman&55.78&27.14&52.69&78.51&35.71&73.9\\
+			GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
+			AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
+			ITEA&22.41&7.14&20.77&27.59&21.43&26.93\\
+			AFP&21.12&15.18&20.48&44.83&25&42.69\\
+			DSR&19.72&19.64&19.71&25&14.29&23.85\\
+			Operon&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
+			gplearn&16.27&8.93&15.48&32.76&7.14&30\\
+			SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
+			EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
+			BSR&2.48&0.89&2.31&10.78&21.43&11.93\\
+			FEAT&0&0.89&0.1&39.66&42.86&40\\
+			FFX&0&0&0&0&0&0\\
+			MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
+			\hline
+		\end{tabular}
+\end{table}
+
+\begin{table}[!htb]
+	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
+	\centering
+		\begin{tabular}{l|rrr|rrr} \hline
+			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
+			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+			RILS-ROLS&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
+			DSR&16.81&18.75&17.02&26.29&14.29&25\\
+			gplearn&15.84&8.93&15.1&24.14&7.14&22.31\\
+			AFP\_FE&15.95&6.43&14.92&57.76&28.57&54.62\\
+			AFP&14.87&7.14&14.04&44.83&25&42.69\\
+			EPLEX&10.02&2.68&9.23&48.71&21.43&45.77\\
+			AIFeynman&1.49&13.73&2.81&9.73&35.71&12.53\\
+			ITEA&1.94&4.46&2.21&26.72&21.43&26.15\\
+			GP-GOMEA&1.62&0.89&1.54&72.84&71.43&72.69\\
+			Operon&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
+			FFX&0.11&0&0.1&19.4&14.29&18.85\\
+			FEAT&0&0.89&0.1&13.79&50&17.69\\
+			SBP-GP&0&0&0&62.07&53.57&61.15\\
+			BSR&0&0&0&7.76&14.29&8.46\\
+			MRGP&0&0&0&0.86&17.86&2.69\\
+			\hline
+		\end{tabular}
+\end{table}
+
+\begin{table}[!htb]
+	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
+	\centering
+	\begin{tabular}{l|rrr|rrr} \hline
+		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
+		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+		RILS-ROLS&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
+		gplearn&13.21&8.93&12.75&14.22&7.14&13.46\\
+		DSR&8.41&16.07&9.23&17.24&14.29&16.92\\
+		EPLEX&8.77&0&7.83&14.22&3.57&13.07\\
+		AFP&7.11&0.89&6.44&8.19&7.14&8.08\\
+		AFP\_FE&6.12&3.57&5.85&5.6&0&5\\
+		ITEA&0.11&0.89&0.19&1.72&10.71&2.69\\
+		AIFeynman&0&0.79&0.09&0&0&0\\
+		Operon&0.09&0&0.08&0&0&0\\
+		GP-GOMEA&0&0&0&0&0&0\\
+		SBP-GP&0&0&0&0&0&0\\
+		BSR&0&0&0&0&0&0\\
+		FEAT&0&0&0&0&14.29&1.54\\
+		FFX&0&0&0&0&0&0\\
+		MRGP&0&0&0&0&0&0\\
+		\hline
+	\end{tabular}
+\end{table}
+
 \subsection{Statistical evaluation}
@@
 
- \\
-
 \newpage

### 2022-10-11 doc/paper.tex
Images for random instances.

@@
 \usepackage{blindtext}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.16}
 
@@
 
+\begin{center}
+ \begin{tikzpicture}
+ 	\begin{axis}[
+		xlabel=$size$,
+		ylabel=$exact\;percentage$,
+		xmin=0, xmax=4,
+		ymin=0, ymax=100,
+		xtick={1,2,3},
+		xticklabels={small,medium,large},   % <---
+		ytick={0,10,...,100}
+		]
+		\addplot[smooth,mark=*,blue] plot coordinates {
+			(1,85)
+			(2,42.5)
+			(3,21.05)
+		};
+		\addlegendentry{No noise}
+
+		\addplot[smooth,color=red,mark=x]
+		plot coordinates {
+			(1,51.67)
+			(2,13.75)
+			(3,5.26)
+		};
+		\addlegendentry{Noise level 0.001}
+
+		\addplot[smooth,color=green,mark=o]
+		plot coordinates {
+			(1,31.67)
+			(2,5)
+			(3,4.21)
+		};
+		\addlegendentry{Noise level 0.01}
+	\end{axis}
+\end{tikzpicture}
+\captionof{figure}{Exact solution percentages for varying levels of noise and formulae sizes}
+\label{fig:compExact_noise_size}
+\end{center}
+
+\begin{center}
+	\begin{tikzpicture}
+		\begin{axis}[
+			xlabel=$size$,
+			ylabel=$R^2 > 0.999\;percentage$,
+			xmin=0, xmax=4,
+			ymin=20, ymax=100,
+			xtick={1,2,3},
+			xticklabels={small,medium,large},   % <---
+			ytick={20,30,...,100}
+			]
+			\addplot[smooth,mark=*,blue] plot coordinates {
+				(1,98.33)
+				(2,62.5)
+				(3,58.95)
+			};
+			\addlegendentry{No noise}
+
+			\addplot[smooth,color=red,mark=x]
+			plot coordinates {
+				(1,93.33)
+				(2,53.75)
+				(3,40)
+			};
+			\addlegendentry{Noise level 0.001}
+
+			\addplot[smooth,color=green,mark=o]
+			plot coordinates {
+				(1,65)
+				(2,31.25)
+				(3,20)
+			};
+			\addlegendentry{Noise level 0.01}
+		\end{axis}
+	\end{tikzpicture}
+	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and formulae sizes}
+	\label{fig:compR2_noise_size}
+\end{center}
+
+\begin{center}
+	\begin{tikzpicture}
+		\begin{axis}[
+			xlabel=$variable\;count$,
+			ylabel=$exact\;percentage$,
+			xmin=0, xmax=6,
+			ymin=0, ymax=100,
+			xtick={1,2,3,4,5},
+			xticklabels={1,2,3,4,5},   % <---
+			ytick={0,10,...,100}
+			]
+			\addplot[smooth,mark=*,blue] plot coordinates {
+				(1,52.31)
+				(2,50)
+				(3,44)
+				(4,37.78)
+				(5,13.33)
+			};
+			\addlegendentry{No noise}
+
+			\addplot[smooth,color=red,mark=x]
+			plot coordinates {
+				(1,16.92)
+				(2,21.67)
+				(3,28)
+				(4,17.78)
+				(5,6.67)
+			};
+			\addlegendentry{Noise level 0.001}
+
+			\addplot[smooth,color=green,mark=o]
+			plot coordinates {
+				(1,9.23)
+				(2,15)
+				(3,12)
+				(4,11.11)
+				(5,6.67)
+			};
+			\addlegendentry{Noise level 0.01}
+		\end{axis}
+	\end{tikzpicture}
+	\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts}
+	\label{fig:compExact_noise_varcnt}
+\end{center}
+
+\begin{center}
+	\begin{tikzpicture}
+		\begin{axis}[
+			xlabel=$variable\;count$,
+			ylabel=$exact\;percentage$,
+			xmin=0, xmax=6,
+			ymin=0, ymax=100,
+			xtick={1,2,3,4,5},
+			xticklabels={1,2,3,4,5},   % <---
+			ytick={0,10,...,100}
+			]
+			\addplot[smooth,mark=*,blue] plot coordinates {
+				(1,86.15)
+				(2,75)
+				(3,72)
+				(4,48.89)
+				(5,40)
+			};
+			\addlegendentry{No noise}
+
+			\addplot[smooth,color=red,mark=x]
+			plot coordinates {
+				(1,64.62)
+				(2,66.67)
+				(3,62)
+				(4,40)
+				(5,40)
+			};
+			\addlegendentry{Noise level 0.001}
+
+			\addplot[smooth,color=green,mark=o]
+			plot coordinates {
+				(1,32.31)
+				(2,43.33)
+				(3,46)
+				(4,24.44)
+				(5,13.33)
+			};
+			\addlegendentry{Noise level 0.01}
+		\end{axis}
+	\end{tikzpicture}
+	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts}
+	\label{fig:compR2_noise_varcnt}
+\end{center}
+
 \subsection{Statistical evaluation}

### 2022-10-12 doc/paper.tex
Reorganized varcnt plots.

@@
 			ylabel=$exact\;percentage$,
-			xmin=0, xmax=6,
+			xmin=0, xmax=5,
 			ymin=0, ymax=100,
-			xtick={1,2,3,4,5},
-			xticklabels={1,2,3,4,5},   % <---
+			xtick={1,2,3,4},
+			xticklabels={1,2,3,4},   % <---
 			ytick={0,10,...,100}
@@
 			\addplot[smooth,mark=*,blue] plot coordinates {
-				(1,52.31)
-				(2,50)
-				(3,44)
-				(4,37.78)
-				(5,13.33)
+				(1,43.33)
+				(2,43.33)
+				(3,46.67)
+				(4,46.67)
 			};
@@
 			plot coordinates {
-				(1,16.92)
-				(2,21.67)
-				(3,28)
-				(4,17.78)
-				(5,6.67)
+				(1,3.33)
+				(2,3.33)
+				(3,26.67)
+				(4,26.67)
 			};
@@
 			plot coordinates {
-				(1,9.23)
-				(2,15)
-				(3,12)
-				(4,11.11)
-				(5,6.67)
+				(1,3.33)
+				(2,3.33)
+				(3,3.33)
+				(4,16.67)
 			};
@@
 	\end{tikzpicture}
-	\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts}
+	\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
 	\label{fig:compExact_noise_varcnt}
@@
 			\addplot[smooth,mark=*,blue] plot coordinates {
-				(1,86.15)
-				(2,75)
-				(3,72)
-				(4,48.89)
-				(5,40)
+				(1,83.33)
+				(2,66.67)
+				(3,73.33)
+				(4,46.67)
 			};
@@
 			plot coordinates {
-				(1,64.62)
-				(2,66.67)
-				(3,62)
-				(4,40)
-				(5,40)
+				(1,56.67)
+				(2,63.33)
+				(3,66.67)
+				(4,46.67)
 			};
@@
 			plot coordinates {
-				(1,32.31)
+				(1,23.33)
 				(2,43.33)
-				(3,46)
-				(4,24.44)
-				(5,13.33)
+				(3,53.33)
+				(4,26.67)
 			};
@@
 	\end{tikzpicture}
-	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts}
+	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
 	\label{fig:compR2_noise_varcnt}

### 2022-10-12 doc/paper.tex
RILS-ROLS pseudocode start and some text revisions.

@@
 
-    In this work we present yet another GP--based approach to solve SR, which utilizes the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated}; in the remaining text, we label the metod by \textsc{Rils-Rols}.
-The main code of the efficient local search is utilization of the ordinary least square method (OLS)~\cite{leng2007ordinary} that is in charge for an efficient finding suitable coefficients of linearised formulas.
+    In this work we present a novel approach to solve SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated} with ordinary least squares method (OLS)~\cite{leng2007ordinary}.
+Briefly, ILS handles combinatorial (discrete) aspects of search space, while OLS helps in the process of coefficient determination, so it handles continuous parts of the search space.
+As will be shown later, the proposed method seems to be very robust w.r.t.
+introduced noise, therefore we called the method RILS-ROLS (with letters R corresponding to regression and robust).
 \fxnote{TODO: maybe expand the core of the algorithm...
@@
 
-	\item It shows high robustness, which is proved by testing methods under different levels of Gaussian white noise.
+	\item It shows high robustness, which is proved by comparison to other algorithms under different levels of Gaussian white noise.
 
@@
 
-	\item The new set of unbiased instances is introduced -- randomly generated formula of various sizes.
-All the other methods were tested against this new test-bed.
-The proposed \textsc{Rils-Rols} method showed to be dominant here as well.
+	\item The new set of unbiased instances is also introduced -- randomly generated formula of various sizes and number of input variables.
+This set was employed to understand the influence of formula size, number of input variables and noise on the solving difficulty.
 \end{enumerate}
@@
 
-\section{Proposed iterated local search method}\label{sec:rils}
-   Before we give details on our \textsc{Rils-Rols} method fro solving SR, we explain the basics of the two main techniques incorporated into our algorithm.
-These are ILS meta-heuristic and OLS methods, respectively.
+\section{The proposed method}\label{sec:rils}
+   Before we give details on our RILS-ROLS method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm. These are ILS meta-heuristic and OLS methods.
 
@@
     Iterated local search (ILS)~\cite{lourencco2003iterated} is an efficient meta-heuristics, whose essential idea is given as follow.
-Iteratively generate a sequence of solutions produced by the (embedded) heuristic, such as local search or  randomized greedy heuristics,  leading
-    towards better solutions than if one uses repeated random trials of that heuristic.
-This simple idea appeared in the literature by Baxter~\cite{baxter1981local} in early 1980s, and, since then, had been many time re-invented by many researches under different names; some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
+Iteratively generate a sequence of solutions produced by the (embedded) heuristic, such as local search or randomized greedy heuristics.
+When the search gets \emph{stuck} in local optimum, a \emph{perturbation} is performed -- this step is usually non-deterministic.
+This simple idea appeared in the literature by Baxter~\cite{baxter1981local} in early 1980s, and, since then, has been  re-invented by many researches under different names; some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
     Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases, combinations of these~\cite{applegate2003chained}.
 
-   In the literate, one of the mostly applied ILS versions is pseudo-coded in Algorithm~\ref{alg:ils}.
-Note that we also used the core of this version in our \textsc{Risl-Rols} algorithm.
-\fxnote{Provjeriti da li je ovo tačno -- popraviti algoritam ako nije sa onim što je korišten...}
+   The most popular version of ILS is shown in Algorithm~\ref{alg:ils}. Note that we use this version of ILS as the backbone of our RILS-ROLS algorithm.
 
@@
   		\begin{algorithmic}[1] 
-  			 \State \textbf{Input}: a COP problem; a LS procedure  of the problem 
+  			 \State \textbf{Input}: problem instance
   	 		\State \textbf{Output}: an approximate (feasible) solution 
-  	 		\State $s \gets$ Generate an initial solution
-  	 		\State  $s \gets LS(s)$
-   	 		\While{\emph{Stopping criteria is not met}}
+  	 		\State $s \gets$ \texttt{Initialize}$()$
+  	 		\State  $s \gets$ \texttt{LocalSearch}($s$)
+   	 		\While{\emph{stopping criteria is not met}}
    	    		 \State  $s' \gets$ \texttt{Perturbation}($s$)
-   	    		 \State  $s' \gets$ \texttt{LS}($s'$)
+   	    		 \State  $s' \gets$ \texttt{LocalSearch}($s'$)
    	    		 \State  $ s \gets$ \texttt{AcceptanceCriterion}($s, s'$)
    	 		\EndWhile
+   	 		\State \Return $s$
    		\end{algorithmic}
@@
 
-An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure.
+An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by local search.
 At each iteration, ILS applies three steps.
-First, the current incumbent solution is perturbed, that is mutated in a way the knowledge of the current best solution is (partially) used at the next iterations.
-Secondly, the perturbed solution is then improved by LS procedure.
+First, the current incumbent solution is perturbed -- it is partially randomized.
+Next, the perturbed solution is improved with LS procedure.
 Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion.
-Usually, this basic variant of ILS incorporates a mechanism of tabu list, that avoids the search getting back to already visited local search within a number of iterations.
+Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back to already visited solutions.
 
@@
 It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model).
-More precisely, given data $({X}, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_n)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized.
-This sum is also know by the term the sum of squared error (SSE).
-There are many methods to minimize SSE; one of the analytical methods is the calculus method that takes into account   partial derivation w.r.t.
+More precisely, given data $({X}, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized.
+This sum is also know as the sum of squared error (SSE).
+There are many methods to minimize SSE.
+One of the analytical approaches is the calculus-oriented -- it takes into account   partial derivation w.r.t.
 $k$ of the cost function $ \sum_{i} |\tilde{y}_i - y_i|^2 $, getting
@@
      	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
-     	 & \sum y_i  = k \sum x_i + b \cdot n 
+     	 & \sum y_i  = k \sum x_i + b \cdot n. 
      \end{align*}
-     which is a system of two equations with two variables ($k$ and $b$) that is  solved efficiently.
-   \subsection{The proposed Rils-Rols}
-    \fxnote{TODO}
+     By solving this system of equations, one can easily obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$.
+\fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor.
+Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }
+   \subsection{RILS-ROLS method}
+   Now we will explain the proposed RILS-ROLS method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
+
+    \begin{algorithm}
+   	\begin{algorithmic}[1] 
+   		\State \textbf{Input}: input training dataset $D_{tr}$
+   		\State \textbf{Output}: symbolic formula solution $s$
+   		\State $D_{tr}' \gets$ \texttt{Sample}($D_{tr}$)
+   		\State $s \gets NodeConstant(0)$ // tree with 0 as root node
+   		\State $s_{fit} \gets$ \texttt{Fitness}($s, D_{tr}'$)
+   		\State $start_{tried}, perturbations_{tried} \gets \emptyset, \emptyset$
+   		\While{\emph{stopping criteria is not met}}
+   			\State $start_{tried} \gets start_{tried} \cup \{s\}$
+   			\State $s_{perturbations} \gets $ \texttt{Generate1PerturbationsAndFitOLS}($s$)
+   			\State $s_{perturbations} \gets $ \texttt{OrderByR2}($s_{perturbations}$)
+   			\For{$p \in s_{perturbations}$}
+   				\If{$p \notin perturbations_{tried}$}
+   					\State $p \gets $ \texttt{Simplify}($p$)
+   					\State $p \gets $ \texttt{LocalSearch}($p$)
+   					\State $p_{fit} \gets$ \texttt{Fitness}($p$)
+   					\State $perturbations_{tried} \gets perturbations_{tried} \cup p$
+   				\EndIf
+   			\EndFor
+   		\EndWhile
+   		\State \Return $s$
+   	\end{algorithmic}
+   	\caption{RILS-ROLS outline.}
+   	\label{alg:rilsrols}
+   \end{algorithm}
+
 \section{Experimental evaluation}\label{sec:experiments}

### 2022-10-12 rils_rols/rils_rols.py

@@ -74,17 +74,8 @@ class RILSROLSRegressor(BaseEstimator):
         while self.time_elapsed<self.max_seconds and Solution.fit_calls<self.max_fit_calls: 
             start_solutions.add(str(start_solution))
             all_preturbations = self.all_preturbations(start_solution, len(X[0]))
-            #self.rg.shuffle(all_preturbations)
-            #print("-------------------------")
-            #print(best_solution)
-            #print("-------------------------")
-            #for p in all_preturbations:
-            #    print(p)
-            #new_solution = self.preturb(best_solution, len(X[0]))
-
-            # TODO: statistically check if this is good criterion for ordering preturbations
             pret_fits = {}
-            for pret in all_preturbations: #[:tournament_members]:
+            for pret in all_preturbations: 
                 pret_ols = copy.deepcopy(pret)
                 pret_ols = pret_ols.fit_constants_OLS(X, y)
                 pret_ols_fit = pret_ols.fitness(X, y)
@@ -94,7 +85,6 @@ class RILSROLSRegressor(BaseEstimator):
 
             impr = False
             p = 0
-            #for pret in all_preturbations:
             for pret, r2Inv in sorted_pret_fits:
                 p+=1
                 self.time_elapsed = time.time()-self.start

### 2022-10-14 doc/paper.tex
Main RILS-ROLS algorithm pseudocode finished.
Some fixing in pseudocode.
Update: OLS section

@@
 It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model).
-More precisely, given data $({X}, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized.
+More precisely, given data $({X}=(X_1, \ldots, X_d)^T, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized.
 This sum is also know as the sum of squared error (SSE).
@@
 
-   $$  \frac{\partial}{\partial k} \sum_{i} |\tilde{y}_i - y_i|^2 = \frac{\partial}{\partial k} \sum ( kx_i+b  - y_i)^2 =  \sum -2x_i(kx_i + b - y_i)  =  \sum -2x_i (\tilde{y}_i - y_i ) . $$
+   $$  \frac{\partial}{\partial k} \sum_{i} |\tilde{y}_i - y_i|^2 = \frac{\partial}{\partial k} \sum ( kX_i+b  - y_i)^2 =  \sum 2X_i(kX_i + b - y_i)  =  \sum -2X_i (y_i - \tilde{y}_i) . $$
 
    Taking into account   partial derivation w.r.t.  $b$, we have 
-    $$  \frac{\partial}{\partial b} \sum_{i} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum ( kx_i+b  - y_i)^2 = \sum -2  (\tilde{y}_i - y_i). $$
+    $$  \frac{\partial}{\partial b} \sum_{i} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum ( kX_i+b  - y_i)^2 = \sum -2  (y_i - \tilde{y}_i). $$
 
@@
     \begin{align*}
-    	  &\sum -2x_i (\tilde{y}_i - y_i )  = 0 \\
-    	  &\sum -2  (\tilde{y}_i - y_i ) = 0.
+    	 % &\sum -2X_i (\tilde{y}_i - y_i )  = 0 \\
+    	  & -2X_1 (y_1 - \tilde{y}_1)  = 0 \\
+    	  & \vdots \\
+    	  & -2X_d (y_d - \tilde{y}_d)  = 0 \\
+    	  &\sum -2  (y_i - \tilde{y}_i) = 0.
     \end{align*}
-     The above system can be transformed to 
-     \begin{align*}
-     	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
-     	 & \sum y_i  = k \sum x_i + b \cdot n. 
-     \end{align*}
-     By solving this system of equations, one can easily obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$.
+     %The above system can be transformed to 
+     %\begin{align*}
+     %	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
+     %	 & \sum y_i  = k \sum x_i + b \cdot d. 
+     %  \end{align*}
+     By solving this system of $(d+1)$ equations, one can obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$.
+%For example, in order to calculate coefficient $k_i$, the following system of equations is
      \fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor.
-Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }
+Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
    \subsection{RILS-ROLS method}

### 2022-10-20 doc/paper.tex
Main algorithm description finished.

@@
    		\State \textbf{Input}: input training dataset $D_{tr}$
-   		\State \textbf{Output}: symbolic formula solution $s$
-   		\State $D_{tr}' \gets$ \texttt{Sample}($D_{tr}$)
-   		\State $s \gets NodeConstant(0)$ // tree with 0 as root node
+   		\State \textbf{Output}: best symbolic formula solution $bs$
+   		\State $n_{tr} \gets |D_{tr}|$
+   		\State $sample_{size} \gets $ \texttt{InitialSampleSize}($n_{tr}$)
+   		\State $D_{tr}' \gets$ \texttt{Sample}($D_{tr}, sample_{size}$)
+   		\State $s \gets NodeConstant(0)$ 
    		\State $s_{fit} \gets$ \texttt{Fitness}($s, D_{tr}'$)
+   		\State $bs, bs_{fit} \gets s, s_{fit}$ \label{line:solSet}
    		\State $start_{tried}, perturbations_{tried} \gets \emptyset, \emptyset$
@@
    			\State $start_{tried} \gets start_{tried} \cup \{s\}$
-   			\State $s_{perturbations} \gets $ \texttt{Generate1PerturbationsAndFitOLS}($s$)
-   			\State $s_{perturbations} \gets $ \texttt{OrderByR2}($s_{perturbations}$)
+   			\State $s_{perturbations} \gets $ \texttt{Generate1Perturbations}($s$) \label{line:sPert}
+   			\State $s_{perturbations} \gets $ \texttt{FitOLS}($s_{perturbations}$, $D_{tr}'$)
+   			\State $s_{perturbations} \gets $ \texttt{OrderByR2}($s_{perturbations}$) \label{line:orderR2}
+   			\State $improved \gets false $
    			\For{$p \in s_{perturbations}$}
-   				\If{$p \notin perturbations_{tried}$}
-   					\State $p \gets $ \texttt{Simplify}($p$)
-   					\State $p \gets $ \texttt{LocalSearch}($p$)
-   					\State $p_{fit} \gets$ \texttt{Fitness}($p$)
-   					\State $perturbations_{tried} \gets perturbations_{tried} \cup p$
+   				\If{$p \in perturbations_{tried}$}
+   					\State \textbf{continue}
    				\EndIf
+  				\State $p \gets $ \texttt{Simplify}($p$) \label{line:simp}
+  				\State $p \gets $ \texttt{LocalSearch}($p$, $D_{tr}'$) \label{line:ls}
+  				\State $p_{fit} \gets$ \texttt{Fitness}($p$, $D_{tr}'$)
+  				\If{$p_{fit} < bs_{fit}$} \label{line:avoid1}
+  					\State $bs, bs_{fit}, improved \gets p, p_{fit}, true$ // new best solution
+  					\State \textbf{break}
+  				\EndIf \label{line:avoid2}
+  				\State $perturbations_{tried} \gets perturbations_{tried} \cup \{p\}$
    			\EndFor
+   			\If{improved}
+   				\State $s \gets bs$ \label{line:improved}
+   			\Else
+   				\State $start_{candidates} \gets $ \texttt{Generate1Perturbations}($bs$)
+   				\If{$start_{candidates} \setminus start_{tried} = \emptyset$} // all 1-perturbations around $bs$ tried
+   					\State $s' \gets $ \texttt{RandomPick}($start_{candidates}$)  \label{line:pert21}
+   					\State $start_{candidates} \gets $ \texttt{Generate1Perturbations}($s'$) \label{line:pert22}
+   				\EndIf
+   				\State $s \gets $ \texttt{RandomPick}($start_{candidates} \setminus start_{tried}$) \label{line:randPick}
+   				\If{not improved for too many iterations}
+   					\State $sample_{size} \gets$ \texttt{IncreaseSampleSize}($sample_{size}, n_{tr}$) \label{line:sampleAdj1}
+   					\State $D_{tr}' \gets$ \texttt{Sample}($D_{tr}, sample_{size}$)\label{line:sampleAdj2}
+   				\EndIf
+   			\EndIf
+   			\If{$R^2$ almost 1 and RMSE almost 0}
+   				\State \textbf{break} // early exit
+   			\EndIf
    		\EndWhile
-   		\State \Return $s$
+   		\State \Return $bs$
    	\end{algorithmic}
-   	\caption{RILS-ROLS outline.}
+   	\caption{RILS-ROLS algorithm.}
    	\label{alg:rilsrols}
    \end{algorithm}
+
+RILS-ROLS algorithms receives training dataset $D_{tr}$ as input.
+$D_{tr}$ can have very large number of records, so the first step of RILS-ROLS is to make a random sample $D_{tr}'$ of size $sample_{size}$.
+Initial sample size is calculated as $\max(0.01 \cdot n_{tr}, 100)$.
+Sample is later dynamically adjusted -- when there are no solution improvements for some number of iterations, the sample size is doubled (lines~\ref{line:sampleAdj1}-\ref{line:sampleAdj2} of Algorithm~\ref{alg:rilsrols}).
+
+As previously stated, solution is usually represented as a tree.
+We use simple solution initialization -- tree root node is set to zero constant.
+We interchangeably use two solution variables: i) $s$ denotes starting (or working) solution and ii) $bs$ stands for the best solution so far.
+Solution quality is measured by evaluating fitness function (more on this in the following Section~\ref{sec:fitness}).
+Before entering the main loop, the best solution is set to initial solution (line~\ref{line:solSet}).
+
+Main loop iterates as long as none of termination criteria is met: i) maximal running time has been reached; ii) maximal number of fitness calls has been made; iii) best solution is sufficiently good.
+The third criterion is based on the $R^2$ and $RMSE$ of the best solution.
+If $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
+On of the first steps in the main loop is to generate perturbations near the starting solution $s$ (line~\ref{line:sPert}). 
+As the name of this procedure (\texttt{Generate1Perturbations}) suggests, perturbation is local -- meaning the closeness of starting solution $s$ and any of perturbations is 1 (we call it 1-perturbation sometimes).
+The precise way of generating perturbation is described in a separate Section~\ref{sec:pertGen}.
+Candidate perturbations are being improved by performing OLS coefficient fitting (procedure \texttt{FitOLS}).
+This means that coefficients in linear combinations are being set by means of ordinary least squares method.
+After this step, perturbations are usually better suited to given sample data $D_{tr}'$. 
+Further, they are sorted w.r.t. $R^2$ metric in the descending order (line~\ref{line:orderR2}). 
+Now, the algorithm enters internal loop -- it iterates over ordered perturbations and aims to find the one which improves the best solution $bs$.
+But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}) after which the local search is performed (line~\ref{line:ls}).
+Solution simplification is done in a symbolical fashion by popular Python library called Sympy~\cite{sympy}.
+Local search tries to find local optima expressions close to the given $p$ -- there is a separate Section~\ref{sec:ls} dedicated to local search. 
+Finally, fitness function value of $p$ is compared to fitness function value of $bs$.
+If it is better, $bs$ is updated correspondingly and internal loop that goes across ordered perturbations is immediately stopped (\emph{first-improvement} strategy).
+Otherwise, the next perturbation is probed.
+Note that probed perturbations are remembered in a set denoted by $perturbations_{tried}$.
+The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}).
+If some of $s_{perturbations}$ around starting solution $s$ yielded an improvement, $bs$ becomes the starting solution $s$ in the next iteration of the main loop (line~\ref{line:improved}). 
+Otherwise, it makes no sense to set starting solution to $bs$, since nothing changed -- search is \emph{trapped} in local optimum.
+Therefore, a randomness needs to be introduced.
+First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{Generate1Perturbations}).
+If at least one of these was not previously used as a starting solution ($start_{tried}$), a single perturbation from the $start_{candidates} \setminus start_{tried}$ is randomly picked (line~\ref{line:randPick}).
+There is small chance that $start_{candidates} \setminus start_{tried} = \emptyset$.
+When that happens, the set of starting solution candidates is equal to perturbations of some randomly selected perturbation of $bs$ (lines \ref{line:pert21}-\ref{line:pert22}) -- which effectively means that perturbations on distance 2 from $bs$ are used.
+There is a very small chance that these 2-perturbations will have empty set difference with $start_{tried}$ set of starting solutions.
+Therefore, 3-perturbations are not considered.
+
+\subsubsection{Fitness function}\label{sec:fitness}
+
+\subsubsection{Perturbations}\label{sec:pertGen}
+
+\subsubsection{Local search}\label{sec:ls}
 
@@
 
- \section{Complete results for a single random seed}\label{sec:appendix-1}
-
- \section{Overview of RILS-ROLS python package}\label{sec:appendix-2}
-
- \section{Analysis within SRBench}
+ \section{Overview of RILS-ROLS python package}\label{sec:appendix-1}
 

### 2022-10-21 doc/paper.tex
Fitness function text finished.

@@
 
-    Thus, we get the system of equation: 
+    Thus, we get the system of equations: 
     \begin{align*}
@@
 If $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
+
 On of the first steps in the main loop is to generate perturbations near the starting solution $s$ (line~\ref{line:sPert}). 
@@
 The precise way of generating perturbation is described in a separate Section~\ref{sec:pertGen}.
+
 Candidate perturbations are being improved by performing OLS coefficient fitting (procedure \texttt{FitOLS}).
@@
 Further, they are sorted w.r.t. $R^2$ metric in the descending order (line~\ref{line:orderR2}).
+
 Now, the algorithm enters internal loop -- it iterates over ordered perturbations and aims to find the one which improves the best solution $bs$.
 But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}) after which the local search is performed (line~\ref{line:ls}).
-Solution simplification is done in a symbolical fashion by popular Python library called Sympy~\cite{sympy}.
+Solution simplification is done in a symbolical fashion by popular Python library called SymPy~\cite{sympy}.
 Local search tries to find local optima expressions close to the given $p$ -- there is a separate Section~\ref{sec:ls} dedicated to local search. 
@@
 The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}).
+
 If some of $s_{perturbations}$ around starting solution $s$ yielded an improvement, $bs$ becomes the starting solution $s$ in the next iteration of the main loop (line~\ref{line:improved}). 
@@
 \subsubsection{Fitness function}\label{sec:fitness}
+
+Symbolic regression objective is to determine the expression governing available data.
+It is also allowed to obtain some equivalent expression, having in mind there are many ways to express some symbolical equation.
+Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, simply because the goal expression is not known at that point -- only target values for some of the input features are known.
+So, different numerical metrics are being used in literature to guide the symbolic regression search process.
+The most popular are the coefficient of determination, also known as $R^2$ and mean squared error (MSE) or root mean squared error (RMSE).
+The important aspect of the solution quality might also be the solution expression complexity.
+This follows the Occam's razor principle that simpler solution is more likely to be a correct one.
+The search process of RILS-ROLS is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
+
+\begin{equation}
+	\label{eq:fitness}
+	fit(s) = (2-R^2(s)) \cdot (1+RMSE(s)) \cdot (1+penalty_{size} \cdot size(S))
+\end{equation}
+
+Since the presented fitness function needs to be minimized, the following conclusions may be drawn:
+\begin{itemize}
+	\item higher $R^2$ is preferred -- ideally, when $R^2(s)=1$, the effect of term $1+R^2(s)$ is neutralized, since 1 is neutral for multiplication;
+	\item lower RMSE is preferred, ideally, when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
+	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle).
+\end{itemize}
+
+The size of expression is calculated by simply counting all nodes in the expression tree -- this includes leaves (variables and constants) and internal nodes (operations).
 

### 2022-10-22 doc/paper.tex
Small update.
Perturbations pseudo-code.

@@
     \begin{algorithm}
+    \small
+    \hspace*{\algorithmicindent} \textbf{Input}: input training dataset $D_{tr}$ \\
+    \hspace*{\algorithmicindent} \textbf{Output}: best symbolic formula solution $bs$
    	\begin{algorithmic}[1] 
-   		\State \textbf{Input}: input training dataset $D_{tr}$
-   		\State \textbf{Output}: best symbolic formula solution $bs$
+   		\Procedure{RILS-ROLS}{$D_{tr}$}
    		\State $n_{tr} \gets |D_{tr}|$
@@
    			\State $start_{tried} \gets start_{tried} \cup \{s\}$
-   			\State $s_{perturbations} \gets $ \texttt{Generate1Perturbations}($s$) \label{line:sPert}
+   			\State $s_{perturbations} \gets $ \texttt{All1Perturbations}($s$) \label{line:sPert}
    			\State $s_{perturbations} \gets $ \texttt{FitOLS}($s_{perturbations}$, $D_{tr}'$)
@@
    			\Else
-   				\State $start_{candidates} \gets $ \texttt{Generate1Perturbations}($bs$)
+   				\State $start_{candidates} \gets $ \texttt{All1Perturbations}($bs$)
    				\If{$start_{candidates} \setminus start_{tried} = \emptyset$} // all 1-perturbations around $bs$ tried
@@
    		\State \Return $bs$
+   		\EndProcedure
    	\end{algorithmic}
-   	\caption{RILS-ROLS algorithm.}
+   	\caption{RILS-ROLS method.}
    	\label{alg:rilsrols}
@@
 On of the first steps in the main loop is to generate perturbations near the starting solution $s$ (line~\ref{line:sPert}). 
-As the name of this procedure (\texttt{Generate1Perturbations}) suggests, perturbation is local -- meaning the closeness of starting solution $s$ and any of perturbations is 1 (we call it 1-perturbation sometimes).
+As the name of this procedure (\texttt{All1Perturbations}) suggests, perturbation is local -- meaning the closeness of starting solution $s$ and any of perturbations is 1 (we call it 1-perturbation sometimes).
 The precise way of generating perturbation is described in a separate Section~\ref{sec:pertGen}.
@@
 Therefore, a randomness needs to be introduced.
-First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{Generate1Perturbations}).
+First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{All1Perturbations}).
 If at least one of these was not previously used as a starting solution ($start_{tried}$), a single perturbation from the $start_{candidates} \setminus start_{tried}$ is randomly picked (line~\ref{line:randPick}).
@@
 
+\begin{algorithm}
+	\hspace*{\algorithmicindent} \textbf{Input}: solution $s$ \\
+	\hspace*{\algorithmicindent} \textbf{Output}: local perturbations (1-perturbations) around solution $s$ -- $s_{perturbations}$
+	\begin{algorithmic}[1] 
+		\Procedure{All1Perturbations}{$s$}
+		\State $s_{perturbations} \gets \emptyset$
+		\State $s \gets$ \texttt{NormalizeConstants}($s$)
+		\State $s \gets$ \texttt{Simplify}($s$)
+		\State $s_{subtrees} \gets$ \texttt{SubTrees}($s$)
+		\For{$ss \in s_{subtrees}$}
+			\If{$ss = s$}
+				\State $s_{perturbations} \gets s_{perturbations} \cup$ \texttt{Node1Perturbations}($ss$)
+			\EndIf
+			\If{$ss.arity \geq 1$}
+				\State $node_{perturbations} \gets$ \texttt{Node1Perturbations}($ss.left$)
+				\For{$np \in node_{perturbations}$}
+					\State $ss_{new} \gets$ \texttt{Replace}($ss$, $ss.left$, $np$)
+					\State $s_{perturbations} \gets s_{perturbations} \cup \{ss_{new}\}$
+				\EndFor
+			\EndIf
+			\If{$ss.arity = 2$}
+				\State $node_{perturbations} \gets$ \texttt{Node1Perturbations}($ss.right$)
+				\For{$np \in node_{perturbations}$}
+					\State $ss_{new} \gets$ \texttt{Replace}($ss$, $ss.right$, $np$)
+					\State $s_{perturbations} \gets s_{perturbations} \cup \{ss_{new}\}$
+				\EndFor
+			\EndIf
+		\EndFor
+		\State \Return $s_{perturbations}$
+		\EndProcedure
+	\end{algorithmic}
+	\caption{Generation of 1-perturbations.}
+	\label{alg:pert}
+\end{algorithm}
+
 \subsubsection{Local search}\label{sec:ls}
@@
 \section{Experimental evaluation}\label{sec:experiments}
+
+\subsection{Datasets and SRBench}
 

### 2022-10-22 doc/paper.tex
Update in Section 3.3.1

@@
 
- \subsection{Ordinary least square method}
+ \subsection{Ordinary least square method}\label{sec:ols}
    Ordinary least square method (OLS) is a linear regression technique.
@@
 RILS-ROLS algorithms receives training dataset $D_{tr}$ as input.
-$D_{tr}$ can have very large number of records, so the first step of RILS-ROLS is to make a random sample $D_{tr}'$ of size $sample_{size}$.
-Initial sample size is calculated as $\max(0.01 \cdot n_{tr}, 100)$.
-Sample is later dynamically adjusted -- when there are no solution improvements for some number of iterations, the sample size is doubled (lines~\ref{line:sampleAdj1}-\ref{line:sampleAdj2} of Algorithm~\ref{alg:rilsrols}).
+$D_{tr}$ can have very large number of records, so the first step of RILS-ROLS is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
+Initial the sample size is calculated as $\max(0.01 \cdot n_{tr}, 100)$.
+The size of sample is later dynamically adjusted through the algorithm's iterations -- when there are no solution improvements for some number of iterations, the sample size is doubled (lines~\ref{line:sampleAdj1}-\ref{line:sampleAdj2} of Algorithm~\ref{alg:rilsrols}).
 
-As previously stated, solution is usually represented as a tree.
+As previously stated, solution is usually represented by means of a tree.
 We use simple solution initialization -- tree root node is set to zero constant.
-We interchangeably use two solution variables: i) $s$ denotes starting (or working) solution and ii) $bs$ stands for the best solution so far.
-Solution quality is measured by evaluating fitness function (more on this in the following Section~\ref{sec:fitness}).
-Before entering the main loop, the best solution is set to initial solution (line~\ref{line:solSet}).
+We interchangeably use two solution variables: ($i$) $s$ denotes starting (or working) solution and ($ii$) $bs$ stands for the best solution so far.
+Solution quality is measured by evaluating the fitness function (more about it in the subsequent Section~\ref{sec:fitness}).
+Before entering the main loop, the best solution \emph{bs} is set to the initial solution (line~\ref{line:solSet}).
 
-Main loop iterates as long as none of termination criteria is met: i) maximal running time has been reached; ii) maximal number of fitness calls has been made; iii) best solution is sufficiently good.
-The third criterion is based on the $R^2$ and $RMSE$ of the best solution.
-If $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
+Main loop iterates as long as none of termination criteria is met: ($i$) maximal running time has been reached; ($ii$) maximal number of fitness calculations has been made; ($iii$) best solution is sufficiently good,
+w.r.t.
+the $R^2$ and $RMSE$ of the best solution.
+More precisely, if $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
 
-On of the first steps in the main loop is to generate perturbations near the starting solution $s$ (line~\ref{line:sPert}). 
-As the name of this procedure (\texttt{All1Perturbations}) suggests, perturbation is local -- meaning the closeness of starting solution $s$ and any of perturbations is 1 (we call it 1-perturbation sometimes).
-The precise way of generating perturbation is described in a separate Section~\ref{sec:pertGen}.
+One of the first steps in the main loop is to generate perturbations near the starting solution $s$ (line~\ref{line:sPert}). 
+As the name of this procedure (\texttt{All1Perturbations}) suggests, perturbation step is local -- meaning the closeness of starting solution $s$ and any of perturbations is 1 (we call it 1-perturbation sometimes).
+The precise way of generating perturbation is described separately, in Section~\ref{sec:pertGen}.
 
 Candidate perturbations are being improved by performing OLS coefficient fitting (procedure \texttt{FitOLS}).
-This means that coefficients in linear combinations are being set by means of ordinary least squares method.
+This means that coefficients in any of linear combinations of current solution are being set by means of ordinary least squares method, described in Section~\ref{sec:ols}.
 After this step, perturbations are usually better suited to given sample data $D_{tr}'$. 
-Further, they are sorted w.r.t. $R^2$ metric in the descending order (line~\ref{line:orderR2}).
+Further, these perturbations are sorted w.r.t. $R^2$ metric in the descending order (line~\ref{line:orderR2}).
 
-Now, the algorithm enters internal loop -- it iterates over ordered perturbations and aims to find the one which improves the best solution $bs$.
+Now, the algorithm enters the internal loop -- it iterates over the ordered perturbations and aims to find the one which improves the best solution $bs$.
 But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}) after which the local search is performed (line~\ref{line:ls}).
 Solution simplification is done in a symbolical fashion by popular Python library called SymPy~\cite{sympy}.
-Local search tries to find local optima expressions close to the given $p$ -- there is a separate Section~\ref{sec:ls} dedicated to local search. 
+Local search tries to find local optima expressions close to the given $p$ -- explained in details in Section~\ref{sec:ls}.  
 Finally, fitness function value of $p$ is compared to fitness function value of $bs$.
-If it is better, $bs$ is updated correspondingly and internal loop that goes across ordered perturbations is immediately stopped (\emph{first-improvement} strategy).
+If a new incumbent is found, $bs$ is updated correspondingly and internal loop that goes across ordered perturbations is immediately terminated (it works in a  \emph{first-improvement} strategy).
 Otherwise, the next perturbation is probed.
-Note that probed perturbations are remembered in a set denoted by $perturbations_{tried}$.
-The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}).
+Note that the probed perturbations are stored in a set denoted by $perturbations_{tried}$.
+The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}), i.e.
+this structure serves as a kind of tabu list, initially proposed in the famous Tablu search algorithm, see~\cite{glover1998tabu}.
 
 If some of $s_{perturbations}$ around starting solution $s$ yielded an improvement, $bs$ becomes the starting solution $s$ in the next iteration of the main loop (line~\ref{line:improved}). 
-Otherwise, it makes no sense to set starting solution to $bs$, since nothing changed -- search is \emph{trapped} in local optimum.
-Therefore, a randomness needs to be introduced.
+Otherwise, it makes no sense to set starting solution to $bs$, as nothing changed -- the search is being  \emph{trapped} in a local optimum.
+In order to avoid this undesired situation, a randomness needs to be triggered.
 First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{All1Perturbations}).
 If at least one of these was not previously used as a starting solution ($start_{tried}$), a single perturbation from the $start_{candidates} \setminus start_{tried}$ is randomly picked (line~\ref{line:randPick}).
-There is small chance that $start_{candidates} \setminus start_{tried} = \emptyset$.
-When that happens, the set of starting solution candidates is equal to perturbations of some randomly selected perturbation of $bs$ (lines \ref{line:pert21}-\ref{line:pert22}) -- which effectively means that perturbations on distance 2 from $bs$ are used.
-There is a very small chance that these 2-perturbations will have empty set difference with $start_{tried}$ set of starting solutions.
-Therefore, 3-perturbations are not considered.
+There is a insignificant chance that $start_{candidates} \setminus start_{tried} = \emptyset$.
+When that happens, the set of starting solution candidates is equal to perturbations of some randomly selected perturbation of $bs$ (lines \ref{line:pert21}-\ref{line:pert22}) -- which effectively means that the perturbations with distance 2 from $bs$ are used.
+Indeed, there is a minor chance that these 2-perturbations will have empty set difference with $start_{tried}$ set of starting solutions.
+Therefore, more expensive 3-perturbations are not considered in our algorithm.
 
@@
 Symbolic regression objective is to determine the expression governing available data.
-It is also allowed to obtain some equivalent expression, having in mind there are many ways to express some symbolical equation.
-Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, simply because the goal expression is not known at that point -- only target values for some of the input features are known.
-So, different numerical metrics are being used in literature to guide the symbolic regression search process.
+It is also allowed to obtain some equivalent expression, keeping in mind that there are multiple ways to express some symbolical equation.
+Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, simply because the goal expression is not known at that point as only target values for some of the input features are known.
+Thus, different numerical metrics are being used in literature to guide the symbolic regression search process.
 The most popular are the coefficient of determination, also known as $R^2$ and mean squared error (MSE) or root mean squared error (RMSE).
 The important aspect of the solution quality might also be the solution expression complexity.
-This follows the Occam's razor principle that simpler solution is more likely to be a correct one.
+This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
 The search process of RILS-ROLS is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
@@
 \begin{itemize}
-	\item higher $R^2$ is preferred -- ideally, when $R^2(s)=1$, the effect of term $1+R^2(s)$ is neutralized, since 1 is neutral for multiplication;
+	\item higher $R^2$ is preferred -- ideally, when $R^2(s)=1$, the effect of term $1+R^2(s)$ is neutralized; %since 1 is neutral for multiplication;
 	\item lower RMSE is preferred, ideally, when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
-	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle).
+	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle); therefore, we award solutions that are more simple with its representation.
 \end{itemize}

### 2022-10-22 doc/paper.tex
Literature extesion

@@
 	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
-	        Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
+	        APF-FE                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
         	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
@@
 			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
-	       Local optimization     & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
+			MRGP & \cite{arnaldo2014multiple} (2014) & It decouples and
+			linearly combines a program's subexpressions via multiple regression on the target variable  \\
+	       Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
+	       FEAT & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees  comprised of activation functions; Differentiable features are trained via gradient descent \\
 	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
@@
 
-	       AI Feynman  & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
+	       AI-Feynman  & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
 	             GOMEA  & \cite{virgolin2021improving} (2021)    & A model-based
@@
 
+Our proposed algorithm was implemented in Python version 3.x.
+All experiments were performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
+The maximum computation time allowed for each run was limited to 1h minutes, i.e., 3600 seconds.
+
+The following algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{AFP-FE}, \textsc{ITEA}, \textsc{AFP}, \textsc{DSR}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{SBP-GP}, \textsc{EPLEX}, \textsc{BSR}, \textsc{FEAT}, \textsc{FFX}, \textsc{MRGP} and our \textsc{Rils}-\textsc{Rols} algorithm.
+
 \subsection{Datasets and SRBench}

### 2022-10-22 doc/paper.tex
Perturbations are now finished.

@@
    					\State $s' \gets $ \texttt{RandomPick}($start_{candidates}$)  \label{line:pert21}
-   					\State $start_{candidates} \gets $ \texttt{Generate1Perturbations}($s'$) \label{line:pert22}
+   					\State $start_{candidates} \gets $ \texttt{All1Perturbations}($s'$) \label{line:pert22}
    				\EndIf
@@
 
+Perturbations allow the algorithm to escape from local optima.
+As previously described, they are performed in two occasions: the first one during the exhaustive examination of neighboring solutions around the starting solution, and the second one being non-exhaustive, during selection of the next starting solution.
+In both cases, the same Algorithm~\ref{alg:pert} is used.
+
 \begin{algorithm}
@@
 		\Procedure{All1Perturbations}{$s$}
-		\State $s_{perturbations} \gets \emptyset$
+		\State $s_{perturbations} \gets \emptyset$ \label{line:pertInit}
 		\State $s \gets$ \texttt{NormalizeConstants}($s$)
@@
 		\State $s_{subtrees} \gets$ \texttt{SubTrees}($s$)
-		\For{$ss \in s_{subtrees}$}
+		\For{$ss \in s_{subtrees}$} \label{line:forSSStart}
 			\If{$ss = s$}
-				\State $s_{perturbations} \gets s_{perturbations} \cup$ \texttt{Node1Perturbations}($ss$)
+				\State $s_{perturbations} \gets s_{perturbations} \cup$ \texttt{NodeChange}($ss$)
 			\EndIf
 			\If{$ss.arity \geq 1$}
-				\State $node_{perturbations} \gets$ \texttt{Node1Perturbations}($ss.left$)
+				\State $node_{perturbations} \gets$ \texttt{NodeChange}($ss.left$)
 				\For{$np \in node_{perturbations}$}
@@
 			\If{$ss.arity = 2$}
-				\State $node_{perturbations} \gets$ \texttt{Node1Perturbations}($ss.right$)
+				\State $node_{perturbations} \gets$ \texttt{NodeChange}($ss.right$)
 				\For{$np \in node_{perturbations}$}
@@
 			\EndIf
-		\EndFor
+		\EndFor \label{line:forSSEnd}
 		\State \Return $s_{perturbations}$
@@
 \end{algorithm}
+
+Initially, the set of perturbations $s_{perturbations}$ is empty (line~\ref{line:pertInit}).
+
+This is followed by constant normalization during which coefficients that enter multiplication, division, addition or subtraction are set to 1, while those entering the power function are rounded to integer, with exception of square root, which is kept intact.
+For example, for expression $3.3\cdot(x+45.1\cdot y^{3.2})\cdot 81\cdot x/\sqrt{y}$ the normalized version is $1\cdot (x+1\cdot y^3)\cdot 1\cdot x/\sqrt{y}$.
+The reason for performing normalization is to reduce the search space of possible perturbations.
+This reduction is reasonable, since normalization preserves the essential functional form.
+(Note that coefficients get tuned later during the OLS phase and local search.)
+
+After normalization, the expression is simplified -- getting compact expression is more likely after normalization than before.
+The previous expression will take form $(x+y^3)\cdot x/\sqrt{y}$ -- this simplification only removed unnecessary coefficients, but in general it can be non-trivial symbolic simplification.
+
+Perturbations are generated by making simple changes on the per-node level of $s$ expression tree.
+Depending on the structure of the expression tree (expression does not have to have unique tree representation), the set of subtrees of the previous expression $(x+y^3)\cdot x/\sqrt{y}$ might be $\{(x+y^3)\cdot x/\sqrt{y}, (x+y^3), x/\sqrt{y}, x, y^3, \sqrt{y}, y\}$.
+This set of subtrees is obtained if left subtree of the whole expression is $(x+y^3)$ while the right one is $x/\sqrt{y}$.
+Lines \ref{line:forSSStart}-\ref{line:forSSEnd} show that there are three possibly overlapping cases when performing perturbations on the per-subtree level.
+
+\emph{Case 1}. 
+Subtree $ss$ is the whole tree $s$.
+Following on the the previous exemplary expression tree, this means that multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
+For example, multiplication can be changed to addition, which forms a perturbation $(x+y^3)+ x/\sqrt{y}$.
+
+\emph{Case 2}. 
+Subtree $ss$ has arity of at least 1. This means that the left subtree exists, so the left subtree node is to be changed. 
+For example, if $ss=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is changed to division). 
+Another example would be the case of unary operation, e.g.
+when $ss=\sqrt{y}$.
+In that case, some of the possible perturbations could be $(x+y^3)\cdot x/\sqrt{\ln{y}}$ (application of logarithm to left subtree $y$) or $(x+y^3)\cdot x/\sqrt{x}$ (changing variable $y$ to $x$), etc.
+
+\emph{Case 3}. 
+Subtree $ss$ is binary operation, meaning the right subtree must exist. 
+The idea is analog as in \emph{Case 2}.
+
+Allowed per-node changes are as follows:
+
+\begin{enumerate}
+	\item Any node to any of its subtrees (excluding itself). For example, if $(x+y^3)$ is changed to $x$, the perturbation is $(x+y^3)\cdot x/\sqrt{y} \rightarrow x\cdot x/\sqrt{y}$. 
+	\item Variable to another variable or constant to variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (y+y^3)\cdot x/\sqrt{y}$.
+	\item Variable to unary operation applied to that variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot \ln{x}/\sqrt{y}$.
+	\item Unary operation to another unary operation. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sin{y}$.
+	\item Binary operation to another binary operation. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot (x + \sqrt{y})$. 
+	\item Variable or constant enter the binary operation with arbitrary variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+x/y^3)\cdot x/\sqrt{y}$. 
+\end{enumerate}
 

### 2022-10-23 doc/paper.tex
Revizije u Sekciji 3.3.2

@@
 
+\fxnote{Dati neku smislenu procjenu kompleksnosti algoritma, ako to nije pretesko. }
 \subsubsection{Fitness function}\label{sec:fitness}
@@
 Perturbations allow the algorithm to escape from local optima.
-As previously described, they are performed in two occasions: the first one during the exhaustive examination of neighboring solutions around the starting solution, and the second one being non-exhaustive, during selection of the next starting solution.
+As previously described, perturbations are performed in two occasions: ($i$) during the exhaustive examination of neighboring solutions around the starting solution, ($ii$)during selection of the next starting solution, a non-exhaustive case.
 In both cases, the same Algorithm~\ref{alg:pert} is used.
@@
 For example, for expression $3.3\cdot(x+45.1\cdot y^{3.2})\cdot 81\cdot x/\sqrt{y}$ the normalized version is $1\cdot (x+1\cdot y^3)\cdot 1\cdot x/\sqrt{y}$.
-The reason for performing normalization is to reduce the search space of possible perturbations.
+The reason for performing normalization is reducing the search space of possible perturbations thus keeping them within a reasonable size.
 This reduction is reasonable, since normalization preserves the essential functional form.
@@
 
-After normalization, the expression is simplified -- getting compact expression is more likely after normalization than before.
-The previous expression will take form $(x+y^3)\cdot x/\sqrt{y}$ -- this simplification only removed unnecessary coefficients, but in general it can be non-trivial symbolic simplification.
+After performing the normalization process, the expression is simplified -- getting compact expression is more likely after normalization than before.
+The previous expression will take form $(x+y^3)\cdot x/\sqrt{y}$.
+The purpose of simplification is removing unnecessary coefficients, but in general it can also be non-trivial symbolic simplification.
 
@@
 Following on the the previous exemplary expression tree, this means that multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
-For example, multiplication can be changed to addition, which forms a perturbation $(x+y^3)+ x/\sqrt{y}$.
+For example, multiplication can be replaced by addition, which forms a perturbation $(x+y^3)+ x/\sqrt{y}$.
 
@@
 Subtree $ss$ has arity of at least 1. This means that the left subtree exists, so the left subtree node is to be changed. 
-For example, if $ss=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is changed to division). 
+For example, if $ss=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
 Another example would be the case of unary operation, e.g.
@@
 Subtree $ss$ is binary operation, meaning the right subtree must exist. 
-The idea is analog as in \emph{Case 2}.
+The analogous idea is applied as in \emph{Case 2}.
 
-Allowed per-node changes are as follows:
+The algorithm allows the following set of carefully chosen per-node changes:
 
@@
 \end{enumerate} 
+\fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene}
 

### 2022-10-23 doc/paper.tex
Rad na opisu rezultata: instance

@@
 
-The following algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{AFP-FE}, \textsc{ITEA}, \textsc{AFP}, \textsc{DSR}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{SBP-GP}, \textsc{EPLEX}, \textsc{BSR}, \textsc{FEAT}, \textsc{FFX}, \textsc{MRGP} and our \textsc{Rils}-\textsc{Rols} algorithm.
+The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{AFP-FE}, \textsc{ITEA}, \textsc{AFP}, \textsc{DSR}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{SBP-GP}, \textsc{EPLEX}, \textsc{BSR}, \textsc{FEAT}, \textsc{FFX}, \textsc{MRGP} and our \textsc{Rils}-\textsc{Rols} algorithm.
 
 \subsection{Datasets and SRBench}
+
+SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and the environment for analysis, see~\cite{la2021contemporary}.
+It brought researchers an easy handled environment to evaluation, compare, and analyse their methods.
+Among all benchmark sets, we involve two real-world inspired benchmark sets into our computational evaluation:
+\begin{itemize}
+	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that correspond to various natural laws.  
+	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. 
+	\item \textsc{Strogatz} benchmark set from~\cite{la2016inference}. 
+	Each dataset is represented by a 2-state system of first-order, ordinary differential equations. 
+	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  the current two states on which it depends.
+These equations describes various non-linear dynamics and exhibiting chaos.
+
+\end{itemize}
+The abovementioned benchmark sets may be biased as models which describe phisical laws may have various symmetries, periodically w.r.t.
+some variables, internal separability on some variables etc.
+In that way, the search process and the search space can be biased and in-advance significantly reduced.
+Thus, some methods may get significant help with this regards, while some others may be in the subordinate situation.
+  In order to permit any kind of favoritism, we generate a set of randomly generated instances, called \textsc{Random}.
+These instances are generated according the following procedure.
+\fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}
 

### 2022-10-23 doc/paper.tex
Local search finished. Control parameters described as well.

@@
     \begin{algorithm}
-    \small
+    \footnotesize
     \hspace*{\algorithmicindent} \textbf{Input}: input training dataset $D_{tr}$ \\
+     \hspace*{\algorithmicindent} \textbf{Control parameters}: size penalty $penalty_{size}$, error tolerance $tolerance_{error}$ \\
     \hspace*{\algorithmicindent} \textbf{Output}: best symbolic formula solution $bs$
@@
    			\EndIf
-   			\If{$R^2$ almost 1 and RMSE almost 0}
+   			\If{$R^2$ almost 1 and RMSE almost 0 w.r.t. $tolerance_{error}$}
    				\State \textbf{break} // early exit
@@
    		\EndWhile
+   		\State $bs \gets $ \texttt{Simplify}($bs$)
+   		\State $bs \gets $ \texttt{RoundModelCoefficients}($bs$)
    		\State \Return $bs$
@@
 RILS-ROLS algorithms receives training dataset $D_{tr}$ as input.
+In addition, it has two control parameters: $penalty_{size}$ and $tolerance_{error}$.
+The first one quantifies the importance of solution expression complexity in the overall solution quality measure (more on this in Section~\ref{sec:fitness}).
+The second parameter is related to the expected noise level in data -- higher noise means that tolerance to errors should be higher.
  $D_{tr}$ can have very large number of records, so the first step of RILS-ROLS is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
@@
 More precisely, if $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
+The sufficiency is controlled with parameter $tolerance_{error}$ -- smaller value means that $R^2$ and $RMSE$ should be closer to 1 and 0, respectively.
 
@@
 Therefore, more expensive 3-perturbations are not considered in our algorithm.
+
+Before returning the final symbolical model, RILS-ROLS peforms the final symbolical simplification and rounding of model coefficients.
+The later is sensitive to control parameter $tolerance_{error}$ -- smaller value means information loss during rounding is smaller, i.e.
+higher number of significant digits is preserved.
+Note that confidence in the symbolical model is reduced when expected noise in data is higher -- the rule of thumb is: for higher expected noise $tolerance_{error}$ should be higher.
 
@@
 	\hspace*{\algorithmicindent} \textbf{Input}: solution $s$ \\
-	\hspace*{\algorithmicindent} \textbf{Output}: local perturbations (1-perturbations) around solution $s$ -- $s_{perturbations}$
+	\hspace*{\algorithmicindent} \textbf{Output}: local perturbations (1-perturbations) of solution $s$ -- $s_{perturbations}$
 	\begin{algorithmic}[1] 
@@
 		\State $s_{subtrees} \gets$ \texttt{SubTrees}($s$)
-		\For{$ss \in s_{subtrees}$} \label{line:forSSStart}
-			\If{$ss = s$}
-				\State $s_{perturbations} \gets s_{perturbations} \cup$ \texttt{NodeChange}($ss$)
-			\EndIf
-			\If{$ss.arity \geq 1$}
-				\State $node_{perturbations} \gets$ \texttt{NodeChange}($ss.left$)
-				\For{$np \in node_{perturbations}$}
-					\State $ss_{new} \gets$ \texttt{Replace}($ss$, $ss.left$, $np$)
-					\State $s_{perturbations} \gets s_{perturbations} \cup \{ss_{new}\}$
-				\EndFor
-			\EndIf
-			\If{$ss.arity = 2$}
-				\State $node_{perturbations} \gets$ \texttt{NodeChange}($ss.right$)
-				\For{$np \in node_{perturbations}$}
-					\State $ss_{new} \gets$ \texttt{Replace}($ss$, $ss.right$, $np$)
-					\State $s_{perturbations} \gets s_{perturbations} \cup \{ss_{new}\}$
-				\EndFor
-			\EndIf
+		\For{$n \in s_{subtrees}$} \label{line:forSSStart}
+			\State $n_{perturbations} \gets$ \texttt{All1PerturbationsAroundNode}($s$, $n$)
+			\State $s_{perturbations} \gets s_{perturbations} \cup n_{perturbations}$	
 		\EndFor \label{line:forSSEnd}
@@
 	\end{algorithmic}
-	\caption{Generation of 1-perturbations.}
+	\caption{Generation of all 1-perturbations for a given solution.}
 	\label{alg:pert}
@@
 
-Initially, the set of perturbations $s_{perturbations}$ is empty (line~\ref{line:pertInit}).
+Initially, the set of perturbations $s_{perturbations}$ is empty (line~\ref{line:pertInit} of Algorithm~\ref{alg:pert}).
 
@@
 This set of subtrees is obtained if left subtree of the whole expression is $(x+y^3)$ while the right one is $x/\sqrt{y}$.
-Lines \ref{line:forSSStart}-\ref{line:forSSEnd} show that there are three possibly overlapping cases when performing perturbations on the per-subtree level.
+For each subtree $n$, the set of perturbations around $n$ is generated (lines \ref{line:forSSStart}-\ref{line:forSSEnd} of Algorithm~\ref{alg:pert}).
+
+Algorithm~\ref{alg:pertNode} shows how perturbations around given subtree (node) are generated.
+
+\begin{algorithm}	
+	\hspace*{\algorithmicindent} \textbf{Input}: solution $s$, node $n$\\
+	\hspace*{\algorithmicindent} \textbf{Output}: 1-perturbations of solution $s$ around node $n$
+	\begin{algorithmic}[1]
+		\Procedure{All1PerturbationsAroundNode}{$s$, $n$}
+		\State $n_{perturbations} \gets \emptyset$
+		\If{$n = s$}
+		\State $n_{perturbations} \gets n_{perturbations} \cup$ \texttt{NodeChanges}($n$)
+		\EndIf
+		\If{$n.arity \geq 1$}
+		\State $n_{changes} \gets$ \texttt{NodeChanges}($n.left$)
+		\For{$nc \in n_{changes}$}
+		\State $new \gets$ \texttt{Replace}($s$, $n.left$, $nc$)
+		\State $n_{perturbations} \gets n_{perturbations} \cup \{new\}$
+		\EndFor
+		\EndIf
+		\If{$n.arity = 2$}
+		\State $n_{changes} \gets$ \texttt{NodeChanges}($n.right$)
+		\For{$nc \in n_{changes}$}
+		\State $new \gets$ \texttt{Replace}($s$, $n.right$, $nc$)
+		\State $n_{perturbations} \gets n_{perturbations} \cup \{new\}$
+		\EndFor
+		\EndIf
+		\State \Return $n_{perturbations}$
+		\EndProcedure
+	\end{algorithmic}
+	\caption{Generation of 1-perturbations for a given solution around given node.}
+	\label{alg:pertNode}
+\end{algorithm}
+
+It can be seen that there are three possibly overlapping cases when performing perturbations on the per-node level.
 
 \emph{Case 1}. 
-Subtree $ss$ is the whole tree $s$.
+Observed node $n$ is the whole tree $s$.
 Following on the the previous exemplary expression tree, this means that multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
@@
 \emph{Case 2}. 
-Subtree $ss$ has arity of at least 1. This means that the left subtree exists, so the left subtree node is to be changed. 
-For example, if $ss=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
+Node $n$ has arity of at least 1. This means that the left subtree exists, so the left subtree node is to be changed. 
+For example, if $n=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
 Another example would be the case of unary operation, e.g.
-when $ss=\sqrt{y}$.
+when $n=\sqrt{y}$.
 In that case, some of the possible perturbations could be $(x+y^3)\cdot x/\sqrt{\ln{y}}$ (application of logarithm to left subtree $y$) or $(x+y^3)\cdot x/\sqrt{x}$ (changing variable $y$ to $x$), etc.
@@
 \subsubsection{Local search}\label{sec:ls}
+
+Perturbations are further improved by means of local search procedure (Algorithm~\ref{alg:ls}).
+
+\begin{algorithm}
+	\hspace*{\algorithmicindent} \textbf{Input}: perturbation $p$, sample training dataset $D_{tr}'$ \\
+	\hspace*{\algorithmicindent} \textbf{Output}: local optimum $bp$ in the vicinity of perturbation $p$
+	\begin{algorithmic}[1] 
+		\Procedure{LocalSearch}{$p$, $D_{tr}'$}
+		\State $bp, bp_{fit} \gets p, $\texttt{Fitness}$(p, D_{tr}')$ 
+		\State $improved \gets true$
+		\While{$improved$}
+			\State $improved \gets false$
+			\State $bp_{candidates} \gets \emptyset$
+			\State $bp_{subtrees} \gets $\texttt{SubTrees}($bp$)
+			\For{$n \in bp_{subtrees}$}
+				\State $n_{candidates} \gets $ \texttt{All1PerturbationsAroundNode}($bp$, $n$)
+				\For{$new \in n_{candidates}$}
+					\State $new \gets$ \texttt{FitOLS}($new$, $D_{tr}'$)
+					\State $new_{fit} \gets$ \texttt{Fitness}($new$, $D_{tr}'$)
+					\If{$new_{fit} < bp_{fit}$}
+						\State $bp, bp_{fit} \gets new, new_{fit}$
+						\State $improved \gets true$
+					\EndIf
+				\EndFor
+			\EndFor
+		\EndWhile
+		\State \Return $bp$
+		\EndProcedure
+	\end{algorithmic}
+	\caption{Local search procedure.}
+	\label{alg:ls}
+\end{algorithm}
+
+For a given perturbation $p$, local search systematically explores all 1-perturbations around $p$.
+It relies on the \emph{best-improvement} strategy, meaning that all 1-perturbations (for all subtrees) are considered.
+Before checking if the candidate solution ($new$) is better that the actual best $bp$, OLS coefficient fitting is performed.
 
@@
 SAMO JEDAN PARAMETAR!!!
+Zapravo dva parametra $penalty_{size}$ i $tolerance_{error}$ pri cemu je drugi manje vise zavistan od ocekivanog 
+nivoa suma -- ne znam kako obrazloziti njegov tuning (mozda prema greski na trening skupu pa izabrati onaj za koji su R2 i RMSE bolji...).
 

### 2022-10-25 doc/paper.tex
Section 3.3.2 i 3.3.3 upodate

@@
 Perturbations allow the algorithm to escape from local optima.
-As previously described, perturbations are performed in two occasions: ($i$) during the exhaustive examination of neighboring solutions around the starting solution, ($ii$)during selection of the next starting solution, a non-exhaustive case.
+As previously described, perturbations are performed in two occasions: ($i$) during the exhaustive examination of neighboring solutions around the starting solution, ($ii$) during selection of the next starting solution, a non-exhaustive case.
 In both cases, the same Algorithm~\ref{alg:pert} is used.
@@
 	\end{algorithmic}
-	\caption{Generation of all 1-perturbations for a given solution.}
+	\caption{Generation of all 1-perturbations of a given solution.}
 	\label{alg:pert}
@@
 		\State $n_{perturbations} \gets \emptyset$
-		\If{$n = s$}
+		\If{$n = s$} \label{alg:alg4-case-1}
 		\State $n_{perturbations} \gets n_{perturbations} \cup$ \texttt{NodeChanges}($n$)
 		\EndIf
-		\If{$n.arity \geq 1$}
+		\If{$n.arity \geq 1$}\label{alg:alg4-case-2}
 		\State $n_{changes} \gets$ \texttt{NodeChanges}($n.left$)
@@
 		\EndIf
-		\If{$n.arity = 2$}
+		\If{$n.arity = 2$}\label{alg:alg4-case-3}
 		\State $n_{changes} \gets$ \texttt{NodeChanges}($n.right$)
@@
 	\end{algorithmic}
-	\caption{Generation of 1-perturbations for a given solution around given node.}
+	\caption{Generation of 1-perturbations of a given solution around given node.}
 	\label{alg:pertNode}
@@
 \emph{Case 1}. 
-Observed node $n$ is the whole tree $s$.
-Following on the the previous exemplary expression tree, this means that multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
-For example, multiplication can be replaced by addition, which forms a perturbation $(x+y^3)+ x/\sqrt{y}$.
+Observed node $n$ is the whole tree $s$ (see line ~\ref{alg:alg4-case-1} in Algorithm~\ref{alg:pertNode}).
+Following on   the previous exemplary expression tree, this means that multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
+For example, multiplication can be replaced by addition, which forms a 1-perturbation expression (tree) $(x+y^3)+ x/\sqrt{y}$.
 
 \emph{Case 2}. 
-Node $n$ has arity of at least 1. This means that the left subtree exists, so the left subtree node is to be changed. 
+Node $n$ has arity of at least 1 (see line ~\ref{alg:alg4-case-2} in Algorithm~\ref{alg:pertNode}). This means that the left subtree exists, so the left subtree node is to be changed. 
 For example, if $n=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
@@
 \emph{Case 3}. 
-Subtree $ss$ is binary operation, meaning the right subtree must exist. 
+Subtree $ss$ is binary operation, meaning the right subtree must exist (Line ~\ref{alg:alg4-case-3} in Algorithm~\ref{alg:pertNode}). 
 The analogous idea is applied as in \emph{Case 2}.
@@
 \end{enumerate} 
+\fxnote{Nekako zbunjuje u Algoritmu 4, pojava NodeChanges)() i Replace().
+Mislim, razumijem iz opisa sta one rade, ali nisam siguran da treba imenovati metode, ako ih barem u kontekstu opisa ne pomenemo direktno po nazivu.
+}
+
 \fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene}
@@
 		\Procedure{LocalSearch}{$p$, $D_{tr}'$}
-		\State $bp, bp_{fit} \gets p, $\texttt{Fitness}$(p, D_{tr}')$ 
+		\State $bp, bp_{fit} \gets p,\ $\texttt{Fitness}$(p,D_{tr}')$ 
 		\State $improved \gets true$
@@
 It relies on the \emph{best-improvement} strategy, meaning that all 1-perturbations (for all subtrees) are considered.
-Before checking if the candidate solution ($new$) is better that the actual best $bp$, OLS coefficient fitting is performed.
+Before checking if the candidate solution ($new$) is better that the actual best $bp$, the OLS coefficient fitting (\texttt{FitOLS}) is performed.
 
@@
 \end{itemize}
-The abovementioned benchmark sets may be biased as models which describe phisical laws may have various symmetries, periodically w.r.t.
+The above-mentioned benchmark sets may be biased as models which describe physical laws may have various symmetries, periodically w.r.t.
 some variables, internal separability on some variables etc.

### 2022-10-25 doc/paper.tex
Experiemntal evaluation: update

@@
 \subsection{Parameter tuning}
-SAMO JEDAN PARAMETAR!!!
-Zapravo dva parametra $penalty_{size}$ i $tolerance_{error}$ pri cemu je drugi manje vise zavistan od ocekivanog 
-nivoa suma -- ne znam kako obrazloziti njegov tuning (mozda prema greski na trening skupu pa izabrati onaj za koji su R2 i RMSE bolji...).
+The \textsc{Rils}-\textsc{Rols} algorithms employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is set to 0.001(?), according to the preliminary experimental evaluation.
+The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose a value for which a larger average $R^2$ and a smaller average RMSE error over all instances from the training set are produced.
+Note that the training set is chosen randomly with the cardinalty of ...
+
+\fxnote{ drugi parametar manje vise zavistan od ocekivanog 
+nivoa suma -- ne znam kako obrazloziti njegov tuning (mozda prema greski na trening skupu pa izabrati onaj za koji su R2 i RMSE bolji...). }
 
 \subsection{Comparison with other methods}
-
+\fxnote{Marko: TODO}
 \begin{table}[!htb]

### 2022-10-25 doc/paper.tex
Explain the results: begin

@@
 The first parameter is set to 0.001(?), according to the preliminary experimental evaluation.
-The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose a value for which a larger average $R^2$ and a smaller average RMSE error over all instances from the training set are produced.
-Note that the training set is chosen randomly with the cardinalty of ...
+The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose $tolerance_{error}=?$ for which a larger average $R^2$ and a smaller average RMSE error over all instances from the training set are produced.
+Note that the training set is chosen randomly with a cardinalty of...
 
@@
 \subsection{Comparison with other methods}
-\fxnote{Marko: TODO}
+In this section, we deal with evaluating the performance of \textsc{Rils-Rols} algorithm with 15 other competitors from the literature that solve the problem of Symbolic regression.
+The results are reported in terms of two numerical tables~, Tables~\ref{tab:comp_noise0},\ref{tab:comp_noise001}, and \ref{tab:comp_noise0001} on real-world benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, utilizing  different values of noise: 0.0, 0.01, and 0.001, respectively.
+
 \begin{table}[!htb]
@@
 			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-			RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
-			AIFeynman&55.78&27.14&52.69&78.51&35.71&73.9\\
-			GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
-			AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
-			ITEA&22.41&7.14&20.77&27.59&21.43&26.93\\
-			AFP&21.12&15.18&20.48&44.83&25&42.69\\
-			DSR&19.72&19.64&19.71&25&14.29&23.85\\
-			Operon&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
-			gplearn&16.27&8.93&15.48&32.76&7.14&30\\
-			SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
-			EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
-			BSR&2.48&0.89&2.31&10.78&21.43&11.93\\
-			FEAT&0&0.89&0.1&39.66&42.86&40\\
-			FFX&0&0&0&0&0&0\\
-			MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
-			\hline
-		\end{tabular}
-\end{table}
-
-\begin{table}[!htb]
-	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
-	\centering
-		\begin{tabular}{l|rrr|rrr} \hline
-			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
-			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-			RILS-ROLS&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
-			DSR&16.81&18.75&17.02&26.29&14.29&25\\
-			gplearn&15.84&8.93&15.1&24.14&7.14&22.31\\
-			AFP\_FE&15.95&6.43&14.92&57.76&28.57&54.62\\
-			AFP&14.87&7.14&14.04&44.83&25&42.69\\
-			EPLEX&10.02&2.68&9.23&48.71&21.43&45.77\\
-			AIFeynman&1.49&13.73&2.81&9.73&35.71&12.53\\
-			ITEA&1.94&4.46&2.21&26.72&21.43&26.15\\
-			GP-GOMEA&1.62&0.89&1.54&72.84&71.43&72.69\\
-			Operon&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
-			FFX&0.11&0&0.1&19.4&14.29&18.85\\
-			FEAT&0&0.89&0.1&13.79&50&17.69\\
-			SBP-GP&0&0&0&62.07&53.57&61.15\\
-			BSR&0&0&0&7.76&14.29&8.46\\
-			MRGP&0&0&0&0.86&17.86&2.69\\
+			\textsc{Rils-Rols}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
+			 \textsc{AI-Feynman} &55.78&27.14&52.69&78.51&35.71&73.9\\
+			 \textsc{Gomea} &26.83&29.46&27.12&71.55&71.43&71.54\\
+			\textsc{AFP-FE} &26.98&20&26.23&59.05&28.57&55.77\\
+			 \textsc{ITEA}&22.41&7.14&20.77&27.59&21.43&26.93\\
+			\textsc{AFP}&21.12&15.18&20.48&44.83&25&42.69\\
+			\textsc{DSR}&19.72&19.64&19.71&25&14.29&23.85\\
+			 \textsc{Operon}&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
+			 \textsc{gplearn}&16.27&8.93&15.48&32.76&7.14&30\\
+			\textsc{SBP-GP}&12.72&11.61&12.6&73.71&78.57&74.23\\
+			\textsc{EPLEX}  &12.39&8.93&12.02&46.98&21.43&44.23\\
+			\textsc{BSR}&2.48&0.89&2.31&10.78&21.43&11.93\\
+			 \textsc{FEAT}&0&0.89&0.1&39.66&42.86&40\\
+			\textsc{FFX}&0&0&0&0&0&0\\
+			\textsc{MRGP}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
 			\hline
@@
 		MRGP&0&0&0&0&0&0\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}[!htb]
+	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
+	\centering
+		\begin{tabular}{l|rrr|rrr} \hline
+			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
+			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+				\textsc{Rils-Rols}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
+				\textsc{DSR}&16.81&18.75&17.02&26.29&14.29&25\\
+			 \textsc{gplearn}&15.84&8.93&15.1&24.14&7.14&22.31\\
+			\textsc{AFP-FE}&15.95&6.43&14.92&57.76&28.57&54.62\\
+			\textsc{AFP}&14.87&7.14&14.04&44.83&25&42.69\\
+				\textsc{EPLEX} &10.02&2.68&9.23&48.71&21.43&45.77\\
+			 \textsc{AI-Feynman}&1.49&13.73&2.81&9.73&35.71&12.53\\
+	         \textsc{ITEA}&1.94&4.46&2.21&26.72&21.43&26.15\\
+			 \textsc{Gomea}&1.62&0.89&1.54&72.84&71.43&72.69\\
+	        \textsc{Operon}&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
+				\textsc{FFX}&0.11&0&0.1&19.4&14.29&18.85\\
+	    \textsc{FEAT}&0&0.89&0.1&13.79&50&17.69\\
+		\textsc{SBP-GP}&0&0&0&62.07&53.57&61.15\\
+			\textsc{BSR}&0&0&0&7.76&14.29&8.46\\
+				\textsc{MRGP}&0&0&0&0.86&17.86&2.69\\
 			\hline

### 2022-10-25 doc/paper.tex
Update

@@
 The first parameter is set to 0.001(?), according to the preliminary experimental evaluation.
-The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose $tolerance_{error}=?$ for which a larger average $R^2$ and a smaller average RMSE error over all instances from the training set are produced.
-Note that the training set is chosen randomly with a cardinalty of...
+The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose $tolerance_{error}=?$ for which a largest average $R^2$ and the smallest average RMSE error over all instances from the training set are produced.
+Note that the training set is chosen randomly with a cardinalty of xx instances.
 
@@
 
-\subsection{Comparison with other methods}
-In this section, we deal with evaluating the performance of \textsc{Rils-Rols} algorithm with 15 other competitors from the literature that solve the problem of Symbolic regression.
-The results are reported in terms of two numerical tables~, Tables~\ref{tab:comp_noise0},\ref{tab:comp_noise001}, and \ref{tab:comp_noise0001} on real-world benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, utilizing  different values of noise: 0.0, 0.01, and 0.001, respectively.
+\subsection{Comparison with other methods on real--world benchark sets}
+In this section, we evaluate the performance of \textsc{Rils-Rols} algorithm with 15 other competitors from the literature that solve the problem of Symbolic regression.
+The results are reported in terms of three numerical Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001} on real-world benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, utilizing  different values of noise: 0.0 (no noise), 0.001, and 0.01, respectively.
+Each table consists of three blocks.
+The first block reports the algorithm whose performances are measured.
+The second block reports, in two columns,  percentages of instances where the exact model has been found by respective algorithms on both, \textsc{Feynman} and \textsc{Strogatz}, benchmark sets.
+The third column provides the overall summary percentage of algorithms' success over all instances.
+The third block displays the results of respective algorithm in the presence of $R^2$ error, that is when $R^2$ error reached the value of 0.999, but not necessary equal to 1.
+\fxnote{Marko: proceed...}
 
@@
 \begin{table}[!htb]
-	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
-	\centering
-	\begin{tabular}{l|rrr|rrr} \hline
-		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
-		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		RILS-ROLS&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
-		gplearn&13.21&8.93&12.75&14.22&7.14&13.46\\
-		DSR&8.41&16.07&9.23&17.24&14.29&16.92\\
-		EPLEX&8.77&0&7.83&14.22&3.57&13.07\\
-		AFP&7.11&0.89&6.44&8.19&7.14&8.08\\
-		AFP\_FE&6.12&3.57&5.85&5.6&0&5\\
-		ITEA&0.11&0.89&0.19&1.72&10.71&2.69\\
-		AIFeynman&0&0.79&0.09&0&0&0\\
-		Operon&0.09&0&0.08&0&0&0\\
-		GP-GOMEA&0&0&0&0&0&0\\
-		SBP-GP&0&0&0&0&0&0\\
-		BSR&0&0&0&0&0&0\\
-		FEAT&0&0&0&0&14.29&1.54\\
-		FFX&0&0&0&0&0&0\\
-		MRGP&0&0&0&0&0&0\\
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}[!htb]
 	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
@@
 				\textsc{MRGP}&0&0&0&0.86&17.86&2.69\\
+			\hline
+		\end{tabular}
+\end{table}
+
+\begin{table}[!htb]
+	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
+	\centering
+	\begin{tabular}{l|rrr|rrr} \hline
+		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
+		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+		\textsc{Rils-Rols}&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
+		 \textsc{gplearn}&13.21&8.93&12.75&14.22&7.14&13.46\\
+		\textsc{DSR}&8.41&16.07&9.23&17.24&14.29&16.92\\
+		\textsc{EPLEX}&8.77&0&7.83&14.22&3.57&13.07\\
+			\textsc{AFP}&7.11&0.89&6.44&8.19&7.14&8.08\\
+	\textsc{AFP-FE}&6.12&3.57&5.85&5.6&0&5\\
+		\textsc{ITEA}&0.11&0.89&0.19&1.72&10.71&2.69\\
+	 \textsc{AI-Feynman}&0&0.79&0.09&0&0&0\\
+		\textsc{Operon}&0.09&0&0.08&0&0&0\\
+		\textsc{Gomea}&0&0&0&0&0&0\\
+		\textsc{SBP-GP}&0&0&0&0&0&0\\
+			\textsc{BSR}&0&0&0&0&0&0\\
+		\textsc{FEAT}&0&0&0&0&14.29&1.54\\
+		\textsc{FFX}&0&0&0&0&0&0\\
+		\textsc{MRGP}&0&0&0&0&0&0\\
 		\hline

### 2022-10-25 doc/paper.tex
Work on Experimental section

@@
 A  GP-based approach, the gene-pool optimal mixing evolutionary algorithm (GOMEA) is studied by Virgolin et al.~\cite{virgolin2021improving}.
-Another evolutionary algorithm, the interaction-transformation EA (ITEA) has been proposed by de Franca et al.~\cite{de2021interaction}.
+Another evolutionary algorithm, the interaction-transformation EA (Itea) has been proposed by de Franca et al.~\cite{de2021interaction}.
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
@@
 The method that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
-A GP approach that uses the idea of semantic back-propagation (SBP-GP) is proposed in~\cite{virgolin2019linear}.
+A GP approach that uses the idea of semantic back-propagation (Sbp-Gp) is proposed in~\cite{virgolin2019linear}.
 Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
@@
 
-	 Machine learning--based method   based on Bayesian symbolic regression (BSR) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms.
-Deep Symbolic Regression (DSR), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
+	 Machine learning--based method   based on Bayesian symbolic regression (Bsr) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms.
+Deep Symbolic Regression (Dsr), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
 This mechanism of search is further investigated in~\cite{landajuela2021improving}.
@@
 
-	Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the EPLEX solver from~\cite{la2019probabilistic,la2016epsilon} and AI Feynman algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method that  combines neural network
+	Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the Eplex solver from~\cite{la2019probabilistic,la2016epsilon} and AI Feynman algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method that  combines neural network
 	fitting.
 The later one is one of the most efficient method for physically inspired models.
-We also mention the Fast Function Extraction (FFX) algorithm developed by McConaghy~\cite{mcconaghy2011ffx},  a non-evolutionary method in combination with a machine learning technique---path-wise regularized learning--- which   quickly prune a huge set of candidate basis functions down to compact models.
+We also mention the Fast Function Extraction (Ffx) algorithm developed by McConaghy~\cite{mcconaghy2011ffx},  a non-evolutionary method in combination with a machine learning technique---path-wise regularized learning--- which   quickly prune a huge set of candidate basis functions down to compact models.
 
@@
 			Algorithm          &   Paper/year &   Short details   \\ \hline
-			GP         &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
-	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
-	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
-	        APF-FE                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
+			\textsc{Gp}        &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
+	        \textsc{Hybrid-Gp}  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
+	        \textsc{Dfe}        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
+	        \textsc{Apf-Fe}                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
         	APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
-        	FFX  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
-             ABCP &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
-			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
-			MRGP & \cite{arnaldo2014multiple} (2014) & It decouples and
+        	\textsc{Ffx}  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
+             \textsc{Abcp} &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
+			\textsc{Eplex}          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
+			\textsc{Mrgp} & \cite{arnaldo2014multiple} (2014) & It decouples and
 			linearly combines a program's subexpressions via multiple regression on the target variable  \\
 	       Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
-	       FEAT & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees  comprised of activation functions; Differentiable features are trained via gradient descent \\
-	       SBP-GP &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
-	       BSR & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
-	       DSR  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
-	       OPERON & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
-	       VNP    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
-	       OccamNet & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\
+	       \textsc{Feat} & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees  comprised of activation functions; Differentiable features are trained via gradient descent \\
+	       \textsc{Sbp-Gp} &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
+	       \textsc{Bsr} & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
+	       \textsc{Dsr}  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
+	       \textsc{Operon} & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
+	       \textsc{Vnp}    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
+	       \textsc{OccamNet} & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\
 
-	       AI-Feynman  & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
-	             GOMEA  & \cite{virgolin2021improving} (2021)    & A model-based
+	       \textsc{AI-Feynman} & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
+	       \textsc{Gomea}  & \cite{virgolin2021improving} (2021)    & A model-based
 	       EA framework called Gene-pool optimal mixing evolutionary algorithm \\
-	       ITEA & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
-	       SA & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
+	       \textsc{Itea} & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
+	       \textsc{Sa} & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
 
-         DRLA & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming \\
-            Taylor GP &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations  \\ \hline
+         \textsc{Drla} & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming \\
+          \textsc{Taylor-Gp} &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations  \\ \hline
 
@@
 
-The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{AFP-FE}, \textsc{ITEA}, \textsc{AFP}, \textsc{DSR}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{SBP-GP}, \textsc{EPLEX}, \textsc{BSR}, \textsc{FEAT}, \textsc{FFX}, \textsc{MRGP} and our \textsc{Rils}-\textsc{Rols} algorithm.
+The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp} and our \textsc{Rils}-\textsc{Rols} algorithm.
 
@@
 The third column provides the overall summary percentage of algorithms' success over all instances.
-The third block displays the results of respective algorithm in the presence of $R^2$ error, that is when $R^2$ error reached the value of 0.999, but not necessary equal to 1.
-\fxnote{Marko: proceed...}
+The third block displays the results of respective algorithm in the presence of $R^2$ error, that is when $R^2$ error reached the value of 0.999, when the algorithm gets terminated providing a correct output w.r.t.\ the error.
+Note that the termination may not necessary be triggered by the error equal to 1.
+This situation is of interest as it may indicate to the existence of an over-fitting.
+This block consists of three rows that indicate the percentage of instances where respective algorithm is successfully terminated (fulfilling condition $R^2 \geq 1$) on the both real--world benchmark sets separately, and the overall percentage of success rate (over all considered instances).
+
+Note that when the algorithm terminates with $R^2=1$ and $RMSE=0$, the match of found model and the exact model is proved -- the results are reported in the second block.
+However, in case when $R^2 \neq 1$, that is $R^2 \geq 0.999$, we manually check these cases comparing the match of obtained model and the exact model, indicating the result.
+\fxnote{Aco, projeri ovu recenicu, da nisam promasio...}
+
+The following conclusions may be drawn from the numerical results:
+
+\begin{itemize}
+	\item Concerning the exact results in case noise is not presented, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, begin successful in 83.57\% cases.
+The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and 27.14\% instances of the benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
+All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered benchmark sets.
+	\item   Concerning the exact results when noise is presented with a value of 0.001, our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model in more than 42\%, considering problems from the both benchmark set.
+Interestingly, \textsc{AI-Feynman} is quite sensible w.r.t.\ the change in noise, as its performances rapidly drop off -- it is successful on just 2.81\% of the all problem instances.
+Better from \textsc{AI-Feynman} are in this case \textsc{Dsr}, \textsc{Gplearn}, and \textsc{Afp-Fe} in this order, whose percentages of success range from about 15--17\%.
+	\item  Concerning the exact results when noise is high, that is with a value of 0.01,  our \textsc{Rils}--\textsc{Rols} is still reasonably good, having found an exact model for  34.77\% of the all problem instances.
+The second best is \textsc{Gplearn} which percentage of success is 12.75\%, followed by \textsc{Dsr} which is successful on just 9.23\% of the all problem instances.
+	\item \fxnote{Marko: opisati rezultate za $R^2 >0.999$}
+\end{itemize}
 
@@
 			 \textsc{Gomea} &26.83&29.46&27.12&71.55&71.43&71.54\\
-			\textsc{AFP-FE} &26.98&20&26.23&59.05&28.57&55.77\\
-			 \textsc{ITEA}&22.41&7.14&20.77&27.59&21.43&26.93\\
-			\textsc{AFP}&21.12&15.18&20.48&44.83&25&42.69\\
-			\textsc{DSR}&19.72&19.64&19.71&25&14.29&23.85\\
+			\textsc{Afp-Fe} &26.98&20&26.23&59.05&28.57&55.77\\
+			 \textsc{Itea}&22.41&7.14&20.77&27.59&21.43&26.93\\
+			\textsc{Afp}&21.12&15.18&20.48&44.83&25&42.69\\
+			\textsc{Dsr}&19.72&19.64&19.71&25&14.29&23.85\\
 			 \textsc{Operon}&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
 			 \textsc{gplearn}&16.27&8.93&15.48&32.76&7.14&30\\
-			\textsc{SBP-GP}&12.72&11.61&12.6&73.71&78.57&74.23\\
-			\textsc{EPLEX}  &12.39&8.93&12.02&46.98&21.43&44.23\\
-			\textsc{BSR}&2.48&0.89&2.31&10.78&21.43&11.93\\
-			 \textsc{FEAT}&0&0.89&0.1&39.66&42.86&40\\
-			\textsc{FFX}&0&0&0&0&0&0\\
-			\textsc{MRGP}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
+			\textsc{Sbp-Gp}&12.72&11.61&12.6&73.71&78.57&74.23\\
+			\textsc{Eplex}  &12.39&8.93&12.02&46.98&21.43&44.23\\
+			\textsc{Bsr}&2.48&0.89&2.31&10.78&21.43&11.93\\
+			 \textsc{Feat}&0&0.89&0.1&39.66&42.86&40\\
+			\textsc{Ffx}&0&0&0&0&0&0\\
+			\textsc{Mrgp}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
 			\hline
@@
 				\textsc{Rils-Rols}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
-				\textsc{DSR}&16.81&18.75&17.02&26.29&14.29&25\\
+				\textsc{Dsr}&16.81&18.75&17.02&26.29&14.29&25\\
 			 \textsc{gplearn}&15.84&8.93&15.1&24.14&7.14&22.31\\
-			\textsc{AFP-FE}&15.95&6.43&14.92&57.76&28.57&54.62\\
-			\textsc{AFP}&14.87&7.14&14.04&44.83&25&42.69\\
-				\textsc{EPLEX} &10.02&2.68&9.23&48.71&21.43&45.77\\
+			\textsc{Afp-Fe}&15.95&6.43&14.92&57.76&28.57&54.62\\
+			\textsc{Afp}&14.87&7.14&14.04&44.83&25&42.69\\
+				\textsc{Eplex} &10.02&2.68&9.23&48.71&21.43&45.77\\
 			 \textsc{AI-Feynman}&1.49&13.73&2.81&9.73&35.71&12.53\\
-	         \textsc{ITEA}&1.94&4.46&2.21&26.72&21.43&26.15\\
+	         \textsc{Itea}&1.94&4.46&2.21&26.72&21.43&26.15\\
 			 \textsc{Gomea}&1.62&0.89&1.54&72.84&71.43&72.69\\
 	        \textsc{Operon}&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
-				\textsc{FFX}&0.11&0&0.1&19.4&14.29&18.85\\
-	    \textsc{FEAT}&0&0.89&0.1&13.79&50&17.69\\
-		\textsc{SBP-GP}&0&0&0&62.07&53.57&61.15\\
-			\textsc{BSR}&0&0&0&7.76&14.29&8.46\\
-				\textsc{MRGP}&0&0&0&0.86&17.86&2.69\\
+				\textsc{Ffx}&0.11&0&0.1&19.4&14.29&18.85\\
+	    \textsc{Feat}&0&0.89&0.1&13.79&50&17.69\\
+		\textsc{Sbp-Gp}&0&0&0&62.07&53.57&61.15\\
+			\textsc{Bsr}&0&0&0&7.76&14.29&8.46\\
+				\textsc{Mrgp}&0&0&0&0.86&17.86&2.69\\
 			\hline
@@
 		 \textsc{gplearn}&13.21&8.93&12.75&14.22&7.14&13.46\\
-		\textsc{DSR}&8.41&16.07&9.23&17.24&14.29&16.92\\
-		\textsc{EPLEX}&8.77&0&7.83&14.22&3.57&13.07\\
-			\textsc{AFP}&7.11&0.89&6.44&8.19&7.14&8.08\\
-	\textsc{AFP-FE}&6.12&3.57&5.85&5.6&0&5\\
-		\textsc{ITEA}&0.11&0.89&0.19&1.72&10.71&2.69\\
+		\textsc{Dsr}&8.41&16.07&9.23&17.24&14.29&16.92\\
+		\textsc{Eplex}&8.77&0&7.83&14.22&3.57&13.07\\
+			\textsc{Afp}&7.11&0.89&6.44&8.19&7.14&8.08\\
+	\textsc{Afp-Fe}&6.12&3.57&5.85&5.6&0&5\\
+		\textsc{Itea}&0.11&0.89&0.19&1.72&10.71&2.69\\
 	 \textsc{AI-Feynman}&0&0.79&0.09&0&0&0\\
@@
 		\textsc{Gomea}&0&0&0&0&0&0\\
-		\textsc{SBP-GP}&0&0&0&0&0&0\\
-			\textsc{BSR}&0&0&0&0&0&0\\
-		\textsc{FEAT}&0&0&0&0&14.29&1.54\\
-		\textsc{FFX}&0&0&0&0&0&0\\
-		\textsc{MRGP}&0&0&0&0&0&0\\
+		\textsc{Sbp-Gp}&0&0&0&0&0&0\\
+			\textsc{Bsr}&0&0&0&0&0&0\\
+		\textsc{Feat}&0&0&0&0&14.29&1.54\\
+		\textsc{Ffx}&0&0&0&0&0&0\\
+		\textsc{Mrgp}&0&0&0&0&0&0\\
 		\hline

### 2022-10-26 doc/paper.tex
Exp. section: working

@@
 
-Note that when the algorithm terminates with $R^2=1$ and $RMSE=0$, the match of found model and the exact model is proved -- the results are reported in the second block.
-However, in case when $R^2 \neq 1$, that is $R^2 \geq 0.999$, we manually check these cases comparing the match of obtained model and the exact model, indicating the result.
-\fxnote{Aco, projeri ovu recenicu, da nisam promasio...}
+%Note that when the algorithm terminates with $R^2=1$ and $RMSE=0$, the obtained model and the exact model are always match (but also checked manually).
+However, in case when the algorithms deliver an error $R^2 \geq 0.999$, but $R^2 \neq 1$, these cases are all  manually checked by comparing weather the produced model match the exact model.
+
+The exact results, thus the number of instances (in percentages) for which the output of respective algorithm match to the exact model, are displayed in the second block of each of the tables.
+
+The numbers of instances (in percentages) for which each algorithms deliver a precise enough model (i.e.
+satisfying $R^2\geq 0.999$ upon its termination) are displayed in the third block of each of the tables.
 
@@
 The second best is \textsc{Gplearn} which percentage of success is 12.75\%, followed by \textsc{Dsr} which is successful on just 9.23\% of the all problem instances.
-	\item \fxnote{Marko: opisati rezultate za $R^2 >0.999$}
+
+	\item When comparing performances of the algorithms in terms of number of instances for which the algorithm's termination led to $R^2 \geq 0.999$ where no noise is integrated, our \textsc{Rils}-\textsc{Rols} is successful with 83.38\%.
+However, in contrast with the exact model percentages form above, there are a few methods delivering better percentages of success than ours, \textsc{Mrgp}, and \textsc{Operon}, with 92.69\%, and 86.93\%.
+In the other hand, as the  exact model percentage rates of these two approaches is rather low (0\% and 16\%) this indicates on a high level of over-fitting  of these algorithms.
+Thus, they are able to obtain a model that is accurate enough on the training data, but the produced model is wrong.
+
+   \item  If comparing the performances of the competitors in terms of number of instances for which the algorithm's termination led to $R^2 \geq 0.999$ where the level of noise is 0.001, our \textsc{Rils}--\textsc{Rols} method has 78.62\% of a success rate.
+\textsc{Operon}, only has a better percentage rate of success among the other competitors, which is 83.08\%.
+However, the over-fitting is conspicuous as this algorithm is rarely able to deliver the model which fits ot the exact one (just in 0.31\%).
+
+   \item  If comparing the performances of the competitors in terms of number of instances for which the algorithm's termination led to $R^2 \geq 0.999$ where the level of noise is 0.01, our \textsc{Rils}--\textsc{Rols} method is still highly accurate, delivering  62.92\% of a success rate.
+Interestingly, it is the best performing in terms of the percentage rate among other competitors.
+Just for the information, the second best is \textsc{Dsr}, with 16.92\% of a success rate.
+It can be concluded that our \textsc{Rils}--\textsc{Rols} method does not pay a big price in presence of a higher noise, like the other methods do.
+It still delivers high-accuracy models for the noisy data, but also many which match to the exact solutions (models).
+
 \end{itemize}

### 2022-10-26 doc/paper.tex
Experimental evaluation: working...

--- 2022-10-25 doc/paper.tex
@@
 
-Our proposed algorithm was implemented in Python version 3.x.
-All experiments were performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
-The maximum computation time allowed for each run was limited to 1h minutes, i.e., 3600 seconds.
-
-The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon},  a python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp} and our \textsc{Rils}-\textsc{Rols} algorithm.
+Our \textsc{Rils}--\textsc{Rols} algorithm is implemented in Python version 3.x.
+All experiments are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
+The maximum computation time allowed for each run was set to 1h minutes, i.e., 3600 seconds.
+
+The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp} and our \textsc{Rils}-\textsc{Rols} algorithm.
 
@@
 SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and the environment for analysis, see~\cite{la2021contemporary}.
-It brought researchers an easy handled environment to evaluation, compare, and analyse their methods.
+It brought researchers an easy handled environment to evaluation, compare, and analyze their methods.
 Among all benchmark sets, we involve two real-world inspired benchmark sets into our computational evaluation:
@@
 In this section, we evaluate the performance of \textsc{Rils-Rols} algorithm with 15 other competitors from the literature that solve the problem of Symbolic regression.
-The results are reported in terms of three numerical Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001} on real-world benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, utilizing  different values of noise: 0.0 (no noise), 0.001, and 0.01, respectively.
-Each table consists of three blocks.
-The first block reports the algorithm whose performances are measured.
-The second block reports, in two columns,  percentages of instances where the exact model has been found by respective algorithms on both, \textsc{Feynman} and \textsc{Strogatz}, benchmark sets.
-The third column provides the overall summary percentage of algorithms' success over all instances.
-The third block displays the results of respective algorithm in the presence of $R^2$ error, that is when $R^2$ error reached the value of 0.999, when the algorithm gets terminated providing a correct output w.r.t.\ the error.
-Note that the termination may not necessary be triggered by the error equal to 1.
-This situation is of interest as it may indicate to the existence of an over-fitting.
-This block consists of three rows that indicate the percentage of instances where respective algorithm is successfully terminated (fulfilling condition $R^2 \geq 1$) on the both real--world benchmark sets separately, and the overall percentage of success rate (over all considered instances).
-
-Note that when the algorithm terminates with $R^2=1$ and $RMSE=0$, the match of found model and the exact model is proved -- the results are reported in the second block.
-However, in case when $R^2 \neq 1$, that is $R^2 \geq 0.999$, we manually check these cases comparing the match of obtained model and the exact model, indicating the result.
-\fxnote{Aco, projeri ovu recenicu, da nisam promasio...}
+The results are reported in terms of three numerical Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}, where two real-world benchmark sets, \textsc{Feynman} and \textsc{Storgatz} are considered, utilizing  different values of the noise levels: 0.0 (no noise), 0.001 (a low-level noise), and 0.01 (a high-level noise), respectively.
+Concerning the added noise, the White Gaussian noise was added to the target ($y$-axis values) as a fraction of the signal RMS value, also applied in~\cite{la2021contemporary}, i.e.
+for target noise level $\alpha$, we have
+$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{N} \sum_{y_i^2}}\right). $$
+
+Each table consist of three blocks.
+The first block reports the algorithm whose performances are reported.
+The second block reports, in two columns,  percentages of instances where the model which matches to the exact one has been found by respective algorithms on both, \textsc{Feynman} and \textsc{Strogatz}, benchmark sets.
+The third column of this block provides the overall summary percentage of success over all instances.
+The third block displays the results of the respective algorithm in the presence of $R^2$ error which can indicate on  accuracy, i.e.
+in our cases when the algorithm  at least reached the accuracy ($R^2$ score) of 0.999.
+Note that the termination of our algorithm may not necessary be triggered by the error equal to 1.
+These results are of interest as it may point out the existence of an over-fitting.
+This block consists of three rows that indicate the percentage of instances where respective algorithm is able to reach the desired accuracy (fulfilling condition $R^2 \geq 0.999$ before a termination due exceeding the time limit) on the both real--world benchmark sets separately, and the overall percentage of success rate (over all considered instances) w.r.t.
+the same criterion of success.
+
+%Note that when the algorithm terminates with $R^2=1$ and $RMSE=0$, the obtained model and the exact model are always match (but also checked manually).
+However, in case when the algorithms deliver an error $R^2 \geq 0.999$, but $R^2 \neq 1$, these cases are all  manually checked by comparing weather the produced model match the exact model.
+
+In short, the exact results, thus the number of instances (in percentages) for which the output of respective algorithm match to the exact model, are displayed in the second block of each of the tables.
+The numbers of instances (in percentages) for which each algorithms deliver a precise enough model (i.e.
+satisfying $R^2\geq 0.999$ upon its termination) are displayed in the third block of each of the tables.
 
@@
 \begin{itemize}
-	\item Concerning the exact results in case noise is not presented, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, begin successful in 83.57\% cases.
-The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and 27.14\% instances of the benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
+	\item Concerning the exact results in case no noise is utilized in the instance problems, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, begin successful in 83.57\% cases.
+The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all instances of the benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
 All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered benchmark sets.
-	\item   Concerning the exact results when noise is presented with a value of 0.001, our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model in more than 42\%, considering problems from the both benchmark set.
-Interestingly, \textsc{AI-Feynman} is quite sensible w.r.t.\ the change in noise, as its performances rapidly drop off -- it is successful on just 2.81\% of the all problem instances.
-Better from \textsc{AI-Feynman} are in this case \textsc{Dsr}, \textsc{Gplearn}, and \textsc{Afp-Fe} in this order, whose percentages of success range from about 15--17\%.
-	\item  Concerning the exact results when noise is high, that is with a value of 0.01,  our \textsc{Rils}--\textsc{Rols} is still reasonably good, having found an exact model for  34.77\% of the all problem instances.
-The second best is \textsc{Gplearn} which percentage of success is 12.75\%, followed by \textsc{Dsr} which is successful on just 9.23\% of the all problem instances.
-	\item \fxnote{Marko: opisati rezultate za $R^2 >0.999$}
+	\item   Concerning the exact results when the target noise is presented with a level of 0.001, our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model in more than 42\% cases considering the problems from the both benchmark sets.
+Interestingly, \textsc{AI-Feynman} is quite sensible w.r.t.\ the increase in the target noise level, as its performances rapidly drop down -- it is successful on just 2.81\% of the all problem instances.
+Better from \textsc{AI-Feynman} are in this case the \textsc{Dsr}, \textsc{Gplearn}, and \textsc{Afp-Fe} in this order of success, whose percentages of success rate range from $\approx$15--17\%.
+	\item  Concerning the exact results when the presence of noise is significant, that is with a level of 0.01,  our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model for  34.77\% of the all problem instances.
+The second best is \textsc{Gplearn} which percentage of success is just 12.75\%, followed by \textsc{Dsr} which is successful for just 9.23\% of the all problem instances.
+
+	\item When comparing performances of the algorithms in terms of number of instances for which the algorithm's termination led to an accurate model, that is $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{Rils}-\textsc{Rols} is successful with the rate of success of 83.38\%.
+However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than ours: \textsc{Mrgp}, and \textsc{Operon}, with 92.69\%, and 86.93\%.
+On the other hand, as the  exact model percentage rates of these two approaches are rather low (0\% and 16\%, respectively) these indicate the presence of a high level over-fitting  of the later two algorithms.
+Thus, they are able to obtain a model that is accurate enough on the training data, but most of the produced models are in essence wrong.
+
+   \item  When comparing the performances of the competitors in terms of number of instances for which the  termination led to an accurate enough model, in the presence of the noise level of 0.001, our \textsc{Rils}--\textsc{Rols} method has 78.62\% of a success rate, concerning all considered instances.
+The \textsc{Operon} solver only has a better percentage of success among the competitors, which is 83.08\%.
+However, the over-fitting is conspicuous as this algorithm is rarely able to obtain the model which matches to the exact one (which is successful for 0.31\% cases).
+
+   \item   When comparing the performances of the competitors in terms of number of instances for which the  termination led to an accurate enough model, in the presence of the high--level noise of 0.01, our \textsc{Rils}--\textsc{Rols} method is still highly accurate, delivering  62.92\% of a success rate.
+Interestingly, it is the best performing in terms of the percentage rate among other competitors.
+Just for the information, the second best approach is \textsc{Dsr}, with a 16.92\% success rate.
+It can be concluded that our \textsc{Rils}--\textsc{Rols} method does not pay a big price in presence of a higher noise, like the other methods do, and seem to be very sensible w.r.t.
+the noise increase.
+Our \textsc{Rils}--\textsc{Rols} method still delivers high-accuracy models for the noisy input data, but also many of them match to the exact solutions (models).
+
 \end{itemize}

### 2022-10-26 doc/paper.tex
Experimental section: working

@@
 	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that correspond to various natural laws.  
-	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. 
+	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.
+
+   \begin{table}
+		\centering
+		\begin{tabular}{l}   \hline
+	       $x = \sqrt{x_1^2 + x_2^2 - 2 x_1 x_2 \cos(\theta_1 - \theta_2)}$ \\
+	       $ \theta_1 = \arcsin(n \sin \theta_2)$ \\
+	       $E =  \frac{m c^2 }{1 - \frac{v^2}{c^2}}$ \\
+	       $\omega = \frac{1 + \frac{v}{c}}{ \sqrt{1 - \frac{v^2}{c^2}}} \omega_0$ \\ \hline
+
+	    \end{tabular}
+		\caption{Some Feynman equations.}
+		\label{tab:Feynamn-Eq}
+	\end{table}
+
 	\item \textsc{Strogatz} benchmark set from~\cite{la2016inference}. 
@@
 These equations describes various non-linear dynamics and exhibiting chaos.
+The equations for some of the datasets of this benchmark are shown in Table~\ref{table:strogatz-ODEs}.
+
+	%table, an instance -- example
+
+	\begin{table}
+		\centering
+		\begin{tabular}{ll} \\ \hline
+			Bacterial representation &   $x' = 20 - x - \frac{x \cdot y}{1 + 0.5 x^2 }$ \\ 
+			                         &   $y' = 10 - \frac{x \cdot y}{1 + 0.5 x^2  }$ \\ \hline
+			Shear Flow               &  $\theta' = \cot(\phi)\cos(\theta)$ \\
+			                         &  $ \phi'  = ( \cos^2(\phi) + 0.1 \cdot \sin^2 (\phi)) \sin(\theta) $ \\ \hline
+		\end{tabular}
+	    \caption{Some Strogatz ODE problems.}
+	    \label{table:strogatz-ODEs}
+	\end{table}
 
@@
 \subsection{Parameter tuning}
-The \textsc{Rils}-\textsc{Rols} algorithms employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
+The \textsc{Rils}-\textsc{Rols} algorithms, apart of the most other methods for SR, employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
 The first parameter is set to 0.001(?), according to the preliminary experimental evaluation.
@@
 for target noise level $\alpha$, we have
-$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{N} \sum_{y_i^2}}\right). $$
+$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{N} \sum {y_i^2}}\right). $$
 

### 2022-10-27 doc/paper.tex
Exp. section: working...

@@
 
+   \item From the above conclusions, our \textsc{Rils}-\textsc{Rols} algorithm is more robust than the other approaches, as shown by the produced results w.r.t.\ different levels of noise in the input data.
+Moreover, this is a new state-of-the-art algorithms when one concerns the problem of SR.
+
 \end{itemize}
@@
 
+\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}
+
+In this section we study scalability of our method in terms of different noise level in the input data as well as different complexity of the exact solutions (models).
+
+First, we divide our benchmark sets into three parts as follows. 
+\begin{itemize}
+	\item Small--sized instances: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 3 to 7 nodes belong to this sub-set.
+	\item Middle--sized instances:  all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 8 to 11 nodes belong to this sub-set.
+	\item Large--sized instances: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 12 to 15 nodes belong to this sub-set. 
+\end{itemize}
+
+The results are displayed in Figure~\ref{fig:compExact_noise_size}.
+They are grouped with accordance to the (three) formed sub-groups ($x$-axis) and for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
+As expected, the success rate is the highest for the small--sized instances; it is sightly bellow 90\% for the clean (no-noise) data.
+For more noisy data, the success rate of the algorithm gets decreased.
+For example, on the small-sized instances on the noisy data with the level of noise of 0.01, the rate of success is about 35 \%.
+
 \begin{center}

### 2022-10-27 doc/paper.tex
Exp. section: working

@@
 They are grouped with accordance to the (three) formed sub-groups ($x$-axis) and for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
-As expected, the success rate is the highest for the small--sized instances; it is sightly bellow 90\% for the clean (no-noise) data.
+The following conclusions may be drawn from here:
+
+\begin{itemize}
+	\item   As expected, the success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% for the clean (no-noise) data.
 For more noisy data, the success rate of the algorithm gets decreased.
-For example, on the small-sized instances on the noisy data with the level of noise of 0.01, the rate of success is about 35 \%.
+For example, on the small-sized instances with the presence of the noise of level 0.0001, and 0.01, the rate of success of \textsc{Rils}--\textsc{Rols} is still reasonably well, about 55\%~ and 35 \%, respectively.
+	\item For middle-sized instance problems, the rate of success is slightly bellow 50\%.
+It also decreases by increasing the level of noise in the target data; for the highest level of chosen noise (of 0.01), the success of rate is about 6\%.
+	\item For the large-sized instance problems without the presence of a noise, the rate fo success of \textsc{Rils}--\textsc{Rols} algorithm is at about 25\%, which shows that increase in the size of exact models affects the algorithm's performance, but within reasonable expectations.
+
+	\item We conclude that the size of exact models (solutions) and the increase of the noise level evenly contribute to overall performance of our \textsc{Rils}--\textsc{Rols} method.
+The success rate of the algorithm (i.e.
+the exact percentage) seems decreasing linearly  with the average growing size of the exact models, regardless of the value of the noise level.
+\end{itemize}
 

### 2022-10-27 doc/paper.tex
Exp. section: working...

@@
 The success rate of the algorithm (i.e.
-the exact percentage) seems decreasing linearly  with the average growing size of the exact models, regardless of the value of the noise level.
+the exact percentage) seems decreasing linearly  with the average growing size of the exact models, regardless of values of the noise level.
+
+	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm -- that is when termination of the algorithm yielded the error $R^2 \geq 0.999$ -- for the input data with the zero noise level on the small--sized random instance problems, it almost reaches the perfect score (i.e.
+$\approx$100\%).
+In the presence of a low noise level (equals to 0.001), the accuracy delivered by the algorithm is still high, at about 95\%.
+Just when a high level of noise (equals to 0.01) is presented in the input data, the accuracy stagnates, but still with the respectable 66\% small-sized instances it reaches at least a precision of $R^2=0.999$.
+However, as we said, a half of them math to the respectable exact models.
+
+	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm on the middle-sized instance problems, it is obtained for 65\% cases in the case when the input data are free of the noise.
+The noisy the data are, the accuracy of the algorithms, as expected, drops off.
+However, not so dramatically~.
+For the level of noise of 0.01, the high--accuracy is reported on $\approx$30\% cases.
+
+	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm on the large-sized instance problems,  the high--accuracy in the data free of the noise presence is reported for 60\% cases.
+Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2\geq 0.999$ upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
+
 \end{itemize}
@@
 \end{center}
+
+Checking the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm w.r.t.\ the number of variables presented in the corresponding exact models of the problem instances is shown by Figures~\ref{fig:compExact_noise_varcnt}--\ref{fig:compR2_noise_varcnt}.
+\fxnote{TODO}
 

### 2022-10-30 doc/paper.tex
Experimental evalaution: Section 4.4.

@@
 In the presence of a low noise level (equals to 0.001), the accuracy delivered by the algorithm is still high, at about 95\%.
-Just when a high level of noise (equals to 0.01) is presented in the input data, the accuracy stagnates, but still with the respectable 66\% small-sized instances it reaches at least a precision of $R^2=0.999$.
+Just when a high level of noise (equals to 0.01) is presented in the input data, the accuracy stagnates, but still on the respectable 66\% small-sized instances it reaches a high--precision of $R^2=0.999$ upon termination.
 However, as we said, a half of them math to the respectable exact models.
@@
 	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm on the large-sized instance problems,  the high--accuracy in the data free of the noise presence is reported for 60\% cases.
-Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2\geq 0.999$ upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
+Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring n accuracy of $R^2\geq 0.999$ upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
 
@@
 
-Checking the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm w.r.t.\ the number of variables presented in the corresponding exact models of the problem instances is shown by Figures~\ref{fig:compExact_noise_varcnt}--\ref{fig:compR2_noise_varcnt}.
-\fxnote{TODO}
+In this section we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm w.r.t.\ the number of variables presented in the corresponding exact models of the problem instances whose sizes are ranging from 7 to 12.
+There is one line plot per each level of noise.
+These are shown by Figure~\ref{fig:compExact_noise_varcnt}.
+The instances are grouped according to the different variable count that are included into respective exact models ($x$-axis).
+For each of the (four) group, the exact percentages of success rate of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
+The following conclusions can be drawn from there.
+
+The rate of success of \textsc{Rils}--\textsc{Rols} algorithm seems to slightly increase as the expected number of variables gets larger in case of the data with no noise;
+	the increase is significant in the case of a higher noise in data.
+For example, the lowest percentages of success for \textsc{Rils}-\textsc{Rols} algorithm are noticed for noisy data where exact models consist of just one or two variables.
+It seems that in these cases the algorithm is more likely favorizing including additional variables at the cost of increasing model accuracy  in order to improve the fitness value over iterations.
+%Obtaining an accurate model with a few variables in the presence of a high level of nose in the data
 
@@
 		\begin{axis}[
-			xlabel=$variable\;count$,
+			xlabel=$variable\;count\;in\;exact\;models$,
 			ylabel=$exact\;percentage$,
@@
 
-\begin{center}
-	\begin{tikzpicture}
-		\begin{axis}[
-			xlabel=$variable\;count$,
-			ylabel=$exact\;percentage$,
-			xmin=0, xmax=5,
-			ymin=0, ymax=100,
-			xtick={1,2,3,4},
-			xticklabels={1,2,3,4},   % <---
-			ytick={0,10,...,100}
-			]
-			\addplot[smooth,mark=*,blue] plot coordinates {
-				(1,83.33)
-				(2,66.67)
-				(3,73.33)
-				(4,46.67)
-			};
-			\addlegendentry{No noise}
-
-			\addplot[smooth,color=red,mark=x]
-			plot coordinates {
-				(1,56.67)
-				(2,63.33)
-				(3,66.67)
-				(4,46.67)
-			};
-			\addlegendentry{Noise level 0.001}
-
-			\addplot[smooth,color=green,mark=o]
-			plot coordinates {
-				(1,23.33)
-				(2,43.33)
-				(3,53.33)
-				(4,26.67)
-			};
-			\addlegendentry{Noise level 0.01}
-		\end{axis}
-	\end{tikzpicture}
-	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
-	\label{fig:compR2_noise_varcnt}
-\end{center}
+%\begin{center}
+%	\begin{tikzpicture}
+%		\begin{axis}[
+%			xlabel=$variable\;count$,
+%			ylabel=$exact\;percentage$,
+%			xmin=0, xmax=5,
+%			ymin=0, ymax=100,
+%			xtick={1,2,3,4},
+%			xticklabels={1,2,3,4},   % <---
+%			ytick={0,10,...,100}
+%			]
+%			\addplot[smooth,mark=*,blue] plot coordinates {
+%				(1,83.33)
+%				(2,66.67)
+%				(3,73.33)
+%				(4,46.67)
+%			};
+%			\addlegendentry{No noise}
+%			
+%			\addplot[smooth,color=red,mark=x]
+%			plot coordinates {
+%				(1,56.67)
+%				(2,63.33)
+%				(3,66.67)
+%				(4,46.67)
+%			};
+%			\addlegendentry{Noise level 0.001}
+%			
+%			\addplot[smooth,color=green,mark=o]
+%			plot coordinates {
+%				(1,23.33)
+%				(2,43.33)
+%				(3,53.33)
+%				(4,26.67)
+%			};
+%			\addlegendentry{Noise level 0.01}
+%		\end{axis}
+%	\end{tikzpicture}
+%	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
+%	\label{fig:compR2_noise_varcnt}
+%\end{center}
 
 \subsection{Statistical evaluation}
-
+ \fxnote{TODO}
 \section{Conclusions and future work}\label{sec:conclusions}

### 2022-10-30 doc/paper.tex
update

@@
 
-In this section we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm w.r.t.\ the number of variables presented in the corresponding exact models of the problem instances whose sizes are ranging from 7 to 12.
-There is one line plot per each level of noise.
+In this section we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm w.r.t.\ the number of variables presented in the corresponding exact models of the problem instances whose sizes are ranging from 7 to 12 varying levels of noise.
+There is one line plot shown per each level of noise.
 These are shown by Figure~\ref{fig:compExact_noise_varcnt}.
@@
 It seems that in these cases the algorithm is more likely favorizing including additional variables at the cost of increasing model accuracy  in order to improve the fitness value over iterations.
+In the presence of zero level od noise, OLS method will find much easier a smaller model (on $\approx$ 45\% cases) of a high  accuracy w.r.t.\ the input data.
+In the next iterations, the method will hardly intend for adding variables in the current best solution at the cost of improving fitness value, as the size of model will contribute more to its increase as the first two product terms in~\ref{eq:fitness} are already small (close to 1).
 	%Obtaining an accurate model with a few variables in the presence of a high level of nose in the data

### 2022-10-30 doc/paper.tex
Som eplots added

@@
 For example, the lowest percentages of success for \textsc{Rils}-\textsc{Rols} algorithm are noticed for noisy data where exact models consist of just one or two variables.
-It seems that in these cases the algorithm is more likely favorizing including additional variables at the cost of increasing model accuracy  in order to improve the fitness value over iterations.
+It seems that in these cases the algorithm is more likely in favor of including additional variables at the cost of increasing model accuracy  in order to improve the fitness value over iterations.
 In the presence of zero level od noise, OLS method will find much easier a smaller model (on $\approx$ 45\% cases) of a high  accuracy w.r.t.\ the input data.
 In the next iterations, the method will hardly intend for adding variables in the current best solution at the cost of improving fitness value, as the size of model will contribute more to its increase as the first two product terms in~\ref{eq:fitness} are already small (close to 1).
+\fxnote{TODO: need to be further expanded...}
 	%Obtaining an accurate model with a few variables in the presence of a high level of nose in the data
 
+\begin{figure}[!ht]
+
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_no_noise.eps}
+		\caption{No noise}
+		\label{fig:noNoise}
+	\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.4\textwidth}
+
+			\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_noise0_001.eps}
+			\caption{Level of noise equal to 0.001}
+			\label{fig:noise0.001}
+		\end{subfigure}
+		\centering
+		\begin{subfigure}[b]{0.40\textwidth}
+					\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_noise0_01.eps}
+					\caption{Level of noise equal to 0.01.}
+					\label{fig:noise0.01}
+				\end{subfigure}
+		\caption{Exact solution percentages for varying levels of noise and variable counts.}
+		\label{fig:compExact_noise_varcnt}
+	\end{figure}
+
+\begin{figure}[!ht]
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_no_noise.eps}
+		\caption{No noise}
+		\label{fig:size-no-noise}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.4\textwidth}
+
+		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_noise0_001.eps}
+		\caption{Level of noise equal to 0.001}
+		\label{fig:size-noise0.001}
+	\end{subfigure}
+	\centering
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_noise0_01.eps}
+		\caption{Level of noise equal to 0.01.}
+		\label{fig:size-noise0.01}
+	\end{subfigure}
+	\caption{Exact solution percentages for varying levels of noise and exact model sizes.}
+	\label{fig:compExact_noise_varsize}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_time_no_noise.eps}
+		\caption{No noise}
+		\label{fig:time-no-noise}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.4\textwidth}
+
+		\includegraphics[  width=180pt,height=140pt]{plots/vars_vs_time_noise0_001.eps}
+		\caption{Level of noise equal to 0.001}
+		\label{fig:time-noise0.001}
+	\end{subfigure}
+	\centering
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=180pt,height=140pt]{plots/vars_vs_time_noise0_001.eps}
+		\caption{Level of noise equal to 0.01.}
+		\label{fig:time-noise0.01}
+	\end{subfigure}
+	\caption{Average runtime comparisons for varying levels of noise and variable counts.}
+	\label{fig:runtime_rils_rols}
+\end{figure}
+
+ \begin{comment}
 \begin{center}
@@
 \end{center}
-
+\end{comment}
 %\begin{center}

### 2022-10-31 doc/paper.tex
update
minor fix
Exp. section: working

@@
 
-In this section we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm w.r.t.\ the number of variables presented in the corresponding exact models of the problem instances whose sizes are ranging from 7 to 12 varying levels of noise.
+In this section we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
 There is one line plot shown per each level of noise.
-These are shown by Figure~\ref{fig:compExact_noise_varcnt}.
-The instances are grouped according to the different variable count that are included into respective exact models ($x$-axis).
-For each of the (four) group, the exact percentages of success rate of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
-The following conclusions can be drawn from there.
-
-The rate of success of \textsc{Rils}--\textsc{Rols} algorithm seems to slightly increase as the expected number of variables gets larger in case of the data with no noise;
-	the increase is significant in the case of a higher noise in data.
-For example, the lowest percentages of success for \textsc{Rils}-\textsc{Rols} algorithm are noticed for noisy data where exact models consist of just one or two variables.
-It seems that in these cases the algorithm is more likely in favor of including additional variables at the cost of increasing model accuracy  in order to improve the fitness value over iterations.
-In the presence of zero level od noise, OLS method will find much easier a smaller model (on $\approx$ 45\% cases) of a high  accuracy w.r.t.\ the input data.
-In the next iterations, the method will hardly intend for adding variables in the current best solution at the cost of improving fitness value, as the size of model will contribute more to its increase as the first two product terms in~\ref{eq:fitness} are already small (close to 1).
+These are shown by Figures~\ref{fig:compExact_noise_varcnt} and~\ref{fig:compExact_noise_varsizes}.
+The instances are grouped according to the different variable count/size of respective exact models ($x$-axis).
+For each group, the exact percentages of success rate of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
+
+ The following conclusions can be drawn from Figure~\ref{fig:compExact_noise_varcnt}.
+
+\begin{itemize}
+    \item The rate of success of \textsc{Rils}--\textsc{Rols} algorithm  slightly decrease as the expected number of variables gets larger in case of the data with no noise.
+    \item The success rate percentages drop off with the presence of noise. The higher the noise level, the smaller the success rate percentages. 
+    \item Interestingly, in the presence of noise, the highest exact percentages are not for the instances whose exact models have one variable, but two or three.
+We argue it by the fact that the early phase of the algorithm will more frequently include additional variables in the solution at the cost of increasing model accuracy to ensure the fitness value improvements over iterations.
+In the presence of the zero noise, OLS method efficiently finds a smaller model (on $\approx$ 50\% cases) of a high  accuracy that fits to the input data.
+However, this is no the case when the data is noisy and the decision of adding more variables is forced.
+By a progression of the algorithms, it gets harder improving the fitness value of the current best solution by adding variables, and other operations are more frequently involved.
+%This conclusion also correlates to the shape of fitness function given by Equation~(\ref{eq:fitness}) where the first two product terms there are already small (close to 1).
 \fxnote{TODO: need to be further expanded...}
 	%Obtaining an accurate model with a few variables in the presence of a high level of nose in the data 
-
-\begin{figure}[!ht]
+\end{itemize}
+
+\begin{figure}[H]
 
@@
 
-\begin{figure}[!ht]
+The  following conclusions may be drawn from Figure~\ref{fig:compExact_noise_varsizes}.
+\begin{itemize}
+	\item The exact percentage rates are decreased as the size of exact models increase, in case of any level of noise is utilized within the input data.
+	\item The highest exact percentages, higher than 70\%, are noticed for the instances with a small-to-middle size  (3--7) exact models.
+However, for the same sizes, for noisy data, these percentages are significantly lower; for example, in case of models of size 7 and the level of noise of 0.001 and 0.01, the exact percentages obtained are 20\% and 10\%, respectively.
+
+	\item   For the largest sizes of (exact) models, for the no noisy data the exact percentages are never lower from 20\%. The other way around holds for noisy data. 
+\end{itemize}
+
+\begin{figure}[H]
 	\begin{subfigure}[b]{0.40\textwidth}
@@
 	\caption{Exact solution percentages for varying levels of noise and exact model sizes.}
-	\label{fig:compExact_noise_varsize}
+	\label{fig:compExact_noise_varsizes}
 \end{figure}
+
+When one concern of the runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set, the results are shown by Figure~\ref{fig:runtime_rils_rols}.
+The following conclusions may be drawn from there.
+
+\begin{itemize}
+	\item abc...\fxnote{TODO}
+\end{itemize}
 
@@
 	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/vars_vs_time_noise0_001.eps}
+		\includegraphics[  width=180pt,height=140pt]{plots/vars_vs_time_noise0_01.eps}
 		\caption{Level of noise equal to 0.01.}

### 2022-10-31 doc/paper.tex
plots updated

@@
 
-When one concern of the runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set, the results are shown by Figure~\ref{fig:runtime_rils_rols}.
+When one concerns of runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are shown in Figure~\ref{fig:runtime_rils_rols}.
+The instances are grouped w.r.t.\ number of variables included into corresponding exact model.
 The following conclusions may be drawn from there.
@@
 \begin{itemize}
-	\item abc...\fxnote{TODO}
+	\item As expected, average runtime is getting increased with the increase of the number of variables. 
+	\item Note that the average runtime in case of the instances whose exact models have the largest number of variables (5) is about 200s.
+	\item The two above-mentioned points indicate efficacy of our method especially in case of expected exact models of a smaller size on the data with small--to--middle levels of noise.
+In these cases, the algorithm is still able to deliver the reasonable exact percentages, which are larger than 50\%.
+Note that
+	the models with these characteristics are desirable in the areas of natural sciences due to their interpret-ability more than models represented by complex expressions.   
 \end{itemize}

### 2022-11-01 doc/paper.tex
Start with statistical evaluation

@@
 \end{itemize}
-The above-mentioned benchmark sets may be biased as models which describe physical laws may have various symmetries, periodically w.r.t.
+The above-mentioned benchmark sets may be biased as models which describe physical laws usually have  symmetries, periodicity w.r.t.
 some variables, internal separability on some variables etc.
@@
 \fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}
+
+All (15) competitor algorithms were run once per each instance.
 
@@
 \subsection{Statistical evaluation}
- \fxnote{TODO}
+
+In order to check the statistical significance of the obtained differences between the studied approaches, we employed the statistical methodology which is outlined below.
+This concerns the 15 approaches on two real-world benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+Initially, Friedman’s test was separately executed for all competitor approaches.
+In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the results of the competitor approaches) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
+The outcome is represented by means of critical difference (CD) plots.
+In a CD plot, the competitor approaches are placed on the horizontal axis according to their average ranking.
+Thereafter, the CD score is computed for a significance level of 0.05.
+If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.
+\fxnote{Marko: continue}
+
 \section{Conclusions and future work}\label{sec:conclusions}

### 2022-11-01 doc/paper.tex
working

@@
 	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  the current two states on which it depends.
-These equations describes various non-linear dynamics and exhibiting chaos.
-The equations for some of the datasets of this benchmark are shown in Table~\ref{table:strogatz-ODEs}.
+These equations describes various non-linear dynamics also exhibiting chaos.
+The equations for some of the datasets that belong to this benchmark are shown in Table~\ref{table:strogatz-ODEs}.
 
@@
 
-In order to check the statistical significance of the obtained differences between the studied approaches, we employed the statistical methodology which is outlined below.
+In order to check the statistical significance of the obtained exact percentages and their differences between the studied approaches, we employed the statistical methodology which is outlined below.
 This concerns the 15 approaches on two real-world benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.

### 2022-11-03 doc/paper.tex
CD plots generated

@@
 It brought researchers an easy handled environment to evaluation, compare, and analyze their methods.
-Among all benchmark sets, we involve two real-world inspired benchmark sets into our computational evaluation:
+Among all benchmark sets, we involve two real-world inspired benchmark sets, the ground-truth regression problems, into our computational evaluation:
 \begin{itemize}
@@
 
-In order to check the statistical significance of the obtained exact percentages and their differences between the studied approaches, we employed the statistical methodology which is outlined below.
-This concerns the 15 approaches on two real-world benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+In order to check the statistical significance of the obtained exact percentages and their differences between the studied approaches, we employed the statistical methodology comparing the results of  the 15 approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
 Initially, Friedman’s test was separately executed for all competitor approaches.
@@
 If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.
-\fxnote{Marko: continue}
+The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}.
+The following conclusions may be drawn from there.
+
+\begin{itemize}
+	\item \fxnote{TODO}
+\end{itemize}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
+		\caption{No noise}
+		\label{fig:CDplots-no-noise}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.4\textwidth}
+
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_001.pdf}
+		\caption{Level of noise equal to 0.001}
+		\label{fig:CDplots-noise0.001}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
+		\caption{Level of noise equal to 0.01.}
+		\label{fig:CDplots-noise0.01}
+	\end{subfigure}
+	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.}
+	\label{fig:cd-plots-exact-pcts}
+\end{figure}
 
@@
  \section{Overview of RILS-ROLS python package}\label{sec:appendix-1}
+
+  \section{Additional statistical analysis}\label{sec:appendix-2}
+
+  \begin{figure}[H]
+  	\begin{subfigure}[b]{0.40\textwidth}
+  		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_0acc.pdf}
+  		\caption{No noise}
+  		\label{fig:CDplotsR2-no-noise}
+  	\end{subfigure}
+  	\hfill
+  	\begin{subfigure}[b]{0.4\textwidth}
+
+  		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_001acc.pdf}
+  		\caption{Level of noise equal to 0.001}
+  		\label{fig:CDplotsR2-noise0.001}
+  	\end{subfigure}
+  	\centering
+  	\begin{subfigure}[b]{0.40\textwidth}
+  		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_01acc.pdf}
+  		\caption{Level of noise equal to 0.01.}
+  		\label{fig:CDplotsR2-noise0.01}
+  	\end{subfigure}
+  	\caption{CD plots comparisons in terms of obtained $R^2$ score over all problem instances from both ground-truth benchmark sets,  varying levels of noise.}
+  	\label{fig:cd-plotsR2-varying_noise}
+  \end{figure}
 

### 2022-11-03 doc/paper.tex
Statistics: described

@@
 \begin{itemize}
-	\item \fxnote{TODO}
+	\item  Concerning instance problems where for the input data no noise is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of   exact percentage rate.
+The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
+There is no statistically significant difference between these two approaches.
+However, these two approaches perform statistically significantly better than the third best (according the the average raking), that is with \textsc{Apf-Fe}.
+This conclusion also holds for the remaining approaches.
+	\item    Concerning instance problems where for the input data a (white) noise of 0.001 is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of the exact percentage rate.
+The second best ranking is achieved by \textsc{Afp-Fe} algorithm.
+However,  there is no statistically significant difference between these two approaches.
+The third best according approach is \textsc{Afp}, which perform statistically equal to \textsc{Afp-Fe}, but statistically worse that our \textsc{Rils}-\textsc{Rols} method.
+For all remaining methods, the later conclusion also holds.
+	\item   Concerning instance problems where for the input data a (white) noise of 0.01 is included, again, \textsc{Rils-Rols} reaches the best average ranking; the second best approach is \textsc{gplearn}.
+The difference between the exact percentages delivered by these two approaches is significant in favor of \textsc{Rils-Rols} approach.
+This is also the case when \textsc{Rils-Rols} is compared to all the remaining approaches.
+
 \end{itemize}

### 2022-11-03 doc/paper.tex
Start with round of revision in the Exp. section

@@
 Our \textsc{Rils}--\textsc{Rols} algorithm is implemented in Python version 3.x.
-All experiments are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
-The maximum computation time allowed for each run was set to 1h minutes, i.e., 3600 seconds.
-
-The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp} and our \textsc{Rils}-\textsc{Rols} algorithm.
+The experiments concerning our method are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
+ The following 14 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
+
+For the (14) competitors, the results are exported from \url{https://cavalab.org/srbench/results/}, also reported in~\cite{la2021contemporary}. 
+The maximum computation time allowed for each run of \textsc{Rils}-\textsc{Rols} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used for all (14) competitors, see~\cite{la2021contemporary}.
+
+All (15) competitor algorithms were run ten times per each instance.
 
@@
 
-SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and the environment for analysis, see~\cite{la2021contemporary}.
-It brought researchers an easy handled environment to evaluation, compare, and analyze their methods.
+SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
+It brought researchers an easy handled environment to evaluation, comparisons, and analysis of their methods.
 Among all benchmark sets, we involve two real-world inspired benchmark sets, the ground-truth regression problems, into our computational evaluation:
@@
 	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that correspond to various natural laws.  
-	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.
+	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}.
+Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.
+Among them, 115 regression problem instances are chosen in the experimental evaluation, with accordance to~\cite{la2021contemporary}.
 
@@
 	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  the current two states on which it depends.
-These equations describes various non-linear dynamics also exhibiting chaos.
+These equations describes natural processes described by non-linear dynamics  exhibiting chaos.
 The equations for some of the datasets that belong to this benchmark are shown in Table~\ref{table:strogatz-ODEs}.
+These problem instances are downloadable from \url{https://github.com/lacava/ode-strogatz}.
+In overall, 14 ground-truth models are used to generate the problem instances used in the comparison, see~\cite{la2021contemporary}.
 
@@
 \end{itemize}
-The above-mentioned benchmark sets may be biased as models which describe physical laws usually have  symmetries, periodicity w.r.t.
+The above-mentioned benchmark sets may be biased as models which describe physical laws that usually impose   symmetries, periodicity w.r.t.
 some variables, internal separability on some variables etc.
-In that way, the search process and the search space can be biased and in-advance significantly reduced.
-Thus, some methods may get significant help with this regards, while some others may be in the subordinate situation.
-  In order to permit any kind of favoritism, we generate a set of randomly generated instances, called \textsc{Random}.
+In that way, the search process and the search space can be, in-advance, significantly reduced.
+Thus, some methods may get significant benefit with this regard, while some others may be in the subordinate situation.
+  In order to permit any kind of favoritism in the input data, we generate a set of randomly generated (non-biased) instances, labelled by \textsc{Random}.
 These instances are generated according the following procedure.
 \fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}
-
-All (15) competitor algorithms were run once per each instance.
 

### 2022-11-04 doc/paper.tex
Conclusions

@@
 \section{Conclusions and future work}\label{sec:conclusions}
+  This paper deals with solving the well--known Symbolic regression (SR)  problem.
+This problem is a generalization of more interdisciplinary appearing  linear and logistic regression problems.
+SR problem have been intensively studied in the literature over the last 15 years, where a few dozens of algorithms were constructed, mainly based on Genetic programming and on the application of different kinds of neural networks.
+We proposed a meta-heuristic approach, called \textsc{Rils}-\textsc{Rols}.
+It is based on the Iterative local search (ILS) scheme.
+The first crucial concept within this scheme is utilizing the oridinary least square method to efficiently determine coefficients in the candidate solutions.
+Another key aspect is the use of a carefully constructed fitness function, which is a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).
+Last but not least, the neighbor of solution in the local search is carefully defined that suits to small modifications of a three that represents solutions (models).
+\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from literature on the two ground truth benchmark sets from literature.
+Additionally, we introduced a non-biased benchmark set of randomly generated instances.
+The experimental evaluation confirmed efficiently of out method which was able to produce the best average ranking in terms of exact percentage in comparison to all other competitors on all ground-truth instances, and in presence of three different levels of noise in the input data.
+In all cases, new best average-percentages are obtained in the literature by means of \textsc{Rils-Rols} method.
+In some cases, these differences are statistically significant in favor of our \textsc{Rils-Rols} method.
+Moreover, scalability and robustness of our method is  checked and confirmed on the randomly generated instances in terms of a few different criteria such as the size of model, the number of variables, average runtimes, etc.
+\fxnote{TODO: case-study about large-scale data to be added}
+
+  In the future work, one could think of  make a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics, or replacing ILS scheme of \textsc{Rils-Rils} with, for example, Variable neighborhood search meta-heuristic.
+Additionally, as a proof of the concept, our tool will be provided to various research communities out of the are of Computer science, such as the ones from physics ot chemistry to seek for new hypotheses or o obtain insights on their experimental data.
 

### 2022-11-04 doc/paper.tex
Do strane 16

@@
 \subsection{Parameter tuning}
-The \textsc{Rils}-\textsc{Rols} algorithms, apart of the most other methods for SR, employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is set to 0.001(?), according to the preliminary experimental evaluation.
-The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose $tolerance_{error}=?$ for which a largest average $R^2$ and the smallest average RMSE error over all instances from the training set are produced.
-Note that the training set is chosen randomly with a cardinalty of xx instances.
+The \textsc{Rils}-\textsc{Rols} algorithm employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is fixed to 0.001(?), according to the preliminary experimental evaluation we conducted.
+The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances; among the following values \{ x, xx, ...
+\} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error over all problem instances from the training set are produced.
+%Note that the training set is chosen randomly with a cardinalty of xx instances.
 
@@
 \subsection{Comparison with other methods on real--world benchark sets}
-In this section, we evaluate the performance of \textsc{Rils-Rols} algorithm with 15 other competitors from the literature that solve the problem of Symbolic regression.
-The results are reported in terms of three numerical Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}, where two real-world benchmark sets, \textsc{Feynman} and \textsc{Storgatz} are considered, utilizing  different values of the noise levels: 0.0 (no noise), 0.001 (a low-level noise), and 0.01 (a high-level noise), respectively.
-Concerning the added noise, the White Gaussian noise was added to the target ($y$-axis values) as a fraction of the signal RMS value, also applied in~\cite{la2021contemporary}, i.e.
+In this section, we evaluate the performance of \textsc{Rils-Rols} algorithm and compare it to the 14 other competitors from the literature.
+The numerical results are reported in terms of the three Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}.
+The results for the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, are given w.r.t.\   the following values of the noise levels of 0.0 (no noise), 0.001 (a low-level noise), and 0.01 (a high-level noise), respectively.
+In details, the white Gaussian noise was added to the target ($y$-axis) values as a fraction of the signal RMS value, also applied in~\cite{la2021contemporary}, i.e.
 for target noise level $\alpha$, we have
-$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{N} \sum {y_i^2}}\right). $$
-
-Each table consist of three blocks.
-The first block reports the algorithm whose performances are reported.
-The second block reports, in two columns,  percentages of instances where the model which matches to the exact one has been found by respective algorithms on both, \textsc{Feynman} and \textsc{Strogatz}, benchmark sets.
-The third column of this block provides the overall summary percentage of success over all instances.
-The third block displays the results of the respective algorithm in the presence of $R^2$ error which can indicate on  accuracy, i.e.
+$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{n} \sum {y_i^2}}\right),$$
+where $n$ relates to the number of items in the input data.
+
+Each table consists of three blocks.
+The first block reports the algorithm whose performances are reported (by a row).
+The second block reports, with two columns,  percentages of the instances where the model which fits to the exact one has been found by respective algorithms on \textsc{Feynman} and \textsc{Strogatz} benchmark set, respectively.
+The third column of this block provides the overall summary exact percentage of success over all instances from the both benchmark sets.
+The third block displays the results of the respective algorithm in terms of the $R^2$ score which indicate on  accuracy, i.e.
 in our cases when the algorithm  at least reached the accuracy ($R^2$ score) of 0.999.
-Note that the termination of our algorithm may not necessary be triggered by the error equal to 1.
-These results are of interest as it may point out the existence of an over-fitting.
-This block consists of three rows that indicate the percentage of instances where respective algorithm is able to reach the desired accuracy (fulfilling condition $R^2 \geq 0.999$ before a termination due exceeding the time limit) on the both real--world benchmark sets separately, and the overall percentage of success rate (over all considered instances) w.r.t.
-the same criterion of success.
+Note that the termination of our algorithm may not always be triggered by reaching an appropriate $R^2$ score of 0.999, but also due to the reached time limit.
+These results are of interest as when compared to corresponding exact percentage it may point out the existence of an over-fitting.
+This block consists of three rows that indicate the percentage of instances where respective algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 \geq 0.999$ upon termination) on the both real--world benchmark sets separately, and the overall percentage of success rate (over all considered instances) w.r.t.
+the same criterion of reaching the desired accuracy.
 
@@
 \begin{itemize}
-	\item Concerning the exact results in case no noise is utilized in the instance problems, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, begin successful in 83.57\% cases.
+	\item \fxnote{Marko: Came up to here!}Concerning the exact results in case no noise is utilized in the instance problems, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, begin successful in 83.57\% cases.
 The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all instances of the benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.

### 2022-11-04 doc/paper.tex
Do Sekcije 4.4.

@@
 \begin{itemize}
-	\item \fxnote{Marko: Came up to here!}Concerning the exact results in case no noise is utilized in the instance problems, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, begin successful in 83.57\% cases.
-The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all instances of the benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
-All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered benchmark sets.
-	\item   Concerning the exact results when the target noise is presented with a level of 0.001, our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model in more than 42\% cases considering the problems from the both benchmark sets.
-Interestingly, \textsc{AI-Feynman} is quite sensible w.r.t.\ the increase in the target noise level, as its performances rapidly drop down -- it is successful on just 2.81\% of the all problem instances.
-Better from \textsc{AI-Feynman} are in this case the \textsc{Dsr}, \textsc{Gplearn}, and \textsc{Afp-Fe} in this order of success, whose percentages of success rate range from $\approx$15--17\%.
-	\item  Concerning the exact results when the presence of noise is significant, that is with a level of 0.01,  our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model for  34.77\% of the all problem instances.
-The second best is \textsc{Gplearn} which percentage of success is just 12.75\%, followed by \textsc{Dsr} which is successful for just 9.23\% of the all problem instances.
+	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
+The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all problem instances from benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
+All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered ground-truth benchmark sets.
+	\item   Concerning the exact results in presence of the target noise with a level of 0.001, our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model for more than 42\% cases considering the problem instances from the both benchmark sets.
+Interestingly, \textsc{AI-Feynman} is quite sensible w.r.t.\ the increase of the target noise level, as its performances rapidly going down -- it is successful on just 2.81\% of the all problem instances.
+Better from \textsc{AI-Feynman} are in this case the \textsc{Dsr}, \textsc{Gplearn}, and \textsc{Afp-Fe} order decreasingly w.r.t.\ the exact percentages of success, ranging from $\approx$15--17\%.
+	\item  Concerning the exact results when the presence of noise is large, that is with a level of 0.01,  our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model for  34.77\% problem instances from the two benchmark sets.
+The second best performing is \textsc{Gplearn} which exact percentage of success is just 12.75\%, followed by \textsc{Dsr} which is successful for just 9.23\% problem instances.
+% over all problem instances.
 
 	\item When comparing performances of the algorithms in terms of number of instances for which the algorithm's termination led to an accurate model, that is $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{Rils}-\textsc{Rols} is successful with the rate of success of 83.38\%.
-However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than ours: \textsc{Mrgp}, and \textsc{Operon}, with 92.69\%, and 86.93\%.
+However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than our algorithm: \textsc{Mrgp}, and \textsc{Operon}, with 92.69\%, and 86.93\%, respectively.
 On the other hand, as the  exact model percentage rates of these two approaches are rather low (0\% and 16\%, respectively) these indicate the presence of a high level over-fitting  of the later two algorithms.
@@
    \item  When comparing the performances of the competitors in terms of number of instances for which the  termination led to an accurate enough model, in the presence of the noise level of 0.001, our \textsc{Rils}--\textsc{Rols} method has 78.62\% of a success rate, concerning all considered instances.
-The \textsc{Operon} solver only has a better percentage of success among the competitors, which is 83.08\%.
-However, the over-fitting is conspicuous as this algorithm is rarely able to obtain the model which matches to the exact one (which is successful for 0.31\% cases).
-
-   \item   When comparing the performances of the competitors in terms of number of instances for which the  termination led to an accurate enough model, in the presence of the high--level noise of 0.01, our \textsc{Rils}--\textsc{Rols} method is still highly accurate, delivering  62.92\% of a success rate.
+The \textsc{Operon} solver is the only one that returns a better percentage of success among the competitors, which is 83.08\%.
+However, the over-fitting is conspicuous as this algorithm is rarely able to obtain the model which matches to the exact one (its exact percentage is equal to 0.31\%).
+
+   \item   When comparing performances of the competitors in terms of number of instances where the termination lead to obtaining an accurate model, in the presence of the high--level noise of 0.01, our \textsc{Rils}--\textsc{Rols} method is still highly accurate, delivering  62.92\% of a success rate.
 Interestingly, it is the best performing in terms of the percentage rate among other competitors.
-Just for the information, the second best approach is \textsc{Dsr}, with a 16.92\% success rate.
-It can be concluded that our \textsc{Rils}--\textsc{Rols} method does not pay a big price in presence of a higher noise, like the other methods do, and seem to be very sensible w.r.t.
+Just for  the information, the second best approach is \textsc{Dsr}, with 16.92\% of the success rate.
+It can be concluded that our \textsc{Rils}--\textsc{Rols} method does not pay a big price in presence of a higher noise, like the other methods which are very sensible w.r.t.
 the noise increase.
-Our \textsc{Rils}--\textsc{Rols} method still delivers high-accuracy models for the noisy input data, but also many of them match to the exact solutions (models).
-
-   \item From the above conclusions, our \textsc{Rils}-\textsc{Rols} algorithm is more robust than the other approaches, as shown by the produced results w.r.t.\ different levels of noise in the input data.
-Moreover, this is a new state-of-the-art algorithms when one concerns the problem of SR.
+Our \textsc{Rils}--\textsc{Rols} method still delivers high-accuracy models for the noisy input data, but also many of them fit to the exact solutions (models).
+
+   \item Following the above conclusions, our \textsc{Rils}-\textsc{Rols} algorithm is more robust than the other competitors, which is confirmed by the produced results w.r.t.\ different levels of noise in the input data.
+Moreover, it can be considered as new state-of-the-art algorithm when one solves the problem of SR.
 
@@
 \subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}
-
+   \fxnote{Marko: Came up to here!}
 In this section we study scalability of our method in terms of different noise level in the input data as well as different complexity of the exact solutions (models).

### 2022-11-05 doc/paper.tex
Update

@@
 \subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}
-   \fxnote{Marko: Came up to here!}
-In this section we study scalability of our method in terms of different noise level in the input data as well as different complexity of the exact solutions (models).
+
+In this section we study the scalability of our method in terms of the size of  instance problems and  the presence of different noise level in the input data.
 
@@
 \begin{itemize}
-	\item Small--sized instances: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 3 to 7 nodes belong to this sub-set.
-	\item Middle--sized instances:  all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 8 to 11 nodes belong to this sub-set.
-	\item Large--sized instances: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 12 to 15 nodes belong to this sub-set. 
+	\item \textit{Small--sized instances}: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 3 to 7 nodes belong to this sub-set.
+	\item \textit{Middle--sized instances}:  all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 8 to 11 nodes belong to this sub-set.
+	\item \textit{Large--sized instances}: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 12 to 15 nodes belong to this sub-set. 
 \end{itemize}
 
-The results are displayed in Figure~\ref{fig:compExact_noise_size}.
-They are grouped with accordance to the (three) formed sub-groups ($x$-axis) and for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
+The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped with accordance to the (three) formed sub-groups ($x$-axis); for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
 The following conclusions may be drawn from here:
-
+   \fxnote{Marko: Came up to here!}
 \begin{itemize}

### 2022-11-05 doc/paper.tex
Do Sekcije 4.5

@@
 The following conclusions may be drawn from here:
-   \fxnote{Marko: Came up to here!}
+
 \begin{itemize}
-	\item   As expected, the success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% for the clean (no-noise) data.
-For more noisy data, the success rate of the algorithm gets decreased.
-For example, on the small-sized instances with the presence of the noise of level 0.0001, and 0.01, the rate of success of \textsc{Rils}--\textsc{Rols} is still reasonably well, about 55\%~ and 35 \%, respectively.
-	\item For middle-sized instance problems, the rate of success is slightly bellow 50\%.
-It also decreases by increasing the level of noise in the target data; for the highest level of chosen noise (of 0.01), the success of rate is about 6\%.
-	\item For the large-sized instance problems without the presence of a noise, the rate fo success of \textsc{Rils}--\textsc{Rols} algorithm is at about 25\%, which shows that increase in the size of exact models affects the algorithm's performance, but within reasonable expectations.
-
-	\item We conclude that the size of exact models (solutions) and the increase of the noise level evenly contribute to overall performance of our \textsc{Rils}--\textsc{Rols} method.
-The success rate of the algorithm (i.e.
-the exact percentage) seems decreasing linearly  with the average growing size of the exact models, regardless of values of the noise level.
-
-	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm -- that is when termination of the algorithm yielded the error $R^2 \geq 0.999$ -- for the input data with the zero noise level on the small--sized random instance problems, it almost reaches the perfect score (i.e.
+	\item   As expected, the exact percentage success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% for the no-noisy data.
+For noisy data, the success rate of the algorithm gets decreased as the level of noise increases.
+For example, on the small-sized problem instances with the noise level  of 0.0001, and 0.01, the exact percentage of \textsc{Rils}--\textsc{Rols} is still reasonably high, at about 55\%~ and 34 \%, respectively.
+	\item For the middle-sized instance problems, the exact percentage rate is slightly bellow 50\%.
+It also decreases by increasing the level of noise in the target data; for the highest level of noise (of 0.01), the success rate of \textsc{Rils}-\textsc{Rols} method is just about 6\%.
+	\item For the large-sized instance problems with no noise is utilized, the exact percentage of \textsc{Rils}--\textsc{Rols} algorithm is at about 25\%, which means that the increase in the size of exact models affects the algorithm's performance, but within the expected range.
+
+	\item From the above, we can conclude that the size of exact models (solutions) and the increase of the noise level both contribute to overall performance of our \textsc{Rils}--\textsc{Rols} method.
+The exact percentage rate of the algorithm seems decreasing linearly  in the (exact) model size, regardless of the noise level values.
+
+	 \item Concerning the high--accuracy percentages delivered by \textsc{Rils}--\textsc{Rols} algorithm -- that is the percentage of problem instances for which the algorithm's termination yielded a model with $R^2 \geq 0.999$ -- for the small--sized problem instances with no noise is recorded, it is almost at the perfect score (i.e.
 $\approx$100\%).
-In the presence of a low noise level (equals to 0.001), the accuracy delivered by the algorithm is still high, at about 95\%.
-Just when a high level of noise (equals to 0.01) is presented in the input data, the accuracy stagnates, but still on the respectable 66\% small-sized instances it reaches a high--precision of $R^2=0.999$ upon termination.
-However, as we said, a half of them math to the respectable exact models.
-
-	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm on the middle-sized instance problems, it is obtained for 65\% cases in the case when the input data are free of the noise.
-The noisy the data are, the accuracy of the algorithms, as expected, drops off.
-However, not so dramatically~.
-For the level of noise of 0.01, the high--accuracy is reported on $\approx$30\% cases.
-
-	 \item Concerning the high--accuracy of the \textsc{Rils}--\textsc{Rols} algorithm on the large-sized instance problems,  the high--accuracy in the data free of the noise presence is reported for 60\% cases.
-Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring n accuracy of $R^2\geq 0.999$ upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
+In the presence of a low noise level (equals to 0.001), the percentages of instance problems with the high--accuracy is still high, at about 95\%.
+In case when the high level of noise (equals to 0.01) is presented in the input data, these percentages stagnate, but still are at a respectable 66\%.
+%small-sized instances it reaches a high--precision of $R^2=0.999$ upon termination.
+	 As we pointed out already, a half of these math to the respectable exact models.
+
+	 \item Concerning the high--accuracy percentage of the \textsc{Rils}--\textsc{Rols} algorithm on the middle-sized instance problems when the input data are free of the noise, it is obtained on 65\% cases.
+The noisy the data are, the accuracy percentages of the algorithm, as expected, drop off; however, not so dramatically.
+For the level of noise of 0.01, the high--accuracy of the final solution is reported on $\approx$30\% cases.
+
+	 \item Concerning the high--accuracy percentages of the \textsc{Rils}--\textsc{Rols} algorithm on the large-sized instance problems with no noise, it gets 60\%.
+Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2\geq 0.999$ for the outcome  upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
 
@@
  	\begin{axis}[
-		xlabel=$size$,
-		ylabel=$exact\;percentage$,
+		xlabel=\textbf{model size},
+		ylabel=\textbf{exact percentage},
 		xmin=0, xmax=4,
@@
 		\begin{axis}[
-			xlabel=$size$,
-			ylabel=$R^2 > 0.999\;percentage$,
+			xlabel=\textbf{model size},
+			ylabel=\textbf{$R^2 > 0.999$ percentage},
 			xmin=0, xmax=4,
@@
 
-In this section we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
-There is one line plot shown per each level of noise.
+In this paragraph we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
+There is three bar plots shown per each level of noise.
 These are shown by Figures~\ref{fig:compExact_noise_varcnt} and~\ref{fig:compExact_noise_varsizes}.
 The instances are grouped according to the different variable count/size of respective exact models ($x$-axis).
-For each group, the exact percentages of success rate of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
+For each group, the exact percentages of success rate of \textsc{Rils}--\textsc{Rols} algorithm on the instance group is shown ($y$-axis).
 
@@
 \begin{itemize}
-    \item The rate of success of \textsc{Rils}--\textsc{Rols} algorithm  slightly decrease as the expected number of variables gets larger in case of the data with no noise.
-    \item The success rate percentages drop off with the presence of noise. The higher the noise level, the smaller the success rate percentages. 
-    \item Interestingly, in the presence of noise, the highest exact percentages are not for the instances whose exact models have one variable, but two or three.
-We argue it by the fact that the early phase of the algorithm will more frequently include additional variables in the solution at the cost of increasing model accuracy to ensure the fitness value improvements over iterations.
-In the presence of the zero noise, OLS method efficiently finds a smaller model (on $\approx$ 50\% cases) of a high  accuracy that fits to the input data.
-However, this is no the case when the data is noisy and the decision of adding more variables is forced.
-By a progression of the algorithms, it gets harder improving the fitness value of the current best solution by adding variables, and other operations are more frequently involved.
+    \item The exact percentage rate of \textsc{Rils}--\textsc{Rols} algorithm  slightly decrease as the expected number of variables gets larger when no noise is presented in the data.
+    \item The exact percentages drop off with the presence of a larger noise level. Thus, the higher the noise level, the smaller the exact percentages are. \fxnote{Marko: came up to here!}
+    \item Interestingly, in the presence of noise, the highest exact percentages are not obtained on the problem instances whose exact models consists of a single variable, but two or three.
+We argue it by the fact that the early phase of the algorithm will more likely try to include additional variables in the solution at the cost of increasing the model accuracy to ensure improving the fitness value over iterations.
+In the presence of the zero noise, OLS method will more likely find a smaller model (on $\approx$ 50\% cases) with a high accuracy that fits to the (no-noisy) input data than the case of noisy data.
+When the data is noisy, the decision of adding more variables at the beginning is likely to be forced than just dealing with short-size solutions.
+By the algorithm's progression, it gets harder improving the best fitness value by adding variables, and other operations are more frequently involved than in previous iterations.
 %This conclusion also correlates to the shape of fitness function given by Equation~(\ref{eq:fitness}) where the first two product terms there are already small (close to 1).
@@
 \begin{itemize}
-	\item The exact percentage rates are decreased as the size of exact models increase, in case of any level of noise is utilized within the input data.
-	\item The highest exact percentages, higher than 70\%, are noticed for the instances with a small-to-middle size  (3--7) exact models.
+	\item The exact percentages are decreased with the increase of size of exact models, in case of any level of noise utilized on the target values.  %within the input data.
+	\item The highest exact percentages, which are higher than 70\%, are noticed for the small-sized problem instances  (the size ranges from 3 to 7) exact models.
 However, for the same sizes, for noisy data, these percentages are significantly lower; for example, in case of models of size 7 and the level of noise of 0.001 and 0.01, the exact percentages obtained are 20\% and 10\%, respectively.
 
-	\item   For the largest sizes of (exact) models, for the no noisy data the exact percentages are never lower from 20\%. The other way around holds for noisy data. 
+	\item   For the problem instances with a largest size of (exact) models for no noisy data, exact percentages are never lower than 20\%. The opposite holds for noisy data. 
 \end{itemize}
@@
 
-When one concerns of runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are shown in Figure~\ref{fig:runtime_rils_rols}.
-The instances are grouped w.r.t.\ number of variables included into corresponding exact model.
+When one concerns of runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are displayed in Figure~\ref{fig:runtime_rils_rols}.
+The instances are grouped w.r.t.\ number of variables included into corresponding exact model ($x$-axis).
 The following conclusions may be drawn from there.
@@
 \begin{itemize}
-	\item As expected, average runtime is getting increased with the increase of the number of variables. 
-	\item Note that the average runtime in case of the instances whose exact models have the largest number of variables (5) is about 200s.
-	\item The two above-mentioned points indicate efficacy of our method especially in case of expected exact models of a smaller size on the data with small--to--middle levels of noise.
-In these cases, the algorithm is still able to deliver the reasonable exact percentages, which are larger than 50\%.
-Note that
-	the models with these characteristics are desirable in the areas of natural sciences due to their interpret-ability more than models represented by complex expressions.   
+	\item As one could expect, average runtime is getting increased with the increase of the number of variables in exact models. 
+	\item Note that the average runtime in case of the instances whose exact models have the largest number of variables (5) is just about 200$s$.
+	\item The two above-mentioned points indicate efficacy of our method especially in case of expected exact models of a small and middle sizes with small--to--middle levels of noise included in the input data.
+In these cases, the algorithm is able to deliver the reasonable exact percentages, which are always larger than 50\%.
+Note that models which have more compact representations (thus, small in their size) are desirable in many areas of natural sciences due to easier interpret-ability more than models represented by a more complex expression.
 \end{itemize}
@@
 \subsection{Statistical evaluation}
-
+\fxnote{Marko: came up to here!}
 In order to check the statistical significance of the obtained exact percentages and their differences between the studied approaches, we employed the statistical methodology comparing the results of  the 15 approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.

### 2022-11-05 doc/paper.tex
Update: added Abstract

@@
 	\begin{abstract}
-		  \fxnote{TODO}
+          This paper solves the well-known prominent problem of Symbolic regression.
+This problem have a wide range of applications.
+For example, the obtained SR models could serve as insight towards  establishing  physical theory behind, thus helping establishing reasonable hypotheses.
+Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology,  modeling analytic representations of the exciton binding energy in the energy science, and many applications in the material science.
+We propose a new meta-heuristic based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
+There are a several concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to determine suitable coefficients in the models (solutions);  ($iii$) a novel fitness function is utilized which combines accuracy score, error score, and the size of model into one, more balanced value.
+The experiments are conducted on two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} to 14 other competitors from the literature under different levels of noise in the input data.
+Our method obtains new best exact percentages on the both benchmark sets comparing to the literature approaches.
+Moreover, new unbiased randomly generated set of instances are introduced and scalability and robustness of our method is demonstrated on these instances in terms of various instance properties.
 	\end{abstract}
@@
     \item The exact percentage rate of \textsc{Rils}--\textsc{Rols} algorithm  slightly decrease as the expected number of variables gets larger when no noise is presented in the data.
-    \item The exact percentages drop off with the presence of a larger noise level. Thus, the higher the noise level, the smaller the exact percentages are. \fxnote{Marko: came up to here!}
+    \item The exact percentages drop off with the presence of a larger noise level. Thus, the higher the noise level, the smaller the exact percentages are.
     \item Interestingly, in the presence of noise, the highest exact percentages are not obtained on the problem instances whose exact models consists of a single variable, but two or three.
@@
 \subsection{Statistical evaluation}
-\fxnote{Marko: came up to here!}
-In order to check the statistical significance of the obtained exact percentages and their differences between the studied approaches, we employed the statistical methodology comparing the results of  the 15 approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+
+In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of  the 15 approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+Note that in this case the exact percentage of each problem instance is given w.r.t.\  10 separately executed runs on that instance.
+
  Initially, Friedman’s test was separately executed for all competitor approaches.
-In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the results of the competitor approaches) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
+In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
 The outcome is represented by means of critical difference (CD) plots.
@@
 \begin{itemize}
-	\item  Concerning instance problems where for the input data no noise is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of   exact percentage rate.
+	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of   exact percentage rate.
 The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
@@
 However, these two approaches perform statistically significantly better than the third best (according the the average raking), that is with \textsc{Apf-Fe}.
-This conclusion also holds for the remaining approaches.
-	\item    Concerning instance problems where for the input data a (white) noise of 0.001 is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of the exact percentage rate.
+This conclusion also holds for the remaining approaches, which are performing statistically significantly weaker than  \textsc{Rils}-\textsc{Rols} method.
+	\item    Concerning the instance problems with the included level of noise of 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.
 The second best ranking is achieved by \textsc{Afp-Fe} algorithm.
 However,  there is no statistically significant difference between these two approaches.
-The third best according approach is \textsc{Afp}, which perform statistically equal to \textsc{Afp-Fe}, but statistically worse that our \textsc{Rils}-\textsc{Rols} method.
+The third best approach is \textsc{Afp}, which perform statistically equal to \textsc{Afp-Fe}, but statistically significantly worse that our \textsc{Rils}-\textsc{Rols} method.
 For all remaining methods, the later conclusion also holds.
-	\item   Concerning instance problems where for the input data a (white) noise of 0.01 is included, again, \textsc{Rils-Rols} reaches the best average ranking; the second best approach is \textsc{gplearn}.
-The difference between the exact percentages delivered by these two approaches is significant in favor of \textsc{Rils-Rols} approach.
-This is also the case when \textsc{Rils-Rols} is compared to all the remaining approaches.
+	\item   Concerning the instance problems in the presence of the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking; the second best approach is \textsc{gplearn}.
+The difference between the exact percentages delivered by these two approaches is statistically significant in favor of \textsc{Rils-Rols} approach.
+This also holds when \textsc{Rils-Rols} is compared to all the remaining approaches.
 
@@
 \section{Conclusions and future work}\label{sec:conclusions}
+
   This paper deals with solving the well--known Symbolic regression (SR)  problem.
@@
 We proposed a meta-heuristic approach, called \textsc{Rils}-\textsc{Rols}.
-It is based on the Iterative local search (ILS) scheme.
-The first crucial concept within this scheme is utilizing the oridinary least square method to efficiently determine coefficients in the candidate solutions.
-Another key aspect is the use of a carefully constructed fitness function, which is a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).
-Last but not least, the neighbor of solution in the local search is carefully defined that suits to small modifications of a three that represents solutions (models).
-\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from literature on the two ground truth benchmark sets from literature.
-Additionally, we introduced a non-biased benchmark set of randomly generated instances.
-The experimental evaluation confirmed efficiently of out method which was able to produce the best average ranking in terms of exact percentage in comparison to all other competitors on all ground-truth instances, and in presence of three different levels of noise in the input data.
-In all cases, new best average-percentages are obtained in the literature by means of \textsc{Rils-Rols} method.
+Our approach is based on the Iterated local search (ILS) scheme.
+The first crucial concept within this scheme is utilizing the oridinary least square method to efficiently determine internal coefficients of the candidate solutions,  partially.
+Another key aspect is the use of a carefully constructed fitness function, which appears as  a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).
+Last but not least, the neighbor of solution in the local search is carefully chosen that suits to small modifications of a three representing solutions (models).
+\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
+Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.
+The experimental evaluation confirmed efficiently of our method which was able to produce the best average ranking results in terms of exact percentage wh comparison to all other competitors on the two ground-truth benchmark sets, in presence of the three different levels of noise in the input data.
+In all cases, new best exact percentages are obtained by means of \textsc{Rils-Rols} method.
 In some cases, these differences are statistically significant in favor of our \textsc{Rils-Rols} method.
-Moreover, scalability and robustness of our method is  checked and confirmed on the randomly generated instances in terms of a few different criteria such as the size of model, the number of variables, average runtimes, etc.
+Moreover, scalability and robustness of this method is  checked and confirmed on unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of model, the number of variables, average runtimes, etc.
 \fxnote{TODO: case-study about large-scale data to be added}
 
-  In the future work, one could think of  make a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics, or replacing ILS scheme of \textsc{Rils-Rils} with, for example, Variable neighborhood search meta-heuristic.
-Additionally, as a proof of the concept, our tool will be provided to various research communities out of the are of Computer science, such as the ones from physics ot chemistry to seek for new hypotheses or o obtain insights on their experimental data.
+  In the future work, one could think of constructing a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics.
+Replacing ILS scheme of \textsc{Rils-Rils} with, a general scheme Variable neighborhood search meta-heuristic is a reasonable option to try out.
+Additionally, as a proof of the efficiency of our algorithm, our tool should be provided to various research communities out of the are of Computer science, such as the ones from physics or chemistry to help for  seeking new hypotheses or to obtain valuable insights on their experimental evaluations.
 
@@
  \section{Overview of RILS-ROLS python package}\label{sec:appendix-1}
+  \fxnote{TODO}
 

### 2022-11-06 doc/paper.tex
Conclusions and Abstract revised

@@
 	\begin{abstract}
-          This paper solves the well-known prominent problem of Symbolic regression.
-This problem have a wide range of applications.
-For example, the obtained SR models could serve as insight towards  establishing  physical theory behind, thus helping establishing reasonable hypotheses.
-Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology,  modeling analytic representations of the exciton binding energy in the energy science, and many applications in the material science.
+          In this paper we solve the well-known, prominent problem of Symbolic regression, intensively studied over the last two decades.
+This problem have a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards  establishing  physical theory behind, thus helping establishing reasonable hypotheses.
+Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology,  modeling analytic representations of the exciton binding energy in the energy science, finding models for band gap of NaCl-type compounds
+         in material science, just to name a few.
 We propose a new meta-heuristic based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
-There are a several concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to determine suitable coefficients in the models (solutions);  ($iii$) a novel fitness function is utilized which combines accuracy score, error score, and the size of model into one, more balanced value.
-The experiments are conducted on two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} to 14 other competitors from the literature under different levels of noise in the input data.
+There are a several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to fit the coefficients in models (solutions);  ($iii$) a novel fitness function is utilized which combines an accuracy score, error score, and the size of model into one, more compact score.
+The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} to 14 other competitors from the literature considering different levels of noise in the input data.
 Our method obtains new best exact percentages on the both benchmark sets comparing to the literature approaches.
-Moreover, new unbiased randomly generated set of instances are introduced and scalability and robustness of our method is demonstrated on these instances in terms of various instance properties.
+Moreover, new unbiased randomly generated set of problem instances are introduced where scalability and robustness of our method is thoroughly demonstrated in terms of various instance properties.
 	\end{abstract}
@@
 
-  This paper deals with solving the well--known Symbolic regression (SR)  problem.
-This problem is a generalization of more interdisciplinary appearing  linear and logistic regression problems.
-SR problem have been intensively studied in the literature over the last 15 years, where a few dozens of algorithms were constructed, mainly based on Genetic programming and on the application of different kinds of neural networks.
+  In this paper we dealt with solving the well--known Symbolic regression (SR)  problem.
+SR problem is a generalization of more interdisciplinary appearing  linear and logistic regression problems.
+%SR problem have been intensively studied in the literature over the last 15 years, where a few dozens of algorithms were constructed, mainly based on Genetic programming and on the application of different kinds of neural networks.
    We proposed a meta-heuristic approach, called \textsc{Rils}-\textsc{Rols}.
-Our approach is based on the Iterated local search (ILS) scheme.
-The first crucial concept within this scheme is utilizing the oridinary least square method to efficiently determine internal coefficients of the candidate solutions,  partially.
-Another key aspect is the use of a carefully constructed fitness function, which appears as  a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).
-Last but not least, the neighbor of solution in the local search is carefully chosen that suits to small modifications of a three representing solutions (models).
+Our approach is built upon   the Iterated local search (ILS) scheme.
+The first crucial concept within this scheme is utilizing the ordinary least square method to efficiently determine internal coefficients that fit the candidate solution,  thus in this way  the search process is focused on considering more promising solutions.
+Another key aspect is the utilization of a carefully constructed fitness function, which appears as  a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).
+Last but not least, a carefully constructed local search is applied systematically exploring solutions obtained as 1--perturbations of the considered solution.
+1--perturbations of a solution are based on applying the six per-node change operations on the solution's tree representation.
+
     \textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
 Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.
-The experimental evaluation confirmed efficiently of our method which was able to produce the best average ranking results in terms of exact percentage wh comparison to all other competitors on the two ground-truth benchmark sets, in presence of the three different levels of noise in the input data.
+The experimental evaluation confirmed efficiently of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmark sets, in presence of all three different levels of noise in the input data.
 In all cases, new best exact percentages are obtained by means of \textsc{Rils-Rols} method.
 In some cases, these differences are  statistically significant in favor of our \textsc{Rils-Rols} method.
-Moreover, scalability and robustness of this method is  checked and confirmed on unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of model, the number of variables, average runtimes, etc.
-\fxnote{TODO: case-study about large-scale data to be added}
-
-  In the future work, one could think of constructing a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics.
-Replacing ILS scheme of \textsc{Rils-Rils} with, a general scheme Variable neighborhood search meta-heuristic is a reasonable option to try out.
-Additionally, as a proof of the efficiency of our algorithm, our tool should be provided to various research communities out of the are of Computer science, such as the ones from physics or chemistry to help for  seeking new hypotheses or to obtain valuable insights on their experimental evaluations.
+Moreover, scalability and robustness of this method is  checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of model, the number of variables in exact models, and average runtimes.
+
+  In the future work, one could think of constructing a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics to further boost quality of the  obtained results.
+For example, replacing ILS scheme of \textsc{Rils-Rils} with  a more general Variable neighborhood search (VNS) scheme is a reasonable option to try out.
+VNS   utilizes more stronger and systematic system of solutions diversification  and thus   escaping from local optima could be much easier.
+Additionally, as a proof of efficiency and benefits of our algorithm, this tool could  be applied to solving problems from various problem domains out of the areas of computer science, for example from physics or chemistry, to help for setting up hypotheses or to obtain valuable insights on   experimental evaluations.
 

### 2022-11-06 doc/paper.tex
Introduction: pocetak revidiranja

@@
 	\begin{abstract}
-          In this paper we solve the well-known, prominent problem of Symbolic regression, intensively studied over the last two decades.
-This problem have a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards  establishing  physical theory behind, thus helping establishing reasonable hypotheses.
-Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology,  modeling analytic representations of the exciton binding energy in the energy science, finding models for band gap of NaCl-type compounds
+          In this paper, we solve the well-known, prominent problem of Symbolic regression, intensively studied within the last two decades.
+This problem has a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards establishing physical theory behind, thus helping establish reasonable hypotheses.
+Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modelling analytic representations of the exciton binding energy in energy science, and finding models for band gaps of NaCl-type compounds
           in material science, just to name a few.
-We propose a new meta-heuristic based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
-There are a several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to fit the coefficients in models (solutions);  ($iii$) a novel fitness function is utilized which combines an accuracy score, error score, and the size of model into one, more compact score.
+We propose a new meta-heuristic-based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
+There are several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to fit the coefficients in models (solutions);  ($iii$) a novel fitness function is utilized which combines an accuracy score, error score, and the size of the model into one, more compact score.
 The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} to 14 other competitors from the literature considering different levels of noise in the input data.
-Our method obtains new best exact percentages on the both benchmark sets comparing to the literature approaches.
-Moreover, new unbiased randomly generated set of problem instances are introduced where scalability and robustness of our method is thoroughly demonstrated in terms of various instance properties.
+Our method obtains new best exact percentages on both benchmark sets compared to the literature approaches.
+Moreover, a new unbiased randomly generated set of problem instances are introduced where the scalability and robustness of our method are thoroughly demonstrated in terms of various instance properties.
 	\end{abstract}
@@
 	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade to study it intensively.
-SR can be seen as a generalization of the well known  concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}.
-All regression models in principle have the same task: given a set of a $n$-dimensional input data and the output data, the aim is to find a  mathematical expression (function) consisting of $n$ (input) variables that fits to the output data w.r.t.
+SR can be seen as a generalization of the well-known concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}.
+All regression models in principle have the same task: given a set of $n$-dimensional input data and the output data, the aim is to find a  mathematical expression (function) consisting of $n$ (input) variables that fit the output data w.r.t.
 some in advance known measure.
@@
 However, when there are some nonlinear relations between variables, which are relevant, linear regression models are not enough.
-This is the point where symbolic regression comes into the play.
-Unlike linear regression, it allows the search over the space of all possible mathematical formulas in order to find the best fitting ones able to  predict the output variable from the input variables.
-The base of constructing the explicit formula are the basis operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.
+This is the point where symbolic regression comes into play.
+Unlike linear regression, it allows the search over the space of all possible mathematical formulas to find the best-fitting ones able to predict the output variable from the input variables.
+The basis of constructing the explicit formula is the basic operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.
+\fxnote{Marko: došao dovde sa ovom sekcijom}
 	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef

### 2022-11-06 paper_resources/doc/paper.tex
Introduction: update

--- 2022-11-06 doc/paper.tex
@@
 The basis of constructing the explicit formula is the basic operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.
-\fxnote{Marko: došao dovde sa ovom sekcijom}
 	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef
 
-	 Concrete examples of application of SR include having a less black--box tool, as it may say much more how SR model achieve predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others.
-Moreover, in that way we may grasp why the variables are related in the obtained way.
-As an example, appearance of an exponential function may associate  to  some physical phenomenon such as intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}.
-Additionally, the SR models, if they are correct, may have    posses  larger extrapolation power than other mathematical models, and especially than neural network--based methods.
-SR models may maximize obtaining physically more reasonable equations that could serve as insight towards  establishing  physical theory behind as the final goal.
+	Concrete examples of the application of SR include having a less black--box tool, as it may say more about how the SR model achieves predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others.
+Moreover, in that way, we may grasp why the variables are related in the obtained way.
+As an example, the appearance of an exponential function may associate with some physical phenomenon such as the intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}.
+Additionally, the SR models, if they are correct, may possess larger extrapolation power than other mathematical models, especially better from the neural network--based methods.
+SR models may maximize obtaining physically more reasonable equations that could serve as an insight towards establishing physical theory behind as the final goal.
 Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}.
 In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities is presented there.
-Applications of SR to discovering physical laws from distorted video is studied in~\cite{udrescu2021symbolic} by means of a unsupervised learning method.
+The application of SR to discovering physical laws from a distorted video is studied in~\cite{udrescu2021symbolic} by means of an unsupervised learning method.
 Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}, tackled by a machine learning method.
-Application of SR to model the mutations effects on protein  stability, in the domain of fundamental and applied biology,  is shown in~\cite{louis2021reviewing}.
+Application of SR to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology,  is shown in~\cite{louis2021reviewing}.
 One of the recent work studies of auto-discovering conserved quantities using trajectory data from unknown dynamical systems, where SR is solved by a machine learning algorithm, see~\cite{liu2021machine}.
@@
 Yet another application to wind speed forecasting is given in~\cite{abdellaoui2021symbolic}.
+
+	\fxnote{Marko: došao dovde sa ovom sekcijom}
 

### 2022-11-07 paper_resources/doc/paper.tex
Section 1: polishing

@@
 	% first the title is needed
-	\title{RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
+	\title{\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
 
@@
 
-	Concrete examples of the application of SR include having a less black--box tool, as it may say more about how the SR model achieves predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others.
+	Concrete examples of the application of SR include obtaining a less black--box tool, as it may say more about how SR models achieve predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others.
 Moreover, in that way, we may grasp why the variables are related in the obtained way.
@@
 Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}.
-In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities is presented there.
+In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities can be found there.
 The application of SR to discovering physical laws from a distorted video is studied in~\cite{udrescu2021symbolic} by means of an unsupervised learning method.
@@
 One of the recent work studies of auto-discovering conserved quantities using trajectory data from unknown dynamical systems, where SR is solved by a machine learning algorithm, see~\cite{liu2021machine}.
-Last but not least, we mention the paper~\cite{liang2019phillips} discovers the application of  SR to model analytic representations of the exciton binding energy.
+Last but not least, we mention the paper~\cite{liang2019phillips} which discovers the application of SR to model analytic representations of the exciton binding energy.
 The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
@@
 
-	\fxnote{Marko: došao dovde sa ovom sekcijom}
-
-	There are many different ways to tackle the SR by achieving the right analytic expressions, most of them are related to machine learning techniques or to the technique of genetic programming (GP) and various approximate methods, such as meta-heuristics.
+	There are many different ways to tackle the SR by achieving the right analytic expressions, most of them are related to machine learning techniques or the technique of genetic programming (GP) and various approximate methods, such as meta-heuristics.
 Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
@@
 Age-fitness Pareto Optimization approach is proposed by Smidt and Lipson~\cite{schmidt2010age}.
-Application of artificial bee colony programming to solve SR is proposed by Karaboga et al.~\cite{karaboga2012artificial}.
-	Influence of local--based heuristics on solving SR is reported by Commenda in his Ph.D.
-thesis~\cite{kommenda2018local}.
-A  GP-based approach, the gene-pool optimal mixing evolutionary algorithm (GOMEA) is studied by Virgolin et al.~\cite{virgolin2021improving}.
-Another evolutionary algorithm, the interaction-transformation EA (Itea) has been proposed by de Franca et al.~\cite{de2021interaction}.
+Application of the artificial bee colony programming to solve SR is proposed by Karaboga et al.~\cite{karaboga2012artificial}.
+	The influence of local--based heuristics on solving SR is reported by Commenda in his PhD thesis~\cite{kommenda2018local}.
+A  GP-based approach, the gene-pool optimal mixing evolutionary algorithm (\textsc{Gomea}) is studied by Virgolin et al.~\cite{virgolin2021improving}.
+Another evolutionary algorithm, the interaction-transformation EA (\textsc{Itea}) has been proposed by de Franca et al.~\cite{de2021interaction}.
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
-A Variable neighborhood programming approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
-	Kommenda et al.~\cite{kommenda2020parameter} proposed a method called OPERON algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in
-	tree-based GP.
-The C++ implementation of OPERON is discussed in~\cite{burlacu2020operon}.
-The method that uses Taylor polynomial to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+A Variable neighbourhood programming approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
+	Kommenda et al.~\cite{kommenda2020parameter} proposed a method called \textsc{Operon} algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in tree-based GP.
+The C++ implementation of \textsc{Operon} is discussed in~\cite{burlacu2020operon}.
+The method that utilizes the Taylor polynomials to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
 A GP approach that uses the idea of semantic back-propagation (Sbp-Gp) is proposed in~\cite{virgolin2019linear}.
 Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
-It is also worth to mention the GP--based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization  with co-evolved fitness estimation.
-This solver is nowadays accepted for the gold standard of symbolic regression.
-
-	Machine learning--based method   based on Bayesian symbolic regression (Bsr) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms.
-Deep Symbolic Regression (Dsr), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
+It is also worth mentioning the GP--based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization with co-evolved fitness estimation.
+This solver is nowadays accepted as the gold standard of symbolic regression.
+
+	Machine learning--based method based on Bayesian symbolic regression (\textsc{Bsr}) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms.
+Deep Symbolic Regression (\textsc{Dsr}), an RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
 This mechanism of search is further investigated in~\cite{landajuela2021improving}.
-A fast neural network approach, called OccamNet,  is proposed in~\cite{costa2020fast}.
+A fast neural network approach, called \textsc{OccamNet},  is proposed in~\cite{costa2020fast}.
 A deep reinforcement learning approach enhanced with genetic programming is given in~\cite{mundhenk2021symbolic}.
 
-	Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the Eplex solver from~\cite{la2019probabilistic,la2016epsilon} and AI Feynman algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method that  combines neural network
-	fitting.
-The later one is one of the most efficient method for physically inspired models.
-We also mention the Fast Function Extraction (Ffx) algorithm developed by McConaghy~\cite{mcconaghy2011ffx},  a non-evolutionary method in combination with a machine learning technique---path-wise regularized learning--- which   quickly prune a huge set of candidate basis functions down to compact models.
-
-	A short chronological overview of the most important  literature methods to solve SR are given in Table~\ref{tab:gp-based}.
+    Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the \textsc{Eplex} solver from~\cite{la2019probabilistic,la2016epsilon} and AI Feynman algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method combined with the neural network fitting.
+The latter is one of the most efficient methods for physically inspired models.
+We also mention the Fast Function Extraction (\textsc{Ffx}) algorithm developed by McConaghy~\cite{mcconaghy2011ffx},  which is a non-evolutionary method   combined with a machine learning technique---path-wise regularized learning--- which prunes quickly a huge set of candidate basis functions down to compact models.
+
+	A short overview of the most important literature methods to solve SR is given in Table~\ref{tab:gp-based} in the chronological order of their appearances.
 
@@
    The progress in the SR field suffered from a lack of uniform, robust, and transparent
-	benchmarking standards over the last two decade. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
+	benchmarking standards over the last two decades. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
 	open-source, reproducible benchmarking platform for SR, called SRBench.
-The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression, by 130 SR datasets for which model forms are known; see more in the aforementioned paper.
+The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression problems, by 130 SR datasets for which model forms are known; see more in the aforementioned paper.
 In the extensive experimental evaluation  where 14
-	symbolic regression methods and 7 machine learning methods are compared on the  set of 252 diverse
-	regression problems.
-The general conclusions derived from there are: ($i$) when comes to real-world problem, the best performing algorithms are those which combine genetic algorithm with parameter estimation; ($ii$) when come to the instances with the presence of noise, the GP--based and deep learning techniques are performing similarly.
-
-	In this work we present a novel approach to solve SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated} with ordinary least squares method (OLS)~\cite{leng2007ordinary}.
-Briefly, ILS handles combinatorial (discrete) aspects of search space, while OLS helps in the process of coefficient determination, so it handles continuous parts of the search space.
-As will be shown later, the proposed method seems to be very robust w.r.t.
-introduced noise, therefore we called the method RILS-ROLS (with letters R corresponding to regression and robust).
-\fxnote{TODO: maybe expand the core of the algorithm...
-}
+	symbolic regression methods and 7 machine learning methods are compared on the set of 252 diverse regression problems.
+The general conclusions derived from there are: ($i$) when comes to real-world problems, the best performing algorithms are those which combine genetic algorithm with a parameter estimation; ($ii$) when comes to the instances with a presence of noise, the GP--based and deep learning techniques are performing similarly.
+
+	In this work we present a novel approach to solve SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated} with the ordinary least square  method (OLS)~\cite{leng2007ordinary}.
+Briefly, ILS handles combinatorial (discrete) aspects of search space, while OLS helps in the process of a coefficient determination, so it handles continuous parts of the search space.
+As will be shown later, the proposed method has shown its robustness w.r.t.
+introduced noise, therefore we called the method \textsc{Rils}-\textsc{Rols}  (with letters R corresponding to regression and robust).
+Additionally, in order to navigate the search towards not only accurate models, but increasing the chances to get the exact one, the algorithms is equipped with a carefully constructed fitness function that utilizes three important scores of a solution (model): RMSE and $R^2$ scores which participate into models accuracy, and a weighted solution size that will contribute penalizing large (mostly non-exact) solutions.
 
@@
 	\begin{enumerate}
-		\item The proposed method outperforms all state-of-the-art methods for ground-truth problems from literature, considered in the SRBench benchmark.
-
-		\item It shows high robustness, which is proved by comparison to other algorithms under different levels of Gaussian white noise.
-
-		\item The method is very efficient, taking in average around xyz seconds to reach exact solution -- when exact solution is found.
-
-		\item The new set of unbiased instances is also introduced -- randomly generated formula of various sizes and number of input variables.
-This set was employed to understand the influence of formula size, number of input variables and noise on the solving difficulty.
+		\item The proposed method outperforms all (14) state-of-the-art methods for ground-truth problems from literature, considered in the SRBench benchmark.
+
+		\item The method shows its high robustness, which is proved by comparison to other algorithms under different levels of Gaussian white noise.
+
+		\item The method is very efficient, taking in average around xyz seconds to reach exact solution -- when exact solution is found. \fxnote{Ovo treba dodati u eksp. sekciji...}
+
+		\item New set of unbiased instances is   introduced that are randomly generated formula of various sizes and number of input variables in exact models.
+This set was employed to methodologically analyze the influence of formula size, number of input variables and noise on the solving difficulty.
 	\end{enumerate}
@@
 	\label{sec:search-space}
-	In this section we formally define the SR problem, followed by defining the search space framework of the problem.
+	In this section we formally define the SR problem, followed by defining the search space framework of the problem. \fxnote{Marko: došao dovde sa ovom sekcijom}
 
@@
 	\section{The proposed method}\label{sec:rils}
-	Before we give details on our RILS-ROLS method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm. These are ILS meta-heuristic and OLS methods.
+	Before we give details on our \textsc{Rils}-\textsc{Rols}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm.
+These are ILS meta-heuristic and OLS methods.
 
@@
 
-	The most popular version of ILS is shown in Algorithm~\ref{alg:ils}. Note that we use this version of ILS as the backbone of our RILS-ROLS algorithm.
+	The most popular version of ILS is shown in Algorithm~\ref{alg:ils}. Note that we use this version of ILS as the backbone of our \textsc{Rils}-\textsc{Rols}  algorithm.
 
@@
 Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
-\subsection{RILS-ROLS method}
-Now we will explain the proposed RILS-ROLS method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
+\subsection{\textsc{Rils}-\textsc{Rols}  method}
+Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
 
@@
 	\begin{algorithmic}[1] 
-		\Procedure{RILS-ROLS}{$D_{tr}$}
+		\Procedure{\textsc{Rils}-\textsc{Rols} }{$D_{tr}$}
 		\State $n_{tr} \gets |D_{tr}|$
@@
 	\end{algorithmic}
-	\caption{RILS-ROLS method.}
+	\caption{\textsc{Rils}-\textsc{Rols}  method.}
 	\label{alg:rilsrols}
@@
 
-RILS-ROLS algorithms receives training dataset $D_{tr}$ as input.
+\textsc{Rils}-\textsc{Rols}  algorithms receives training dataset $D_{tr}$ as input.
 In addition, it has two control parameters: $penalty_{size}$ and $tolerance_{error}$.
@@
 The second parameter is related to the expected noise level in data -- higher noise means that tolerance to errors should be higher.
-$D_{tr}$ can have very large number of records, so the first step of RILS-ROLS is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
+$D_{tr}$ can have very large number of records, so the first step of \textsc{Rils}-\textsc{Rols}  is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
 Initial the sample size is calculated as $\max(0.01 \cdot n_{tr}, 100)$.
@@
 
-Before returning the final symbolical model, RILS-ROLS peforms the final symbolical simplification and rounding of model coefficients.
+Before returning the final symbolical model, \textsc{Rils}-\textsc{Rols}  peforms the final symbolical simplification and rounding of model coefficients.
 The later is sensitive to control parameter $tolerance_{error}$ -- smaller value means information loss during rounding is smaller, i.e.
@@
 This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
-The search process of RILS-ROLS is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
+The search process of \textsc{Rils}-\textsc{Rols}  is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
 
@@
 
-\section{Overview of RILS-ROLS python package}\label{sec:appendix-1}
+\section{Overview of \textsc{Rils}-\textsc{Rols}  python package}\label{sec:appendix-1}
 \fxnote{TODO}

### 2022-11-07 paper_resources/doc/paper.tex
Section 2: proofread

@@
 	\label{sec:search-space}
-	In this section we formally define the SR problem, followed by defining the search space framework of the problem. \fxnote{Marko: došao dovde sa ovom sekcijom}
+	In this section we formally define the SR problem, followed by defining the search space framework of the problem.
 
@@
 Suppose that there exists an analytical model of the form $f(\textbf{x})= g^*(\textbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.
-		The goal of SR is to learn a mapping $\tilde{f}(\textbf{x})=  \tilde{g}(\textbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the presented  white noise using given input data.
+		The goal of SR is to learn a mapping $\tilde{f}(\textbf{x})=  \tilde{g}(\textbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the presented  white noise within the given input data.
 
@@
 That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree.
-How accurate is this mapping, we compute in the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).
+How accurate is this mapping, we compute on the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).
 Interestingly, the search space of SR consists of its discrete and continuous part.
@@
 For the most physical models, these coefficients may receive any real value, that is they are continuous in its nature.
-
-	\fxnote{TODO: needs for extension...}
 
@@
 	\section{The proposed method}\label{sec:rils}
+		\fxnote{TODO: needs for extension...}
 	Before we give details on our \textsc{Rils}-\textsc{Rols}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm.

### 2022-11-07 paper_resources/doc/paper.tex
Section 3: start to polish

@@
 	\section{The proposed method}\label{sec:rils}
-		\fxnote{TODO: needs for extension...}
+
 	Before we give details on our \textsc{Rils}-\textsc{Rols}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm.
@@
 First, the current incumbent solution is perturbed -- it is partially randomized.
-Next, the perturbed solution is improved with LS procedure.
+Next, the perturbed solution is improved by a LS procedure.
 Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion.
@@
 %For example, in order to calculate coefficient $k_i$, the following system of equations is
-\fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor.
+%\fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor.
 Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
 \subsection{\textsc{Rils}-\textsc{Rols}  method}
-Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
+Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.  \fxnote{Marko: došao dovde!}
 

### 2022-11-07 paper_resources/doc/paper.tex
Update in Section 3.2

@@
 	%  \end{align*}
-By solving this system of $(d+1)$ equations, one can obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$.
+By solving the above system of $(d+1)$ equations, one can obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$.
 %For example, in order to calculate coefficient $k_i$, the following system of equations is
@@
 \subsection{\textsc{Rils}-\textsc{Rols}  method}
-Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.  \fxnote{Marko: došao dovde!}
+Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
 
@@
 $D_{tr}$ can have very large number of records, so the first step of \textsc{Rils}-\textsc{Rols}  is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
-Initial the sample size is calculated as $\max(0.01 \cdot n_{tr}, 100)$.
+Initial the sample size is chosen as $\max(0.01 \cdot n_{tr}, 100)$.
 The size of sample is later dynamically adjusted through the algorithm's iterations -- when there are no solution improvements for some number of iterations, the sample size is doubled (lines~\ref{line:sampleAdj1}-\ref{line:sampleAdj2} of Algorithm~\ref{alg:rilsrols}).
@@
 As previously stated, solution is usually represented by means of a tree.
-We use simple solution initialization -- tree root node is set to zero constant.
+We use a simple solution initialization -- tree root node is set to zero constant.
 We interchangeably use two solution variables: ($i$) $s$ denotes starting (or working) solution and ($ii$) $bs$ stands for the best solution so far.
@@
 w.r.t.
-the $R^2$ and $RMSE$ of the best solution.
+its $R^2$ and $RMSE$ scores.
 More precisely, if $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
@@
 Candidate perturbations are being improved by performing OLS coefficient fitting (procedure \texttt{FitOLS}).
-This means that coefficients in any of linear combinations of current solution are being set by means of ordinary least squares method, described in Section~\ref{sec:ols}.
+This means that coefficients in any of linear combinations of current solution are being set by applying  ordinary least square method, already described in Section~\ref{sec:ols}.
 After this step, perturbations are usually better suited to given sample data $D_{tr}'$. 
@@
 But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}) after which the local search is performed (line~\ref{line:ls}).
-Solution simplification is done in a symbolical fashion by popular Python library called SymPy~\cite{sympy}.
-Local search tries to find local optima expressions close to the given $p$ -- explained in details in Section~\ref{sec:ls}.  
-Finally, fitness function value of $p$ is compared to fitness function value of $bs$.
-If a new incumbent is found, $bs$ is updated correspondingly and internal loop that goes across ordered perturbations is immediately terminated (it works in a  \emph{first-improvement} strategy).
+Solution simplification is done in a symbolical fashion by popular \texttt{SymPy} Python package~\cite{sympy}.
+Local search tries to find local optima expressions close to the given $p$ -- explained in detail in Section~\ref{sec:ls}.  
+Finally, the fitness function value of $p$ is compared to the fitness function value of $bs$.
+If a new incumbent is found, $bs$ is updated correspondingly and the internal loop that goes across ordered perturbations is immediately terminated (it works in a  \emph{first-improvement} strategy).
 Otherwise, the next perturbation is probed.
@@
 The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}), i.e.
-this structure serves as a kind of tabu list, initially proposed in the famous Tablu search algorithm, see~\cite{glover1998tabu}.
+$perturbations_{tried}$ serves as a kind of tabu list, initially proposed in the known Tablu search algorithm, see~\cite{glover1998tabu}.
+\fxnote{Marko: došao dovde!}
 

### 2022-11-08 paper_resources/doc/paper.tex
Update in Section 3.2

@@
 		\State $s' \gets $ \texttt{RandomPick}($start_{candidates}$)  \label{line:pert21}
-		\State $start_{candidates} \gets $ \texttt{All1Perturbations}($s'$) \label{line:pert22}
+		\State $start_{candidates} \gets $ \texttt{All1Perturbations}($s'$) \label{line:pert22} // 2-permutations of \textit{bs}
 		\EndIf
@@
 The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}), i.e.
-$perturbations_{tried}$ serves as a kind of tabu list, initially proposed in the known Tablu search algorithm, see~\cite{glover1998tabu}.
-\fxnote{Marko: došao dovde!}
+$perturbations_{tried}$ serves as a kind of tabu list, which is known from the Tablu search meta-heuristic, see~\cite{glover1998tabu}.
 
@@
 Otherwise, it makes no sense to set starting solution to $bs$, as nothing changed -- the search is being  \emph{trapped} in a local optimum.
-In order to avoid this undesired situation, a randomness needs to be triggered.
+In order to avoid this undesired situation, randomness needs to be triggered.
 First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{All1Perturbations}).
 If at least one of these was not previously used as a starting solution ($start_{tried}$), a single perturbation from the $start_{candidates} \setminus start_{tried}$ is randomly picked (line~\ref{line:randPick}).
-There is a insignificant chance that $start_{candidates} \setminus start_{tried} = \emptyset$.
+There is a minor chance that $start_{candidates} \setminus start_{tried} = \emptyset$.
 When that happens, the set of starting solution candidates is equal to perturbations of some randomly selected perturbation of $bs$ (lines \ref{line:pert21}-\ref{line:pert22}) -- which effectively means that the perturbations with distance 2 from $bs$ are used.
-Indeed, there is a minor chance that these 2-perturbations will have empty set difference with $start_{tried}$ set of starting solutions.
-Therefore, more expensive 3-perturbations are not considered in our algorithm.
-
-Before returning the final symbolical model, \textsc{Rils}-\textsc{Rols}  peforms the final symbolical simplification and rounding of model coefficients.
-The later is sensitive to control parameter $tolerance_{error}$ -- smaller value means information loss during rounding is smaller, i.e.
-higher number of significant digits is preserved.
+Indeed, there is almost no chance that these 2-perturbations will have an empty set difference with $start_{tried}$ set of starting solutions.
+Therefore, more expensive 3-perturbations will not be considered in our algorithm.
+
+Before returning the final symbolical model, \textsc{Rils}-\textsc{Rols}  performs the final symbolical simplification and rounding of model coefficients.
+The latter is sensitive to control parameter $tolerance_{error}$ -- a smaller value means the information loss during rounding is smaller, i.e.
+a higher number of significant digits is preserved.
 Note that confidence in the symbolical model is reduced when expected noise in data is higher -- the rule of thumb is: for higher expected noise $tolerance_{error}$ should be higher.
@@
 \subsubsection{Fitness function}\label{sec:fitness}
-
+\fxnote{Marko: stigao do ovog dijela...}
 Symbolic regression objective is to determine the expression governing available data.

### 2022-11-08 paper_resources/doc/paper.tex
Chapetr 3: polished

@@
 \subsubsection{Fitness function}\label{sec:fitness}
-\fxnote{Marko: stigao do ovog dijela...}
-Symbolic regression objective is to determine the expression governing available data.
+
+Symbolic regression objective is to determine the expression fitting available data.
 It is also allowed to obtain some equivalent expression, keeping in mind that there are multiple ways to express some symbolical equation.
@@
 The most popular are the coefficient of determination, also known as $R^2$ and mean squared error (MSE) or root mean squared error (RMSE).
-The important aspect of the solution quality might also be the solution expression complexity.
+The important aspect of the solution quality might also be the solution expression complexity, which may correspond to the model size of its tree representation.
 This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
@@
 	\item lower RMSE is preferred, ideally, when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
-	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle); therefore, we award solutions that are more simple with its representation.
+	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle); therefore, we award those solutions with a more simple representation. 
 \end{itemize}
@@
 Perturbations are generated by making simple changes on the per-node level of $s$ expression tree.
-Depending on the structure of the expression tree (expression does not have to have unique tree representation), the set of subtrees of the previous expression $(x+y^3)\cdot x/\sqrt{y}$ might be $\{(x+y^3)\cdot x/\sqrt{y}, (x+y^3), x/\sqrt{y}, x, y^3, \sqrt{y}, y\}$.
-This set of subtrees is obtained if left subtree of the whole expression is $(x+y^3)$ while the right one is $x/\sqrt{y}$.
-For each subtree $n$, the set of perturbations around $n$ is generated (lines \ref{line:forSSStart}-\ref{line:forSSEnd} of Algorithm~\ref{alg:pert}).
-
-Algorithm~\ref{alg:pertNode} shows how perturbations around given subtree (node) are generated.
+Depending on the structure of the expression tree (note that expression does not have to have unique tree representation), the set of subtrees of the previous expression $(x+y^3)\cdot x/\sqrt{y}$ might be $\{(x+y^3)\cdot x/\sqrt{y}, (x+y^3), x/\sqrt{y}, x, y^3, \sqrt{y}, y\}$.
+%This set of subtrees is obtained if left subtree of the whole expression is $(x+y^3)$ while the right one is $x/\sqrt{y}$.
+For each subtree $n$, the set of perturbations around $n$ is generated (lines \ref{line:forSSStart}-\ref{line:forSSEnd} in Algorithm~\ref{alg:pert}).
+
+Algorithm~\ref{alg:pertNode} shows how perturbations around given subtree are generated.
 
@@
 
+ \fxnote{Marko: stigao do ovog dijela...}
+
 \section{Experimental evaluation}\label{sec:experiments}
@@
 
-	\begin{table}
+	\begin{table}[!ht]
 		\centering

### 2022-11-08 paper_resources/doc/paper.tex
minor fix

@@
 
-\subsection{Comparison with other methods on real--world benchark sets}
+\subsection{Comparison with other methods on the   ground--truth benchmark sets}
 In this section, we evaluate the performance of \textsc{Rils-Rols} algorithm and compare it to the 14 other competitors from the literature.

### 2022-11-08 paper_resources/doc/paper.tex
Abstract additinally revised

@@
 We propose a new meta-heuristic-based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
-There are several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to fit the coefficients in models (solutions);  ($iii$) a novel fitness function is utilized which combines an accuracy score, error score, and the size of the model into one, more compact score.
-The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} to 14 other competitors from the literature considering different levels of noise in the input data.
-Our method obtains new best exact percentages on both benchmark sets compared to the literature approaches.
-Moreover, a new unbiased randomly generated set of problem instances are introduced where the scalability and robustness of our method are thoroughly demonstrated in terms of various instance properties.
+There are several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to   determine the best--fitting   coefficients in considered models (solutions);  ($iii$) a novel fitness function is utilized which combines an accuracy score, error score, and the weighted size of the model into one, more compact score.
+The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} algorithm to 14 other competitors from the literature considering different levels of noise in the input data.
+Our method obtains new best exact percentages on both benchmark sets compared to other literature approaches.
+Moreover, a new unbiased randomly generated set of problem instances are introduced where the scalability of our method is thoroughly demonstrated in terms of various instance properties.
 	\end{abstract}

### 2022-11-09 paper_resources/doc/paper.tex
Results were wrong on the SRBEnch site!!!

@@
 		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		\textsc{Rils-Rols}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
-		\textsc{AI-Feynman} &55.78&27.14&52.69&78.51&35.71&73.9\\
-		\textsc{Gomea} &26.83&29.46&27.12&71.55&71.43&71.54\\
-		\textsc{Afp-Fe} &26.98&20&26.23&59.05&28.57&55.77\\
-		\textsc{Itea}&22.41&7.14&20.77&27.59&21.43&26.93\\
-		\textsc{Afp}&21.12&15.18&20.48&44.83&25&42.69\\
-		\textsc{Dsr}&19.72&19.64&19.71&25&14.29&23.85\\
-		\textsc{Operon}&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
-		\textsc{gplearn}&16.27&8.93&15.48&32.76&7.14&30\\
-		\textsc{Sbp-Gp}&12.72&11.61&12.6&73.71&78.57&74.23\\
-		\textsc{Eplex}  &12.39&8.93&12.02&46.98&21.43&44.23\\
-		\textsc{Bsr}&2.48&0.89&2.31&10.78&21.43&11.93\\
-		\textsc{Feat}&0&0.89&0.1&39.66&42.86&40\\
-		\textsc{Ffx}&0&0&0&0&0&0\\
-		\textsc{Mrgp}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
+		RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
+		AIFeynman&55.78&27.14&52.65&78.51&35.71&73.83\\
+		GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
+		AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
+		ITEA&22.41&7.14&20.77&27.59&21.43&26.92\\
+		AFP&21.12&15.18&20.48&44.83&25&42.69\\
+		DSR&19.72&19.64&19.71&25&14.29&23.85\\
+		Operon&16.55&11.43&16&86.21&\bf{92.86}&86.92\\
+		gplearn&16.27&8.93&15.48&32.76&7.14&30\\
+		SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
+		EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
+		BSR&2.48&0.89&2.31&10.78&21.43&11.92\\
+		FEAT&0&0.89&0.1&39.66&42.86&40\\
+		FFX&0&0&0&0&0&0\\
+		MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
 		\hline
@@
 		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		\textsc{Rils-Rols}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
-		\textsc{Dsr}&16.81&18.75&17.02&26.29&14.29&25\\
-		\textsc{gplearn}&15.84&8.93&15.1&24.14&7.14&22.31\\
-		\textsc{Afp-Fe}&15.95&6.43&14.92&57.76&28.57&54.62\\
-		\textsc{Afp}&14.87&7.14&14.04&44.83&25&42.69\\
-		\textsc{Eplex} &10.02&2.68&9.23&48.71&21.43&45.77\\
-		\textsc{AI-Feynman}&1.49&13.73&2.81&9.73&35.71&12.53\\
-		\textsc{Itea}&1.94&4.46&2.21&26.72&21.43&26.15\\
-		\textsc{Gomea}&1.62&0.89&1.54&72.84&71.43&72.69\\
-		\textsc{Operon}&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
-		\textsc{Ffx}&0.11&0&0.1&19.4&14.29&18.85\\
-		\textsc{Feat}&0&0.89&0.1&13.79&50&17.69\\
-		\textsc{Sbp-Gp}&0&0&0&62.07&53.57&61.15\\
-		\textsc{Bsr}&0&0&0&7.76&14.29&8.46\\
-		\textsc{Mrgp}&0&0&0&0.86&17.86&2.69\\
+		RILS-ROLS&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
+		AIFeynman&33.08&22.14&31.89&77.39&42.86&73.64\\
+		AFP\_FE&21.9&15.71&21.23&52.16&35.71&50.38\\
+		DSR&19.14&19.29&19.15&25.86&14.29&24.62\\
+		AFP&19.66&13.57&19&44.4&21.43&41.92\\
+		gplearn&16.99&9.29&16.16&31.9&7.14&29.23\\
+		ITEA&14.57&7.14&13.77&27.59&21.43&26.92\\
+		Operon&13.19&5&12.31&85.78&\bf{92.86}&86.54\\
+		GP-GOMEA&11.03&7.14&10.62&70.26&71.43&70.38\\
+		EPLEX&9.57&9.29&9.54&47.84&25&45.38\\
+		SBP-GP&0.78&0&0.69&75.43&64.29&74.23\\
+		BSR&0.6&0.71&0.62&10.34&14.29&10.77\\
+		FFX&0&0&0&0&0&0\\
+		FEAT&0&0&0&42.24&50&43.08\\
+		MRGP&0&0&0&\bf{92.24}&85.71&\bf{91.54}\\
 		\hline
@@
 		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		\textsc{Rils-Rols}&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
-		\textsc{gplearn}&13.21&8.93&12.75&14.22&7.14&13.46\\
-		\textsc{Dsr}&8.41&16.07&9.23&17.24&14.29&16.92\\
-		\textsc{Eplex}&8.77&0&7.83&14.22&3.57&13.07\\
-		\textsc{Afp}&7.11&0.89&6.44&8.19&7.14&8.08\\
-		\textsc{Afp-Fe}&6.12&3.57&5.85&5.6&0&5\\
-		\textsc{Itea}&0.11&0.89&0.19&1.72&10.71&2.69\\
-		\textsc{AI-Feynman}&0&0.79&0.09&0&0&0\\
-		\textsc{Operon}&0.09&0&0.08&0&0&0\\
-		\textsc{Gomea}&0&0&0&0&0&0\\
-		\textsc{Sbp-Gp}&0&0&0&0&0&0\\
-		\textsc{Bsr}&0&0&0&0&0&0\\
-		\textsc{Feat}&0&0&0&0&14.29&1.54\\
-		\textsc{Ffx}&0&0&0&0&0&0\\
-		\textsc{Mrgp}&0&0&0&0&0&0\\
+		RILS-ROLS&\bf{36.29}&\bf{22.14}&\bf{34.77}&64.91&46.43&62.92\\
+		AFP\_FE&20.78&13.57&20&52.59&32.14&50.38\\
+		DSR&18.97&18.57&18.92&26.29&14.29&25\\
+		AFP&16.9&11.43&16.31&42.67&21.43&40.38\\
+		gplearn&16.87&9.29&16.05&29.13&10.71&27.13\\
+		AIFeynman&13.03&9.29&12.61&71.43&39.29&67.86\\
+		EPLEX&8.71&4.29&8.23&56.03&21.43&52.31\\
+		ITEA&7.84&6.43&7.69&27.59&21.43&26.92\\
+		GP-GOMEA&5.09&1.43&4.69&73.71&71.43&73.46\\
+		Operon&2.07&0.71&1.92&85.78&\bf{92.86}&86.54\\
+		BSR&0.09&0&0.08&12.07&10.71&11.92\\
+		SBP-GP&0&0&0&75&75&75\\
+		FEAT&0&0&0&40.52&42.86&40.77\\
+		FFX&0&0&0&2.59&3.57&2.69\\
+		MRGP&0&0&0&\bf{91.81}&60.71&\bf{88.46}\\
 		\hline

### 2022-11-09 paper_resources/doc/paper.tex
Results revisions.

--- 2022-11-08 paper_resources/doc/paper.tex
@@
 Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.
-Among them, 115 regression problem instances are chosen in the experimental evaluation, with accordance to~\cite{la2021contemporary}.
+Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to~\cite{la2021contemporary}.
 
@@
 \begin{itemize}
-	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{Rils}--\textsc{Rols}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
+	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{Rils-Rols}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
 The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all problem instances from benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
 All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered ground-truth benchmark sets.
-	\item   Concerning the exact results in presence of the target noise with a level of 0.001, our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model for more than 42\% cases considering the problem instances from the both benchmark sets.
-Interestingly, \textsc{AI-Feynman} is quite sensible w.r.t.\ the increase of the target noise level, as its performances rapidly going down -- it is successful on just 2.81\% of the all problem instances.
-Better from \textsc{AI-Feynman} are in this case the \textsc{Dsr}, \textsc{Gplearn}, and \textsc{Afp-Fe} order decreasingly w.r.t.\ the exact percentages of success, ranging from $\approx$15--17\%.
-	\item  Concerning the exact results when the presence of noise is large, that is with a level of 0.01,  our \textsc{Rils}--\textsc{Rols} is still performing reasonably well, having found an exact model for  34.77\% problem instances from the two benchmark sets.
-The second best performing is \textsc{Gplearn} which exact percentage of success is just 12.75\%, followed by \textsc{Dsr} which is successful for just 9.23\% problem instances.
-% over all problem instances.
-
-	\item When comparing performances of the algorithms in terms of number of instances for which the algorithm's termination led to an accurate model, that is $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{Rils}-\textsc{Rols} is successful with the rate of success of 83.38\%.
-However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than our algorithm: \textsc{Mrgp}, and \textsc{Operon}, with 92.69\%, and 86.93\%, respectively.
-On the other hand, as the  exact model percentage rates of these two approaches are rather low (0\% and 16\%, respectively) these indicate the presence of a high level over-fitting  of the later two algorithms.
-Thus, they are able to obtain a model that is accurate enough on the training data, but most of the produced models are in essence wrong.
-
-	\item  When comparing the performances of the competitors in terms of number of instances for which the  termination led to an accurate enough model, in the presence of the noise level of 0.001, our \textsc{Rils}--\textsc{Rols} method has 78.62\% of a success rate, concerning all considered instances.
-The \textsc{Operon} solver is the only one that returns a better percentage of success among the competitors, which is 83.08\%.
-However, the over-fitting is conspicuous as this algorithm is rarely able to obtain the model which matches to the exact one (its exact percentage is equal to 0.31\%).
-
-	\item   When comparing performances of the competitors in terms of number of instances where the termination lead to obtaining an accurate model, in the presence of the high--level noise of 0.01, our \textsc{Rils}--\textsc{Rols} method is still highly accurate, delivering  62.92\% of a success rate.
-Interestingly, it is the best performing in terms of the percentage rate among other competitors.
-Just for  the information, the second best approach is \textsc{Dsr}, with 16.92\% of the success rate.
-It can be concluded that our \textsc{Rils}--\textsc{Rols} method does not pay a big price in presence of a higher noise, like the other methods which are very sensible w.r.t.
-the noise increase.
-Our \textsc{Rils}--\textsc{Rols} method still delivers high-accuracy models for the noisy input data, but also many of them fit to the exact solutions (models).
+	\item   Concerning the exact results in presence of the target noise with a level of 0.001, our \textsc{Rils-Rols} is still performing very-well, having found an exact model for 42.08\% cases considering the problem instances from the both benchmark sets.
+The second best approach is \textsc{AI-Feynman} solving in total 31.89\% cases, as before, being better when used on \textsc{Feynman} instances than on \textsc{Strogatz}.
+Approache \textsc{AFP\_FE} shows to be robust w.r.t.
+noise so its performances only slightly deteriorate in comparison to the no-noise scenario.
+This puts it on the third place with overall accuracy of 21.23\%.
+Other approaches reach accuracy bellow 20\%.
+	\item  Concerning the exact results when the presence of noise is large, that is with a level of 0.01,  our \textsc{Rils-Rols} is still performing robustly, having found an exact model for  34.77\% problem instances from the two benchmark sets.
+The second best is now \textsc{AFT\_FE} reaching 20\% correct solutions.
+\textsc{AI-Feynman} performances are degraded significantly under this level of noise, so it is ranked only 6th overall.
+
+	\item When comparing performances of the algorithms in terms of number of instances for which the model has $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{Rils}-\textsc{Rols} is successful with the rate of success of 83.38\% (third place).
+However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than our algorithm: \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
+On the other hand, the exact model percentages of these two approaches are rather low (0\% and 16\%, respectively).
+These two algorithms are therefore more appropriate in scenarios when the underlying (ground-truth) model is unknown, so-called black-box regression.
+
+	\item  In the presence of the noise level of 0.001, our \textsc{Rils-Rols} method has 78.62\% of a success rate (third place).
+As before, \textsc{MRGP} and \textsc{Operon} are showing good performances.
+
+	\item   When noise is 0.01 the situation is almost the same, \textsc{MRGP} and \textsc{Operon} are the best and second best with 88.46\% and 86.54\% accuracy, respectively.
+\textsc{GP-GOMEA} now reaches third place with 73.46\%, while the proposed \textsc{RILS-ROLS} is fifth with 62.92\% $R^2$ accuracy.
 
 	\item Following the above conclusions, our \textsc{Rils}-\textsc{Rols} algorithm is more robust than the other competitors, which is confirmed by the produced results w.r.t.\ different levels of noise in the input data.
-Moreover, it can be considered as new state-of-the-art algorithm when one solves the problem of SR.
+Moreover, it can be considered as new state-of-the-art algorithm when one solves the problems of SR with known ground-truth models.
 
@@
 		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		\textsc{Rils-Rols}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
-		\textsc{AI-Feynman} &55.78&27.14&52.69&78.51&35.71&73.9\\
-		\textsc{Gomea} &26.83&29.46&27.12&71.55&71.43&71.54\\
-		\textsc{Afp-Fe} &26.98&20&26.23&59.05&28.57&55.77\\
-		\textsc{Itea}&22.41&7.14&20.77&27.59&21.43&26.93\\
-		\textsc{Afp}&21.12&15.18&20.48&44.83&25&42.69\\
-		\textsc{Dsr}&19.72&19.64&19.71&25&14.29&23.85\\
-		\textsc{Operon}&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
+		\textsc{RILS-ROLS}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
+		\textsc{AIFeynman}&55.78&27.14&52.65&78.51&35.71&73.83\\
+		\textsc{GP-GOMEA}&26.83&29.46&27.12&71.55&71.43&71.54\\
+		\textsc{AFP\_FE}&26.98&20&26.23&59.05&28.57&55.77\\
+		\textsc{ITEA}&22.41&7.14&20.77&27.59&21.43&26.92\\
+		\textsc{AFP}&21.12&15.18&20.48&44.83&25&42.69\\
+		\textsc{DSR}&19.72&19.64&19.71&25&14.29&23.85\\
+		\textsc{Operon}&16.55&11.43&16&86.21&\bf{92.86}&86.92\\
 		\textsc{gplearn}&16.27&8.93&15.48&32.76&7.14&30\\
-		\textsc{Sbp-Gp}&12.72&11.61&12.6&73.71&78.57&74.23\\
-		\textsc{Eplex}  &12.39&8.93&12.02&46.98&21.43&44.23\\
-		\textsc{Bsr}&2.48&0.89&2.31&10.78&21.43&11.93\\
-		\textsc{Feat}&0&0.89&0.1&39.66&42.86&40\\
-		\textsc{Ffx}&0&0&0&0&0&0\\
-		\textsc{Mrgp}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
+		\textsc{SBP-GP}&12.72&11.61&12.6&73.71&78.57&74.23\\
+		\textsc{EPLEX}&12.39&8.93&12.02&46.98&21.43&44.23\\
+		\textsc{BSR}&2.48&0.89&2.31&10.78&21.43&11.92\\
+		\textsc{FEAT}&0&0.89&0.1&39.66&42.86&40\\
+		\textsc{FFX}&0&0&0&0&0&0\\
+		\textsc{MRGP}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
 		\hline
@@
 		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		\textsc{Rils-Rols}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
-		\textsc{Dsr}&16.81&18.75&17.02&26.29&14.29&25\\
-		\textsc{gplearn}&15.84&8.93&15.1&24.14&7.14&22.31\\
-		\textsc{Afp-Fe}&15.95&6.43&14.92&57.76&28.57&54.62\\
-		\textsc{Afp}&14.87&7.14&14.04&44.83&25&42.69\\
-		\textsc{Eplex} &10.02&2.68&9.23&48.71&21.43&45.77\\
-		\textsc{AI-Feynman}&1.49&13.73&2.81&9.73&35.71&12.53\\
-		\textsc{Itea}&1.94&4.46&2.21&26.72&21.43&26.15\\
-		\textsc{Gomea}&1.62&0.89&1.54&72.84&71.43&72.69\\
-		\textsc{Operon}&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
-		\textsc{Ffx}&0.11&0&0.1&19.4&14.29&18.85\\
-		\textsc{Feat}&0&0.89&0.1&13.79&50&17.69\\
-		\textsc{Sbp-Gp}&0&0&0&62.07&53.57&61.15\\
-		\textsc{Bsr}&0&0&0&7.76&14.29&8.46\\
-		\textsc{Mrgp}&0&0&0&0.86&17.86&2.69\\
+		\textsc{RILS-ROLS}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
+		\textsc{AIFeynman}&33.08&22.14&31.89&77.39&42.86&73.64\\
+		\textsc{AFP\_FE}&21.9&15.71&21.23&52.16&35.71&50.38\\
+		\textsc{DSR}&19.14&19.29&19.15&25.86&14.29&24.62\\
+		\textsc{AFP}&19.66&13.57&19&44.4&21.43&41.92\\
+		\textsc{gplearn}&16.99&9.29&16.16&31.9&7.14&29.23\\
+		\textsc{ITEA}&14.57&7.14&13.77&27.59&21.43&26.92\\
+		\textsc{Operon}&13.19&5&12.31&85.78&\bf{92.86}&86.54\\
+		\textsc{GP-GOMEA}&11.03&7.14&10.62&70.26&71.43&70.38\\
+		\textsc{EPLEX}&9.57&9.29&9.54&47.84&25&45.38\\
+		\textsc{SBP-GP}&0.78&0&0.69&75.43&64.29&74.23\\
+		\textsc{BSR}&0.6&0.71&0.62&10.34&14.29&10.77\\
+		\textsc{FFX}&0&0&0&0&0&0\\
+		\textsc{FEAT}&0&0&0&42.24&50&43.08\\
+		\textsc{MRGP}&0&0&0&\bf{92.24}&85.71&\bf{91.54}\\
 		\hline
@@
 		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
-		\textsc{Rils-Rols}&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
-		\textsc{gplearn}&13.21&8.93&12.75&14.22&7.14&13.46\\
-		\textsc{Dsr}&8.41&16.07&9.23&17.24&14.29&16.92\\
-		\textsc{Eplex}&8.77&0&7.83&14.22&3.57&13.07\\
-		\textsc{Afp}&7.11&0.89&6.44&8.19&7.14&8.08\\
-		\textsc{Afp-Fe}&6.12&3.57&5.85&5.6&0&5\\
-		\textsc{Itea}&0.11&0.89&0.19&1.72&10.71&2.69\\
-		\textsc{AI-Feynman}&0&0.79&0.09&0&0&0\\
-		\textsc{Operon}&0.09&0&0.08&0&0&0\\
-		\textsc{Gomea}&0&0&0&0&0&0\\
-		\textsc{Sbp-Gp}&0&0&0&0&0&0\\
-		\textsc{Bsr}&0&0&0&0&0&0\\
-		\textsc{Feat}&0&0&0&0&14.29&1.54\\
-		\textsc{Ffx}&0&0&0&0&0&0\\
-		\textsc{Mrgp}&0&0&0&0&0&0\\
+		\textsc{RILS-ROLS}&\bf{36.29}&\bf{22.14}&\bf{34.77}&64.91&46.43&62.92\\
+		\textsc{AFP\_FE}&20.78&13.57&20&52.59&32.14&50.38\\
+		\textsc{DSR}&18.97&18.57&18.92&26.29&14.29&25\\
+		\textsc{AFP}&16.9&11.43&16.31&42.67&21.43&40.38\\
+		\textsc{gplearn}&16.87&9.29&16.05&29.13&10.71&27.13\\
+		\textsc{AIFeynman}&13.03&9.29&12.61&71.43&39.29&67.86\\
+		\textsc{EPLEX}&8.71&4.29&8.23&56.03&21.43&52.31\\
+		\textsc{ITEA}&7.84&6.43&7.69&27.59&21.43&26.92\\
+		\textsc{GP-GOMEA}&5.09&1.43&4.69&73.71&71.43&73.46\\
+		\textsc{Operon}&2.07&0.71&1.92&85.78&\bf{92.86}&86.54\\
+		\textsc{BSR}&0.09&0&0.08&12.07&10.71&11.92\\
+		\textsc{SBP-GP}&0&0&0&75&75&75\\
+		\textsc{FEAT}&0&0&0&40.52&42.86&40.77\\
+		\textsc{FFX}&0&0&0&2.59&3.57&2.69\\
+		\textsc{MRGP}&0&0&0&\bf{91.81}&60.71&\bf{88.46}\\
 		\hline

### 2022-11-10 paper_resources/doc/paper.tex
New CD plots generated

@@
 
+%time-avg-noise0.0.eps
+
+\begin{figure}[!ht]
+
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.0.eps}
+		\caption{No noise}
+		\label{fig:noNoise-time}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+
+		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.001.eps}
+		\caption{Level of noise equal to 0.001}
+		\label{fig:noise0.001-time}
+	\end{subfigure}
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.01.eps}
+		\caption{Level of noise equal to 0.01.}
+		\label{fig:noise0.01-time}
+	\end{subfigure}
+	\caption{Average runtimes on the instance problems where the exact solution has  been reached (considered only those algorithms whose the exact percentage is at least 5\% of all runs).}
+	\label{fig:time-avg-exact-noise}
+\end{figure}
+
+In Figure~\ref{fig:time-avg-exact-noise}, average runtimes of the algorithms on those instance problems from the both ground-truth benchmarks for which the exact model has  been found are compared.
+Those algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant here and therefore included into comparisons.
+The results are grouped varying different (three) levels of noise, each presented by a plot, where the algorithms are labelled on $x$-axis, while their average runtimes are shown on $y$-axis.
+The following conclusions are drawn from here.
+
+\begin{itemize}
+	\item \fxnote{TODO...}
+\end{itemize}
+
 \subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}
@@
 The following conclusions may be drawn from there.
+\fxnote{Marko: update of the content needed.}
 

### 2022-11-10 paper_resources/doc/paper.tex
Runtime analysis: described

@@
 Those algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant here and therefore included into comparisons.
-The results are grouped varying different (three) levels of noise, each presented by a plot, where the algorithms are labelled on $x$-axis, while their average runtimes are shown on $y$-axis.
+The results are grouped varying different (three) levels of noise, each presented by a plot, where the algorithms are labelled on $x$-axis, while respective average runtimes are shown on $y$-axis.
+Note that $y$-axis is logarithmically scaled.
 The following conclusions are drawn from here.
@@
 \begin{itemize}
-	\item \fxnote{TODO...}
+	\item When considering the instance problems where no noise is detected, the lowest average runtime  is reported for \textsc{Rils}-\textsc{Rols} algorithm (228$s$).
+A slightly worse runtime is obtained by \textsc{Dsr} algorithm (232$s$).
+However, note that the exact percentage of \textsc{Rils}--\textsc{Rols} is far better from \textsc{Dsr} (60.62\% vs.
+19.71\%).
+	All remaining approaches deliver an order of magnitude larger average runtimes that that of the \textsc{Rils}--\textsc{Rols} method.
+	\item  When considering the instance problems where a noise level of 0.001 is included,    the lowest average runtime  is again obtained by \textsc{Rils}-\textsc{Rols} algorithm (108$s$).
+The second best average runtime is obtained by \textsc{Dsr}, but this time significantly worse (622$s$) from the former algorithm.
+	\item When considering the instance problems with a noise level of 0.01, a similar conclusion may be drawn as that from the previous point. 
 \end{itemize}

### 2022-11-10 paper_resources/doc/paper.tex
CD plots: description updated

@@
 
-\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}
+\subsection{Statistical evaluation}
+
+In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{Rils}--\textsc{Rols} to 14 other approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+Note that the exact percentage of each problem instance that comes into the statistical observation is given as the average of  10 separately executed runs for that instance.
+
+Initially, Friedman’s test was separately executed for all competitor approaches.
+In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
+The outcome is represented by means of critical difference (CD) plots.
+In each CD plot, the (15) competitor approaches are placed on the horizontal axis according to their average ranking.
+Thereafter, the CD score is computed for a significance level of 0.05.
+If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.
+The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}.
+The following conclusions may be drawn from there.
+
+\begin{itemize}
+	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of   exact percentage rate.
+The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
+There is no statistically significant difference between these two approaches w.r.t.\ obtained exact percentages.
+However, these two approaches perform statistically significantly better than the third best approach according the the average raking, \textsc{Apf-Fe}.
+This conclusion also holds for the remaining approaches, which are performing statistically significantly worse than  \textsc{Rils}-\textsc{Rols} method.
+	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.
+The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
+However,  there is no statistically significant difference between these two approaches.
+The third best approach is \textsc{Afp-Fe} which perform statistically equal to \textsc{Afp} and \textsc{AI-Feynman}, but statistically significantly worse than our \textsc{Rils}-\textsc{Rols} method.
+For all remaining approaches,  \textsc{Rils}--\textsc{Rols} performs statistically better in terms of obtained exact percentages.
+	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking according to obtained exact percentages; the second best approach is \textsc{Afp-Fe} and \textsc{Afp}.
+These latter three approaches perform statistically equal.
+	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is tied to \textsc{gplearn}.
+The the exact percentages obtained by the latter two approaches are statistically worse than those of the \textsc{Rils}--\textsc{Rols} method.
+This also holds when \textsc{Rils-Rols} is compared to all   remaining approaches.
+
+\end{itemize}
+
+\begin{figure}[!ht]
+	\centering
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
+		\caption{No noise}
+		\label{fig:CDplots-no-noise}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.4\textwidth}
+
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_001.pdf}
+		\caption{Level of noise equal to 0.001}
+		\label{fig:CDplots-noise0.001}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.40\textwidth}
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
+		\caption{Level of noise equal to 0.01.}
+		\label{fig:CDplots-noise0.01}
+	\end{subfigure}
+	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.}
+	\label{fig:cd-plots-exact-pcts}
+\end{figure}
+
+\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}\label{sec:scalability-rils-rols}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[!ht]
 
@@
 
-\subsection{Statistical evaluation}
-
-In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of  the 15 approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
-Note that in this case the exact percentage of each problem instance is given w.r.t.\  10 separately executed runs on that instance.
-
-Initially, Friedman’s test was separately executed for all competitor approaches.
-In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
-The outcome is represented by means of critical difference (CD) plots.
-In a CD plot, the competitor approaches are placed on the horizontal axis according to their average ranking.
-Thereafter, the CD score is computed for a significance level of 0.05.
-If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.
-The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}.
-The following conclusions may be drawn from there.
-\fxnote{Marko: update of the content needed.}
-
-\begin{itemize}
-	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of   exact percentage rate.
-The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
-There is no statistically significant difference between these two approaches.
-However, these two approaches perform statistically significantly better than the third best (according the the average raking), that is with \textsc{Apf-Fe}.
-This conclusion also holds for the remaining approaches, which are performing statistically significantly weaker than  \textsc{Rils}-\textsc{Rols} method.
-	\item    Concerning the instance problems with the included level of noise of 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.
-The second best ranking is achieved by \textsc{Afp-Fe} algorithm.
-However,  there is no statistically significant difference between these two approaches.
-The third best approach is \textsc{Afp}, which perform statistically equal to \textsc{Afp-Fe}, but statistically significantly worse that our \textsc{Rils}-\textsc{Rols} method.
-For all remaining methods, the later conclusion also holds.
-	\item   Concerning the instance problems in the presence of the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking; the second best approach is \textsc{gplearn}.
-The difference between the exact percentages delivered by these two approaches is statistically significant in favor of \textsc{Rils-Rols} approach.
-This also holds when \textsc{Rils-Rols} is compared to all the remaining approaches.
-
-\end{itemize}
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
-		\caption{No noise}
-		\label{fig:CDplots-no-noise}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.4\textwidth}
-
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_001.pdf}
-		\caption{Level of noise equal to 0.001}
-		\label{fig:CDplots-noise0.001}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
-		\caption{Level of noise equal to 0.01.}
-		\label{fig:CDplots-noise0.01}
-	\end{subfigure}
-	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.}
-	\label{fig:cd-plots-exact-pcts}
-\end{figure}
-
 \section{Conclusions and future work}\label{sec:conclusions}

### 2022-11-10 paper_resources/doc/paper.tex
polish

@@
 	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
+		\includegraphics[  width=320pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
 		\caption{No noise}
@@
 		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
-		\caption{Level of noise equal to 0.01.}
+		\caption{Level of noise equal to 0.01.\fxnote{polish labels}}
 		\label{fig:CDplots-noise0.01}
 	\end{subfigure}
-	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.}
+	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise. \fxnote{Polish labels}}
 	\label{fig:cd-plots-exact-pcts}

### 2022-11-11 paper_resources/doc/paper.tex
Revisions: Abstract and Conclusions

@@
 	\begin{abstract}
-		In this paper, we solve the well-known, prominent problem of Symbolic regression, intensively studied within the last two decades.
-This problem has a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards establishing physical theory behind, thus helping establish reasonable hypotheses.
-Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modelling analytic representations of the exciton binding energy in energy science, and finding models for band gaps of NaCl-type compounds
+		In this paper, we solve the well-known, prominent  Symbolic regression problem, intensively studied within the last two decades.
+This problem has a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards establishing physical theory behind, thus helping to establish reasonable hypotheses.
+Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modelling analytic representations of the exciton binding energy in energy science,   finding models for band gaps of NaCl-type compounds
 		in material science, just to name a few.
 We propose a new meta-heuristic-based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
-There are several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used within the local search procedure to make it efficient and to   determine the best--fitting   coefficients in considered models (solutions);  ($iii$) a novel fitness function is utilized which combines an accuracy score, error score, and the weighted size of the model into one, more compact score.
-The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} algorithm to 14 other competitors from the literature considering different levels of noise in the input data.
-Our method obtains new best exact percentages on both benchmark sets compared to other literature approaches.
+There are several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used in the search to make it efficient with  determining the best--fitting   coefficients in considered solutions (models);  ($iii$) a novel fitness function is utilized which combines the three known measures: $R^2$ score, RMSE score, and the size of the model which is weighted by a parameter.
+The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} algorithm to 14 other competitors from the literature where different levels of the Gaussian white noise in the input data are utilized.
+Our method obtains new best exact percentages on both benchmark sets compared to other literature approaches regardless of varying the level of nose.
 Moreover, a new unbiased randomly generated set of problem instances are introduced where the scalability of our method is thoroughly demonstrated in terms of various instance properties.
@@
 
-In this paper we dealt with solving the well--known Symbolic regression (SR)  problem.
-SR problem is a generalization of more interdisciplinary appearing  linear and logistic regression problems.
-%SR problem have been intensively studied in the literature over the last 15 years, where a few dozens of algorithms were constructed, mainly based on Genetic programming and on the application of different kinds of neural networks.
+In this paper, we dealt with solving the well--known Symbolic regression (SR)  problem. SR problem is a generalization of more interdisciplinary known problems of linear and logistic regression.    
 We proposed a meta-heuristic approach, called \textsc{Rils}-\textsc{Rols}.
 Our approach is built upon the Iterated local search (ILS) scheme.
-The first crucial concept within this scheme is utilizing the ordinary least square method to efficiently determine internal coefficients that fit the candidate solution,  thus in this way  the search process is focused on considering more promising solutions.
-Another key aspect is the utilization of a carefully constructed fitness function, which appears as  a combination of three important scores: RMSE, $R^2$  scores and the size of model (solution).
+The first crucial concept within this scheme is utilizing the ordinary least square method to efficiently determine internal coefficients that are the best fitting to the candidate solution.
+Thus, the search process is primarily focused on considering already promising solutions in the continuous part of the search space rather than applying enhanced heuristics to search for those coefficients.
+Another key aspect is the utilization of a carefully constructed fitness function in the search, which appeared as a combination of three important scores: RMSE, $R^2$  scores and the size of the model (solution).
 Last but not least, a carefully constructed local search is applied systematically exploring solutions obtained as 1--perturbations of the considered solution.
@@
 
-\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
+\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from the literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
 Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.
-The experimental evaluation confirmed efficiently of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmark sets, in presence of all three different levels of noise in the input data.
-In all cases, new best exact percentages are obtained by means of \textsc{Rils-Rols} method.
-In some cases, these differences are  statistically significant in favor of our \textsc{Rils-Rols} method.
-Moreover, scalability and robustness of this method is  checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of model, the number of variables in exact models, and average runtimes.
-
-In the future work, one could think of constructing a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics to further boost quality of the  obtained results.
-For example, replacing ILS scheme of \textsc{Rils-Rils} with  a more general Variable neighborhood search (VNS) scheme is a reasonable option to try out.
-VNS   utilizes more stronger and systematic system of solutions diversification  and thus   escaping from local optima could be much easier.
-Additionally, as a proof of efficiency and benefits of our algorithm, this tool could  be applied to solving problems from various problem domains out of the areas of computer science, for example from physics or chemistry, to help for setting up hypotheses or to obtain valuable insights on   experimental evaluations.
+The experimental evaluation confirmed the efficiency of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmarks in the presence of all three different levels of noise in the input data.
+In all cases, new best exact percentages are obtained using \textsc{Rils-Rols} method.
+Moreover, the scalability and robustness of this method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
+
+In future work, one could think of constructing a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics to further boost the quality of the obtained results.
+For example, replacing ILS scheme of \textsc{Rils-Rils} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option to give it a try.
+VNS   utilizes a more stronger and systematic system of solutions diversification and thus escaping from local optima could be much easier.
+Additionally, as proof of the efficiency and benefits of our algorithm, this tool could be applied to solving problems from various problem domains out of the area of computer science, for example from physics or chemistry, to help for setting up hypotheses or to obtain valuable insights on experimental evaluations.
 

### 2022-11-11 paper_resources/doc/paper.tex
Update: conclusion

@@
 In all cases, new best exact percentages are obtained using \textsc{Rils-Rols} method.
-Moreover, the scalability and robustness of this method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
+More in details,
+our algorithm was able to obtain the right model on 60.62\%, 42.08\%, and 34.77\% problem instances in the presence of the noise level of 0.0, 0.001, and 0.01, respectively.
+Just for the shake of comparisons, the second best approach \textsc{AI-Feynman}, when the noise level of 0.0 and 0.001 is included, obtained an exact percentage rate of 52.65\%, and 31.89\%, respectively.
+In case of the highest noise level, the second best approach was \textsc{Afp-Fe}, obtaining an exact percentage rate of 20\%.
+Additionally, the scalability and robustness of this method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
 

### 2022-11-12 paper_resources/doc/paper.tex
New CD plots: per each run

@@
 In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{Rils}--\textsc{Rols} to 14 other approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
-Note that the exact percentage of each problem instance that comes into the statistical observation is given as the average of  10 separately executed runs for that instance.
+Note that an indicator random variable is involved per each run of the algorithms.
+Thus, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model within  considered run.
+Thus, we involved 1300 results into our statistical evaluation per each algorithm.
+Note that at some cases some of the 14 competitors are not known from \url{https://cavalab.org/srbench/results/} due to some reasons.
+For these cases, we simply count a 0 as the score.
 
 Initially, Friedman’s test was separately executed for all competitor approaches.
-In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
+In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained results of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
 The outcome is represented by means of critical difference (CD) plots.
@@
 The following conclusions may be drawn from there.
+\fxnote{Marko: update text}
 
@@
 	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=320pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
+		\includegraphics[  width=320pt,height=180pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
 		\caption{No noise}
@@
 
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_001.pdf}
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
 		\caption{Level of noise equal to 0.001}
@@
 	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
+		\includegraphics[  width=290pt,height=180pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
 		\caption{Level of noise equal to 0.01.\fxnote{polish labels}}

### 2022-11-13 paper_resources/doc/paper.tex
CD plots: description updated

@@
 The following conclusions may be drawn from there.
+
+\begin{itemize}
+	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of obtained exact models.
+The second best average ranking is achieved by \textsc{AI-Feynman} algorithm.
+There is  statistically significant difference between these two approaches w.r.t.\ number of found exact models.
+The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{Rils}-\textsc{Rols} w.r.t.\ delivered average raking.
+	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the found exact models.
+The second best ranking is obtained by \textsc{AI-Feynman} algorithm.
+There is again a statistically significant difference between the results obtained by these two approaches.
+The third best approach is \textsc{Afp-Fe} which perform statistically worse from \textsc{AI-Feynman}.
+	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} method produces the best average ranking according to obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \text{Dsr}, and \textsc{Afp}.
+These latter three approaches perform statistically equal, but significantly worse than \text{Rils}-\textsc{Rols} method.
+	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}.
+Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data.
+Thus, despite being efficient on no-noisy data, it seem that \textsc{AI-Feynman} is very sensitive to the noise, which is not that dramatically conspicuous with our \textsc{Rils}-\textsc{Rols} method.
+
 	 \fxnote{Marko: update text}
-
-\begin{itemize}
-	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of   exact percentage rate.
-The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
-There is no statistically significant difference between these two approaches w.r.t.\ obtained exact percentages.
-However, these two approaches perform statistically significantly better than the third best approach according the the average raking, \textsc{Apf-Fe}.
-This conclusion also holds for the remaining approaches, which are performing statistically significantly worse than  \textsc{Rils}-\textsc{Rols} method.
-	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.
-The second best ranking is achieved by \textsc{AI-Feynman} algorithm.
-However,  there is no statistically significant difference between these two approaches.
-The third best approach is \textsc{Afp-Fe} which perform statistically equal to \textsc{Afp} and \textsc{AI-Feynman}, but statistically significantly worse than our \textsc{Rils}-\textsc{Rols} method.
-For all remaining approaches,  \textsc{Rils}--\textsc{Rols} performs statistically better in terms of obtained exact percentages.
-	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking according to obtained exact percentages; the second best approach is \textsc{Afp-Fe} and \textsc{Afp}.
-These latter three approaches perform statistically equal.
-	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is tied to \textsc{gplearn}.
-The the exact percentages obtained by the latter two approaches are statistically worse than those of the \textsc{Rils}--\textsc{Rols} method.
-This also holds when \textsc{Rils-Rols} is compared to all   remaining approaches.
-
 \end{itemize}

### 2022-11-14 paper_resources/doc/paper.tex
Update...

@@
 	\begin{abstract}
-		In this paper, we solve the well-known, prominent  Symbolic regression problem, intensively studied within the last two decades.
+		In this paper, we solve the well-known, prominent  Symbolic regression problem, intensively studied in the literature within the last two decades.
 This problem has a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards establishing physical theory behind, thus helping to establish reasonable hypotheses.
@@
 		in material science, just to name a few.
-We propose a new meta-heuristic-based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve the problem of Symbolic regression.
-There are several key concepts utilized within this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used in the search to make it efficient with  determining the best--fitting   coefficients in considered solutions (models);  ($iii$) a novel fitness function is utilized which combines the three known measures: $R^2$ score, RMSE score, and the size of the model which is weighted by a parameter.
-The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} algorithm to 14 other competitors from the literature where different levels of the Gaussian white noise in the input data are utilized.
-Our method obtains new best exact percentages on both benchmark sets compared to other literature approaches regardless of varying the level of nose.
-Moreover, a new unbiased randomly generated set of problem instances are introduced where the scalability of our method is thoroughly demonstrated in terms of various instance properties.
+We propose a new meta-heuristic-based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve this problem.
+There are several key concepts utilized in this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used in the search to make it efficient by quickly determining the best--fitting   coefficients in considered solutions (models);  ($iii$) a novel fitness function is utilized which combines the three known measures: $R^2$ score, RMSE score, and the size of the model which is weighted by an internal parameter.
+The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} algorithm to 14 other competitors from the literature with the presence of different levels of the Gaussian white noise in the input data.
+Our method is able to obtain new best exact percentages on both benchmark sets compared to other literature approaches regardless of varying the level of nose.
+Moreover, the performance of \textsc{Rils}-\textsc{Rols} is less sensitive with the increase of the level of noise in the data, as it is the other approaches.
+		Additionally, a new unbiased randomly generated set of problem instances are introduced where the scalability of our method is thoroughly demonstrated in terms of various instance properties.
+\textsc{Rils}-\textsc{Rols} method can be considered as a new state-of-the-art method for solving the problem of Symbolic regression.
+%for the non blck box problem instances?
 	\end{abstract}
@@
 	\begin{enumerate}
-		\item The proposed method outperforms all (14) state-of-the-art methods for ground-truth problems from literature, considered in the SRBench benchmark.
-
-		\item The method shows its high robustness, which is proved by comparison to other algorithms under different levels of Gaussian white noise.
-
-		\item The method is very efficient, taking in average around xyz seconds to reach exact solution -- when exact solution is found. \fxnote{Ovo treba dodati u eksp. sekciji...}
-
-		\item New set of unbiased instances is   introduced that are randomly generated formula of various sizes and number of input variables in exact models.
-This set was employed to methodologically analyze the influence of formula size, number of input variables and noise on the solving difficulty.
+		\item The proposed method outperforms 14 state-of-the-art methods for the problem instances from the two ground-truth benchmark sets from literature, used in the benchmarking platform SRBench.
+
+		\item The method shows its high robustness, which is proved by its comparison to the other algorithms in presence of different levels of Gaussian white noise in the input data.
+
+		\item The method is very efficient, taking in average less than 3 minutes to reach the exact solution, on the problem instances where it was possible.
+For example, the second best approach in terms of the delivered exact percentage, \textsc{AI-Feynman}, needs significantly more time, which is around 45 minutes.
+
+		\item A new set of unbiased instances is introduced that consists of randomly generated formulae of various sizes and number of input variables presenting exact models that need to be found.
+This set was employed to analyze the effect of the model size, the number of input variables in the model and the level of noise on the solving difficulty.
 	\end{enumerate}
@@
 
-In order to check the statistical significance of the obtained exact percentages and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{Rils}--\textsc{Rols} to 14 other approaches on all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{Rils}--\textsc{Rols} to 14 other approaches over all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
 Note that an indicator random variable is involved per each run of the algorithms.
-Thus, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model within  considered run.
-Thus, we involved 1300 results into our statistical evaluation per each algorithm.
-Note that at some cases some of the 14 competitors are not known from \url{https://cavalab.org/srbench/results/} due to some reasons.
-For these cases, we simply count a 0 as the score.
+Thus, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model per each run.
+More precisely, we involved 1300 results into our statistical evaluation for each of the algorithms.
+Note that  results of some of the 14 competitors are not known from \url{https://cavalab.org/srbench/results/} due to some unknown reasons (most likely algorithm is terminated running out of memory or due to the chosen  value of an internal parameter).
+For these runs, we simply count a 0 for the score.
 
@@
 If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.
-The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}.
+Three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts} per each level of noise.
 The following conclusions may be drawn from there.
@@
 \begin{itemize}
-	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of obtained exact models.
+	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of the number of obtained exact models.
 The second best average ranking is achieved by \textsc{AI-Feynman} algorithm.
 There is  statistically significant difference between these two approaches w.r.t.\ number of found exact models.
-The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{Rils}-\textsc{Rols} w.r.t.\ delivered average raking.
-	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the found exact models.
+The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{Rils}-\textsc{Rols} w.r.t.\ delivered average ranking.
+	\item    Concerning the instance problems with the included  level of noise of 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the found exact models.
 The second best ranking is obtained by \textsc{AI-Feynman} algorithm.
 There is again a statistically significant difference between the results obtained by these two approaches.
-The third best approach is \textsc{Afp-Fe} which perform statistically worse from \textsc{AI-Feynman}.
-	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} method produces the best average ranking according to obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \text{Dsr}, and \textsc{Afp}.
+The third best approach is \textsc{Afp-Fe} which performs statistically worse than \textsc{AI-Feynman} approach.
+	\item  Concerning the instance problems with the included noise level of  0.01, again, \textsc{Rils-Rols} method produces the best average ranking according to positively evaluated runs, i.e.
+the runs with obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \textsc{Dsr}, and \textsc{Afp}.
 These latter three approaches perform statistically equal, but significantly worse than \text{Rils}-\textsc{Rols} method.
-	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}.
+	The fourth best approach according to delivered average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}.
 Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data.
-Thus, despite being efficient on no-noisy data, it seem that \textsc{AI-Feynman} is very sensitive to the noise, which is not that dramatically conspicuous with our \textsc{Rils}-\textsc{Rols} method.
-
-	 \fxnote{Marko: update text}
+Thus, despite being efficient on no-noisy data, it seems that \textsc{AI-Feynman} is very sensitive to the level of noise increase, which is not that dramatically conspicuous with our \textsc{Rils}-\textsc{Rols} method.
+
 \end{itemize}

### 2022-11-14 paper_resources/doc/paper.tex
Minor polishing

@@
 
-\section{Additional statistical analysis}\label{sec:appendix-2}
-
-\begin{figure}[H]
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_0acc.pdf}
-		\caption{No noise}
-		\label{fig:CDplotsR2-no-noise}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.4\textwidth}
-
-		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_001acc.pdf}
-		\caption{Level of noise equal to 0.001}
-		\label{fig:CDplotsR2-noise0.001}
-	\end{subfigure}
-	\centering
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_01acc.pdf}
-		\caption{Level of noise equal to 0.01.}
-		\label{fig:CDplotsR2-noise0.01}
-	\end{subfigure}
-	\caption{CD plots comparisons in terms of obtained $R^2$ score over all problem instances from both ground-truth benchmark sets,  varying levels of noise.}
-	\label{fig:cd-plotsR2-varying_noise}
-\end{figure}
+%\section{Additional statistical analysis}\label{sec:appendix-2}
+
+%\begin{figure}[H]
+%	\begin{subfigure}[b]{0.40\textwidth}
+%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_0acc.pdf}
+%		\caption{No noise}
+%		\label{fig:CDplotsR2-no-noise}
+%	\end{subfigure}
+%	\hfill
+%	\begin{subfigure}[b]{0.4\textwidth}
+%		
+%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_001acc.pdf}
+%		\caption{Level of noise equal to 0.001}
+%		\label{fig:CDplotsR2-noise0.001}
+%	\end{subfigure}
+%	\centering
+%	\begin{subfigure}[b]{0.40\textwidth}
+%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_01acc.pdf}
+%		\caption{Level of noise equal to 0.01.}
+%		\label{fig:CDplotsR2-noise0.01}
+%	\end{subfigure}
+%	\caption{CD plots comparisons in terms of obtained $R^2$ score over all problem instances from both ground-truth benchmark sets,  varying levels of noise.}
+%	\label{fig:cd-plotsR2-varying_noise}
+%\end{figure}
 

### 2022-11-14 paper_resources/doc/paper.tex
Finished revision of abstract and first section.

--- 2022-11-14 paper_resources/doc/paper.tex
@@
 	% first the title is needed
-	\title{\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
+	\title{\textsc{RILS}-\textsc{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
 
@@
 	\begin{abstract}
-		In this paper, we solve the well-known, prominent  Symbolic regression problem, intensively studied in the literature within the last two decades.
-This problem has a wide range of applications;  for example, the obtained SR models could serve theoretically, providing insight towards establishing physical theory behind, thus helping to establish reasonable hypotheses.
-Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modelling analytic representations of the exciton binding energy in energy science,   finding models for band gaps of NaCl-type compounds
+		In this paper, we solve the well-known symbolic regression problem.
+This problem has been intensively studied in the literature and has a wide range of applications.
+The symbolic regression models could provide insights towards establishing physical theory behind experimentally observed data.
+Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modeling analytic representations of the exciton binding energy in energy science, finding models for band gaps of NaCl-type compounds
 		in material science, just to name a few.
-We propose a new meta-heuristic-based approach, called \textsc{Rils}-\textsc{Rols} algorithm to solve this problem.
-There are several key concepts utilized in this algorithm: ($i$) Iterated local search scheme is used as the backbone; ($ii$) ordinary least square method is used in the search to make it efficient by quickly determining the best--fitting   coefficients in considered solutions (models);  ($iii$) a novel fitness function is utilized which combines the three known measures: $R^2$ score, RMSE score, and the size of the model which is weighted by an internal parameter.
-The experiments are conducted on the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz} comparing \textsc{Rils}-\textsc{Rols} algorithm to 14 other competitors from the literature with the presence of different levels of the Gaussian white noise in the input data.
-Our method is able to obtain new best exact percentages on both benchmark sets compared to other literature approaches regardless of varying the level of nose.
-Moreover, the performance of \textsc{Rils}-\textsc{Rols} is less sensitive with the increase of the level of noise in the data, as it is the other approaches.
-		Additionally, a new unbiased randomly generated set of problem instances are introduced where the scalability of our method is thoroughly demonstrated in terms of various instance properties.
-\textsc{Rils}-\textsc{Rols} method can be considered as a new state-of-the-art method for solving the problem of Symbolic regression.
-%for the non blck box problem instances?
+
+		We propose a new meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS} to solve this problem.
+\textsc{RILS}-\textsc{ROLS} is based on the following elements: ($i$) iterated local search is the method backbone, mainly solving combinatorial and some continuous aspects of the problem; ($ii$) ordinary least square method is focused on the continuous aspect of the search space -- it efficiently determines the best--fitting coefficients of linear combinations within solution equations;  ($iii$) a novel fitness function combines three important model quality measures: $R^2$ score, RMSE score, and the size of the model (or model complexity).
+
+		The experiments are conducted on the two well-known ground-truth benchmark sets called \textsc{Feynman} and \textsc{Strogatz}.
+\textsc{RILS}-\textsc{ROLS} was compared to 14 other competitors from the literature with  presence of different levels of the Gaussian white noise in the input data.
+Our method outperformed all 14 competitors with respect to the true symbolic model accuracy percentage under all level of noise.
+		In addition to evaluation on known ground-truth datasets, a new randomly generated set of problem instances is introduced.
+The goal of \textsc{Random} dataset was to test the scalability of our method with respect to incremental equation sizes and different levels of noise.
+\textsc{RILS}-\textsc{ROLS} can be considered as a new state-of-the-art method for solving the problem of symbolic regression when ground-truth equations are known.
 	\end{abstract}
@@
 
-	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade to study it intensively.
-SR can be seen as a generalization of the well-known concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}.
-All regression models in principle have the same task: given a set of $n$-dimensional input data and the output data, the aim is to find a  mathematical expression (function) consisting of $n$ (input) variables that fit the output data w.r.t.
-some in advance known measure.
-This computationally intensive task is in general provenly NP--hard~\cite{virgolin2022symbolic}.
-When aiming a model to be a linear combination of input variables, it represents the problem of linear regression.
-However, when there are some nonlinear relations between variables, which are relevant, linear regression models are not enough.
-This is the point where symbolic regression comes into play.
-Unlike linear regression, it allows the search over the space of all possible mathematical formulas to find the best-fitting ones able to predict the output variable from the input variables.
-The basis of constructing the explicit formula is the basic operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.
+	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade.
+SR can be seen as a generalization of more specific variants of regression in which the functional form is fixed, e.g.
+the well-known linear regression, polynomial regression~\cite{stimson1978interpreting}, etc.
+All regression models have the same goal: given a set of $n$-dimensional input data and its corresponding continuous output target variable, the aim is to find a  mathematical expression (function) of $n$ (input) variables that best \emph{fits} the target variable.
+%This computationally intensive task is in general provenly NP--hard~\cite{virgolin2022symbolic}.
+	In the case of linear regression, the model is always a linear combination of input variables.
+This is in general not good enough, since target variable might be dependent on some nonlinear function among input variables.
+Unlike linear regression, SR allows the search over much larger space of possible mathematical formulas to find the best-fitting ones, i.e.
+those able to predict the target variable from the input variables.
+The basis of constructing explicit formula is in elementary operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and others.
 	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef
 
-	Concrete examples of the application of SR include obtaining a less black--box tool, as it may say more about how SR models achieve predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others.
-Moreover, in that way, we may grasp why the variables are related in the obtained way.
-As an example, the appearance of an exponential function may associate with some physical phenomenon such as the intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}.
-Additionally, the SR models, if they are correct, may possess larger extrapolation power than other mathematical models, especially better from the neural network--based methods.
-SR models may maximize obtaining physically more reasonable equations that could serve as an insight towards establishing physical theory behind as the final goal.
+	SR models tend to be interpretable, unlike artificial neural networks.
+Coefficients inside SR formulas might indicate the absolute or relative importance of certain input variables.
+Moreover, relations among variables might be described in an elegant way.
+For example, the appearance of an exponential function can be associated with some physical phenomenon such as the intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}.
+Additionally, the SR models often have high generalization power unlike some models with fixed functional forms such as polynomial regression.
+
 	Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}.
-In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities can be found there.
-The application of SR to discovering physical laws from a distorted video is studied in~\cite{udrescu2021symbolic} by means of an unsupervised learning method.
-Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}, tackled by a machine learning method.
-Application of SR to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology,  is shown in~\cite{louis2021reviewing}.
-One of the recent work studies of auto-discovering conserved quantities using trajectory data from unknown dynamical systems, where SR is solved by a machine learning algorithm, see~\cite{liu2021machine}.
-Last but not least, we mention the paper~\cite{liang2019phillips} which discovers the application of SR to model analytic representations of the exciton binding energy.
-The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
-Yet another application to wind speed forecasting is given in~\cite{abdellaoui2021symbolic}.
-
-	There are many different ways to tackle the SR by achieving the right analytic expressions, most of them are related to machine learning techniques or the technique of genetic programming (GP) and various approximate methods, such as meta-heuristics.
+In particular, this paper describes the discovery of a series of new oxide perovskite catalysts with improved activities.
+The application of SR to discovering physical laws from a distorted video is studied in~\cite{udrescu2021symbolic}.
+Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}.
+Paper \cite{louis2021reviewing} shows how SR is used to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology.
+One recent study \cite{liu2021machine} is concerned of auto-discovering conserved quantities using trajectory data from unknown dynamical systems.
+Paper~\cite{liang2019phillips} shows the application of SR to model analytic representations of the exciton binding energy.
+The use of SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
+SR application to wind speed forecasting is given in~\cite{abdellaoui2021symbolic}.
+
+	There are many different ways to tackle the SR.
+Most of them are based on the machine learning techniques, genetic programming (GP) or some other meta-heuristics.
 Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
@@
 Application of the artificial bee colony programming to solve SR is proposed by Karaboga et al.~\cite{karaboga2012artificial}.
-	The influence of local--based heuristics on solving SR is reported by Commenda in his PhD thesis~\cite{kommenda2018local}.
-A  GP-based approach, the gene-pool optimal mixing evolutionary algorithm (\textsc{Gomea}) is studied by Virgolin et al.~\cite{virgolin2021improving}.
-Another evolutionary algorithm, the interaction-transformation EA (\textsc{Itea}) has been proposed by de Franca et al.~\cite{de2021interaction}.
+	Application of local-based heuristics for solving SR is reported by Commenda in his PhD thesis~\cite{kommenda2018local}.
+A GP-based approach, the gene-pool optimal mixing evolutionary algorithm (\textsc{GOMEA}) is studied by Virgolin et al.~\cite{virgolin2021improving}.
+Another evolutionary algorithm, the interaction-transformation EA (\textsc{ITEA}) has been proposed by de Franca et al.~\cite{de2021interaction}.
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
-A Variable neighbourhood programming approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
+A variable neighbourhood programming approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
 	Kommenda et al.~\cite{kommenda2020parameter} proposed a method called \textsc{Operon} algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in tree-based GP.
@@
 A GP approach that uses the idea of semantic back-propagation (Sbp-Gp) is proposed in~\cite{virgolin2019linear}.
-Empirical analysis of variance between many GP--based methods for SR is discussed in~\cite{kammerer2021empirical}.
-It is also worth mentioning the GP--based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization with co-evolved fitness estimation.
+Empirical analysis of variance between many GP-based methods for SR is discussed in~\cite{kammerer2021empirical}.
+It is also worth to mention the GP-based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization with co-evolved fitness estimation.
 This solver is nowadays accepted as the gold standard of symbolic regression.
 
-	Machine learning--based method based on Bayesian symbolic regression (\textsc{Bsr}) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms.
-Deep Symbolic Regression (\textsc{Dsr}), an RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search.
+	Method based on Bayesian symbolic regression (\textsc{BSR}) is proposed in~\cite{jin2019bayesian} -- this method belongs to a family of Markov Chain Monte Carlo algorithms (MCMC).
+Deep Symbolic Regression (\textsc{DSR}), an RNN approach, is proposed in~\cite{petersen2019deep} -- it utilizes the policy gradient search.
 This mechanism of search is further investigated in~\cite{landajuela2021improving}.
 A fast neural network approach, called \textsc{OccamNet},  is proposed in~\cite{costa2020fast}.
-A deep reinforcement learning approach enhanced with genetic programming is given in~\cite{mundhenk2021symbolic}.
-
-    Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the \textsc{Eplex} solver from~\cite{la2019probabilistic,la2016epsilon} and AI Feynman algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method combined with the neural network fitting.
-The latter is one of the most efficient methods for physically inspired models.
-We also mention the Fast Function Extraction (\textsc{Ffx}) algorithm developed by McConaghy~\cite{mcconaghy2011ffx},  which is a non-evolutionary method   combined with a machine learning technique---path-wise regularized learning--- which prunes quickly a huge set of candidate basis functions down to compact models.
-
-	A short overview of the most important literature methods to solve SR is given in Table~\ref{tab:gp-based} in the chronological order of their appearances.
-
-	\begin{table}[!ht]
+A deep reinforcement learning approach enhanced with genetic programming is proposed in~\cite{mundhenk2021symbolic}.
+
+    Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the \textsc{Eplex} solver from~\cite{la2019probabilistic,la2016epsilon} and \textsc{AI Feynman} algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method combined with the neural network fitting.
+The latter is one of the most efficient methods for physically-inspired models.
+We also mention the Fast Function Extraction (\textsc{FFX}) algorithm developed by McConaghy~\cite{mcconaghy2011ffx}, which is a non-evolutionary method combined with a machine learning technique called path-wise-regularized learning, which quickly prunes a huge set of candidate basis functions down to compact models.
+
+	A short overview of the most important literature methods to solve SR is given in Table~\ref{tab:gp-based}.
+
+	\begin{table}[!h]
 		\centering
@@
 				Algorithm          &   Paper/year &   Short details   \\ \hline
-				\textsc{Gp}        &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
-				\textsc{Hybrid-Gp}  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
-				\textsc{Dfe}        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
-				\textsc{Apf-Fe}                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
-				APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
-				\textsc{Ffx}  & \cite{mcconaghy2011ffx} (2011)  & The Fast Function Extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
-				\textsc{Abcp} &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
-				\textsc{Eplex}          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection  \\ 
-				\textsc{Mrgp} & \cite{arnaldo2014multiple} (2014) & It decouples and
+				\textsc{GP}        &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
+				\textsc{Hybrid-GP}  &   \cite{raidl1998hybrid} (1998)   & GP-based method; solutions are locally optimized with OLS to find optimum coefficients for top-level terms \\ 
+				\textsc{DFE}        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
+				\textsc{APF-FE}                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness Pareto optimization approach using co-evolved fitness estimation   \\
+				APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness Pareto optimization approach                        \\
+				\textsc{FFX}  & \cite{mcconaghy2011ffx} (2011)  & The fast function extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
+				\textsc{ABCP} &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
+				\textsc{EPLEX}          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$-lexicase selection  \\ 
+				\textsc{MRGP} & \cite{arnaldo2014multiple} (2014) & It decouples and
 				linearly combines a program's subexpressions via multiple regression on the target variable  \\
-				Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants Optimization in GP by Nonlinear Least Square \\
-				\textsc{Feat} & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees  comprised of activation functions; Differentiable features are trained via gradient descent \\
-				\textsc{Sbp-Gp} &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
-				\textsc{Bsr} & \cite{jin2019bayesian} (2019) & ML--based approach; Bayesian symbolic regression  \\ 
-				\textsc{Dsr}  & \cite{petersen2019deep} (2019) & Deep Symbolic Regression based on a RNN approach further utilizing the policy gradient search \\
+				Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants optimization in GP by nonlinear least squares \\
+				\textsc{FEAT} & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees comprised of activation functions; differentiable features are trained via gradient descent \\
+				\textsc{SBP-GP} &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
+				\textsc{BSR} & \cite{jin2019bayesian} (2019) & ML-based approach; Bayesian symbolic regression  \\ 
+				\textsc{DSR}  & \cite{petersen2019deep} (2019) & Deep symbolic regression based on a RNN approach further utilizing the policy gradient search \\
 				\textsc{Operon} & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
-				\textsc{Vnp}    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
+				\textsc{VNP}    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
 				\textsc{OccamNet} & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\
 
-				\textsc{AI-Feynman} & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it  combines neural network fitting \\
-				\textsc{Gomea}  & \cite{virgolin2021improving} (2021)    & A model-based
-				EA framework called Gene-pool optimal mixing evolutionary algorithm \\
-				\textsc{Itea} & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
-				\textsc{Sa} & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
-
-				\textsc{Drla} & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming \\
-				\textsc{Taylor-Gp} &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations  \\ \hline
+				\textsc{AI-Feynman} & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it also uses neural network fitting \\
+				\textsc{GOMEA}  & \cite{virgolin2021improving} (2021)    & A model-based
+				EA framework called gene-pool optimal mixing evolutionary algorithm \\
+				\textsc{ITEA} & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
+				\textsc{SA} & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
+
+				\textsc{DRLA} & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming \\
+				\textsc{Taylor-GP} &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations  \\ \hline
 
 		\end{tabularx} }
-		\caption{Overview of methods to solve SR.}
+		\caption{SR methods overview.}
 		\label{tab:gp-based}
@@
 
-   The progress in the SR field suffered from a lack of uniform, robust, and transparent
-	benchmarking standards over the last two decades. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
+   The SR researches lack uniform, robust, and transparent
+	benchmarking standards. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
 	open-source, reproducible benchmarking platform for SR, called SRBench.
-The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression problems, by 130 SR datasets for which model forms are known; see more in the aforementioned paper.
-In the extensive experimental evaluation  where 14
+The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression problems, with 130 SR datasets for which exact (\emph{ground-truth}) models are known; see more in the aforementioned paper.
+In their extensive experimental evaluation, 14
 	symbolic regression methods and 7 machine learning methods are compared on the set of 252 diverse regression problems.
-The general conclusions derived from there are: ($i$) when comes to real-world problems, the best performing algorithms are those which combine genetic algorithm with a parameter estimation; ($ii$) when comes to the instances with a presence of noise, the GP--based and deep learning techniques are performing similarly.
-
-	In this work we present a novel approach to solve SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated} with the ordinary least square  method (OLS)~\cite{leng2007ordinary}.
-Briefly, ILS handles combinatorial (discrete) aspects of search space, while OLS helps in the process of a coefficient determination, so it handles continuous parts of the search space.
+The remaining 122 SR datasets belong to a class of so-called \emph{black-box} problems for which the \emph{ground-truth} is unknown.
+One of the most interesting conclusions from La Cava et al.
+research is that algorithms specialize in either solving \emph{ground-truth} problems, or \emph{black-box} problems, but not both.
+
+	In this work we present a novel approach to solve \emph{ground-truth}-based SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated} with the ordinary least square method (OLS)~\cite{leng2007ordinary}.
+ILS mostly handles combinatorial (discrete) aspects of search space, while OLS helps in the process of a coefficient determination, so it handles some continuous parts of the search space.
 As will be shown later, the proposed method has shown its robustness w.r.t.
-introduced noise, therefore we called the method \textsc{Rils}-\textsc{Rols}  (with letters R corresponding to regression and robust).
-Additionally, in order to navigate the search towards not only accurate models, but increasing the chances to get the exact one, the algorithms is equipped with a carefully constructed fitness function that utilizes three important scores of a solution (model): RMSE and $R^2$ scores which participate into models accuracy, and a weighted solution size that will contribute penalizing large (mostly non-exact) solutions.
-
-	The main contributions of this work may be summarized as follows:
+introduced noise, therefore we called the method \textsc{RILS}-\textsc{ROLS}  (with letters R corresponding to regression and robust).
+Additionally, in order to navigate the search toward exact model (and not only accurate one) the algorithm is equipped with a carefully constructed fitness function that utilizes three important model characteristics: RMSE and $R^2$ scores which participate into models accuracy, and a weighted solution size that penalizies too complex models.
+
+	The summary of main contributions is as follows:
 
 	\begin{enumerate}
-		\item The proposed method outperforms 14 state-of-the-art methods for the problem instances from the two ground-truth benchmark sets from literature, used in the benchmarking platform SRBench.
-
-		\item The method shows its high robustness, which is proved by its comparison to the other algorithms in presence of different levels of Gaussian white noise in the input data.
-
-		\item The method is very efficient, taking in average less than 3 minutes to reach the exact solution, on the problem instances where it was possible.
-For example, the second best approach in terms of the delivered exact percentage, \textsc{AI-Feynman}, needs significantly more time, which is around 45 minutes.
-
-		\item A new set of unbiased instances is introduced that consists of randomly generated formulae of various sizes and number of input variables presenting exact models that need to be found.
-This set was employed to analyze the effect of the model size, the number of input variables in the model and the level of noise on the solving difficulty.
+		\item The proposed method outperforms 14 comparison methods on two \emph{ground-truth} benchmark sets from literature -- these methods and benchmarks are used in SRBench platform.
+
+		\item The method shows its high robustness, which is proved by its comparison to the other algorithms in the presence of different levels of Gaussian white noise in the input data.
+
+		\item The method is very efficient, taking in average less than 4 minutes to reach the exact solution, on the problem instances where it was possible.
+
+		\item A new set of unbiased instances is introduced -- it consists of randomly generated formulae of various sizes and number of input variables.
+This set was employed to analyze the effect of the model size and the level of noise on the solving difficulty.
 	\end{enumerate}
@@
 
-	Before we give details on our \textsc{Rils}-\textsc{Rols}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm.
+	Before we give details on our \textsc{RILS}-\textsc{ROLS}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm.
 These are ILS meta-heuristic and OLS methods.
@@
 
-	The most popular version of ILS is shown in Algorithm~\ref{alg:ils}. Note that we use this version of ILS as the backbone of our \textsc{Rils}-\textsc{Rols}  algorithm.
+	The most popular version of ILS is shown in Algorithm~\ref{alg:ils}. Note that we use this version of ILS as the backbone of our \textsc{RILS}-\textsc{ROLS}  algorithm.
 
@@
 Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
-\subsection{\textsc{Rils}-\textsc{Rols}  method}
-Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
+\subsection{\textsc{RILS}-\textsc{ROLS}  method}
+Now we will explain the proposed \textsc{RILS}-\textsc{ROLS}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
 
@@
 	\begin{algorithmic}[1] 
-		\Procedure{\textsc{Rils}-\textsc{Rols} }{$D_{tr}$}
+		\Procedure{\textsc{RILS}-\textsc{ROLS} }{$D_{tr}$}
 		\State $n_{tr} \gets |D_{tr}|$
@@
 	\end{algorithmic}
-	\caption{\textsc{Rils}-\textsc{Rols}  method.}
+	\caption{\textsc{RILS}-\textsc{ROLS}  method.}
 	\label{alg:rilsrols}
@@
 
-\textsc{Rils}-\textsc{Rols}  algorithms receives training dataset $D_{tr}$ as input.
+\textsc{RILS}-\textsc{ROLS}  algorithms receives training dataset $D_{tr}$ as input.
 In addition, it has two control parameters: $penalty_{size}$ and $tolerance_{error}$.
@@
 The second parameter is related to the expected noise level in data -- higher noise means that tolerance to errors should be higher.
-$D_{tr}$ can have very large number of records, so the first step of \textsc{Rils}-\textsc{Rols}  is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
+$D_{tr}$ can have very large number of records, so the first step of \textsc{RILS}-\textsc{ROLS}  is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
 Initial the sample size is chosen as $\max(0.01 \cdot n_{tr}, 100)$.
@@
 
-Before returning the final symbolical model, \textsc{Rils}-\textsc{Rols}  performs the final symbolical simplification and rounding of model coefficients.
+Before returning the final symbolical model, \textsc{RILS}-\textsc{ROLS}  performs the final symbolical simplification and rounding of model coefficients.
 The latter is sensitive to control parameter $tolerance_{error}$ -- a smaller value means the information loss during rounding is smaller, i.e.
@@
 This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
-The search process of \textsc{Rils}-\textsc{Rols}  is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
+The search process of \textsc{RILS}-\textsc{ROLS}  is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
 
@@
 
-Our \textsc{Rils}--\textsc{Rols} algorithm is implemented in Python version 3.x.
+Our \textsc{RILS}--\textsc{ROLS} algorithm is implemented in Python version 3.x.
 The experiments concerning our method are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
@@
 For the (14) competitors, the results are exported from \url{https://cavalab.org/srbench/results/}, also reported in~\cite{la2021contemporary}. 
-The maximum computation time allowed for each run of \textsc{Rils}-\textsc{Rols} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used for all (14) competitors, see~\cite{la2021contemporary}.
+The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used for all (14) competitors, see~\cite{la2021contemporary}.
 
@@
 \subsection{Parameter tuning}
-The \textsc{Rils}-\textsc{Rols} algorithm employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
+The \textsc{RILS}-\textsc{ROLS} algorithm employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
 The first parameter is fixed to 0.001(?), according to the preliminary experimental evaluation we conducted.
@@
 \subsection{Comparison with other methods on the   ground--truth benchmark sets}
-In this section, we evaluate the performance of \textsc{Rils-Rols} algorithm and compare it to the 14 other competitors from the literature.
+In this section, we evaluate the performance of \textsc{RILS-ROLS} algorithm and compare it to the 14 other competitors from the literature.
 The numerical results are reported in terms of the three Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}.
@@
 \begin{itemize}
-	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{Rils-Rols}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
+	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{RILS-ROLS}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
 The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all problem instances from benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
 All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered ground-truth benchmark sets.
-	\item   Concerning the exact results in presence of the target noise with a level of 0.001, our \textsc{Rils-Rols} is still performing very-well, having found an exact model for 42.08\% cases considering the problem instances from the both benchmark sets.
+	\item   Concerning the exact results in presence of the target noise with a level of 0.001, our \textsc{RILS-ROLS} is still performing very-well, having found an exact model for 42.08\% cases considering the problem instances from the both benchmark sets.
 The second best approach is \textsc{AI-Feynman} solving in total 31.89\% cases, as before, being better when used on \textsc{Feynman} instances than on \textsc{Strogatz}.
@@
 Other approaches reach accuracy bellow 20\%.
-	\item  Concerning the exact results when the presence of noise is large, that is with a level of 0.01,  our \textsc{Rils-Rols} is still performing robustly, having found an exact model for  34.77\% problem instances from the two benchmark sets.
+	\item  Concerning the exact results when the presence of noise is large, that is with a level of 0.01,  our \textsc{RILS-ROLS} is still performing robustly, having found an exact model for  34.77\% problem instances from the two benchmark sets.
 The second best is now \textsc{AFT\_FE} reaching 20\% correct solutions.
@@
 
-	\item When comparing performances of the algorithms in terms of number of instances for which the model has $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{Rils}-\textsc{Rols} is successful with the rate of success of 83.38\% (third place).
+	\item When comparing performances of the algorithms in terms of number of instances for which the model has $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
 However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than our algorithm: \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
@@
 
-	\item  In the presence of the noise level of 0.001, our \textsc{Rils-Rols} method has 78.62\% of a success rate (third place).
+	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% of a success rate (third place).
 As before, \textsc{MRGP} and \textsc{Operon} are showing good performances.
@@
 
-	\item Following the above conclusions, our \textsc{Rils}-\textsc{Rols} algorithm is more robust than the other competitors, which is confirmed by the produced results w.r.t.\ different levels of noise in the input data.
+	\item Following the above conclusions, our \textsc{RILS}-\textsc{ROLS} algorithm is more robust than the other competitors, which is confirmed by the produced results w.r.t.\ different levels of noise in the input data.
 Moreover, it can be considered as new state-of-the-art algorithm when one solves the problems of SR with known ground-truth models.
@@
 \begin{itemize}
-	\item When considering the instance problems where no noise is detected, the lowest average runtime  is reported for \textsc{Rils}-\textsc{Rols} algorithm (228$s$).
+	\item When considering the instance problems where no noise is detected, the lowest average runtime  is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228$s$).
 A slightly worse runtime is obtained by \textsc{Dsr} algorithm (232$s$).
-However, note that the exact percentage of \textsc{Rils}--\textsc{Rols} is far better from \textsc{Dsr} (60.62\% vs.
+However, note that the exact percentage of \textsc{RILS}--\textsc{ROLS} is far better from \textsc{Dsr} (60.62\% vs.
 19.71\%).
-	All remaining approaches deliver an order of magnitude larger average runtimes that that of the \textsc{Rils}--\textsc{Rols} method.
-	\item  When considering the instance problems where a noise level of 0.001 is included,    the lowest average runtime  is again obtained by \textsc{Rils}-\textsc{Rols} algorithm (108$s$).
+	All remaining approaches deliver an order of magnitude larger average runtimes that that of the \textsc{RILS}--\textsc{ROLS} method.
+	\item  When considering the instance problems where a noise level of 0.001 is included,    the lowest average runtime  is again obtained by \textsc{RILS}-\textsc{ROLS} algorithm (108$s$).
 The second best average runtime is obtained by \textsc{Dsr}, but this time significantly worse (622$s$) from the former algorithm.
@@
 
-In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{Rils}--\textsc{Rols} to 14 other approaches over all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{RILS}--\textsc{ROLS} to 14 other approaches over all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
 Note that an indicator random variable is involved per each run of the algorithms.
@@
 \begin{itemize}
-	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of the number of obtained exact models.
+	\item  Concerning the instance problems where no noise is included, \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models.
 The second best average ranking is achieved by \textsc{AI-Feynman} algorithm.
 There is  statistically significant difference between these two approaches w.r.t.\ number of found exact models.
-The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{Rils}-\textsc{Rols} w.r.t.\ delivered average ranking.
-	\item    Concerning the instance problems with the included  level of noise of 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the found exact models.
+The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{RILS}-\textsc{ROLS} w.r.t.\ delivered average ranking.
+	\item    Concerning the instance problems with the included  level of noise of 0.001, \textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking in terms of the found exact models.
 The second best ranking is obtained by \textsc{AI-Feynman} algorithm.
@@
 The third best approach is \textsc{Afp-Fe} which performs statistically worse than \textsc{AI-Feynman} approach.
-	\item  Concerning the instance problems with the included noise level of  0.01, again, \textsc{Rils-Rols} method produces the best average ranking according to positively evaluated runs, i.e.
+	\item  Concerning the instance problems with the included noise level of  0.01, again, \textsc{RILS-ROLS} method produces the best average ranking according to positively evaluated runs, i.e.
 the runs with obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \textsc{Dsr}, and \textsc{Afp}.
-These latter three approaches perform statistically equal, but significantly worse than \text{Rils}-\textsc{Rols} method.
+These latter three approaches perform statistically equal, but significantly worse than \text{RILS}-\textsc{ROLS} method.
 	The fourth best approach according to delivered average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}.
 Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data.
-Thus, despite being efficient on no-noisy data, it seems that \textsc{AI-Feynman} is very sensitive to the level of noise increase, which is not that dramatically conspicuous with our \textsc{Rils}-\textsc{Rols} method.
+Thus, despite being efficient on no-noisy data, it seems that \textsc{AI-Feynman} is very sensitive to the level of noise increase, which is not that dramatically conspicuous with our \textsc{RILS}-\textsc{ROLS} method.
 
@@
 
-\subsection{Scalability of \textsc{Rils}-\textsc{Rols} algorithm}\label{sec:scalability-rils-rols}
+\subsection{Scalability of \textsc{RILS}-\textsc{ROLS} algorithm}\label{sec:scalability-rils-rols}
 
@@
 
-The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped with accordance to the (three) formed sub-groups ($x$-axis); for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis).
+The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped with accordance to the (three) formed sub-groups ($x$-axis); for each of them the exact percentage rate of success of \textsc{RILS}--\textsc{ROLS} algorithm is shown ($y$-axis).
 The following conclusions may be drawn from here:
@@
 For noisy data, the success rate of the algorithm gets decreased as the level of noise increases.
-For example, on the small-sized problem instances with the noise level  of 0.0001, and 0.01, the exact percentage of \textsc{Rils}--\textsc{Rols} is still reasonably high, at about 55\%~ and 34 \%, respectively.
+For example, on the small-sized problem instances with the noise level  of 0.0001, and 0.01, the exact percentage of \textsc{RILS}--\textsc{ROLS} is still reasonably high, at about 55\%~ and 34 \%, respectively.
 	\item For the middle-sized instance problems, the exact percentage rate is slightly bellow 50\%.
-It also decreases by increasing the level of noise in the target data; for the highest level of noise (of 0.01), the success rate of \textsc{Rils}-\textsc{Rols} method is just about 6\%.
-	\item For the large-sized instance problems with no noise is utilized, the exact percentage of \textsc{Rils}--\textsc{Rols} algorithm is at about 25\%, which means that the increase in the size of exact models affects the algorithm's performance, but within the expected range.
-
-	\item From the above, we can conclude that the size of exact models (solutions) and the increase of the noise level both contribute to overall performance of our \textsc{Rils}--\textsc{Rols} method.
+It also decreases by increasing the level of noise in the target data; for the highest level of noise (of 0.01), the success rate of \textsc{RILS}-\textsc{ROLS} method is just about 6\%.
+	\item For the large-sized instance problems with no noise is utilized, the exact percentage of \textsc{RILS}--\textsc{ROLS} algorithm is at about 25\%, which means that the increase in the size of exact models affects the algorithm's performance, but within the expected range.
+
+	\item From the above, we can conclude that the size of exact models (solutions) and the increase of the noise level both contribute to overall performance of our \textsc{RILS}--\textsc{ROLS} method.
 The exact percentage rate of the algorithm seems decreasing linearly  in the (exact) model size, regardless of the noise level values.
 
-	\item Concerning the high--accuracy percentages delivered by \textsc{Rils}--\textsc{Rols} algorithm -- that is the percentage of problem instances for which the algorithm's termination yielded a model with $R^2 \geq 0.999$ -- for the small--sized problem instances with no noise is recorded, it is almost at the perfect score (i.e.
+	\item Concerning the high--accuracy percentages delivered by \textsc{RILS}--\textsc{ROLS} algorithm -- that is the percentage of problem instances for which the algorithm's termination yielded a model with $R^2 \geq 0.999$ -- for the small--sized problem instances with no noise is recorded, it is almost at the perfect score (i.e.
 $\approx$100\%).
@@
 
-	\item Concerning the high--accuracy percentage of the \textsc{Rils}--\textsc{Rols} algorithm on the middle-sized instance problems when the input data are free of the noise, it is obtained on 65\% cases.
+	\item Concerning the high--accuracy percentage of the \textsc{RILS}--\textsc{ROLS} algorithm on the middle-sized instance problems when the input data are free of the noise, it is obtained on 65\% cases.
 The noisy the data are, the accuracy percentages of the algorithm, as expected, drop off; however, not so dramatically.
@@
 
-	\item Concerning the high--accuracy percentages of the \textsc{Rils}--\textsc{Rols} algorithm on the large-sized instance problems with no noise, it gets 60\%.
+	\item Concerning the high--accuracy percentages of the \textsc{RILS}--\textsc{ROLS} algorithm on the large-sized instance problems with no noise, it gets 60\%.
 Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2\geq 0.999$ for the outcome  upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
@@
 
-In this paragraph we investigate the  scalability of our \textsc{Rils}--\textsc{Rols} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
+In this paragraph we investigate the  scalability of our \textsc{RILS}--\textsc{ROLS} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
 There is three bar plots shown per each level of noise.
@@
 The instances are grouped according to the different variable count/size of respective exact models ($x$-axis).
-For each group, the exact percentages of success rate of \textsc{Rils}--\textsc{Rols} algorithm on the instance group is shown ($y$-axis).
+For each group, the exact percentages of success rate of \textsc{RILS}--\textsc{ROLS} algorithm on the instance group is shown ($y$-axis).
 
@@
 \begin{itemize}
-	\item The exact percentage rate of \textsc{Rils}--\textsc{Rols} algorithm  slightly decrease as the expected number of variables gets larger when no noise is presented in the data.
+	\item The exact percentage rate of \textsc{RILS}--\textsc{ROLS} algorithm  slightly decrease as the expected number of variables gets larger when no noise is presented in the data.
 	\item The exact percentages drop off with the presence of a larger noise level. Thus, the higher the noise level, the smaller the exact percentages are.
@@
 
-When one concerns of runtime analysis of the \textsc{Rils}--\textsc{Rols} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are displayed in Figure~\ref{fig:runtime_rils_rols}.
+When one concerns of runtime analysis of the \textsc{RILS}--\textsc{ROLS} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are displayed in Figure~\ref{fig:runtime_rils_rols}.
 The instances are grouped w.r.t.\ number of variables included into corresponding exact model ($x$-axis).
@@
 In this paper, we dealt with solving the well--known Symbolic regression (SR)  problem. SR problem is a generalization of more interdisciplinary known problems of linear and logistic regression.    
-We proposed a meta-heuristic approach, called \textsc{Rils}-\textsc{Rols}.
+We proposed a meta-heuristic approach, called \textsc{RILS}-\textsc{ROLS}.
 Our approach is built upon the Iterated local search (ILS) scheme.
@@
 
-\textsc{Rils-Rols} method is compared to the 14 other competitor algorithms from the literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
+\textsc{RILS-ROLS} method is compared to the 14 other competitor algorithms from the literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
 Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.
 The experimental evaluation confirmed the efficiency of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmarks in the presence of all three different levels of noise in the input data.
-In all cases, new best exact percentages are obtained using \textsc{Rils-Rols} method.
+In all cases, new best exact percentages are obtained using \textsc{RILS-ROLS} method.
 More in details,
@@
 
-In future work, one could think of constructing a hybrid of \textsc{Rils-Rols} method with some other meta-heuristics to further boost the quality of the obtained results.
-For example, replacing ILS scheme of \textsc{Rils-Rils} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option to give it a try.
+In future work, one could think of constructing a hybrid of \textsc{RILS-ROLS} method with some other meta-heuristics to further boost the quality of the obtained results.
+For example, replacing ILS scheme of \textsc{RILS-RILS} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option to give it a try.
 VNS   utilizes a more stronger and systematic system of solutions diversification and thus escaping from local optima could be much easier.
@@
 
-\section{Overview of \textsc{Rils}-\textsc{Rols}  python package}\label{sec:appendix-1}
+\section{Overview of \textsc{RILS}-\textsc{ROLS}  python package}\label{sec:appendix-1}
 \fxnote{TODO}

### 2022-11-16 paper_resources/doc/paper.tex
Finished with section 2.

@@
 	\label{sec:search-space}
-	In this section we formally define the SR problem, followed by defining the search space framework of the problem.
+	In this section we formally define the SR problem.
 
 	\begin{definition}
-		Given is a dataset $D = \{(x_i, y_i)\}_{i=1}^n$, where $\textbf{x} \in \mathbb{R}^d$ represents input variables (features), and $y$ target variable.
-Suppose that there exists an analytical model of the form $f(\textbf{x})= g^*(\textbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.
-		The goal of SR is to learn a mapping $\tilde{f}(\textbf{x})=  \tilde{g}(\textbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the presented  white noise within the given input data.
+		Given is a dataset $D = \{(\mathbf{x_i}, y_i)\}_{i=1}^n$, where $\mathbf{x_i} \in \mathbb{R}^d$ represents i-th feature (input) vector while $y_i \in \mathbb{R}$ is its corresponding target (output) variable.
+Suppose that there exists an analytical model of the form $f(\mathbf{x})= g^*(\mathbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.
+		The goal of SR is to learn a mapping $\tilde{f}(\mathbf{x})=  \tilde{g}(\mathbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is observed white noise within the given input data.
 
@@
 	Koza~\cite{koza1994genetic} introduced the problem of SR as a specific application of genetic programming.
-GP deals with the object called programs, which need to be optimized.
-In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants; as an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example} In essence, syntax trees are elements of the search space of SR.
+GP can be used to optimize nonlinear structures such as computer programs.
+In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants.
+As an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example}.
+In essence, all valid syntax trees form the solution search space of SR.
 That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree.
-How accurate is this mapping, we compute on the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$).
-Interestingly, the search space of SR consists of its discrete and continuous part.
-More precisely, the model we are seeking for might be obtained as a composition of some functions from a (finite) set of mathematical functions.
-It is common to use the set of the following elementary mathematical functions in the experiments: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, and $a^x$.
-It is allowed to link functions will all four operators: $+$, $-$, $\times$, and $/$.
-After fixing functions that build models, the set of optimal coefficients that  fits to this model must be provided.
-For the most physical models, these coefficients may receive any real value, that is they are continuous in its nature.
+The solution accuracy can be computed on the basis of historical data $D$ and the chosen error measure such as $MSE$, $RMSE$, $R^2$, some combination of them, etc.
+Interestingly, the SR search space nature is twofold: discrete and continuous.
+It is primarily modeled as a problem of discrete (combinatorial) optimization, since the number of possible solution functional forms is countable.
+However, it may also include elements solved by means of continuous (global) optimization, e.g., constants (coefficients) fitting.
+It is common to use the set of the following elementary mathematical functions: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, $a^x$, and a set of standard arithmetic operators: $+$, $-$, $\times$, and $/$.
 
@@
 
-		\caption{Syntax tree representation for the expression $\sin x \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
+		\caption{Syntax tree representation for the expression $\sin{x} \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
 		\label{fig:syntax-tree-example}

### 2022-11-17 paper_resources/doc/paper.tex
Finished with OLS derivations.

@@
 However, it may also include elements solved by means of continuous (global) optimization, e.g., constants (coefficients) fitting.
-It is common to use the set of the following elementary mathematical functions: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, $a^x$, and a set of standard arithmetic operators: $+$, $-$, $\times$, and $/$.
+It is common to use the set of the following elementary mathematical functions: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, $a^x$, and a set of standard arithmetic operators: $+$, $-$, $\cdot$, and $/$.
 
@@
 			]
-			\node (A) {$\times$} 
+			\node (A) {$\cdot$} 
 			child { node (B) {$\sin$}
@@
 			}
-			child {node (C) {$\times$}
+			child {node (C) {$\cdot$}
 				%child { node {x}
@@
 
-		\caption{Syntax tree representation for the expression $\sin{x} \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
+		\caption{Syntax tree representation for the expression $\sin{x} \cdot   ( x \cdot  x / y  )  = \frac{x^2 \sin x }{y}$}
 		\label{fig:syntax-tree-example}
@@
 
-	Before we give details on our \textsc{RILS}-\textsc{ROLS}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm.
-These are ILS meta-heuristic and OLS methods.
+	Before we give details on our \textsc{RILS}-\textsc{ROLS}  method for solving SR, we will explain two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least squares (OLS).
 
 	\subsection{Iterated local search}
-	Iterated local search (ILS)~\cite{lourencco2003iterated} is an efficient meta-heuristics, whose essential idea is given as follow.
-Iteratively generate a sequence of solutions produced by the (embedded) heuristic, such as local search or randomized greedy heuristics.
+	ILS~\cite{lourencco2003iterated} is an efficient meta-heuristics that iteratively generates a sequence of solutions produced by the (embedded) heuristic, such as local search (LS) or randomized greedy heuristics.
 When the search gets \emph{stuck} in local optimum, a \emph{perturbation} is performed -- this step is usually non-deterministic.
-This simple idea appeared in the literature by Baxter~\cite{baxter1981local} in early 1980s, and, since then, has been  re-invented by many researches under different names; some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
-	Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases, combinations of these~\cite{applegate2003chained}.
-
-	The most popular version of ILS is shown in Algorithm~\ref{alg:ils}. Note that we use this version of ILS as the backbone of our \textsc{RILS}-\textsc{ROLS}  algorithm.
+This simple idea was proposed by Baxter~\cite{baxter1981local} in early 1980s, and, since then, has been  re-invented by many researches under different names.
+Some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
+	Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases, combinations of previous~\cite{applegate2003chained}.
+The most popular version of ILS is shown in Algorithm~\ref{alg:ils}.
+(Note that we use this version of ILS as the backbone of our \textsc{RILS}-\textsc{ROLS} algorithm.)
 
@@
 			\State \textbf{Input}: problem instance
-			\State \textbf{Output}: an approximate (feasible) solution 
+			\State \textbf{Output}: feasible solution 
 			\State $s \gets$ \texttt{Initialize}$()$
 			\State  $s \gets$ \texttt{LocalSearch}($s$)
-			\While{\emph{stopping criteria is not met}}
+			\While{\emph{stopping criteria are not met}}
 			\State  $s' \gets$ \texttt{Perturbation}($s$)
@@
 		\end{algorithmic}
-		\caption{An ILS framework from   literature.}
+		\caption{General ILS method.}
 		\label{alg:ils}
@@
 At each iteration, ILS applies three steps.
-First, the current incumbent solution is perturbed -- it is partially randomized.
-Next, the perturbed solution is improved by a LS procedure.
-Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion.
+First, the current incumbent solution $s$ is perturbed -- it is partially randomized, yielding new solution $s'$.
+Next, the solution $s'$ is potentially improved by a LS procedure.
+Thirdly, the newly obtained solution $s'$  possibly becomes new incumbent -- this is decided upon the acceptance criterion.
 Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back to already visited solutions.
@@
 It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model).
-More precisely, given data $({X}=(X_1, \ldots, X_d)^T, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized.
-This sum is also know as the sum of squared error (SSE).
+More precisely, given previously introduced dataset $D$ of $n$ points $(\mathbf{x_i}, y_i)$ where each $\mathbf{x_i}$ is $d$-dimensional, the task is to determine linear mapping $\tilde{y} = \mathbf{k} \mathbf{x} + b$, that is coefficients (line slope) $\mathbf{k} = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i}^{n} (\tilde{y}_i - y_i)^2 $ is minimized.
+This sum is also know as the sum of squared errors (SSE).
 There are many methods to minimize SSE.
-One of the analytical approaches is the calculus-oriented -- it takes into account   partial derivation w.r.t.
-$k$ of the cost function $ \sum_{i} |\tilde{y}_i - y_i|^2 $, getting
-
-	$$  \frac{\partial}{\partial k} \sum_{i} |\tilde{y}_i - y_i|^2 = \frac{\partial}{\partial k} \sum ( kX_i+b  - y_i)^2 =  \sum 2X_i(kX_i + b - y_i)  =  \sum -2X_i (y_i - \tilde{y}_i) . $$
-
-	Taking into account   partial derivation w.r.t.  $b$, we have 
-	$$  \frac{\partial}{\partial b} \sum_{i} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum ( kX_i+b  - y_i)^2 = \sum -2  (y_i - \tilde{y}_i). $$
-
-	Thus, we get the system of equations: 
+One of the analytical approaches is the calculus-oriented -- it takes into account partial derivatives of SSE w.r.t.
+$k_j,\; j \in \{1, ..., d\}$:
+
+	$$  \frac{\partial}{\partial k_j} \sum_{i}^{n} (\tilde{y}_i - y_i)^2 = \frac{\partial}{\partial k_j} \sum_{i}^{n} ( \mathbf{k}\mathbf{x_i}+b  - y_i)^2 =  \sum_{i}^{n} 2x_{ij}(\mathbf{k}\mathbf{x_i} + b - y_i)  =   .
+$$
+
+	Similarly, by taking into account  partial derivation w.r.t. $b$, we have: 
+	$$  \frac{\partial}{\partial b} \sum_{i}^{n} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum_{i}^{n} ( \mathbf{k}\mathbf{x_i}+b  - y_i)^2 = \sum_{i}^{n} -2  (y_i - \tilde{y}_i). $$
+
+	Finally, by setting each partial derivative to zero, we get the system of $d+1$ equations with $d+1$ unknowns ($\mathbf{k}=(k_1, ..., k_d)$ and $b$): 
 	\begin{align*}
-		% &\sum -2X_i (\tilde{y}_i - y_i )  = 0 \\
-		& -2X_1 (y_1 - \tilde{y}_1)  = 0 \\
+		& \sum_{i}^{n} -2x_{i1} (y_i - \tilde{y}_i) = 0 \\
 		& \vdots \\
-		& -2X_d (y_d - \tilde{y}_d)  = 0 \\
-		&\sum -2  (y_i - \tilde{y}_i) = 0.
+		& \sum_{i}^{n} -2x_{id} (y_i - \tilde{y}_i) = 0 \\
+		&\sum_{i}^{n} -2  (y_i - \tilde{y}_i) = 0.
 	\end{align*}
@@
 	%  \end{align*}
-By solving the above system of $(d+1)$ equations, one can obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$.
-%For example, in order to calculate coefficient $k_i$, the following system of equations is
-%\fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor.
-Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
+
+\fxnote{TODO: ACA: dodati vremensku slozenost za OLS. }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
 \subsection{\textsc{RILS}-\textsc{ROLS}  method}

### 2022-11-17 paper_resources/doc/paper.tex
Update: Section 3.2

@@
 Thirdly, the newly obtained solution $s'$  possibly becomes new incumbent -- this is decided upon the acceptance criterion.
-Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back to already visited solutions.
+Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back into already visited solutions.
 
@@
 
-	$$  \frac{\partial}{\partial k_j} \sum_{i}^{n} (\tilde{y}_i - y_i)^2 = \frac{\partial}{\partial k_j} \sum_{i}^{n} ( \mathbf{k}\mathbf{x_i}+b  - y_i)^2 =  \sum_{i}^{n} 2x_{ij}(\mathbf{k}\mathbf{x_i} + b - y_i)  =   .
-$$
+	$$  \frac{\partial}{\partial k_j} \sum_{i}^{n} (\tilde{y}_i - y_i)^2 = \frac{\partial}{\partial k_j} \sum_{i=1}^{n} ( \mathbf{k}\mathbf{x_i}+b  - y_i)^2 =  \sum_{i=1}^{n} 2x_{ij}(\mathbf{k}\mathbf{x_i} + b - y_i).$$
 
 	Similarly, by taking into account  partial derivation w.r.t. $b$, we have: 
-	$$  \frac{\partial}{\partial b} \sum_{i}^{n} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum_{i}^{n} ( \mathbf{k}\mathbf{x_i}+b  - y_i)^2 = \sum_{i}^{n} -2  (y_i - \tilde{y}_i). $$
+	$$  \frac{\partial}{\partial b} \sum_{i=1}^{n} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum_{i=1}^{n} ( \mathbf{k}\mathbf{x_i}+b  - y_i)^2 = \sum_{i=1}^{n} -2  (y_i - \tilde{y}_i). $$
 
@@
 	\begin{align*}
-		& \sum_{i}^{n} -2x_{i1} (y_i - \tilde{y}_i) = 0 \\
+		& \sum_{i=1}^{n} -2x_{i1} (y_i - \tilde{y}_i) = 0 \\
 		& \vdots \\
-		& \sum_{i}^{n} -2x_{id} (y_i - \tilde{y}_i) = 0 \\
-		&\sum_{i}^{n} -2  (y_i - \tilde{y}_i) = 0.
+		& \sum_{i=1}^{n} -2x_{id} (y_i - \tilde{y}_i) = 0 \\
+		&\sum_{i=1}^{n} -2  (y_i - \tilde{y}_i) = 0.
 	\end{align*}
@@
 
-\fxnote{TODO: ACA: dodati vremensku slozenost za OLS. }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
+%https://www.thekerneltrip.com/machine/learning/computational-complexity-learning-algorithms/
+%https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
+To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization, Winograd or Strassen algorithm, just to name a few, may be used  depending on solver of linear equations used as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
+For example, Cholesky decomposition, widely used in solving the problem of linear regression, requires a matrix inversions and matrix multiplications, needs $d^3$ computation cost to find an inverse of the matrix associated to the linear system, where $d$ stands for the number of input features.
+It is worth to mention that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent.
+Using Gradient Descent (GD),  the above complexity reduces to $O(n^2d )$.
+The learning rate in GD has to be carefully chosen, as it dictates how quick the algorithm is and how fast it converges.
+Therefore, when comes to input data with large number of features, GS is preferred over OLS.
+
+%%\fxnote{TODO: ACA: dodati vremensku slozenost za OLS. }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
 \subsection{\textsc{RILS}-\textsc{ROLS}  method}

### 2022-11-17 paper_resources/doc/paper.tex
fix

@@
 %https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
-To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization, Winograd or Strassen algorithm, just to name a few, may be used  depending on solver of linear equations used as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
-For example, Cholesky decomposition, widely used in solving the problem of linear regression, requires a matrix inversions and matrix multiplications, needs $d^3$ computation cost to find an inverse of the matrix associated to the linear system, where $d$ stands for the number of input features.
+To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization, LU decomposition, Winograd or Strassen algorithm, just to name a few, may be used depending on solver of linear equations as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
+For example, by Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications, needs $d^3$ computation cost to find an inverse of the matrix associated to the linear system, where $d$ stands for the number of input features.
 It is worth to mention that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent.

### 2022-11-19 paper_resources/doc/paper.tex
Update...

@@
 %https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
-To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization, LU decomposition, Winograd or Strassen algorithm, just to name a few, may be used depending on solver of linear equations as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
-For example, by Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications, needs $d^3$ computation cost to find an inverse of the matrix associated to the linear system, where $d$ stands for the number of input features.
-It is worth to mention that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent.
-Using Gradient Descent (GD),  the above complexity reduces to $O(n^2d )$.
+To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization or LU decomposition for matrix inversion, and Winograd or Strassen algorithm for matrix multiplication depending on a solver of linear equations chosen as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
+For example, by using Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications;  computation cost of $d^3$ is required to find an inverse of the matrix associated to the linear system, which is the most consuming part of the algorithm.
+Thus, OLS using close-form matrix techniques performs in $O(d^3)$ time complexity.
+%, where $d$ stands for the number of input features.
+It is worth mentioning that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent (GD)~\cite{andrychowicz2016learning}.
+Using GD,  the above complexity reduces to $O(n^2d )$.
 The learning rate in GD has to be carefully chosen, as it dictates how quick the algorithm is and how fast it converges.

### 2022-11-19 paper_resources/doc/paper.tex
Update: plots
Experimental evaluation: polish

@@
 	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{RILS-ROLS}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
-The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% and just 27.14\% of all problem instances from benchmark set \textsc{Feynman} and \textsc{Strogatz}, respectively.
-All other approaches are performing significantly worse, and none of them is able to solve more than 30\% instances of any of the two considered ground-truth benchmark sets.
-	\item   Concerning the exact results in presence of the target noise with a level of 0.001, our \textsc{RILS-ROLS} is still performing very-well, having found an exact model for 42.08\% cases considering the problem instances from the both benchmark sets.
-The second best approach is \textsc{AI-Feynman} solving in total 31.89\% cases, as before, being better when used on \textsc{Feynman} instances than on \textsc{Strogatz}.
-Approache \textsc{AFP\_FE} shows to be robust w.r.t.
+The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% problem instances from \textsc{Feynman} set, and just 27.14\%  problem instances from benchmark set   \textsc{Strogatz}, respectively.
+All other approaches are performing much worse, and none of them is able to solve more than 30\% instances of any of the two considered ground-truth benchmark sets.
+	\item   Concerning the exact results in presence of the   noise  level of 0.001, our \textsc{RILS-ROLS} is still performing very well, having found an exact model for 42.08\% cases considering all problem instances from the both ground-truth benchmark sets.
+The second best approach is \textsc{AI-Feynman} which solved in total 31.89\% problem instances; as  already noticed, this algorithm performs better when applied on the instances from \textsc{Feynman} benchmark set than it is the case of \textsc{Strogatz} benchmark set.
+Approach  \textsc{AFP-FE} shows to be robust w.r.t.
 noise so its performances only slightly deteriorate in comparison to the no-noise scenario.
@@
 Other approaches reach   accuracy bellow 20\%.
-	\item  Concerning the exact results when the presence of noise is large, that is with a level of 0.01,  our \textsc{RILS-ROLS} is still performing robustly, having found an exact model for  34.77\% problem instances from the two benchmark sets.
-The second best is now \textsc{AFT\_FE} reaching 20\% correct solutions.
-\textsc{AI-Feynman} performances are degraded significantly under this level of noise, so it is ranked only 6th overall.
-
-	\item When comparing performances of the algorithms in terms of number of instances for which the model has $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
-However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching even better percentages of success than our algorithm: \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
+	\item  Concerning the exact results when the presence of noise is large, that is the noise level of 0.01,  our \textsc{RILS-ROLS} is still performing robustly, having found an exact model for  34.77\% problem instances considering the both ground-truth benchmark sets.
+The second best is   \textsc{AFP-FE} reaching 20\% correct solutions.
+\textsc{AI-Feynman} performances are degraded significantly under this level of noise, so it is ranked only 6th overall, reaching the accuracy of 12.61\%.
+
+	\item When comparing performances of the algorithms in terms of number of instances for which the obtained final model reaches $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
+However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching   better percentages of success than our algorithm: \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
 On the other hand, the exact model percentages of these two approaches are rather low (0\% and 16\%, respectively).
@@
 
-	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% of a success rate (third place).
+	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% of a success rate (ranked on the third place).
 As before, \textsc{MRGP} and \textsc{Operon} are showing good performances.
 
-	\item   When noise is 0.01 the situation is almost the same, \textsc{MRGP} and \textsc{Operon} are the best and second best with 88.46\% and 86.54\% accuracy, respectively.
+	\item   When noise level is 0.01, the situation is almost the same, \textsc{MRGP} and \textsc{Operon} are the best and second best with 88.46\% and 86.54\% accuracy, respectively.
 \textsc{GP-GOMEA} now reaches third place with 73.46\%, while the proposed \textsc{RILS-ROLS} is fifth with 62.92\% $R^2$ accuracy.
@@
 		\textsc{RILS-ROLS}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
-		\textsc{AIFeynman}&55.78&27.14&52.65&78.51&35.71&73.83\\
+		\textsc{AI-Feynman}&55.78&27.14&52.65&78.51&35.71&73.83\\
 		\textsc{GP-GOMEA}&26.83&29.46&27.12&71.55&71.43&71.54\\
-		\textsc{AFP\_FE}&26.98&20&26.23&59.05&28.57&55.77\\
+		\textsc{AFP-FE}&26.98&20&26.23&59.05&28.57&55.77\\
 		\textsc{ITEA}&22.41&7.14&20.77&27.59&21.43&26.92\\
@@
 		\textsc{RILS-ROLS}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
-		\textsc{AIFeynman}&33.08&22.14&31.89&77.39&42.86&73.64\\
-		\textsc{AFP\_FE}&21.9&15.71&21.23&52.16&35.71&50.38\\
+		\textsc{AI-Feynman}&33.08&22.14&31.89&77.39&42.86&73.64\\
+		\textsc{AFP-FE}&21.9&15.71&21.23&52.16&35.71&50.38\\
 		\textsc{DSR}&19.14&19.29&19.15&25.86&14.29&24.62\\
@@
 		\textsc{RILS-ROLS}&\bf{36.29}&\bf{22.14}&\bf{34.77}&64.91&46.43&62.92\\
-		\textsc{AFP\_FE}&20.78&13.57&20&52.59&32.14&50.38\\
+		\textsc{AFP-FE}&20.78&13.57&20&52.59&32.14&50.38\\
 		\textsc{DSR}&18.97&18.57&18.92&26.29&14.29&25\\
@@
 		\textsc{gplearn}&16.87&9.29&16.05&29.13&10.71&27.13\\
-		\textsc{AIFeynman}&13.03&9.29&12.61&71.43&39.29&67.86\\
+		\textsc{AI-Feynman}&13.03&9.29&12.61&71.43&39.29&67.86\\
 		\textsc{EPLEX}&8.71&4.29&8.23&56.03&21.43&52.31\\
@@
 
-In Figure~\ref{fig:time-avg-exact-noise}, average runtimes of the algorithms on those instance problems from the both ground-truth benchmarks for which the exact model has  been found are compared.
-Those algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant here and therefore included into comparisons.
-The results are grouped varying different (three) levels of noise, each presented by a plot, where the algorithms are labelled on $x$-axis, while respective average runtimes are shown on $y$-axis.
+In Figure~\ref{fig:time-avg-exact-noise}, average runtimes of the algorithms on those instance problems from the both ground-truth benchmark sets for which respective exact model has  been found, are compared.
+The algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant  and therefore included here, while others are omitted.
+The runtimes of each algorithm  are averaged w.r.t\  different levels of noise, and presented by a bar plot.
+Algorithms are labeled on $x$-axis, while respective average runtimes are shown on $y$-axis.
 Note that $y$-axis is logarithmically scaled.
@@
 \begin{itemize}
-	\item When considering the instance problems where no noise is detected, the lowest average runtime  is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228$s$).
+	\item When considering the instance problems with no noise is included, the lowest average runtime  is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228$s$).
 A slightly worse runtime is obtained by \textsc{Dsr} algorithm (232$s$).
@@
 19.71\%).
-	All remaining approaches deliver an order of magnitude larger average runtimes that that of the \textsc{RILS}--\textsc{ROLS} method.
-	\item  When considering the instance problems where a noise level of 0.001 is included,    the lowest average runtime  is again obtained by \textsc{RILS}-\textsc{ROLS} algorithm (108$s$).
-The second best average runtime is obtained by \textsc{Dsr}, but this time significantly worse (622$s$) from the former algorithm.
-	\item When considering the instance problems with a noise level of 0.01, a similar conclusion may be drawn as that from the previous point. 
+	All remaining approaches deliver an order of magnitude larger average runtimes than that of the \textsc{RILS}--\textsc{ROLS} method.
+	\item  When considering the instance problems with the noise level of 0.001,    the lowest average runtime  is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108$s$).
+The second best average runtime is produced by \textsc{Dsr}, but this time significantly larger (622$s$) from the former algorithm.
+	\item When considering the instance problems with the noise level of 0.01, a similar conclusion may be drawn as that from the previous point. 
 \end{itemize}
@@
 	 	\centering
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=320pt,height=180pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
+	\begin{subfigure}[b]{0.6\textwidth} 
+		\includegraphics[  width=340pt,height=180pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
 		\caption{No noise}
@@
 
-	\begin{subfigure}[b]{0.4\textwidth}
-
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
+	\begin{subfigure}[b]{0.6\textwidth}
+
+		\includegraphics[  width=340pt,height=180pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
 		\caption{Level of noise equal to 0.001}
@@
 
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=290pt,height=180pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
-		\caption{Level of noise equal to 0.01.\fxnote{polish labels}}
+	\begin{subfigure}[b]{0.6\textwidth}
+		\includegraphics[  width=340pt,height=180pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
+		\caption{Level of noise equal to 0.01. }
 		\label{fig:CDplots-noise0.01}
 	\end{subfigure}
-	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise. \fxnote{Polish labels}}
+	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.  }
 	\label{fig:cd-plots-exact-pcts}

### 2022-11-22 paper_resources/doc/paper.tex
Expression caching subsection.

@@
 
-	Finally, by setting each partial derivative to zero, we get the system of $d+1$ equations with $d+1$ unknowns ($\mathbf{k}=(k_1, ..., k_d)$ and $b$): 
+	Finally, by setting each partial derivative to zero, we get the system of $d+1$ linear equations with $d+1$ unknowns ($\mathbf{k}=(k_1, ..., k_d)$ and $b$): 
 	\begin{align*}
@@
 %https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
-To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization or LU decomposition for matrix inversion, and Winograd or Strassen algorithm for matrix multiplication depending on a solver of linear equations chosen as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
-For example, by using Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications;  computation cost of $d^3$ is required to find an inverse of the matrix associated to the linear system, which is the most consuming part of the algorithm.
+To solve this system one can use Cholesky  factorization or LU decomposition for matrix inversion, and Winograd or Strassen algorithm for matrix multiplication, depending on a solver of linear equations chosen as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
+For example, by using Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications.
+In that case the computation cost of $O(d^3)$ is required to find an inverse of the matrix associated to the linear system, which is the most consuming part of the algorithm.
 Thus, OLS using close-form matrix techniques performs in $O(d^3)$ time complexity.
@@
 It is worth mentioning that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent (GD)~\cite{andrychowicz2016learning}.
-Using GD,  the above complexity reduces to $O(n^2d )$.
-The learning rate in GD has to be carefully chosen, as it dictates how quick the algorithm is and how fast it converges.
-Therefore, when comes to input data with large number of features, GS is preferred over OLS.
-
-%%\fxnote{TODO: ACA: dodati vremensku slozenost za OLS. }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
+When using GD the complexity becomes $O(n^2d )$.
+% The learning rate in GD has to be carefully chosen, as it dictates how quick the algorithm is and how fast it converges.
+
 \subsection{\textsc{RILS}-\textsc{ROLS}  method}
@@
 We use a simple solution initialization -- tree root node is set to zero constant.
-We interchangeably use two solution variables: ($i$) $s$ denotes starting (or working) solution and ($ii$) $bs$ stands for the best solution so far.
+We interchangeably use two solution variables: ($i$) $s$ denotes starting (or working) solution and ($ii$) $bs$ stands for the best solution so far, also known as the incumbent solution.
 Solution quality is measured by evaluating the fitness function (more about it in the subsequent Section~\ref{sec:fitness}).
@@
 Now, the algorithm enters the internal loop -- it iterates over the ordered perturbations and aims to find the one which improves the best solution $bs$.
-But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}) after which the local search is performed (line~\ref{line:ls}).
+But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}), after which the local search is performed (line~\ref{line:ls}).
 Solution simplification is done in a symbolical fashion by popular \texttt{SymPy} Python package~\cite{sympy}.
@@
 Finally, the fitness function value of $p$ is compared to the fitness function value of $bs$.
-If a new incumbent is found, $bs$ is updated correspondingly and the internal loop that goes across ordered perturbations is immediately terminated (it works in a  \emph{first-improvement} strategy).
+If fitness of $p$ is better, $bs$ is updated correspondingly and the internal loop, that goes across ordered perturbations, is immediately terminated (it works in a  \emph{first-improvement} strategy).
 Otherwise, the next perturbation is probed.
@@
 Otherwise, it makes no sense to set starting solution to $bs$, as nothing changed -- the search is being  \emph{trapped} in a local optimum.
-In order to avoid this undesired situation, randomness needs to be triggered.
+Randomness is introduced in order to avoid this undesired situation.
 First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{All1Perturbations}).
@@
 When that happens, the set of starting solution candidates is equal to perturbations of some randomly selected perturbation of $bs$ (lines \ref{line:pert21}-\ref{line:pert22}) -- which effectively means that the perturbations with distance 2 from $bs$ are used.
-Indeed, there is almost no chance that these 2-perturbations will have an empty set difference with $start_{tried}$ set of starting solutions.
-Therefore, more expensive 3-perturbations will not be considered in our algorithm.
+There is a very small chance that these 2-perturbations will have an empty set difference with $start_{tried}$ set of starting solutions.
+Therefore, 3-perturbations are not considered in our algorithm.
 
@@
 Symbolic regression objective is to determine the expression fitting available data.
-It is also allowed to obtain some equivalent expression, keeping in mind that there are multiple ways to express some symbolical equation.
-Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, simply because the goal expression is not known at that point as only target values for some of the input features are known.
-Thus, different numerical metrics are being used in literature to guide the symbolic regression search process.
-The most popular are the coefficient of determination, also known as $R^2$ and mean squared error (MSE) or root mean squared error (RMSE).
-The important aspect of the solution quality might also be the solution expression complexity, which may correspond to the model size of its tree representation.
+It is also allowed to obtain some equivalent expression, since there are multiple ways to express some symbolical equation.
+Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, because the goal expression is not known at that point -- only target values for some of the input data are known.
+Thus, various numerical metrics are being used in literature to guide the symbolic regression search process.
+The most popular are the coefficient of determination, also known as $R^2$, and the mean squared error (MSE) or root mean squared error (RMSE).
+Also, the important aspect of the solution quality is the solution expression complexity, which may correspond to the model size of its tree representation.
 This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
@@
 \begin{itemize}
-	\item higher $R^2$ is preferred -- ideally, when $R^2(s)=1$, the effect of term $1+R^2(s)$ is neutralized; %since 1 is neutral for multiplication;
-	\item lower RMSE is preferred, ideally, when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
-	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle); therefore, we award those solutions with a more simple representation. 
+	\item higher $R^2$ is preferred -- ideally, when $R^2(s)=1$, the effect of term $2-R^2(s)$ is neutralized; %since 1 is neutral for multiplication;
+	\item lower RMSE is preferred -- ideally, when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
+	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle); therefore, simpler solutions are favorable. 
 \end{itemize}
 
-The size of expression is calculated by simply counting all nodes in the expression tree -- this includes leaves (variables and constants) and internal nodes (operations).
+The size of expression is calculated by counting all nodes in the expression tree -- this includes leaves (variables and constants) and internal nodes (operations).
+
+\subsubsection{Expression caching}
+
+In order to speed-up the fitness evaluation, we employ \emph{expression caching}.
+This means that values attached to expression trees or subtrees are persisted in key-value structure, such that the key is tree (subtree) textual representation, while the value is the $|D_{tr}'|$-sized vector of corresponding expression values on the sample training dataset $D_{tr}'$.
+(Of course, once the $D_{tr}'$ changes, which happens relatively rarely, the whole cache is cleared.)
+Caching is performed in a partial way -- when determining the value of a given expression $T$, it is not required to find the exact \emph{hit} inside the cache.
+So, if some subexpression (subtree) of $T$ is present in the cache, its value will be reused and further combined to calculate the whole fitness function value.
+
+For example, let us have an expression $T = y^2 \cdot (x+y)/z - sin(x+y)$, sample training dataset $D_{tr}'=\{([1, 2, 5], 7), ([3, 4, 3], 5), ([4, 5, 3], 6), ([6, 7, 4], 3), ([3, 3, 6], 2)\}$ (here, input feature vector is labeled by $[x, y, z]$), and expression cache consisting of the following key-value entries $cache=\{(x+y, [3, 7, 9, 13, 6]), (y^2, [4, 16, 25, 49, 9])\}$.
+Expression $T$ does not need to be fully evaluated since some of its parts are inside the cache: $y^2$ and $x+y$.
+(Note that variables alone do not need to enter the cache, since they are already available as columns of  $D_{tr}'$.)
+Each newly evaluated (sub)expression (except constant or variable alone) enters the cache.
+In this example, the new entries will correspond to keys $(x+y)/z$, $y^2 \cdot (x+y)/z$, $sin(x+y)$ and $y^2 \cdot (x+y)/z - sin(x+y)$.
+The maximal number of cache entries is set to 5000. Once this number is reached, the cache is cleared.
 

### 2022-11-22 paper_resources/doc/paper.tex
Finished up to Algorithm 4.

@@
 
-\fxnote{Dati neku smislenu procjenu kompleksnosti algoritma, ako to nije pretesko. }
+%\fxnote{Dati neku smislenu procjenu kompleksnosti algoritma, ako to nije pretesko. Aca: zasad bih ovo izbegao, nezgodno je. Ako budu trazili recenzenti, uradicemo.}
+
 \subsubsection{Fitness function}\label{sec:fitness}
@@
 For example, for expression $3.3\cdot(x+45.1\cdot y^{3.2})\cdot 81\cdot x/\sqrt{y}$ the normalized version is $1\cdot (x+1\cdot y^3)\cdot 1\cdot x/\sqrt{y}$.
-The reason for performing normalization is reducing the search space of possible perturbations thus keeping them within a reasonable size.
+The reason for performing normalization is reducing the search space of possible perturbations.
 This reduction is reasonable, since normalization preserves the essential functional form.
-(Note that coefficients get tuned later during the OLS phase and local search.)
+(Note that coefficients get tuned later: the linear coefficient during the OLS phase, and the remaining during local search.)
 
@@
 The previous expression will take form $(x+y^3)\cdot x/\sqrt{y}$.
-The purpose of simplification is removing unnecessary coefficients, but in general it can also be non-trivial symbolic simplification.
+In this particular case, the simplification will usually only remove unnecessary coefficients, but in general it can also perform some non-trivial symbolic simplification.
 
@@
 %This set of subtrees is obtained if left subtree of the whole expression is $(x+y^3)$ while the right one is $x/\sqrt{y}$.
-For each subtree $n$, the set of perturbations around $n$ is generated (lines \ref{line:forSSStart}-\ref{line:forSSEnd} in Algorithm~\ref{alg:pert}).
+Further, the set of perturbations around each subtree $n$ is generated (lines \ref{line:forSSStart}-\ref{line:forSSEnd} in Algorithm~\ref{alg:pert}).
 

### 2022-11-22 paper_resources/doc/paper.tex
Update

@@
 This means that coefficients in any of linear combinations of current solution are being set by applying  ordinary least square method, already described in Section~\ref{sec:ols}.
+\fxnote{Marko: Aco, dodaj ono oko  nelinearnog dijela i pordešavanja koeficijenata koji se traže u predefinisanom skupu vrijednosti...}
 After this step, perturbations are usually better suited to given sample data $D_{tr}'$. 
@@
 In order to speed-up the fitness evaluation, we employ \emph{expression caching}.
-This means that values attached to expression trees or subtrees are persisted in key-value structure, such that the key is tree (subtree) textual representation, while the value is the $|D_{tr}'|$-sized vector of corresponding expression values on the sample training dataset $D_{tr}'$.
-(Of course, once the $D_{tr}'$ changes, which happens relatively rarely, the whole cache is cleared.)
+This means that values attached to expression trees or subtrees are persisted in key-value structure, such that the key is tree (subtree) textual representation, while the value is the $|D_{tr}'|$-size  vector of corresponding expression values on the sample training dataset $D_{tr}'$.
+(Of course, once the $D_{tr}'$ changes, which happens not that frequently, the whole cache is cleared.)
 Caching is performed in a partial way -- when determining the value of a given expression $T$, it is not required to find the exact \emph{hit} inside the cache.
@@
 
-For example, let us have an expression $T = y^2 \cdot (x+y)/z - sin(x+y)$, sample training dataset $D_{tr}'=\{([1, 2, 5], 7), ([3, 4, 3], 5), ([4, 5, 3], 6), ([6, 7, 4], 3), ([3, 3, 6], 2)\}$ (here, input feature vector is labeled by $[x, y, z]$), and expression cache consisting of the following key-value entries $cache=\{(x+y, [3, 7, 9, 13, 6]), (y^2, [4, 16, 25, 49, 9])\}$.
+For example, let  $T = y^2 \cdot (x+y)/z - \sin(x+y)$ be an expression, and $D_{tr}'=\{([1, 2, 5], 7), ([3, 4, 3], 5), ([4, 5, 3], 6), ([6, 7, 4], 3), ([3, 3, 6], 2)\}$ be a sample training dataset (here, input feature vector is labeled by $[x, y, z]$); let expression cache consisting of the following key-value entries $cache=\{(x+y, [3, 7, 9, 13, 6]), (y^2, [4, 16, 25, 49, 9])\}$.
 Expression $T$ does not need to be fully evaluated since some of its parts are inside the cache: $y^2$ and $x+y$.
-(Note that variables alone do not need to enter the cache, since they are already available as columns of  $D_{tr}'$.)
+(Note that single variables do not need to enter the cache, since they are already available as columns of  $D_{tr}'$.)
 Each newly evaluated (sub)expression (except constant or variable alone) enters the cache.
-In this example, the new entries will correspond to keys $(x+y)/z$, $y^2 \cdot (x+y)/z$, $sin(x+y)$ and $y^2 \cdot (x+y)/z - sin(x+y)$.
+In this example, the new entries will correspond to keys $(x+y)/z$, $y^2 \cdot (x+y)/z$, $\sin(x+y)$ and $y^2 \cdot (x+y)/z - \sin(x+y)$.
 The maximal number of cache entries is set to 5000. Once this number is reached, the cache is cleared.
@@
 Before checking if the candidate solution ($new$) is better that the actual best $bp$, the OLS coefficient fitting (\texttt{FitOLS}) is performed.
-
- \fxnote{Marko: stigao do ovog dijela...}
 

### 2022-11-23 paper_resources/doc/paper.tex
Number of perturbations, only discussed.

@@
 Node $n$ has arity of at least 1 (see line ~\ref{alg:alg4-case-2} in Algorithm~\ref{alg:pertNode}). This means that the left subtree exists, so the left subtree node is to be changed. 
-For example, if $n=x+y^3$ the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
-Another example would be the case of unary operation, e.g.
-when $n=\sqrt{y}$.
-In that case, some of the possible perturbations could be $(x+y^3)\cdot x/\sqrt{\ln{y}}$ (application of logarithm to left subtree $y$) or $(x+y^3)\cdot x/\sqrt{x}$ (changing variable $y$ to $x$), etc.
+For example, if $n=x+y^3$, the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
+Another example would be the case of unary operation, e.g., when $n=\sqrt{y}$.
+In that case, some of possible perturbations could be $(x+y^3)\cdot x/\sqrt{\ln{y}}$ (application of logarithm to left subtree $y$) or $(x+y^3)\cdot x/\sqrt{x}$ (changing variable $y$ to $x$), etc.
 
 \emph{Case 3}. 
-Subtree $ss$ is binary operation, meaning the right subtree must exist (Line ~\ref{alg:alg4-case-3} in Algorithm~\ref{alg:pertNode}). 
+Node $n$ is binary operation, meaning the right subtree must exist (Line ~\ref{alg:alg4-case-3} in Algorithm~\ref{alg:pertNode}). 
 The analogous idea is applied as in \emph{Case 2}.
 
-The algorithm allows the following set of carefully chosen per-node changes:
+The algorithm allows the following set of carefully chosen per-node changes (method named \texttt{NodeChanges} in Algorithm~\ref{alg:pertNode}):
 
@@
 \end{enumerate}
-\fxnote{Nekako zbunjuje u Algoritmu 4, pojava NodeChanges)() i Replace().
+
+Method named \texttt{Replace}$(s, n, nc)$ inside Algorithm~\ref{alg:pertNode} is simply used to replace the node $n$ with node $nc$ inside the given expression tree $s$.    
+%\fxnote{Nekako zbunjuje u Algoritmu 4, pojava NodeChanges)() i Replace().
 Mislim, razumijem iz opisa sta one rade, ali nisam siguran da treba imenovati metode, ako ih barem u kontekstu opisa ne pomenemo direktno po nazivu.
-}
-
-\fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene}
+ACA: za NodeChanges stoji opis operacija iznad, sad sam ubacio i u tekst da je to sustina metode NodeChanges.
+Za replace sam takodje dao objasnjenje.}
+
+\fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene.
+ACA: tesko je ovo izracunati, u principu za svaki cvor, dakle, celo drvo ili bilo koje pod-drvo ide ovaj spisak gore, dakle, neki red velicine d*C(T), gde je C(T) broj poddrveca iz datog drveta T, a d je neka konstanta, tj.
+broj mogucih perturbacija jednog poddrveta.
+Sad koliko ima poddrveca, moze se izracunati ovako nekako, ali ne bih to ukljucivao osim ako nam ne zatraze.
+Dakle, za drvo T broj poddrveca $C(T) = C(T.left)+C(T.right)+1$ (ovo jedan za bas to celo drvo u datom rekurzivnom koraku), sad kad je drvo T od N cvorova balansirano, dobija se diferencna jednacina $C(N)=2*C(N/2)+1$, a njeno resenje je O(N) mislim.
+Kad se raspise dobija se $C(N) = 2*2*C(N/4)+2 = 2*2*2*C(N/8)+3 = ...
+= 2^(\log_2(N))*C(1)+\log_2(N) = N + \log_2(N) = O(N)$ posto je $C(1)=1$, to je list drveta}
 

### 2022-11-25 paper_resources/doc/paper.tex
Some polishing

@@
 
-\fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene.
+%\fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene.
 ACA: tesko je ovo izracunati, u principu za svaki cvor, dakle, celo drvo ili bilo koje pod-drvo ide ovaj spisak gore, dakle, neki red velicine d*C(T), gde je C(T) broj poddrveca iz datog drveta T, a d je neka konstanta, tj.
@@
 The experiments concerning our method are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
-The following 14 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
-
-For the (14) competitors, the results are exported from \url{https://cavalab.org/srbench/results/}, also reported in~\cite{la2021contemporary}. 
-The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used for all (14) competitors, see~\cite{la2021contemporary}.
-
-All (15) competitor algorithms were run ten times per each instance.
+The following 13 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
+
+For the (13) competitors, the results are exported from \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
+The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used in case of all (13) competitors, see~\cite{la2021contemporary}.
+
+All    algorithms were run ten times per each problem instance.
 
@@
 SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
-It brought researchers an easy handled environment to evaluation, comparisons, and analysis of their methods.
-Among all benchmark sets, we involve two real-world inspired benchmark sets, the ground-truth regression problems, into our computational evaluation:
+It brings researchers an easy handled environment to evaluate, compare, and analyze their methods.
+Among all benchmark sets, we involve two real-world inspired ground-truth benchmark sets that represent types of regression problems, into our computational evaluation:
 \begin{itemize}
-	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that correspond to various natural laws.  
+	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that describes   various natural laws.  
 	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}.
 Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.
-Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to~\cite{la2021contemporary}.
+Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to the results reported in~\cite{la2021contemporary}.
 
@@
 	Each dataset is represented by a 2-state system of first-order, ordinary differential equations. 
-	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  the current two states on which it depends.
+	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  in dependence of the current two states.
 These equations describes natural processes described by non-linear dynamics  exhibiting chaos.
@@
 These problem instances are downloadable from \url{https://github.com/lacava/ode-strogatz}.
-In overall, 14 ground-truth models are used to generate the problem instances used in the comparison, see~\cite{la2021contemporary}.
+In overall, 14 ground-truth models are used to generate the problem instances used in the comparison, also in accordance with~\cite{la2021contemporary}.
 
@@
 Thus, some methods may get significant benefit with this regard, while some others may be in the subordinate situation.
-In order to permit any kind of favoritism in the input data, we generate a set of randomly generated (non-biased) instances, labelled by \textsc{Random}.
+In order to permit any kind of favoritism in the input data, we generate a set of randomly generated (non-biased) SR problem instances; this benchmark set is labelled by \textsc{Random}.
 These instances are generated according the following procedure.
@@
 For example, replacing ILS scheme of \textsc{RILS-RILS} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option to give it a try.
-VNS   utilizes a more stronger and systematic system of solutions diversification and thus escaping from local optima could be much easier.
-Additionally, as proof of the efficiency and benefits of our algorithm, this tool could be applied to solving problems from various problem domains out of the area of computer science, for example from physics or chemistry, to help for setting up hypotheses or to obtain valuable insights on experimental evaluations.
+VNS   utilizes a more stronger and systematic system of solutions diversification and thus escaping from local optima could be much easier and the convergence much faster.
+Additionally, as proof of the efficiency and benefits of our algorithm, this tool could be applied to solving problems from various problem domains out of the area of computer science, for example from physics or chemistry, to help for setting up reasonable hypotheses or to obtain valuable insights on experimental evaluations.
 

### 2022-11-25 paper_resources/doc/paper.tex
Polishing in the Exp. section

@@
 \end{itemize}
-The above-mentioned benchmark sets may be biased as models which describe physical laws that usually impose   symmetries, periodicity w.r.t.
+The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   symmetries, periodicity w.r.t.
 some variables, internal separability on some variables etc.
-In that way, the search process and the search space can be, in-advance, significantly reduced.
-Thus, some methods may get significant benefit with this regard, while some others may be in the subordinate situation.
+In that way, the search process and the search space can be pre-processed and thus significantly reduced.
+Thereby, some methods may get significant benefit with this regard, while some others may be in a subordinate situation.
 In order to permit any kind of favoritism in the input data, we generate a set of randomly generated (non-biased) SR problem instances; this benchmark set is labelled by \textsc{Random}.
@@
 \subsection{Parameter tuning}
-The \textsc{RILS}-\textsc{ROLS} algorithm employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is fixed to 0.001(?), according to the preliminary experimental evaluation we conducted.
-The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances; among the following values \{ x, xx, ...
-\} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error over all problem instances from the training set are produced.
+The \textsc{RILS}-\textsc{ROLS} algorithm employs two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is fixed to 0.001(?), according to the preliminary experimental evaluation.
+The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances.
+Among the following values \{ x, xx, ...
+\} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error on all problem instances from the training set are produced.
 %Note that the training set is chosen randomly with a cardinalty of xx instances.
@@
 \subsection{Comparison with other methods on the   ground--truth benchmark sets}
-In this section, we evaluate the performance of \textsc{RILS-ROLS} algorithm and compare it to the 14 other competitors from the literature.
+In this section, we evaluate the performance of \textsc{RILS-ROLS} algorithm and compare it to the 13 other competitors from the literature.
 The numerical results are reported in terms of the three Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}.
-The results for the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, are given w.r.t.\   the following values of the noise levels of 0.0 (no noise), 0.001 (a low-level noise), and 0.01 (a high-level noise), respectively.
-In details, the white Gaussian noise was added to the target ($y$-axis) values as a fraction of the signal RMS value, also applied in~\cite{la2021contemporary}, i.e.
-for target noise level $\alpha$, we have
+The results for the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, are given w.r.t.\   the following level of noise: 0.0 (no-noisy data), 0.001 (low-level noise), and 0.01 (high-level noise), respectively.
+In details, the white Gaussian noise was added to the target ($y$-axis) values as a fraction of the signal RMS value, applied also in~\cite{la2021contemporary}, i.e.
+for target noise level $\alpha$ we have
 $$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{n} \sum {y_i^2}}\right),$$
@@
 Each table consists of three blocks.
-The first block reports the algorithm whose performances are reported (by a row).
-The second block reports, with two columns,  percentages of the instances where the model which fits to the exact one has been found by respective algorithms on \textsc{Feynman} and \textsc{Strogatz} benchmark set, respectively.
-The third column of this block provides the overall summary exact percentage of success over all instances from the both benchmark sets.
-The third block displays the results of the respective algorithm in terms of the $R^2$ score which indicate on  accuracy, i.e.
-in our cases when the algorithm  at least reached the accuracy ($R^2$ score) of 0.999.
+The first block reports the algorithm (by a row) whose performances are reported.
+The second block reports in two columns  percentages of the instances where the exact model has been found by respective algorithms on \textsc{Feynman} and \textsc{Strogatz} benchmark set, respectively.
+The third column of this block provides the overall summary exact percentage of success of the algorithm over all instances from the both benchmark sets.
+The third block displays the results of the respective algorithm in terms of the final $R^2$ score which indicates on accuracy of found solution -- by our criterion when the algorithm  at least reached the accuracy ($R^2$ score) of 0.999.
 Note that the termination of our algorithm may not always be triggered by reaching an appropriate $R^2$ score of 0.999, but also due to the reached time limit.
-These results are of interest as when compared to corresponding exact percentage it may point out the existence of an over-fitting.
-This block consists of three rows that indicate the percentage of instances where respective algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 \geq 0.999$ upon termination) on the both real--world benchmark sets separately, and the overall percentage of success rate (over all considered instances) w.r.t.
-the same criterion of reaching the desired accuracy.
+These results are of a particular interest as they may point out on the presence of strong over-fitting in contrast to finding the right model.
+This block consists of three rows that indicate the percentage of instances where respective algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 \geq 0.999$ upon termination) on the both ground--truth benchmark sets separately, and the overall percentage of success rate (over all considered instances) w.r.t.
+the criterion of reaching the final accuracy of 0.999.
 
@@
 
-In short, the exact results, thus the number of instances (in percentages) for which the output of respective algorithm match to the exact model, are displayed in the second block of each of the tables.
+In short, the exact results, thus the number of instances (in percentages) for which the output of respective algorithm is able to find the exact model, are displayed in the second block of each of the tables.
 The numbers of instances (in percentages) for which each algorithms deliver a precise enough model (i.e.

### 2022-11-26 paper_resources/doc/paper.tex
Finished up to 4.1.

@@
 
-	\section{The proposed method}\label{sec:rils}
-
-	Before we give details on our \textsc{RILS}-\textsc{ROLS}  method for solving SR, we will explain two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least squares (OLS).
+	\section{The proposed RILS-ROLS method}\label{sec:rils}
+
+ 	Our method relies on the following operations: $+$, $-$, $\cdot$, $/$, $\sqrt{x}$, $x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $a^x$, where $a^x$ is only consequently used -- it is never explicitly introduced in the search space.
+Beside this, the following set of constants enters the search space explicitly: $-1$, $0$, $1$, $2$, $\pi$ and $10$.
+	Before we give details on our   method for solving SR, we will explain two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least squares (OLS).
 
@@
 This means that coefficients in any of linear combinations of current solution are being set by applying  ordinary least square method, already described in Section~\ref{sec:ols}.
-\fxnote{Marko: Aco, dodaj ono oko  nelinearnog dijela i pordešavanja koeficijenata koji se traže u predefinisanom skupu vrijednosti...}
 After this step, perturbations are usually better suited to given sample data $D_{tr}'$. 
@@
 	\item Any node to any of its subtrees (excluding itself). For example, if $(x+y^3)$ is changed to $x$, the perturbation is $(x+y^3)\cdot x/\sqrt{y} \rightarrow x\cdot x/\sqrt{y}$. 
-	\item Variable to another variable or constant to variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (y+y^3)\cdot x/\sqrt{y}$.
+	\item Constant to variable. For example,  $(1+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sqrt{y}$.
 	\item Variable to unary operation applied to that variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot \ln{x}/\sqrt{y}$.
@@
 		\For{$n \in bp_{subtrees}$}
-		\State $n_{candidates} \gets $ \texttt{All1PerturbationsAroundNode}($bp$, $n$)
+		\State $n_{candidates} \gets $ \texttt{All1PerturbationsAroundNodeExtended}($bp$, $n$)
 		\For{$new \in n_{candidates}$}
@@
 
-For a given perturbation $p$, local search systematically explores all 1-perturbations around $p$.
+For a given perturbation $p$, local search systematically explores extended set of 1-perturbations around $p$.
 It relies on the \emph{best-improvement} strategy, meaning that all 1-perturbations (for all subtrees) are considered.
-Before checking if the candidate solution ($new$) is better that the actual best $bp$, the OLS coefficient fitting (\texttt{FitOLS}) is performed.
+Before checking if the candidate solution ($new$) is better than the actual best $bp$, the OLS coefficient fitting (\texttt{FitOLS}) takes place.
+The set of used 1-perturbations is increased in comparison to those used previously. Namely, in addition to those six possible types of node changes, the following four are added:
+
+\begin{enumerate}
+	\setcounter{enumi}{6}
+	\item Any node to any constant or variable. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow y \cdot x / \sqrt{y}$ or  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+\pi) \cdot x / \sqrt{y}$.
+	\item Any node to unary operation applied to it. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\ln{\sqrt{y}}$.
+	\item Any node to binary operation applied to that node and some variable or constant. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sqrt{y} - x$.
+	\item Constant to its multiple, where possible multipliers are $\{$0.01, 0.1, 0.2, 0.5, 0.8, 0.9, 1.1, 1.2, 2, 5, 10, 20, 50, 100$\}$.
+For example, $(1+y^3)\cdot x/\sqrt{y} \rightarrow (1.2+y^3)\cdot x/\sqrt{y}$.
+\end{enumerate}
+
+Change under number 10 is very important -- it performs the general coefficient tuning, unlike OLS that considers only coefficients in linear combinations.
 
@@
 
-Our \textsc{RILS}--\textsc{ROLS} algorithm is implemented in Python version 3.x.
-The experiments concerning our method are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.
+Our \textsc{RILS}--\textsc{ROLS} algorithm is implemented in Python 3.9.0.
+All experiments concerning our method are conducted in the single-core mode, on a PC with Intel i9-9900KF CPU @3.6GHz, 64GB RAM, under Windows 10 Pro OS.
+The RAM consumption was very small (up to few hundred megabytes) -- beside memory space needed to load input dataset, the only considerable amount is reserved for expression cache.
+
 The following 13 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
 
-For the (13) competitors, the results are exported from \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
-The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used in case of all (13) competitors, see~\cite{la2021contemporary}.
-
-All    algorithms were run ten times per each problem instance.
+For the (13) competitors, the results are exported from SRBench \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
+The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1 hour, while the maximal number of fitness function evaluations is set to 1 million.
+All other algorithms from SRBench used the time limit that was equal or bellow 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
+We did not use the full time limit of 8 hours because it was not necessary -- we empirically concluded that there were no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
+
+All non-deterministic algorithms (including \textsc{RILS}-\textsc{ROLS}) were run ten times per each problem instance, where each run used different setting of random number generator seed.
 

### 2022-11-26 rils_rols/rils_rols.py

@@ -6,7 +6,7 @@ from random import Random, shuffle
 from sklearn.base import BaseEstimator
 import copy
 from sympy import *
-from .node import Node, NodeConstant, NodePow, NodeVariable, NodePlus, NodeMinus, NodeMultiply, NodeDivide, NodeSqr, NodeSqrt, NodeLn, NodeExp, NodeSin, NodeCos
+from .node import Node, NodeConstant, NodeVariable, NodePlus, NodeMinus, NodeMultiply, NodeDivide, NodeSqr, NodeSqrt, NodeLn, NodeExp, NodeSin, NodeCos
 
 import warnings
 
@@ -20,14 +20,12 @@ class RILSROLSRegressor(BaseEstimator):
     improvements_cnt = 0
     tries_cnt = 0
 
-    def __init__(self, max_fit_calls=100000, max_seconds=100, complexity_penalty=0.001, error_tolerance=1e-16, sample_share=0.01,  trigonometry=True, random_state=0):
+    def __init__(self, max_fit_calls=100000, max_seconds=100, complexity_penalty=0.001, error_tolerance=1e-16,random_state=0):
         self.max_seconds = max_seconds
         self.max_fit_calls = max_fit_calls
         self.complexity_penalty = complexity_penalty
         self.random_state = random_state
         self.error_tolerance = error_tolerance
-        self.trigonometry = trigonometry
-        self.sample_share = sample_share
 
 
     def __reset(self):
@@ -46,17 +44,13 @@ class RILSROLSRegressor(BaseEstimator):
         self.allowed_nodes=[NodeConstant(-1), NodeConstant(0), NodeConstant(0.5), NodeConstant(1), NodeConstant(2), NodeConstant(math.pi), NodeConstant(10)]
         for i in range(variableCount):
             self.allowed_nodes.append(NodeVariable(i))
-        self.allowed_nodes+=[NodePlus(), NodeMinus(), NodeMultiply(), NodeDivide(), NodeSqr(), NodeSqrt(),NodeLn(), NodeExp()]
-        if self.trigonometry:
-            print("Adding trigonometric functions")
-            self.allowed_nodes+=[NodeSin(), NodeCos()]#, NodeArcSin(), NodeArcCos()]
[…]

### 2022-11-26 testPMLB_ground_truth.py

@@ -27,7 +27,7 @@ noise_level = float(sys.argv[7])
 test_size = 0.25
 label="target"
 
-pmlb_cache = "../../pmlb/datasets"
+pmlb_cache = "../../../pmlb/datasets"
 '''
 excluded_feynman = ["feynman_I_26_2", "feynman_I_30_5", "feynman_test_10"] # this are using arcsin or arcos
 ground_truth_regr_datasets = list(filter(lambda x: (x.startswith("feynman") or x.startswith("strogatz")) and not x in excluded_feynman, listdir(pmlb_cache)))

### 2022-11-26 test_other.py

@@ -13,8 +13,6 @@ time = 3600
 max_fit = 10000000
 noise_level = 0
 complexity_penalty = 0.01 # 0.001 default
-trigonometry = True
-sample_share = 0.05
 
 instance_files = [f for f in listdir(instances_dir) if isfile(join(instances_dir, f))]
 #instance_files = ["random_04_01_0010000_04.data"]
@@ -51,9 +49,9 @@ for fpath in instance_files:
         y_train = utils.noisefy(y_train, noise_level, random_state)
 
     if noise_level == 0:
-        rils = RILSROLSRegressor(max_fit_calls=max_fit, max_seconds=time, random_state = random_state, complexity_penalty=complexity_penalty, trigonometry=trigonometry, sample_share=sample_share)
+        rils = RILSROLSRegressor(max_fit_calls=max_fit, max_seconds=time, random_state = random_state, complexity_penalty=complexity_penalty)
     else:
-        rils = RILSROLSRegressor(max_fit_calls=max_fit, max_seconds=time, random_state = random_state, error_tolerance=noise_level, complexity_penalty=complexity_penalty, trigonometry=trigonometry, sample_share=sample_share)
+        rils = RILSROLSRegressor(max_fit_calls=max_fit, max_seconds=time, random_state = random_state, error_tolerance=noise_level, complexity_penalty=complexity_penalty)
     rils.fit(X_train, y_train)
     report_string = rils.fit_report_string(X_train, y_train)
     rils_R2 = -1

### 2022-11-27 rils_rols/node.py
Polishing code.

@@ -30,12 +30,12 @@ class Node:
         if self.arity==0:
             return self.evaluate_inner(X, None, None)
         elif self.arity == 1:
-            leftVal = self.left.evaluate(X)
-            return self.evaluate_inner(X,leftVal, None)
+            left_val = self.left.evaluate(X)
+            return self.evaluate_inner(X,left_val, None)
         elif self.arity==2:
-            leftVal = self.left.evaluate(X)
-            rightVal = self.right.evaluate(X)
-            return self.evaluate_inner(X,leftVal,rightVal)
+            left_val = self.left.evaluate(X)
+            right_val = self.right.evaluate(X)
+            return self.evaluate_inner(X,left_val,right_val)
         else:
             raise Exception("Arity > 2 is not allowed.")
 
@@ -71,14 +71,14 @@ class Node:
 
     def expand_fast(self):
         if type(self)==type(NodePlus()) or type(self)==type(NodeMinus()): # TODO: check if minus is happening
-            leftFact = self.left.expand_fast()
+            left_fact = self.left.expand_fast()
             right = self.right
             if type(self)==type(NodeMinus()):
                 right = NodeMultiply()
                 right.left = NodeConstant(-1)
                 right.right = copy.deepcopy(self.right)
-            rightFact = right.expand_fast()
-            return leftFact+rightFact
+            right_fact = right.expand_fast()
+            return left_fact+right_fact
         return [copy.deepcopy(self)]
 
     def is_allowed_left_argument(self, node_arg):
@@ -96,40 +96,31 @@ class Node:
         return hash(str(self))
 
     def all_nodes_exact(self):
-        thisList = [self]
+        this_list = [self]
         if self.arity==0:
-            return thisList
+            return this_list
         elif self.arity==1:
-            return thisList+self.left.all_nodes_exact()
+            return this_list+self.left.all_nodes_exact()
         elif self.arity==2:
-            return thisList+self.left.all_nodes_exact()+self.right.all_nodes_exact()
+            return this_list+self.left.all_nodes_exact()+self.right.all_nodes_exact()
         else:
             raise Exception("Arity greater than 2 is not allowed.")
 
     def size(self):
-        leftSize = 0
+        left_size = 0
         if self.left!=None:
-            leftSize = self.left.size()
-        rightSize = 0
+            left_size = self.left.size()
+        right_size = 0
         if self.right!=None:
-            rightSize = self.right.size()
-        return 1+leftSize+rightSize
+            right_size = self.right.size()
[…]

### 2022-11-27 rils_rols/rils_rols.py

@@ -15,18 +15,12 @@ warnings.filterwarnings("ignore")
 
 class RILSROLSRegressor(BaseEstimator):
 
-    improvements_by_type = {}
-    tries_by_type = {}
-    improvements_cnt = 0
-    tries_cnt = 0
-
     def __init__(self, max_fit_calls=100000, max_seconds=100, complexity_penalty=0.001, error_tolerance=1e-16,random_state=0):
         self.max_seconds = max_seconds
         self.max_fit_calls = max_fit_calls
         self.complexity_penalty = complexity_penalty
         self.random_state = random_state
         self.error_tolerance = error_tolerance
-
 
     def __reset(self):
         self.model = None
@@ -68,21 +62,20 @@ class RILSROLSRegressor(BaseEstimator):
         best_solution =  Solution([NodeConstant(0)], self.complexity_penalty)
         best_fitness = best_solution.fitness(X, y)
         self.main_it = 0
-        checked_preturbations = set([])
+        checked_perturbations = set([])
         start_solutions = set([])
         start_solution = copy.deepcopy(best_solution)
         while self.time_elapsed<self.max_seconds and Solution.fit_calls<self.max_fit_calls: 
             start_solutions.add(str(start_solution))
-            all_preturbations = self.all_preturbations(start_solution, len(X[0]))
+            all_perturbations = self.all_perturbations(start_solution, len(X[0]))
             pret_fits = {}
-            for pret in all_preturbations: 
+            for pret in all_perturbations: 
                 pret_ols = copy.deepcopy(pret)
                 pret_ols = pret_ols.fit_constants_OLS(X, y)
                 pret_ols_fit = pret_ols.fitness(X, y)
                 pret_fits[pret]=pret_ols_fit[0]
 
             sorted_pret_fits = sorted(pret_fits.items(), key = lambda x: x[1])
-
             impr = False
             p = 0
             for pret, r2Inv in sorted_pret_fits:
@@ -90,10 +83,10 @@ class RILSROLSRegressor(BaseEstimator):
                 self.time_elapsed = time.time()-self.start
                 if self.time_elapsed>self.max_seconds:
                     break
-                if str(pret) in checked_preturbations:
+                if str(pret) in checked_perturbations:
                     print(str(p)+"/"+str(len(sorted_pret_fits))+". "+str(pret)+" SKIPPED")
                     continue
-                checked_preturbations.add(str(pret))
[…]

### 2022-11-27 rils_rols/solution.py

@@ -1,7 +1,6 @@
 import copy
 from math import e, inf
 import math
-
 from .node import NodeAbs, NodeArcCos, NodeArcSin, NodeArcTan, NodeCeil, NodeConstant, NodeCos, NodeExp, NodeFloor, NodeLn, NodeMax, NodeMin, NodeMultiply, NodePlus, NodePow, NodeSgn, NodeSin, NodeTan, NodeVariable
 from .utils import R2, RMSE
 from sympy import *
@@ -9,7 +8,6 @@ from sympy.core.numbers import ImaginaryUnit
 from sympy.core.symbol import Symbol
 import numpy as np
 import statsmodels.api as sma
-
 
 class Solution:
 
@@ -24,6 +22,7 @@ class Solution:
         cls.fit_calls=0
 
     def __init__(self, factors, complexity_penalty):
+        # factors are basically subexpressions that enter linear combination, e.g. 2*x+3y*sin(x*y) --> factors = [2x, 3y*sin(x*y)]
         self.factors =  copy.deepcopy(factors)
         self.complexity_penalty = complexity_penalty
 
@@ -54,7 +53,6 @@ class Solution:
         for fact in self.factors:
             totSize+=fact.size()
         return totSize
-        
 
     def fit_constants_OLS(self, X, y):
         new_factors = []

### 2022-11-27 test_other.py

@@ -15,15 +15,12 @@ noise_level = 0
 complexity_penalty = 0.01 # 0.001 default
 
 instance_files = [f for f in listdir(instances_dir) if isfile(join(instances_dir, f))]
-#instance_files = ["random_04_01_0010000_04.data"]
 
 out_path = "out_{0}.txt".format(datetime.now().strftime("%Y_%m_%d_%H_%M_%S"))
 with open(out_path, "w") as f:
     f.write("Tests started\n")
 
 for fpath in instance_files:
-    #if not "random_04_01_0010000_04" in fpath:
-    #    continue
     print("Running instance "+fpath)
     with open(instances_dir+"/"+ fpath) as f:
         lines = f.readlines()

### 2022-11-27 paper_resources/doc/paper.tex

@@
 It brings researchers an easy handled environment to evaluate, compare, and analyze their methods.
-Among all benchmark sets, we involve two real-world inspired ground-truth benchmark sets that represent types of regression problems, into our computational evaluation:
+We involve two real-world inspired ground-truth benchmark sets that represent types of regression problems, into our computational evaluation:
 \begin{itemize}

### 2022-11-27 paper_resources/doc/paper.tex
Up to Section 4.4

@@
 All other algorithms from SRBench used the time limit that was equal or bellow 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
-We did not use the full time limit of 8 hours because it was not necessary -- we empirically concluded that there were no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
+We did not use the full time limit of 8 hours because it was not necessary -- we empirically concluded that there almost no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
 
@@
 It brings researchers an easy handled environment to evaluate, compare, and analyze their methods.
-We involve two real-world inspired ground-truth benchmark sets that represent types of regression problems, into our computational evaluation:
+We involve two real-world inspired ground-truth benchmark sets from SRBench, that represent various types of regression problems, into our computational evaluation:
 \begin{itemize}
@@
 	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}.
-Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.
-Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to the results reported in~\cite{la2021contemporary}.
+Some exact models (equations) of problem instances from this benchmark are listed in Table~\ref{tab:Feynamn-Eq}.
+Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to the results reported in~\cite{la2021contemporary} that used the same problem instances.
 
@@
 	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  in dependence of the current two states.
-These equations describes natural processes described by non-linear dynamics  exhibiting chaos.
+These equations describes natural processes modelled by non-linear dynamics  exhibiting chaos.
 The equations for some of the datasets that belong to this benchmark are shown in Table~\ref{table:strogatz-ODEs}.
@@
 \end{itemize}
-The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   symmetries, periodicity w.r.t.
+The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   various symmetries, periodicity w.r.t.
 some variables, internal separability on some variables etc.
-In that way, the search process and the search space can be pre-processed and thus significantly reduced.
+In that way, the search process and the search space can be pre-defined and thus significantly reduced.
 Thereby, some methods may get significant benefit with this regard, while some others may be in a subordinate situation.
-In order to permit any kind of favoritism in the input data, we generate a set of randomly generated (non-biased) SR problem instances; this benchmark set is labelled by \textsc{Random}.
+In order to permit any kind of favoritism caused by physical lows behind the input data, we generate a set of randomly generated (non-biased) SR problem instances; this benchmark set is therefore labelled by \textsc{Random}.
 These instances are generated according the following procedure.
@@
 
+Another purpose of having these instances is  systematically  providing conclusions on robustness and scalability of the RILS-ROLS method w.r.t.\ various instance size parameters.
+
 \subsection{Parameter tuning}
 The \textsc{RILS}-\textsc{ROLS} algorithm employs two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is fixed to 0.001(?), according to the preliminary experimental evaluation.
+The first parameter is fixed empirically to 0.001(?), according to the preliminary results.
 The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances.
@@
 \subsection{Comparison with other methods on the   ground--truth benchmark sets}
-In this section, we evaluate the performance of \textsc{RILS-ROLS} algorithm and compare it to the 13 other competitors from the literature.
+In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to the 13 other competitors from the literature.
 The numerical results are reported in terms of the three Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}.
 The results for the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, are given w.r.t.\   the following level of noise: 0.0 (no-noisy data), 0.001 (low-level noise), and 0.01 (high-level noise), respectively.
-In details, the white Gaussian noise was added to the target ($y$-axis) values as a fraction of the signal RMS value, applied also in~\cite{la2021contemporary}, i.e.
+In details, the white Gaussian noise is added to the target ($y$-axis) values as a fraction of the signal RMS value, applied also in~\cite{la2021contemporary}, i.e.
 for target noise level $\alpha$ we have
-$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{n} \sum {y_i^2}}\right),$$
+$$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{n} \sum _{i=1}^n{y_i^2}}\right),$$
 where $n$ relates to the number of items in the input data.
 
-Each table consists of three blocks.
-The first block reports the algorithm (by a row) whose performances are reported.
-The second block reports in two columns  percentages of the instances where the exact model has been found by respective algorithms on \textsc{Feynman} and \textsc{Strogatz} benchmark set, respectively.
-The third column of this block provides the overall summary exact percentage of success of the algorithm over all instances from the both benchmark sets.
-The third block displays the results of the respective algorithm in terms of the final $R^2$ score which indicates on accuracy of found solution -- by our criterion when the algorithm  at least reached the accuracy ($R^2$ score) of 0.999.
-Note that the termination of our algorithm may not always be triggered by reaching an appropriate $R^2$ score of 0.999, but also due to the reached time limit.
-These results are of a particular interest as they may point out on the presence of strong over-fitting in contrast to finding the right model.
-This block consists of three rows that indicate the percentage of instances where respective algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 \geq 0.999$ upon termination) on the both ground--truth benchmark sets separately, and the overall percentage of success rate (over all considered instances) w.r.t.
+Each table consists of three blocks. The performances of all (14) algorithms are displayed in respective rows.  
+The first block gives the label of the algorithm  whose performance is reported.
+The second block reports by two columns the relative percentages of all (10) algorithm runs on all problem instances for which the exact model has been found by respective algorithm  on \textsc{Feynman} and \textsc{Strogatz} benchmark set, respectively.
+The third column of this block provides the overall   relative exact percentage of success of the algorithm over all runs on all problem instances from the both benchmark sets.
+The third block displays the results of the respective algorithm in terms of   final $R^2$ score which indicate  on accuracy of found solution.
+The solution is considered accurate if it     produced an $R^2$ score larger that  0.999.
+Note that the termination of our algorithm may not always be triggered by reaching an appropriate $R^2$ score, but also due to the reached time limit.
+These kind of results are of a particular interest as they may point out on the presence of strong over-fitting of algorithms in contrast to the primary goal, that is finding the right model.
+This block consists of three columns that provide the relative percentage of algorithm runs on the instances where he algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 > 0.999$ upon termination) on the both ground--truth benchmark sets separately, and the overall percentage ov all (10) runs on all considered problem instances.
+%) w.r.t.
 the criterion of reaching the final accuracy of 0.999.
@@
 
-In short, the exact results, thus the number of instances (in percentages) for which the output of respective algorithm is able to find the exact model, are displayed in the second block of each of the tables.
-The numbers of instances (in percentages) for which each algorithms deliver a precise enough model (i.e.
-satisfying $R^2\geq 0.999$ upon its termination) are displayed in the third block of each of the tables.
+In short, the exact results, thus the number of algorithm runs over all instances (in percentages) for which the output of respective algorithm is able to find the exact model, are displayed in the second block of each  table.
+The numbers of runs   (in percentages) for which an algorithm  delivers a precise enough model (i.e.
+the outcome satisfying $R^2>  0.999$) are displayed in the third block of each of the tables.
 
@@
 \begin{itemize}
-	\item Concerning the exact percentages in case no noise is utilized in the input data of the instance problems, the best performing algorithm is our \textsc{RILS-ROLS}, able to find the solution that match to the right model on 57.84\% problems instances of the benchmark set \textsc{Feynman}; the same algorithm was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% cases.
-The second best performing  approach is \textsc{AI-Feynman}, successful in solving 55.78\% problem instances from \textsc{Feynman} set, and just 27.14\%  problem instances from benchmark set   \textsc{Strogatz}, respectively.
-All other approaches are performing much worse, and none of them is able to solve more than 30\% instances of any of the two considered ground-truth benchmark sets.
-	\item   Concerning the exact results in presence of the   noise  level of 0.001, our \textsc{RILS-ROLS} is still performing very well, having found an exact model for 42.08\% cases considering all problem instances from the both ground-truth benchmark sets.
-The second best approach is \textsc{AI-Feynman} which solved in total 31.89\% problem instances; as  already noticed, this algorithm performs better when applied on the instances from \textsc{Feynman} benchmark set than it is the case of \textsc{Strogatz} benchmark set.
+	\item Concerning the exact percentages in case when no noise is utilized in the input data, the best performing algorithm is our \textsc{RILS-ROLS}, able to find the solution that match to the right model on 57.84\% runs over all problems instances of the benchmark set \textsc{Feynman}; it was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% runs.
+The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\%   runs over all problem instances from \textsc{Feynman} set, and just 27.14\% runs over the problem instances from benchmark set   \textsc{Strogatz}, respectively.
+All other approaches are performing much worse, and none of them is able to delver the exact solution for more than 30\% runs over the instances of any of the two considered ground-truth benchmark sets.
+	\item   Concerning the exact results in presence of the   noise  level of 0.001, our \textsc{RILS-ROLS} is still performing very well, having found an exact model for 42.08\% runs considering all problem instances from the both ground-truth benchmark sets.
+The second best approach is \textsc{AI-Feynman} which is successful on 31.89\% runs over all problem instances; as  already noticed, this algorithm performs better when applied on the instances from \textsc{Feynman} benchmark set than it is the case of \textsc{Strogatz} benchmark set.
 Approach  \textsc{AFP-FE} shows to be robust w.r.t.
@@
 Other approaches reach   accuracy bellow 20\%.
-	\item  Concerning the exact results when the presence of noise is large, that is the noise level of 0.01,  our \textsc{RILS-ROLS} is still performing robustly, having found an exact model for  34.77\% problem instances considering the both ground-truth benchmark sets.
+	\item  Concerning the exact results when the presence of noise is large with  the noise level of 0.01,  our \textsc{RILS-ROLS} is still performing robustly, having found an exact model for  34.77\% runes over all problem instances considering the both ground-truth benchmark sets.
 The second best is   \textsc{AFP-FE} reaching 20\% correct solutions.
@@
 
-	\item When comparing performances of the algorithms in terms of number of instances for which the obtained final model reaches $R^2 \geq 0.999$, in case when no noise is integrated, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
+	\item When comparing performances of the algorithms in terms of algorithm runs for which the obtained final model fulfills an accuracy of $R^2 > 0.999$, in case when no noise is integrated, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
 However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching   better percentages of success than our algorithm: \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
@@
 In Figure~\ref{fig:time-avg-exact-noise}, average runtimes of the algorithms on those instance problems from the both ground-truth benchmark sets for which respective exact model has  been found, are compared.
-The algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant  and therefore included here, while others are omitted.
+The algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant  and therefore included here, while others are just omitted.
 The runtimes of each algorithm  are averaged w.r.t\  different levels of noise, and presented by a bar plot.
-Algorithms are labeled on $x$-axis, while respective average runtimes are shown on $y$-axis.
+Algorithms are labeled on $x$-axis, while respective average runtimes (oer all runs) are shown on $y$-axis.
 Note that $y$-axis is logarithmically scaled.
@@
 \begin{itemize}
-	\item When considering the instance problems with no noise is included, the lowest average runtime  is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228$s$).
+	\item When considering the instance problems with no-noisy input data, the lowest average runtime  is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228$s$).
 A slightly worse runtime is obtained by \textsc{Dsr} algorithm (232$s$).
-However, note that the exact percentage of \textsc{RILS}--\textsc{ROLS} is far better from \textsc{Dsr} (60.62\% vs.
+However, note that the relative exact percentage produced by \textsc{RILS}--\textsc{ROLS} is far better from \textsc{Dsr} (60.62\% vs.
 19.71\%).
-	All remaining approaches deliver an order of magnitude larger average runtimes than that of the \textsc{RILS}--\textsc{ROLS} method.
-	\item  When considering the instance problems with the noise level of 0.001,    the lowest average runtime  is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108$s$).
+	All remaining approaches deliver an order of magnitude larger average runtimes than that of the \textsc{RILS}--\textsc{ROLS} method in case of runs when the exact model has been reached.
+	\item  When considering the instance problems with the noise level of 0.001,    the lowest average runtime  to find the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108$s$).
 The second best average runtime is produced by \textsc{Dsr}, but this time significantly larger (622$s$) from the former algorithm.
-	\item When considering the instance problems with the noise level of 0.01, a similar conclusion may be drawn as that from the previous point. 
+	\item When considering the instance problems with the noise level of 0.01, a similar conclusion may be drawn as that from above. 
 \end{itemize}

### 2022-11-27 paper_resources/doc/paper.tex
Section 4.4.

@@
 
-In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{RILS}--\textsc{ROLS} to 14 other approaches over all problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{RILS}--\textsc{ROLS} to 14 other approaches over all algorithm runs of the problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
 Note that an indicator random variable is involved per each run of the algorithms.
-Thus, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model per each run.
-More precisely, we involved 1300 results into our statistical evaluation for each of the algorithms.
-Note that  results of some of the 14 competitors are not known from \url{https://cavalab.org/srbench/results/} due to some unknown reasons (most likely algorithm is terminated running out of memory or due to the chosen  value of an internal parameter).
+Thus, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model at that run.
+More precisely, we involved 1300 results into our statistical evaluation for each algorithm.
+Note that  results of some of the 13 competitors are not known from SRBench \url{https://cavalab.org/srbench/results/} due to   unknown reasons (most likely algorithm is terminated running out of memory or due to   chosen algorithm configuration settings).
 For these runs, we simply count a 0 for the score.
@@
 The outcome is represented by means of critical difference (CD) plots.
-In each CD plot, the (15) competitor approaches are placed on the horizontal axis according to their average ranking.
+In each CD plot, the (14) competitor approaches are placed on the horizontal axis according to their average ranking.
 Thereafter, the CD score is computed for a significance level of 0.05.
@@
 \begin{itemize}
-	\item  Concerning the instance problems where no noise is included, \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models.
+	\item  Concerning the instance problems where no noise is included, \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models over all runs.
 The second best average ranking is achieved by \textsc{AI-Feynman} algorithm.
-There is  statistically significant difference between these two approaches w.r.t.\ number of found exact models.
+There is  statistically significant difference between these two approaches w.r.t.\ number of found exact solutions.
 The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{RILS}-\textsc{ROLS} w.r.t.\ delivered average ranking.
-	\item    Concerning the instance problems with the included  level of noise of 0.001, \textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking in terms of the found exact models.
+	\item    Concerning the instance problems with the included  level of noise of 0.001, \textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking in terms of the found exact solutions.
 The second best ranking is obtained by \textsc{AI-Feynman} algorithm.
 There is again a statistically significant difference between the results obtained by these two approaches.
-The third best approach is \textsc{Afp-Fe} which performs statistically worse than \textsc{AI-Feynman} approach.
+The third best approach is \textsc{Afp-Fe} which performs statistically worse than \textsc{AI-Feynman}.
 	\item  Concerning the instance problems with the included noise level of  0.01, again, \textsc{RILS-ROLS} method produces the best average ranking according to positively evaluated runs, i.e.
 the runs with obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \textsc{Dsr}, and \textsc{Afp}.
-These latter three approaches perform statistically equal, but significantly worse than \text{RILS}-\textsc{ROLS} method.
+The  latter three approaches perform statistically equal, but significantly worse than \text{RILS}-\textsc{ROLS} method.
 	The fourth best approach according to delivered average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}.
 Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data.
-Thus, despite being efficient on no-noisy data, it seems that \textsc{AI-Feynman} is very sensitive to the level of noise increase, which is not that dramatically conspicuous with our \textsc{RILS}-\textsc{ROLS} method.
+Thus, despite being efficient on the no-noisy data, it seems that \textsc{AI-Feynman} is very sensitive w.r.t.
+increase in the level of noise, which is not that dramatically conspicuous with our \textsc{RILS}-\textsc{ROLS} method.
 

### 2022-11-27 paper_resources/doc/paper.tex
Paper polishing.

@@
 All other algorithms from SRBench used the time limit that was equal or bellow 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
-We did not use the full time limit of 8 hours because it was not necessary -- we empirically concluded that there almost no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
+We did not use the full time limit of 8 hours because we empirically concluded that there were almost no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
 
@@
 
-SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
-It brings researchers an easy handled environment to evaluate, compare, and analyze their methods.
-We involve two real-world inspired ground-truth benchmark sets from SRBench, that represent various types of regression problems, into our computational evaluation:
+SRBench (\url{https://cavalab.org/srbench/}) is an open-source benchmarking project which merges a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
+SRBench considers two types of symbolic regression problems: 1) \emph{ground-truth} problems, for which the exact model is known, and 2) \emph{black-box} problems, for which the exact model is not known.
+In our work, we consider only the former one, since \textsc{RILS-ROLS} was not designed to solve \emph{black-box} problems.
+There are two groups of instances in SRBench \emph{ground-truth} problem set:
 \begin{itemize}
-	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that describes   various natural laws.  
-	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}.
-Some exact models (equations) of problem instances from this benchmark are listed in Table~\ref{tab:Feynamn-Eq}.
-Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to the results reported in~\cite{la2021contemporary} that used the same problem instances.
+	\item \textsc{Feynman} instances are inspired by physics and formulas/models that describes various natural laws.  
+	There are 116 instances, where each one consists of $10^5$  samples (see \cite{udrescu2020ai} for more details).
+Some exact models (equations) of \textsc{Feynman} instances are listed in Table~\ref{tab:Feynamn-Eq}.
 
@@
 
-	\item \textsc{Strogatz} benchmark set from~\cite{la2016inference}. 
-	Each dataset is represented by a 2-state system of first-order, ordinary differential equations. 
-	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  in dependence of the current two states.
-These equations describes natural processes modelled by non-linear dynamics  exhibiting chaos.
-The equations for some of the datasets that belong to this benchmark are shown in Table~\ref{table:strogatz-ODEs}.
-These problem instances are downloadable from \url{https://github.com/lacava/ode-strogatz}.
-In overall, 14 ground-truth models are used to generate the problem instances used in the comparison, also in accordance with~\cite{la2021contemporary}.
+	\item \textsc{Strogatz} instances are introduced in \cite{la2016inference}. 
+	Each instance represents a 2-state system of first-order, ordinary differential equations. 
+	The aim of each problem is to predict the rate of change of the subsequent state.
+These equations describe natural processes modeled by non-linear dynamics exhibiting chaos.
+The equations for some of the datasets that belong \textsc{Strogatz} are shown in Table~\ref{table:strogatz-ODEs}.
+In overall, there are 14 \textsc{Strogatz} instances.
 
@@
 \end{itemize}
+
+\fxnote{ACA: do ovde sam pregledao}
 The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   various symmetries, periodicity w.r.t.
@@
 \newpage
+%\section*{References}
+\bibliographystyle{abbrv}	
+\bibliography{bib}
+
+\newpage
 \appendix
@@
 \section{Overview of \textsc{RILS}-\textsc{ROLS} python package}\label{sec:appendix-1}
-\fxnote{TODO}
+
+\textsc{RILS-ROLS} algorithm is available for install on the well-known Python package repository \url{https://pypi.org}, so it can be easily installed by typing commands:
+\begin{verbatim}
+	pip install rils-rols
+\end{verbatim}
+\textsc{RILS-ROLS} project page is at \url{https://pypi.org/project/rils-rols}. Here, one can find a minimal working example on how-to-use \textsc{RILS-ROLS}:
+
+\begin{verbatim}
+from rils_rols.rils_rols import RILSROLSRegressor
+from math import sin, log
+
+regr = RILSROLSRegressor()
+
+# toy dataset 
+X = [[3, 4], [1, 2], [-10, 20], [10, 10], [100, 100], [22, 23]]
+y = [sin(x1)+2.3*log(x2) for x1, x2 in X]
+
+# RILSROLSRegressor inherits BaseEstimator (sklearn)
+regr.fit(X, y)
+
+# this prints out the learned model
+print("Final model is "+str(regr.model))
+
+# applies the model to a list of input vectors
+X_test = [[4, 4], [3, 3]]
+y_test = regr.predict(X_test)
+print(y_test) 
+\end{verbatim}
+
+Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found at the project GitHub page \url{https://github.com/kartelj/rils-rols}.
 
@@
 
-\newpage
-%\section*{References}
-\bibliographystyle{abbrv}	
-\bibliography{bib}
-
 \end{document}

### 2022-11-27 formula_gen.py

@@ -1,140 +1,0 @@
-from msilib.schema import Error
-import sys
-import copy
-import math
-from rils_rols.node import Node, NodePlus, NodeVariable, NodeMinus, NodeMultiply, NodeDivide, NodeSqr, NodeSqrt, NodeLn, NodeExp, NodeSin, NodeCos, NodeConstant
-import random
-from sympy import symbols, simplify, lambdify, I
-import os
-import warnings
-
-warnings.filterwarnings("error")
-
-def random_tree(size, allowed_nodes, rg, parent=None):
-    if size<1:
-        raise Exception("Random tree cannot have size smaller than 1.")
-    if size==1:
-        allowed_terms = list(filter(lambda x: x.arity==0 , allowed_nodes)) 
-        node = copy.deepcopy(allowed_terms[rg.randrange(len(allowed_terms))])
-        return node
-    elif size == 2:
-        interm = list(filter(lambda x: x.arity==1, allowed_nodes))
-        node = copy.deepcopy(interm[rg.randrange(len(interm))])
-        node.left = random_tree(size-1, allowed_nodes, rg, node)
-        return node
-    else:
-        min_arity = 1
-        if parent is not None and parent.arity==1:
-            min_arity = 2 # this is to avoid unary compositions like f(g(h...)), although f(g(..)) can happen because of above elif, but no more than 2 unary compositions will happen in non-simplified form
-        interm = list(filter(lambda x: x.arity>=min_arity, allowed_nodes))
-        node = copy.deepcopy(interm[rg.randrange(len(interm))])
-        if node.arity == 1:
-            node.left = random_tree(size-1, allowed_nodes, rg, node)
-        else:
-            if rg.randint(0,1)==0:
-                left_size = math.floor(size/2)
-                right_size = size - left_size - 1
-            else:
-                right_size = math.floor(size/2)
-                left_size = size - right_size - 1
-            node.left = random_tree(left_size, allowed_nodes, rg, node)
-            node.right = random_tree(right_size, allowed_nodes, rg, node)
-        return node
-
-def contains_all_vars(expr : Node, var_cnt):
-    for i in range(var_cnt):
-        if not expr.contains(NodeVariable(i)):
-            return False
-    return True
-
[…]

### 2022-11-27 test_other.py

@@ -1,64 +1,0 @@
-from datetime import datetime
-from random import Random
-from rils_rols.rils_rols import RILSROLSRegressor
-from rils_rols import utils
-from os import listdir
-from os.path import isfile, join
-
-
-instances_dir = "paper_resources/chemistry_data/instances" 
-random_state = 23654
-train_perc = 0.75
-time = 3600
-max_fit = 10000000
-noise_level = 0
-complexity_penalty = 0.01 # 0.001 default
-
-instance_files = [f for f in listdir(instances_dir) if isfile(join(instances_dir, f))]
-
-out_path = "out_{0}.txt".format(datetime.now().strftime("%Y_%m_%d_%H_%M_%S"))
-with open(out_path, "w") as f:
-    f.write("Tests started\n")
-
-for fpath in instance_files:
-    print("Running instance "+fpath)
-    with open(instances_dir+"/"+ fpath) as f:
-        lines = f.readlines()
-        train_cnt = int(len(lines)*train_perc)
-        rg = Random(random_state)
-        rg.shuffle(lines)
-        X_train = []
-        y_train= []    
-        X_test = []
-        y_test = []
-        for i in range(len(lines)):
-            line = lines[i]       
-            tokens = line.split(sep="\t")
-            newX = [float(t) for t in tokens[:len(tokens)-1]]
-            newY = float(tokens[len(tokens)-1])
-            if i<train_cnt:
-                X_train.append(newX)
-                y_train.append(newY)
-            else:
-                X_test.append(newX)
-                y_test.append(newY)
-
-        y_train = utils.noisefy(y_train, noise_level, random_state)
-
-    if noise_level == 0:
-        rils = RILSROLSRegressor(max_fit_calls=max_fit, max_seconds=time, random_state = random_state, complexity_penalty=complexity_penalty)
-    else:
-        rils = RILSROLSRegressor(max_fit_calls=max_fit, max_seconds=time, random_state = random_state, error_tolerance=noise_level, complexity_penalty=complexity_penalty)
-    rils.fit(X_train, y_train)
-    report_string = rils.fit_report_string(X_train, y_train)
-    rils_R2 = -1
-    rils_RMSE = -1
-    try:
-        yp = rils.predict(X_test)
-        rils_R2 = utils.R2(y_test, yp)
-        rils_RMSE = utils.RMSE(y_test, yp)
[…]

### 2022-11-27 paper_resources/doc/paper.tex
Appendix A: stylized acc. to Python style

@@
 \npthousandsep{}
+\usepackage{pythonhighlight}
 
@@
 \textsc{RILS-ROLS} algorithm is available for install on the well-known Python package repository \url{https://pypi.org}, so it can be easily installed by typing commands:
-\begin{verbatim}
+\begin{python} 
 	pip install rils-rols
-\end{verbatim}
+\end{python}
 \textsc{RILS-ROLS} project page is at \url{https://pypi.org/project/rils-rols}. Here, one can find a minimal working example on how-to-use \textsc{RILS-ROLS}:
 
-\begin{verbatim}
+\begin{python}
 from rils_rols.rils_rols import RILSROLSRegressor
@@
 print(y_test) 
-\end{verbatim}
-
-Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found at the project GitHub page \url{https://github.com/kartelj/rils-rols}.
+\end{python}
+
+Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found under the project GitHub page \url{https://github.com/kartelj/rils-rols}.
 

### 2022-11-27 setup.py
Dependencies added in the setup.py.

@@ -5,7 +5,7 @@ with open("README.md", "r") as fh:
 
 setup(
     name='rils-rols',
-    version='0.4',
+    version='0.5',
     description='RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares',
     long_description= long_description,
     long_description_content_type  = "text/markdown",
@@ -20,5 +20,6 @@ setup(
     ],
     python_requires= ">=3.6",
     py_modules=["rils-rols"],
-    package_dir = {'rils-rols':'rils_rols'}
+    package_dir = {'rils-rols':'rils_rols'}, 
+    install_requires=["scikit-learn", "sympy", "statsmodels"],
 )

### 2022-11-27 paper_resources/doc/paper.tex

@@
 These instances are generated according the following procedure.
-\fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}
+\fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance + koliko instanci, itd.}
 
@@
 
-In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{RILS}--\textsc{ROLS} to 14 other approaches over all algorithm runs of the problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
-Note that an indicator random variable is involved per each run of the algorithms.
-Thus, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model at that run.
-More precisely, we involved 1300 results into our statistical evaluation for each algorithm.
+In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{RILS}--\textsc{ROLS} to 13 other approaches over all algorithm runs on the problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+Note that an indicator random variable is involved for each run of each algorithm.
+More precisely, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model at specific run.
+More precisely, we involved 1300 results into our statistical evaluation per each algorithm.
 Note that  results of some of the 13 competitors are not known from SRBench \url{https://cavalab.org/srbench/results/} due to   unknown reasons (most likely algorithm is terminated running out of memory or due to   chosen algorithm configuration settings).
-For these runs, we simply count a 0 for the score.
+For these runs, we simply indicate a 0 as their score.
 
@@
 	\item  Concerning the instance problems with the included noise level of  0.01, again, \textsc{RILS-ROLS} method produces the best average ranking according to positively evaluated runs, i.e.
-the runs with obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \textsc{Dsr}, and \textsc{Afp}.
+those runs with found  exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \textsc{Dsr}, and \textsc{Afp}.
 The  latter three approaches perform statistically equal, but significantly worse than \text{RILS}-\textsc{ROLS} method.
@@
 Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data.
-Thus, despite being efficient on the no-noisy data, it seems that \textsc{AI-Feynman} is very sensitive w.r.t.
-increase in the level of noise, which is not that dramatically conspicuous with our \textsc{RILS}-\textsc{ROLS} method.
+Thus, despite being efficient when comes to the no-noisy data,  \textsc{AI-Feynman} shows to be very sensitive w.r.t.
+increase of the level of noise, which is not that dramatically conspicuous with our \textsc{RILS}-\textsc{ROLS} method.
 
@@
 
-In this section we study the scalability of our method in terms of the size of  instance problems and  the presence of different noise level in the input data.
-
-First, we divide our benchmark sets into three parts as follows. 
+In this section we study the scalability of our method in terms of the size of  instance problems and  the presence of different noise levels in the input data.
+First, for the shake of simplicity of presenting,  we split the instances from \textsc{Random} benchmark sets into three parts as follows.
 \begin{itemize}
-	\item \textit{Small--sized instances}: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 3 to 7 nodes belong to this sub-set.
-	\item \textit{Middle--sized instances}:  all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 8 to 11 nodes belong to this sub-set.
-	\item \textit{Large--sized instances}: all instances from \textsc{Random} benchmark whose the corresponding exact models tree representations have from 12 to 15 nodes belong to this sub-set. 
+	\item \textit{Small--sized instances}: any instance  from \textsc{Random} benchmark whose   corresponding exact model  tree representation  has from 3 to 7 nodes belongs to this sub-set.
+	\item \textit{Medium--sized instances}:  any instance  from \textsc{Random} benchmark whose   corresponding exact model tree representation  has from 8 to 11 nodes belongs to this sub-set.
+	\item \textit{Large--sized instances}: any instances from \textsc{Random} benchmark whose   corresponding exact model  tree representation  has from 12 to 15 nodes belongs to this sub-set. 
 \end{itemize}
 
-The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped with accordance to the (three) formed sub-groups ($x$-axis); for each of them the exact percentage rate of success of \textsc{RILS}--\textsc{ROLS} algorithm is shown ($y$-axis).
-The following conclusions may be drawn from here:
+The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped with accordance to the above (three) formed sub-groups ($x$-axis); for each of them relative exact percentage rate   of \textsc{RILS}--\textsc{ROLS} algorithm is shown ($y$-axis).
+The following conclusions may be drawn from there.
 
 \begin{itemize}
-	\item   As expected, the exact percentage success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% for the no-noisy data.
-For noisy data, the success rate of the algorithm gets decreased as the level of noise increases.
-For example, on the small-sized problem instances with the noise level  of 0.0001, and 0.01, the exact percentage of \textsc{RILS}--\textsc{ROLS} is still reasonably high, at about 55\%~ and 34 \%, respectively.
-	\item For the middle-sized instance problems, the exact percentage rate is slightly bellow 50\%.
-It also decreases by increasing the level of noise in the target data; for the highest level of noise (of 0.01), the success rate of \textsc{RILS}-\textsc{ROLS} method is just about 6\%.
-	\item For the large-sized instance problems with no noise is utilized, the exact percentage of \textsc{RILS}--\textsc{ROLS} algorithm is at about 25\%, which means that the increase in the size of exact models affects the algorithm's performance, but within the expected range.
-
-	\item From the above, we can conclude that the size of exact models (solutions) and the increase of the noise level both contribute to overall performance of our \textsc{RILS}--\textsc{ROLS} method.
-The exact percentage rate of the algorithm seems decreasing linearly  in the (exact) model size, regardless of the noise level values.
-
-	\item Concerning the high--accuracy percentages delivered by \textsc{RILS}--\textsc{ROLS} algorithm -- that is the percentage of problem instances for which the algorithm's termination yielded a model with $R^2 \geq 0.999$ -- for the small--sized problem instances with no noise is recorded, it is almost at the perfect score (i.e.
-$\approx$100\%).
-In the presence of a low noise level (equals to 0.001), the percentages of instance problems with the high--accuracy is still high, at about 95\%.
+	\item   As expected, the exact percentage success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% (over all XXx runs) in case of no-noisy data.
+For the noisy data, the exact success rate is getting decreased as the level of noise increases.
+For example, on the small-sized problem instances with the noise level  of 0.0001, and 0.01, the exact percentage achieved by \textsc{RILS}--\textsc{ROLS} algorithm is still reasonably high, at about 55\%~ and 34 \%, respectively.
+	\item For the medium-sized instance problems where noise is not presented, the exact percentage rate of \textsc{RILS}-\textsc{ROLS} is slightly bellow 50\%.
+It also decreases by increasing the level of noise in the target data; for the highest level of noise (of 0.01), the success rate of \textsc{RILS}-\textsc{ROLS} method is just at about 6\%.
+	\item For the large-sized instance problems where no noise is utilized, the exact percentage rate of \textsc{RILS}--\textsc{ROLS} algorithm is at about 25\%, which means that the increase in the size of exact models affects the algorithm's performance, but not dramatically.
+
+	\item From the above, we can conclude that the size of exact models (solutions) and the increase of   level of noise both contribute to overall performance of our \textsc{RILS}--\textsc{ROLS} method.
+However, the exact percentage rate of the algorithm seems to decrease linearly  in the size of (exact) model, regardless of the noise level values.
+
+	\item Concerning  the percentage of  runs over all random instances for which \textsc{RILS-ROLS} terminates by producing an accurate model, that is a model with $R^2 > 0.999$, for the small--sized problem instances where no noise is included, \textsc{RILS}-\textsc{ROLS} delivers  the perfect score almost.
+In the presence of a low noise level (equals to 0.001), this percentage  is still holding high, at about 95\%.
 In case when the high level of noise (equals to 0.01) is presented in the input data, these percentages stagnate, but still are at a respectable 66\%.
 %small-sized instances it reaches a high--precision of $R^2=0.999$ upon termination.
-	As we pointed out already, a half of these math to the respectable exact models.
-
-	\item Concerning the high--accuracy percentage of the \textsc{RILS}--\textsc{ROLS} algorithm on the middle-sized instance problems when the input data are free of the noise, it is obtained on 65\% cases.
-The noisy the data are, the accuracy percentages of the algorithm, as expected, drop off; however, not so dramatically.
-For the level of noise of 0.01, the high--accuracy of the final solution is reported on $\approx$30\% cases.
-
-	\item Concerning the high--accuracy percentages of the \textsc{RILS}--\textsc{ROLS} algorithm on the large-sized instance problems with no noise, it gets 60\%.
-Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2\geq 0.999$ for the outcome  upon termination) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of the considered large--sized instance problems.
+	As  pointed out already, for a half of these cases the respectable exact models were found by the algorithm.
+
+	\item Concerning  the medium-sized instance problems when the input data are free of the noise,   the final outcome reached the high precision in 65\% of all algorithm runs.
+The noisy the data are, these percentages, as expected, drop off; however, it is not so dramatically.
+For the level of noise of 0.01, the high--accuracy of the final solution is reported on $\approx$30\% of all runs.
+
+	\item Concerning  the large-sized instance problems with no noise, the  final solution reached the high precision in 60\% of all runs.
+Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2> 0.999$ for  the  outcome) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of all runs concerning the large--sized instance problems.
 
@@
 
-In this paragraph we investigate the  scalability of our \textsc{RILS}--\textsc{ROLS} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
+\fxnote{Marko: revidirano do ovog dijela...}In this paragraph we investigate the  scalability of our \textsc{RILS}--\textsc{ROLS} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
 There is three bar plots shown per each level of noise.

### 2022-11-28 paper_resources/doc/paper.tex
Up to Section 5: revisions

@@
 			};
-			\addlegendentry{No noise}
+			\addlegendentry{$\alpha=0.00$}
 
@@
 			};
-			\addlegendentry{Noise level 0.001}
+			\addlegendentry{$\alpha=0.001$}
 
@@
 			};
-			\addlegendentry{Noise level 0.01}
+			\addlegendentry{$\alpha=0.01$}
 		\end{axis}
@@
 
-\fxnote{Marko: revidirano do ovog dijela...}In this paragraph we investigate the  scalability of our \textsc{RILS}--\textsc{ROLS} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
-There is three bar plots shown per each level of noise.
-These are shown by Figures~\ref{fig:compExact_noise_varcnt} and~\ref{fig:compExact_noise_varsizes}.
-The instances are grouped according to the different variable count/size of respective exact models ($x$-axis).
-For each group, the exact percentages of success rate of \textsc{RILS}--\textsc{ROLS} algorithm on the instance group is shown ($y$-axis).
+In the rest of the section,  we investigate scalability of our \textsc{RILS}--\textsc{ROLS} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
+There are three bar plots generated per each level of noise, shown by Figures~\ref{fig:compExact_noise_varcnt}--\ref{fig:compExact_noise_varsizes}.
+The instances are grouped according to the different variable count/size of respective exact models ($x$-axis) that correspond to them.
+For each group, the exact percentages obtained by \textsc{RILS}--\textsc{ROLS} algorithm group are shown on $y$-axis.
 
@@
 \begin{itemize}
-	\item The exact percentage rate of \textsc{RILS}--\textsc{ROLS} algorithm  slightly decrease as the expected number of variables gets larger when no noise is presented in the data.
-	\item The exact percentages drop off with the presence of a larger noise level. Thus, the higher the noise level, the smaller the exact percentages are.
-	\item Interestingly, in the presence of noise, the highest exact percentages are not obtained on the problem instances whose exact models consists of a single variable, but two or three.
-We argue it by the fact that the early phase of the algorithm will more likely try to include additional variables in the solution at the cost of increasing the model accuracy to ensure improving the fitness value over iterations.
-In the presence of the zero noise, OLS method will more likely find a smaller model (on $\approx$ 50\% cases) with a high accuracy that fits to the (no-noisy) input data than the case of noisy data.
+	\item For the no-noisy data, the exact percentage rate of \textsc{RILS}--\textsc{ROLS} algorithm  slightly decrease as the expected number of variables increases in the exact models. 
+	\item The exact percentages drop off with the presence of a larger noise level. As expected, the higher the noise level, the smaller the exact percentages are.
+	\item Interestingly, in the presence of noise in the data, the highest exact percentages are not obtained for the problem instances which have exact models consisted of a single variable, but two or three.
+We argue it by the fact that the early phase of the algorithm will more likely trying to include additional variables in current solution at the cost of increasing the model accuracy to ensure improving the fitness value over iterations.
+For the no--noisy data, OLS method will more likely find a small-sized high-accuracy model (in our experiments that happened on $\approx$ 50\% runs) that fits to the (no-noisy) input data than the case of noisy data.
 When the data is noisy, the decision of adding more variables at the beginning is likely to be forced than just dealing with short-size solutions.
-By the algorithm's progression, it gets harder improving the best fitness value by adding variables, and other operations are more frequently involved than in previous iterations.
+%By the progression of the algorithm, it gets harder improving the best fitness value by adding variables, and other operations are more frequently involved than in previous iterations.
 %This conclusion also correlates to the shape of fitness function given by Equation~(\ref{eq:fitness}) where the first two product terms there are already small (close to 1).
@@
 \begin{itemize}
-	\item The exact percentages are decreased with the increase of size of exact models, in case of any level of noise utilized on the target values.  %within the input data.
-	\item The highest exact percentages, which are higher than 70\%, are noticed for the small-sized problem instances  (the size ranges from 3 to 7) exact models.
-However, for the same sizes, for noisy data, these percentages are significantly lower; for example, in case of models of size 7 and the level of noise of 0.001 and 0.01, the exact percentages obtained are 20\% and 10\%, respectively.
-
-	\item   For the problem instances with a largest size of (exact) models for no noisy data, exact percentages are never lower than 20\%. The opposite holds for noisy data. 
+	\item The exact percentages are decreased with increase in  the size of exact models, in case of any level of noise utilized on the target values.  %within the input data.
+	\item The highest exact percentages, which are larger than 70\%, are noticed in case of the small-sized problem instances  (the size of models ranges from 3 to 7).
+However, for the same sizes, for noisy data, these percentages are significantly lower; for example, in case of the instances whose exact models are of size 7 when utilizing the level of noise of 0.001 and 0.01, the exact percentages obtained are 20\% and 10\%, respectively.
+
+	\item   For the problem instances with the largest size of (exact) models in case of the no noisy data, exact percentages are never lower than 20\%. The opposite holds for noisy data. 
 \end{itemize}
@@
 
-When one concerns of runtime analysis of the \textsc{RILS}--\textsc{ROLS} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are displayed in Figure~\ref{fig:runtime_rils_rols}.
-The instances are grouped w.r.t.\ number of variables included into corresponding exact model ($x$-axis).
+When one concerns of the runtime analysis of \textsc{RILS}--\textsc{ROLS} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are displayed in Figure~\ref{fig:runtime_rils_rols}.
+The instances are grouped w.r.t.\ number of variables involved into corresponding exact models ($x$-axis).
 The following conclusions may be drawn from there.
@@
 	\item Note that the average runtime in case of the instances whose exact models have the largest number of variables (5) is just about 200$s$.
-	\item The two above-mentioned points indicate efficacy of our method especially in case of expected exact models of a small and middle sizes with small--to--middle levels of noise included in the input data.
-In these cases, the algorithm is able to deliver the reasonable exact percentages, which are always larger than 50\%.
-Note that models which have more compact representations (thus, small in their size) are desirable in many areas of natural sciences due to easier interpret-ability more than models represented by a more complex expression.
+	\item The two above-mentioned points indicate efficacy of our method especially in case of the instances with small-to-medium sized exact models in the presence of small--to--middle noise levels included in the input data.
+In these cases, the algorithm is able to deliver a reasonable exact percentage rate, which are always larger than 50\%.
+Note that models which have more compact representations (thus, small in their size) are desirable in many areas of natural sciences as they are easy interpret-able than models represented by a more complex mathematical formula.
 \end{itemize}

### 2022-11-28 paper_resources/doc/paper.tex
Section 5: polishing

@@
 			};
-			\addlegendentry{Noise level 0.01}
+			\addlegendentry{$\alpha= 0.01$}
 		\end{axis}
@@
 
-In this paper, we dealt with solving the well--known Symbolic regression (SR)  problem. SR problem is a generalization of more interdisciplinary known problems of linear and logistic regression.    
-We proposed a meta-heuristic approach, called \textsc{RILS}-\textsc{ROLS}.
-Our approach is built upon the Iterated local search (ILS) scheme.
-The first crucial concept within this scheme is utilizing the ordinary least square method to efficiently determine internal coefficients that are the best fitting to the candidate solution.
-Thus, the search process is primarily focused on considering already promising solutions in the continuous part of the search space rather than applying enhanced heuristics to search for those coefficients.
+In this paper, we dealt with solving the well--known Symbolic regression (SR)  problem.
+SR problem is a generalization of more interdisciplinary known problems such as linear and logistic regression.
+We proposed a meta-heuristic approach, called \textsc{RILS}-\textsc{ROLS}, which is built upon the Iterated local search (ILS) scheme.
+The first crucial concept within this scheme is utilizing the ordinary least square method to efficiently determine best-fitting internal coefficients to the candidate solution.
+% Thus, the search process is primarily focused on considering already promising solutions in the continuous part of the search space rather than applying enhanced heuristics to search for those coefficients.
 Another key aspect is the utilization of a carefully constructed fitness function in the search, which appeared as a combination of three important scores: RMSE, $R^2$  scores and the size of the model (solution).
-Last but not least, a carefully constructed local search is applied systematically exploring solutions obtained as 1--perturbations of the considered solution.
+Last but not least, a carefully constructed local search is applied systematically exploring solutions obtained as 1--perturbations of the considered solution, represented as trees.
 1--perturbations of a solution are based on applying the six per-node change operations on the solution's tree representation.
 
-\textsc{RILS-ROLS} method is compared to the 14 other competitor algorithms from the literature on the two ground truth benchmark sets from literature, namely \textsc{Feynman} and \textsc{Strogatz}.
+\textsc{RILS-ROLS} method is compared to the 14 other competitor algorithms from the literature on the two ground--truth benchmark sets from the literature, namely \textsc{Feynman} and \textsc{Strogatz}.
 Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.
 The experimental evaluation confirmed the efficiency of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmarks in the presence of all three different levels of noise in the input data.
-In all cases, new best exact percentages are obtained using \textsc{RILS-ROLS} method.
+In all cases, new best exact percentages are obtained by our \textsc{RILS-ROLS} method.
 More in details,
-our algorithm was able to obtain the right model on 60.62\%, 42.08\%, and 34.77\% problem instances in the presence of the noise level of 0.0, 0.001, and 0.01, respectively.
-Just for the shake of comparisons, the second best approach \textsc{AI-Feynman}, when the noise level of 0.0 and 0.001 is included, obtained an exact percentage rate of 52.65\%, and 31.89\%, respectively.
+our algorithm was able to obtain the right model on 60.62\%, 42.08\%, and 34.77\% runs over all considered problem instances in the presence of different noise levels: 0.0, 0.001, and 0.01, respectively.
+For the shake of comparisons, the second best approach \textsc{AI-Feynman}, when the noise level of 0.0 and 0.001 is included, obtains the exact percentages of 52.65\%, and 31.89\%, respectively.
 In case of the highest noise level, the second best approach was \textsc{Afp-Fe}, obtaining an exact percentage rate of 20\%.
-Additionally, the scalability and robustness of this method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
+Additionally, the scalability and robustness of \textsc{RILS}-\textsc{ROLS} method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
 
@@
 VNS   utilizes a more stronger and systematic system of solutions diversification and thus escaping from local optima could be much easier and the convergence much faster.
-Additionally, as proof of the efficiency and benefits of our algorithm, this tool could be applied to solving problems from various problem domains out of the area of computer science, for example from physics or chemistry, to help for setting up reasonable hypotheses or to obtain valuable insights on experimental evaluations.
+Additionally, as proof of the efficiency and usefulness of our algorithm, this tool could be applied to solving problems from various problem domains out of the area of computer science, for example from physics or chemistry, to help for setting up reasonable hypotheses or to obtain valuable insights on obtained experimental evaluations.
 

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
BMC template: converted

--- 2022-11-28 paper_resources/doc/paper.tex
@@
-\documentclass[a4paper,12pt]{elsarticle}
-% vim: tw=0 wm=0
-
-\setcounter{tocdepth}{3}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{longtable}
-\usepackage{comment}
-\usepackage{placeins}
-\usepackage{mathtools}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{enumitem}
-\usepackage[utf8]{inputenc}
-\usepackage{booktabs}
-\usepackage{array}
-\usepackage[pdfencoding=auto,psdextra]{hyperref}
-\usepackage{booktabs}
-\usepackage{bookmark}% faster updated bookmarks
-\usepackage{hypcap} % fix the links
-\evensidemargin\oddsidemargin
-\usepackage{graphicx}
-\pagestyle{plain}
-\usepackage{xcolor}
-\newcommand\ToDo[1]{\textcolor{red}{#1}}
+%% BioMed_Central_Tex_Template_v1.06
+%%                                      %
+%  bmc_article.tex            ver: 1.06 %
+%                                       %
+
+%%IMPORTANT: do not delete the first line of this template
+%%It must be present to enable the BMC Submission system to
+%%recognise this template!!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% https://www.biomedcentral.com/getpublished                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% https://miktex.org/                                             %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
+\documentclass{bmcart}
+
+%%% Load packages
+\usepackage{amsthm,amsmath}
 \usepackage{tabularx}
@@
 \usepackage{amsthm}
-%\usepackage{changes}
+
 \usepackage{tikz}
-\usepackage{fullpage}
+%\usepackage{fullpage}
 \usepackage{calc}
@@
 \usepackage{pgfplots}
-\pgfplotsset{compat=1.16}
-
-\usepackage{numprint}
-\npdecimalsign{.}
-\npthousandsep{}
+%\pgfplotsset{compat=1.16}
 \usepackage{pythonhighlight}
 
-\usepackage[draft,nomargin,inline]{fixme}
-\fxsetface{inline}{\itshape}
-\fxsetface{env}{\itshape}
-%\fxuselayouts{margin}
-%\fxuselayouts{inline}
-\fxusetheme{color}
-
+\usepackage{mathtools}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{url}
-\newcommand{\keywords}[1]{\par\aDSvspace\baselineskip
-	\noindent\keywordname\enspace\ignorespaces#1}
-
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\definecolor{canaryyellow}{rgb}{1.0, 0.94, 0.0}
-\definecolor{brightgreen}{rgb}{0.4, 1.0, 0.0}
-\definecolor{jazzberryjam}{rgb}{0.65, 0.04, 0.37}
-
-%defining of command
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
-\newcommand\str[1]{\texttt{#1}}
-\newcommand\pL[1][]{\ensuremath{p^{\mathrm{L}#1}}}
-\newcommand\pR[1][]{\ensuremath{p^{\mathrm{R}#1}}}
-\newcommand\qL{\ensuremath{q^\mathrm{L}}}
-\newcommand\qR{\ensuremath{q^\mathrm{R}}}
-\newcommand\pLH{\ensuremath{\hat{p}^\mathrm{L}}}
-\newcommand\pRH{\ensuremath{\hat{p}^\mathrm{R}}}
-\newcommand{\Vext}{\ensuremath{V_\mathrm{{ext}}}}
-\newcommand\UB{\ensuremath{\mathrm{UB}}}
-\newcommand\Sigmand{\ensuremath{\Sigma^\mathrm{nd}}}
-\newcommand{\mdmwnpp}{MDMWNPP\xspace}
-
-\renewcommand{\labelenumii}{\theenumii}
-\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}
-\setlength{\leftmarginii}{1.8ex}
 \raggedbottom
-\algnewcommand\algorithmicforeach{\textbf{for each}}
-\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
+%\algnewcommand\algorithmicforeach{\textbf{for each}}
+%\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
 
@@
 
+\usepackage{fixme}
+
+%\RequirePackage[numbers]{natbib}
+%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
+%\RequirePackage{hyperref}
+\usepackage[utf8]{inputenc} %unicode support
+%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                             %%
+%%  If you wish to display your graphics for   %%
+%%  your own use using includegraphic or       %%
+%%  includegraphics, then comment out the      %%
+%%  following two lines of code.               %%
+%%  NB: These line *must* be included when     %%
+%%  submitting to BMC.                         %%
+%%  All figure files must be submitted as      %%
+%%  separate graphics through the BMC          %%
+%%  submission process, not included in the    %%
+%%  submitted article.                         %%
+%%                                             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\def\includegraphic{}
+%\def\includegraphics{}
+
+%%% Put your definitions there:
+\startlocaldefs
+\endlocaldefs
+
+%%% Begin ...
 \begin{document}
 
-	%\setlength{\parindent}{0pt}  % disallow indentations
-	%\numberwithin{table}{1}
-	%\mainmatter  % start of an individual contribution
-
-	% first the title is needed
-	\title{\textsc{RILS}-\textsc{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
-
-	\author[1]{Aleksandar Kartelj}
-	\author[2]{Marko Djukanovi\'c}
-	\address[1]{$kartelj@matf.bg.ac.rs$, \\  Faculty of Mathematics, University of Belgrade, Serbia}
-	\address[2]{$ marko.djukanovic@pmf.unibl.org$,\\   Faculty of Natural Sciences and Mathematics, University of Banja Luka, Bosnia and Herzegovina}
-	\begin{abstract}
+%%% Start of article front matter
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{ {RILS}-{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors here                   %%
+%%                                          %%
+%% Specify information, if available,       %%
+%% in the form:                             %%
+%%   <key>={<id1>,<id2>}                    %%
+%%   <key>=                                 %%
+%% Comment or delete the keys which are     %%
+%% not used. Repeat \author command as much %%
+%% as required.                             %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author[
+  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
+  corref={aff1},                       % id of corresponding address, if any
+% noteref={n1},                        % id's of article notes, if any
+  email={kartelj@matf.bg.ac.rs}   % email address
+]{\inits{A.K.}\fnm{Aleksandar} \snm{Kartelj}}
+\author[
+  addressref={aff2},
+  email={marko.djukanovic@pmf.unibl.org}
+]{\inits{M.DJ.}\fnm{Marko} \snm{Djukanović}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\address[id=aff1]{%                           % unique id
+  \orgdiv{Department of Informatics, Faculty of Mathematics},             % department, if any
+  \orgname{University of Belgrade},          % university, etc
+  \city{Belgrade},                              % city
+  \cny{Serbia}                                    % country
+}
+\address[id=aff2]{%
+  \orgdiv{Faculty of Sciences and Mathematics},
+  \orgname{University of Banja Luka},
+  %\street{},
+  %\postcode{}
+  \city{Banja Luka},
+  \cny{Bosnia and Herzegovina}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\begin{artnotes}
+%%\note{Sample of title note}     % note to the article
+%\note[id=n1]{Equal contributor} % note, connected to author
+%\end{artnotes}
+
+\end{fmbox}% comment this for two column layout
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                           %%
+%% The Abstract begins here                  %%
+%%                                           %%
+%% Please refer to the Instructions for      %%
+%% authors on https://www.biomedcentral.com/ %%
+%% and include the section headings          %%
+%% accordingly for your article type.        %%
+%%                                           %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{abstractbox}
+
+\begin{abstract} % abstract
 In this paper, we solve the well-known symbolic regression problem.
@@
 \end{abstract}
-	\maketitle
-
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The keywords begin here                  %%
+%%                                          %%
+%% Put each keyword in separate \kwd{}.     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{keyword}
+\kwd{Symbolic regression}
+\kwd{Iterated local search}
+\kwd{Ordinary least square}
+\end{keyword}
+
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
+\end{abstractbox}
+%
+%\end{fmbox}% uncomment this for two column layout
+
+\end{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                            %%
+%% The Main Body begins here                  %%
+%%                                            %%
+%% Please refer to the instructions for       %%
+%% authors on:                                %%
+%% https://www.biomedcentral.com/getpublished %%
+%% and include the section headings           %%
+%% accordingly for your article type.         %%
+%%                                            %%
+%% See the Results and Discussion section     %%
+%% for details on how to create sub-sections  %%
+%%                                            %%
+%% use \cite{...} to cite references          %%
+%%  \cite{koon} and                           %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
+%%                                            %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+% <put your article body there>
+
+%%%%%%%%%%%%%%%%
+%% Background %%
+%%
 	\section{Introduction}\label{sec:introduction}
@@
 
-	%\section{Literature review}\label{sec:lit-rev}
-
 	\section{The proposed RILS-ROLS method}\label{sec:rils}
@@
 \end{align*}
-	%The above system can be transformed to 
-	%\begin{align*}
-	%	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
-	%	 & \sum y_i  = k \sum x_i + b \cdot d. 
-	%  \end{align*}
 
@@
 
-%\fxnote{Dati neku smislenu procjenu kompleksnosti algoritma, ako to nije pretesko. Aca: zasad bih ovo izbegao, nezgodno je. Ako budu trazili recenzenti, uradicemo.}
-
 \subsubsection{Fitness function}\label{sec:fitness}
@@
 Method named \texttt{Replace}$(s, n, nc)$ inside Algorithm~\ref{alg:pertNode} is simply used to replace the node $n$ with node $nc$ inside the given expression tree $s$.
-%\fxnote{Nekako zbunjuje u Algoritmu 4, pojava NodeChanges)() i Replace().
-Mislim, razumijem iz opisa sta one rade, ali nisam siguran da treba imenovati metode, ako ih barem u kontekstu opisa ne pomenemo direktno po nazivu.
-ACA: za NodeChanges stoji opis operacija iznad, sad sam ubacio i u tekst da je to sustina metode NodeChanges.
-Za replace sam takodje dao objasnjenje.}
-
-%\fxnote{Dati kompleksnost velicine skupa perturbacija u odnosu na velicinu drveta i dopustene promjene.
-ACA: tesko je ovo izracunati, u principu za svaki cvor, dakle, celo drvo ili bilo koje pod-drvo ide ovaj spisak gore, dakle, neki red velicine d*C(T), gde je C(T) broj poddrveca iz datog drveta T, a d je neka konstanta, tj.
-broj mogucih perturbacija jednog poddrveta.
-Sad koliko ima poddrveca, moze se izracunati ovako nekako, ali ne bih to ukljucivao osim ako nam ne zatraze.
-Dakle, za drvo T broj poddrveca $C(T) = C(T.left)+C(T.right)+1$ (ovo jedan za bas to celo drvo u datom rekurzivnom koraku), sad kad je drvo T od N cvorova balansirano, dobija se diferencna jednacina $C(N)=2*C(N/2)+1$, a njeno resenje je O(N) mislim.
-Kad se raspise dobija se $C(N) = 2*2*C(N/4)+2 = 2*2*2*C(N/8)+3 = ...
-= 2^(\log_2(N))*C(1)+\log_2(N) = N + \log_2(N) = O(N)$ posto je $C(1)=1$, to je list drveta}
 
@@
 Before checking if the candidate solution ($new$) is better than the actual best $bp$, the OLS coefficient fitting (\texttt{FitOLS}) takes place.
+
 The set of used 1-perturbations is increased in comparison to those used previously. Namely, in addition to those six possible types of node changes, the following four are added:
@@
 
-\fxnote{ACA: do ovde sam pregledao}
 The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   various symmetries, periodicity w.r.t.
-some variables, internal separability on some variables etc.
-In that way, the search process and the search space can be pre-defined and thus significantly reduced.
-Thereby, some methods may get significant benefit with this regard, while some others may be in a subordinate situation.
-In order to permit any kind of favoritism caused by physical lows behind the input data, we generate a set of randomly generated (non-biased) SR problem instances; this benchmark set is therefore labelled by \textsc{Random}.
-These instances are generated according the following procedure.
-\fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance + koliko instanci, itd.}
-
-Another purpose of having these instances is  systematically  providing conclusions on robustness and scalability of the RILS-ROLS method w.r.t.\ various instance size parameters.
+some variables, internal separability on some variables, etc.
+In order to test \textsc{RILS-ROLS} robustness and scalability in unbiased setting, we generated a set of random SR problem instances called \textsc{Random}.
+These instances have a varying size (total number of expression nodes) and number of variables.
+In total, there are 235 random instances, or 5 randomly generated instances for each of the following 47 (size, number of variables) combinations $\{(3, 1), \{4, 5\} \times \{1, 2\}, \{6\} \times \{1, 2, 3\}, \{7, 8, 9, 10, 11, 12\} \times \{1, 2, 3, 4\}, \{13, 14, 15\} \times \{1, 2, 3, 4, 5\}\}$.
+Each of \textsc{Random} instances has 10 thousands randomly generated samples.
+
+Some \textsc{Random} instances are shown in Table~\ref{tbl:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
+
+\begin{table}
+	\centering
+	\begin{tabular}{ll} \\ \hline
+		random\_04\_02\_0010000\_00 &	$\ln{(x_0 + x_1)}$\\
+		random\_07\_02\_0010000\_00 &	$(x_0 + 10)\cdot (x_1 + 1)$\\
+		random\_08\_02\_0010000\_00 &	$(x_0 + \ln{x_0})*(x_1 + 10)$\\
+		random\_10\_03\_0010000\_02 &	$\ln{(\sqrt{x_0} \cdot x_1/\cos{x_2})}$\\
+		random\_12\_04\_0010000\_04 &	$\sqrt{x_3 \cdot \exp{x_1} + \cos{(x_2 \cdot \sin{x_0})}}$\\
+		random\_15\_03\_0010000\_04	&   $x_0 \cdot x_1/2 + (\cos{(x_2)} - \pi^2)^2$\\
+		\hline
+	\end{tabular}
+	\caption{Some \textsc{Random} instance problems.}
+	\label{table:random}
+\end{table}
 
@@
 This block consists of three columns that provide the relative percentage of algorithm runs on the instances where he algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 > 0.999$ upon termination) on the both ground--truth benchmark sets separately, and the overall percentage ov all (10) runs on all considered problem instances.
-%) w.r.t.
-the criterion of reaching the final accuracy of 0.999.
-
-%Note that when the algorithm terminates with $R^2=1$ and $RMSE=0$, the obtained model and the exact model are always match (but also checked manually).
-However, in case when the algorithms deliver an error $R^2 \geq 0.999$, but $R^2 \neq 1$, these cases are all  manually checked by comparing weather the produced model match the exact model.
 
@@
 
-%time-avg-noise0.0.eps
-
 \begin{figure}[!ht]
@@
 	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.0.eps}
+		\includegraphics[width=190pt,height=150pt]{plots/time-avg-noise0.0.eps}
 		\caption{No noise}
@@
 
-		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.001.eps}
+		\includegraphics[  width=190pt,height=150pt]{plots/time-avg-noise0.001.eps}
 		\caption{Level of noise equal to 0.001}
@@
 	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.01.eps}
+		\includegraphics[  width=190pt,height=150pt]{plots/time-avg-noise0.01.eps}
 		\caption{Level of noise equal to 0.01.}
@@
 	\centering
-	\begin{subfigure}[b]{0.6\textwidth} 
-		\includegraphics[  width=340pt,height=180pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
+	\begin{subfigure}[b]{0.75\textwidth} 
+		\includegraphics[  width=300pt,height=180pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
 		\caption{No noise}
@@
 
-	\begin{subfigure}[b]{0.6\textwidth}
-
-		\includegraphics[  width=340pt,height=180pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
+	\begin{subfigure}[b]{0.75\textwidth}
+
+		\includegraphics[  width=300pt,height=180pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
 		\caption{Level of noise equal to 0.001}
@@
 
-	\begin{subfigure}[b]{0.6\textwidth}
-		\includegraphics[  width=340pt,height=180pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
+	\begin{subfigure}[b]{0.75\textwidth}
+		\includegraphics[  width=300pt,height=180pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
 		\caption{Level of noise equal to 0.01. }
@@
 
-\begin{figure}[H]
+\begin{figure}[!ht]
 	\begin{subfigure}[b]{0.40\textwidth}
@@
 
-\begin{comment}
-	\begin{center}
-		\begin{tikzpicture}
-			\begin{axis}[
-				xlabel=$variable\;count\;in\;exact\;models$,
-				ylabel=$exact\;percentage$,
-				xmin=0, xmax=5,
-				ymin=0, ymax=100,
-				xtick={1,2,3,4},
-				xticklabels={1,2,3,4},   % <---
-				ytick={0,10,...,100}
-				]
-				\addplot[smooth,mark=*,blue] plot coordinates {
-					(1,43.33)
-					(2,43.33)
-					(3,46.67)
-					(4,46.67)
-				};
-				\addlegendentry{No noise}
-
-				\addplot[smooth,color=red,mark=x]
-				plot coordinates {
-					(1,3.33)
-					(2,3.33)
-					(3,26.67)
-					(4,26.67)
-				};
-				\addlegendentry{Noise level 0.001}
-
-				\addplot[smooth,color=green,mark=o]
-				plot coordinates {
-					(1,3.33)
-					(2,3.33)
-					(3,3.33)
-					(4,16.67)
-				};
-				\addlegendentry{Noise level 0.01}
-			\end{axis}
-		\end{tikzpicture}
-		\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
-		\label{fig:compExact_noise_varcnt}
-	\end{center}
-\end{comment}
-%\begin{center}
-%	\begin{tikzpicture}
-	%		\begin{axis}[
-		%			xlabel=$variable\;count$,
-		%			ylabel=$exact\;percentage$,
-		%			xmin=0, xmax=5,
-		%			ymin=0, ymax=100,
-		%			xtick={1,2,3,4},
-		%			xticklabels={1,2,3,4},   % <---
-		%			ytick={0,10,...,100}
-		%			]
-		%			\addplot[smooth,mark=*,blue] plot coordinates {
-			%				(1,83.33)
-			%				(2,66.67)
-			%				(3,73.33)
-			%				(4,46.67)
-			%			};
-		%			\addlegendentry{No noise}
-		%			
-		%			\addplot[smooth,color=red,mark=x]
-		%			plot coordinates {
-			%				(1,56.67)
-			%				(2,63.33)
-			%				(3,66.67)
-			%				(4,46.67)
-			%			};
-		%			\addlegendentry{Noise level 0.001}
-		%			
-		%			\addplot[smooth,color=green,mark=o]
-		%			plot coordinates {
-			%				(1,23.33)
-			%				(2,43.33)
-			%				(3,53.33)
-			%				(4,26.67)
-			%			};
-		%			\addlegendentry{Noise level 0.01}
-		%		\end{axis}
-	%	\end{tikzpicture}
-%	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
-%	\label{fig:compR2_noise_varcnt}
-%\end{center}
-
 \section{Conclusions and future work}\label{sec:conclusions}
@@
 
-\newpage
-%\section*{References}
-\bibliographystyle{abbrv}	
-\bibliography{bib}
-
-\newpage
-\appendix
-
+\section*{Appendix}
 \section{Overview of \textsc{RILS}-\textsc{ROLS} python package}\label{sec:appendix-1}
@@
 
-%\section{Additional statistical analysis}\label{sec:appendix-2}
-
-%\begin{figure}[H]
-%	\begin{subfigure}[b]{0.40\textwidth}
-%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_0acc.pdf}
-%		\caption{No noise}
-%		\label{fig:CDplotsR2-no-noise}
-%	\end{subfigure}
-%	\hfill
-%	\begin{subfigure}[b]{0.4\textwidth}
-%		
-%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_001acc.pdf}
-%		\caption{Level of noise equal to 0.001}
-%		\label{fig:CDplotsR2-noise0.001}
-%	\end{subfigure}
-%	\centering
-%	\begin{subfigure}[b]{0.40\textwidth}
-%		\includegraphics[  width=220pt,height=140pt]{plots/Feynman__strogatz_noise_0_01acc.pdf}
-%		\caption{Level of noise equal to 0.01.}
-%		\label{fig:CDplotsR2-noise0.01}
-%	\end{subfigure}
-%	\caption{CD plots comparisons in terms of obtained $R^2$ score over all problem instances from both ground-truth benchmark sets,  varying levels of noise.}
-%	\label{fig:cd-plotsR2-varying_noise}
-%\end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Backmatter begins here                   %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{backmatter}
+
+\section*{Acknowledgements}%% if any
+Text for this section\ldots
+
+\section*{Funding}%% if any
+Text for this section\ldots
+
+\section*{Abbreviations}%% if any
+Text for this section\ldots
+
+\section*{Availability of data and materials}%% if any
+Text for this section\ldots
+
+\section*{Ethics approval and consent to participate}%% if any
+Text for this section\ldots
+
+\section*{Competing interests}
+The authors declare that they have no competing interests.
+
+\section*{Consent for publication}%% if any
+Text for this section\ldots
+
+\section*{Authors' contributions}
+Text for this section \ldots
+
+\section*{Authors' information}%% if any
+Text for this section\ldots
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  Bmc_mathpys.bst  will be used to                       %%
+%%  create a .BBL file for submission.                     %%
+%%  After submission of the .TEX file,                     %%
+%%  you will be prompted to submit your .BBL file.         %%
+%%                                                         %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% if your bibliography is in bibtex format, use those commands:
+\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
+\bibliography{bib}      % Bibliography file (usually '*.bib' )
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Figures                       %%
+%%                               %%
+%% NB: this is for captions and  %%
+%% Titles. All graphics must be  %%
+%% submitted separately and NOT  %%
+%% included in the Tex document  %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% Do not use \listoffigures as most will included as separate files
+
+\section*{Additional Files}
+  \subsection*{Additional file 1 --- Sample additional file title}
+    Additional file descriptions text (including details of how to
+    view the file, if it is in a non-standard format or the file extension).  This might
+    refer to a multi-page table or a figure...
+
+\end{backmatter}
 \end{document}

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_article.py

@@ -1,0 +1,2 @@
+pip install rils-rols
+

### 2022-12-01 paper_resources/doc/paper.tex
Tuning paragraph.

@@
 		\end{tabular}
-		\caption{Some Feynman equations.}
+		\caption{Some \textsc{Feynman} instances.}
 		\label{tab:Feynamn-Eq}
@@
 		\end{tabular}
-		\caption{Some Strogatz ODE problems.}
+		\caption{Some Strogatz ODE instances.}
 		\label{table:strogatz-ODEs}
@@
 
-\fxnote{ACA: do ovde sam pregledao}
 The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   various symmetries, periodicity w.r.t.
-some variables, internal separability on some variables etc.
-In that way, the search process and the search space can be pre-defined and thus significantly reduced.
-Thereby, some methods may get significant benefit with this regard, while some others may be in a subordinate situation.
-In order to permit any kind of favoritism caused by physical lows behind the input data, we generate a set of randomly generated (non-biased) SR problem instances; this benchmark set is therefore labelled by \textsc{Random}.
-These instances are generated according the following procedure.
-\fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance + koliko instanci, itd.}
-
-Another purpose of having these instances is  systematically  providing conclusions on robustness and scalability of the RILS-ROLS method w.r.t.\ various instance size parameters.
+some variables, internal separability on some variables, etc.
+In order to test \textsc{RILS-ROLS} robustness and scalability in unbiased setting, we generated a set of random SR problem instances called \textsc{Random}.
+These instances have a varying size (total number of expression nodes) and number of variables.
+In total, there are 235 random instances, or 5 randomly generated instances for each of the following 47 (size, number of variables) combinations $\{(3, 1), \{4, 5\} \times \{1, 2\}, \{6\} \times \{1, 2, 3\}, \{7, 8, 9, 10, 11, 12\} \times \{1, 2, 3, 4\}, \{13, 14, 15\} \times \{1, 2, 3, 4, 5\}\}$.
+Each of \textsc{Random} instances has 10 thousands randomly generated samples.
+Some \textsc{Random} instances are shown in Table~\ref{table:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
+
+	\begin{table}
+	\centering
+	\begin{tabular}{ll} \\ \hline
+		random\_04\_02\_0010000\_00 &	$\ln{(x_0 + x_1)}$\\
+		random\_07\_02\_0010000\_00 &	$(x_0 + 10)\cdot (x_1 + 1)$\\
+		random\_08\_02\_0010000\_00 &	$(x_0 + \ln{x_0})*(x_1 + 10)$\\
+		random\_10\_03\_0010000\_02 &	$\ln{(\sqrt{x_0} \cdot x_1/\cos{x_2})}$\\
+		random\_12\_04\_0010000\_04 &	$\sqrt{x_3 \cdot \exp{x_1} + \cos{(x_2 \cdot \sin{x_0})}}$\\
+		random\_15\_03\_0010000\_04	&   $x_0 \cdot x_1/2 + (\cos{(x_2)} - \pi^2)^2$\\
+		\hline
+	\end{tabular}
+	\caption{Some \textsc{Random} instances.}
+	\label{table:random}
+\end{table}
 
 \subsection{Parameter tuning}
-The \textsc{RILS}-\textsc{ROLS} algorithm employs two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is fixed empirically to 0.001(?), according to the preliminary results.
-The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances.
-Among the following values \{ x, xx, ...
-\} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error on all problem instances from the training set are produced.
-%Note that the training set is chosen randomly with a cardinalty of xx instances.
+The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters, $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in \ref{sec:appendix-1}).
+The second parameter is negatively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ takes lower values and vice-versa.
 

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Moved to JBD format.

@@
 		\end{tabular}
-		\caption{Some Strogatz ODE problems.}
+		\caption{Some \textsc{Strogatz} ODE instances.}
 		\label{table:strogatz-ODEs}
@@
 
-Some \textsc{Random} instances are shown in Table~\ref{tbl:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
+Some \textsc{Random} instances are shown in Table~\ref{table:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
 
@@
 	\end{tabular}
-	\caption{Some \textsc{Random} instance problems.}
+	\caption{Some \textsc{Random} instances.}
 	\label{table:random}
@@
 \subsection{Parameter tuning}
-The \textsc{RILS}-\textsc{ROLS} algorithm employs two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is fixed empirically to 0.001(?), according to the preliminary results.
-The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances.
-Among the following values \{ x, xx, ...
-\} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error on all problem instances from the training set are produced.
-%Note that the training set is chosen randomly with a cardinalty of xx instances.
+The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters, $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in \ref{sec:appendix-1}).
+The second parameter is negatively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ takes lower values and vice-versa.
 

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_article.py
Removed auto-generated files.

@@ -1,2 +1,0 @@
-pip install rils-rols
-

### 2022-12-01 paper_resources/doc/paper.tex
Section 1: round 2 of polishing

@@
 		\end{tabular}
-		\caption{Some \textsc{Feynman} instances.}
+		\caption{Some Feynman equations.}
 		\label{tab:Feynamn-Eq}
@@
 		\end{tabular}
-		\caption{Some Strogatz ODE instances.}
+		\caption{Some Strogatz ODE problems.}
 		\label{table:strogatz-ODEs}
@@
 Each of \textsc{Random} instances has 10 thousands randomly generated samples.
-Some \textsc{Random} instances are shown in Table~\ref{table:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
+Some \textsc{Random} instances are shown in Table~\ref{tbl:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
 
@@
 	\end{tabular}
-	\caption{Some \textsc{Random} instances.}
+	\caption{Some \textsc{Random} problems.}
 	\label{table:random}
@@
 \subsection{Parameter tuning}
-The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in \ref{sec:appendix-1}).
-The second parameter is negatively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ takes lower values and vice-versa.
+The \textsc{RILS}-\textsc{ROLS} algorithm employs two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is fixed empirically to 0.001(?), according to the preliminary results.
+The second parameter is tuned by monitoring the two errors the algorithm produced on a randomly chosen training set of xx problem instances.
+Among the following values \{ x, xx, ...
+\} we chose $tolerance_{error}=?$ for which the largest average $R^2$ and the smallest average RMSE error on all problem instances from the training set are produced.
+%Note that the training set is chosen randomly with a cardinalty of xx instances.
 

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
removed paper

@@
 the well-known linear regression, polynomial regression~\cite{stimson1978interpreting}, etc.
-All regression models have the same goal: given a set of $n$-dimensional input data and its corresponding continuous output target variable, the aim is to find a  mathematical expression (function) of $n$ (input) variables that best \emph{fits} the target variable.
+All regression models have the same goal: given a set of $n$-dimensional input data and its corresponding continuous output target variable, the aim is to find a  mathematical expression (function) of $n$ (input) variables that   \emph{fits} best to the target variable.
 %This computationally intensive task is in general provenly NP--hard~\cite{virgolin2022symbolic}.
@@
 Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}.
-Paper \cite{louis2021reviewing} shows how SR is used to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology.
-One recent study \cite{liu2021machine} is concerned of auto-discovering conserved quantities using trajectory data from unknown dynamical systems.
-Paper~\cite{liang2019phillips} shows the application of SR to model analytic representations of the exciton binding energy.
+Paper \cite{louis2021reviewing} provides the application of SR to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology.
+A recent study in \cite{liu2021machine} is concerned of auto-discovering conserved quantities using trajectory data from unknown dynamical systems.
+The application of SR to model analytic representations of the exciton binding energy is shown in~\cite{liang2019phillips}.
 The use of SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
@@
 	There are many different ways to tackle the SR.
-Most of them are based on the machine learning techniques, genetic programming (GP) or some other meta-heuristics.
+Most of them are based on   machine learning techniques, genetic programming (GP) or some other meta-heuristics.
 Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
@@
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
-A variable neighbourhood programming approach to solve SR  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
+A variable neighbourhood programming approach  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
 Kommenda et al.~\cite{kommenda2020parameter} proposed a method called \textsc{Operon} algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in tree-based GP.
@@
 The method that utilizes the Taylor polynomials to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
-A GP approach that uses the idea of semantic back-propagation (Sbp-Gp) is proposed in~\cite{virgolin2019linear}.
+A GP approach that uses the idea of semantic back-propagation (SBP-GP) is proposed in~\cite{virgolin2019linear}.
 Empirical analysis of variance between many GP-based methods for SR is discussed in~\cite{kammerer2021empirical}.
@@
 
-Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the \textsc{Eplex} solver from~\cite{la2019probabilistic,la2016epsilon} and \textsc{AI Feynman} algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method combined with the neural network fitting.
+Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the \textsc{Eplex} solver from~\cite{la2019probabilistic,la2016epsilon} and \textsc{AI-Feynman} algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method combined with the neural network fitting.
 The latter is one of the most efficient methods for physically-inspired models.
@@
 benchmarking standards. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
-open-source, reproducible benchmarking platform for SR, called SRBench.
+open-source, reproducible benchmarking platform for SR, called \texttt{SRBench}.
 The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression problems, with 130 SR datasets for which exact (\emph{ground-truth}) models are known; see more in the aforementioned paper.
@@
 introduced noise, therefore we called the method \textsc{RILS}-\textsc{ROLS}  (with letters R corresponding to regression and robust).
-Additionally, in order to navigate the search toward exact model (and not only accurate one) the algorithm is equipped with a carefully constructed fitness function that utilizes three important model characteristics: RMSE and $R^2$ scores which participate into models accuracy, and a weighted solution size that penalizies too complex models.
+Additionally, in order to navigate the search toward exact model (and not only accurate one) the algorithm is equipped with a carefully constructed fitness function that combines three important model characteristics: RMSE and $R^2$ scores which participate into models accuracy, and a weighted solution size that penalizes too complex models.
 
@@
 \begin{enumerate}
-	\item The proposed method outperforms 14 comparison methods on two \emph{ground-truth} benchmark sets from literature -- these methods and benchmarks are used in SRBench platform.
+	\item The proposed method outperforms 14 comparison methods on two \emph{ground-truth} benchmark sets from literature -- these methods and benchmarks are used in \texttt{SRBench} platform.
 
@@
 	\hfill
-	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{subfigure}[b]{0.47\textwidth}
 
@@
 	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{subfigure}[b]{0.47\textwidth}
 		\includegraphics[  width=190pt,height=150pt]{plots/time-avg-noise0.01.eps}
@@
 
-	\begin{subfigure}[b]{0.40\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
 		\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_no_noise.eps}
@@
 	\hfill
-	\begin{subfigure}[b]{0.4\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
 
@@
 \begin{figure}[!ht]
-	\begin{subfigure}[b]{0.40\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
 		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_no_noise.eps}
@@
 \begin{figure}[!ht]
-	\begin{subfigure}[b]{0.40\textwidth}
+	\begin{subfigure}[b]{0.45\textwidth}
 		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_time_no_noise.eps}

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Minor changes.

--- 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
@@
 
-\subsection{Comparison with other methods on the   ground--truth benchmark sets}
+\subsection{Comparison with other methods on the ground-truth benchmark sets}
 In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to the 13 other competitors from the literature.

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Round 2: up to Section 3.3.1

--- 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
@@
 \usepackage{pythonhighlight}
-
+\usepackage{fixme}
+\fxsetup{status=draft} % <====== add this line
 \usepackage{mathtools}
@@
 It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model).
-More precisely, given previously introduced dataset $D$ of $n$ points $(\mathbf{x_i}, y_i)$ where each $\mathbf{x_i}$ is $d$-dimensional, the task is to determine linear mapping $\tilde{y} = \mathbf{k} \mathbf{x} + b$, that is coefficients (line slope) $\mathbf{k} = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i}^{n} (\tilde{y}_i - y_i)^2 $ is minimized.
+More precisely, given   dataset $D$ of $n$ points $(\mathbf{x_i}, y_i)$ where each $\mathbf{x_i}$ is $d$-dimensional, the task is to determine linear mapping $\tilde{y} = \mathbf{k} \mathbf{x} + b$, that is coefficients (line slope) $\mathbf{k} = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i}^{n} (\tilde{y}_i - y_i)^2 $ is minimized.
 This sum is also know as the sum of squared errors (SSE).
@@
 But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}), after which the local search is performed (line~\ref{line:ls}).
-Solution simplification is done in a symbolical fashion by popular \texttt{SymPy} Python package~\cite{sympy}.
+Solution simplification is done in a symbolical fashion by popular  Python package \texttt{SymPy}~\cite{sympy}.
 Local search tries to find local optima expressions close to the given $p$ -- explained in detail in Section~\ref{sec:ls}.  
@@
 If some of $s_{perturbations}$ around starting solution $s$ yielded an improvement, $bs$ becomes the starting solution $s$ in the next iteration of the main loop (line~\ref{line:improved}). 
-Otherwise, it makes no sense to set starting solution to $bs$, as nothing changed -- the search is being  \emph{trapped} in a local optimum.
+Otherwise, it makes no sense to set starting solution to $bs$ -- the search is being  \emph{trapped} in a local optimum.
 Randomness is introduced in order to avoid this undesired situation.
@@
 a higher number of significant digits is preserved.
-Note that confidence in the symbolical model is reduced when expected noise in data is higher -- the rule of thumb is: for higher expected noise $tolerance_{error}$ should be higher.
+Note that confidence in the symbolical model is reduced when expected noise in data is higher -- the rule of thumb is: for higher expected noise, $tolerance_{error}$ should be higher.
 
 \subsubsection{Fitness function}\label{sec:fitness}
+\fxnote{Marko: Dosao dovde!}
 
@@
 
-For the (13) competitors, the results are exported from SRBench \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
+For the (13) competitors, the results are exported from \texttt{SRBench} \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
 The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1 hour, while the maximal number of fitness function evaluations is set to 1 million.
-All other algorithms from SRBench used the time limit that was equal or bellow 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
+All other algorithms from \texttt{SRBench} used the time limit that was equal or bellow 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
 We did not use the full time limit of 8 hours because we empirically concluded that there were almost no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
@@
 
-\subsection{Datasets and SRBench}
-
-SRBench (\url{https://cavalab.org/srbench/}) is an open-source benchmarking project which merges a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
-SRBench considers two types of symbolic regression problems: 1) \emph{ground-truth} problems, for which the exact model is known, and 2) \emph{black-box} problems, for which the exact model is not known.
+\subsection{Datasets and \texttt{SRBench}}
+
+\texttt{SRBench} (\url{https://cavalab.org/srbench/}) is an open-source benchmarking project which merges a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
+\texttt{SRBench} considers two types of symbolic regression problems: 1) \emph{ground-truth} problems, for which the exact model is known, and 2) \emph{black-box} problems, for which the exact model is not known.
 In our work, we consider only the former one, since \textsc{RILS-ROLS} was not designed to solve \emph{black-box} problems.
-There are two groups of instances in SRBench \emph{ground-truth} problem set:
+There are two groups of instances in \texttt{SRBench} \emph{ground-truth} problem set:
 \begin{itemize}
@@
 More precisely, we involved 1300 results into our statistical evaluation per each algorithm.
-Note that  results of some of the 13 competitors are not known from SRBench \url{https://cavalab.org/srbench/results/} due to   unknown reasons (most likely algorithm is terminated running out of memory or due to   chosen algorithm configuration settings).
+Note that  results of some of the 13 competitors are not known from \texttt{SRBench} \url{https://cavalab.org/srbench/results/} due to   unknown reasons (most likely algorithm is terminated running out of memory or due to   chosen algorithm configuration settings).
 For these runs, we simply indicate a 0 as their score.

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Polishing up to statistical evaluation.

--- 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
@@
 
-We propose a new meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS} to solve this problem.
+We propose an efficient meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS} to solve this problem.
 \textsc{RILS}-\textsc{ROLS} is based on the following elements: ($i$) iterated local search is the method backbone, mainly solving combinatorial and some continuous aspects of the problem; ($ii$) ordinary least square method is focused on the continuous aspect of the search space -- it efficiently determines the best--fitting coefficients of linear combinations within solution equations;  ($iii$) a novel fitness function combines three important model quality measures: $R^2$ score, RMSE score, and the size of the model (or model complexity).
@@
 The experiments are conducted on the two well-known ground-truth benchmark sets called \textsc{Feynman} and \textsc{Strogatz}.
-\textsc{RILS}-\textsc{ROLS} was compared to 14 other competitors from the literature with  presence of different levels of the Gaussian white noise in the input data.
-Our method outperformed all 14 competitors with respect to the true symbolic model accuracy percentage under all level of noise.
+\textsc{RILS}-\textsc{ROLS} was compared to 14 other competitors from the literature.
+Our method outperformed all 14 competitors with respect to the true symbolic model accuracy percentage under varying levels of noise.
+It also showed to be the most efficient considering the average running time of reaching the exact model.
 In addition to evaluation on known ground-truth datasets, a new randomly generated set of problem instances is introduced.
@@
 \subsection{Parameter tuning}
+
 The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in \ref{sec:appendix-1}).
-The second parameter is negatively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ takes lower values and vice-versa.
-
-\fxnote{ drugi parametar manje vise zavistan od ocekivanog 
-	nivoa suma -- ne znam kako obrazloziti njegov tuning (mozda prema greski na trening skupu pa izabrati onaj za koji su R2 i RMSE bolji...). }
-
-\subsection{Comparison with other methods on the ground-truth benchmark sets}
-In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to the 13 other competitors from the literature.
-The numerical results are reported in terms of the three Tables~\ref{tab:comp_noise0}--\ref{tab:comp_noise001}.
-The results for the two ground-truth benchmark sets, \textsc{Feynman} and \textsc{Storgatz}, are given w.r.t.\   the following level of noise: 0.0 (no-noisy data), 0.001 (low-level noise), and 0.01 (high-level noise), respectively.
-In details, the white Gaussian noise is added to the target ($y$-axis) values as a fraction of the signal RMS value, applied also in~\cite{la2021contemporary}, i.e.
-for target noise level $\alpha$ we have
+The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in the Appendix).
+The second parameter is positively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ should take higher values and vice-versa.
+More precisely, in case there is no noise, we used the default setting $tolerance_{error}=10^{-16}$, while in noisy scenarios we set $tolerance_{error}$ to the corresponding noise level (0.001 or 0.01).
+For setting $penalty_{size}$ and $tolerance_{error}$ on new datasets one can either keep the default settings or use some wrapper tuning algorithm around \textsc{RILS-ROLS} regressor, e.g., grid-search w.r.t.
+training or validation accuracy.
+
+\subsection{Comparison to other methods}
+In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to 13 other competitors from the literature.
+The numerical results are reported in Tables~\ref{tab:comp_noise0}-\ref{tab:comp_noise001}.
+The results for \textsc{Feynman} and \textsc{Storgatz} are given w.r.t.\  the following levels of noise: 0.0 (no-noisy data), 0.001 (low-level noise), and 0.01 (high-level noise).
+More precisely, the white Gaussian noise is added to the target variable the same way as in~\cite{la2021contemporary}:
 $$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{n} \sum _{i=1}^n{y_i^2}}\right),$$
@@
 
-Each table consists of three blocks. The performances of all (14) algorithms are displayed in respective rows.  
-The first block gives the label of the algorithm  whose performance is reported.
-The second block reports by two columns the relative percentages of all (10) algorithm runs on all problem instances for which the exact model has been found by respective algorithm  on \textsc{Feynman} and \textsc{Strogatz} benchmark set, respectively.
-The third column of this block provides the overall   relative exact percentage of success of the algorithm over all runs on all problem instances from the both benchmark sets.
-The third block displays the results of the respective algorithm in terms of   final $R^2$ score which indicate  on accuracy of found solution.
-The solution is considered accurate if it     produced an $R^2$ score larger that  0.999.
-Note that the termination of our algorithm may not always be triggered by reaching an appropriate $R^2$ score, but also due to the reached time limit.
-These kind of results are of a particular interest as they may point out on the presence of strong over-fitting of algorithms in contrast to the primary goal, that is finding the right model.
-This block consists of three columns that provide the relative percentage of algorithm runs on the instances where he algorithm is able to reach the desired accuracy (fulfilling the condition $R^2 > 0.999$ upon termination) on the both ground--truth benchmark sets separately, and the overall percentage ov all (10) runs on all considered problem instances.
-
-In short, the exact results, thus the number of algorithm runs over all instances (in percentages) for which the output of respective algorithm is able to find the exact model, are displayed in the second block of each  table.
-The numbers of runs   (in percentages) for which an algorithm  delivers a precise enough model (i.e.
-the outcome satisfying $R^2>  0.999$) are displayed in the third block of each of the tables.
+Each table consists of two blocks, where the first one gives the exact model accuracy, while the second is related to the less relevant statistical accuracy based on the $R^2$ metric.
+The exact model accuracy shows how often the method reaches true formula (ground-truth).
+Regarding statistical accuracy, the solution is considered accurate if it produced an $R^2$ score larger than 0.999.
+Note that for each instance there were 10 runs, so in total there were at most 1160 successful runs for \textsc{Feynman} and 140 for \textsc{Strogatz}.
 
@@
 \begin{itemize}
-	\item Concerning the exact percentages in case when no noise is utilized in the input data, the best performing algorithm is our \textsc{RILS-ROLS}, able to find the solution that match to the right model on 57.84\% runs over all problems instances of the benchmark set \textsc{Feynman}; it was even more impressive in solving problem instances from benchmark set \textsc{Strogatz}, being successful on 83.57\% runs.
-The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\%   runs over all problem instances from \textsc{Feynman} set, and just 27.14\% runs over the problem instances from benchmark set   \textsc{Strogatz}, respectively.
-All other approaches are performing much worse, and none of them is able to delver the exact solution for more than 30\% runs over the instances of any of the two considered ground-truth benchmark sets.
-	\item   Concerning the exact results in presence of the   noise  level of 0.001, our \textsc{RILS-ROLS} is still performing very well, having found an exact model for 42.08\% runs considering all problem instances from the both ground-truth benchmark sets.
-The second best approach is \textsc{AI-Feynman} which is successful on 31.89\% runs over all problem instances; as  already noticed, this algorithm performs better when applied on the instances from \textsc{Feynman} benchmark set than it is the case of \textsc{Strogatz} benchmark set.
-Approach  \textsc{AFP-FE} shows to be robust w.r.t.
+	\item Concerning the exact percentages in case when no noise is utilized in the input data, the best performing algorithm is our \textsc{RILS-ROLS}.
+It found the exact solution in 57.84\% of runs for \textsc{Feynman} instances.
+It was even more impressive in solving \textsc{Strogatz} instances, being successful in 83.57\% runs.
+The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\% runs for \textsc{Feynman} set, and 27.14\% runs for the problem instances from benchmark set \textsc{Strogatz}.
+All other approaches perform significantly worse, and none of them is able to deliver the exact solution for more than 30\% runs over the instances of any of the two considered ground-truth benchmark sets.
+The overall results are in favor of \textsc{RILS-ROLS} with 60.62\%, while the second best is \textsc{AI-Feynman} with 52.65\%.
+	\item  Concerning the exact results in presence of the small noise (0.001), our \textsc{RILS-ROLS} is still performing very well, finding an exact model in 42.08\% of runs considering all problem instances.
+The second best approach is again \textsc{AI-Feynman} being successful in 31.89\% runs.
+As in no-noise scenario, there is a significant difference in \textsc{AI-Feynman} performances among two sets of instances -- it performs much better on \textsc{Feynman} instances than on \textsc{Strogatz}.
+It is also worth mentioning that \textsc{AFP-FE} shows to be robust w.r.t.
 noise so its performances only slightly deteriorate in comparison to the no-noise scenario.
@@
 Other approaches reach accuracy bellow 20\%.
-	\item  Concerning the exact results when the presence of noise is large with  the noise level of 0.01,  our \textsc{RILS-ROLS} is still performing robustly, having found an exact model for  34.77\% runes over all problem instances considering the both ground-truth benchmark sets.
+	\item  Concerning the scenario with high noise (level of 0.01), our \textsc{RILS-ROLS} is still performing quite well -- it finds and exact model in 34.77\% runs.
 The second best is \textsc{AFP-FE} reaching 20\% correct solutions.
-\textsc{AI-Feynman} performances are degraded significantly under this level of noise, so it is ranked only 6th overall, reaching the accuracy of 12.61\%.
-
-	\item When comparing performances of the algorithms in terms of algorithm runs for which the obtained final model fulfills an accuracy of $R^2 > 0.999$, in case when no noise is integrated, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
-However, in contrast with the exact model percentages comparisons from above, there are a few methods reaching   better percentages of success than our algorithm: \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
+\textsc{AI-Feynman} performances degrade significantly under this level of noise, so it is ranked only 6th overall, reaching the accuracy of 12.61\%.
+
+	\item One more interesting method is \textsc{DSR}.
+It shows the perfect robustness to noise and agnosticism to benchmark dataset -- it has near 19\% exact model accuracy in all 6 combinations of benchmark dataset (\textsc{Feynman} or \textsc{Strogatz}) and noise level (0, 0.001 or 0.01).
+
+	\item When comparing performances of the algorithms in terms of $R^2 > 0.999$ accuracy, in no-noise scenario, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
+Better methods in terms of this accuracy are \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
 On the other hand, the exact model percentages of these two approaches are rather low (0\% and 16\%, respectively).
-These two algorithms are therefore more appropriate in scenarios when the underlying (ground-truth) model is unknown, so-called black-box regression.
-
-	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% of a success rate (ranked on the third place).
-As before, \textsc{MRGP} and \textsc{Operon} are showing good performances.
+These two algorithms are therefore more appropriate in scenarios when the underlying (ground-truth) model is unknown, so-called \emph{black-box} regression.
+
+	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% of a success rate (ranked third, again).  As before, \textsc{MRGP} and \textsc{Operon} are best two here.
 
@@
 
-	\item Following the above conclusions, our \textsc{RILS}-\textsc{ROLS} algorithm is more robust than the other competitors, which is confirmed by the produced results w.r.t.\ different levels of noise in the input data.
-Moreover, it can be considered as new state-of-the-art algorithm when one solves the problems of SR with known ground-truth models.
+	\item We can conclude that \textsc{RILS}-\textsc{ROLS} achieves state-of-the-art performances regarding exact model accuracy.
+It also shows high robustness to noise.
+Regarding statistical accuracy, which is not so relevant for the ground-truth problems, \textsc{RILS}-\textsc{ROLS} also performs quite well.
 
@@
 	\end{subfigure}
-	\caption{Average runtimes on the instance problems where the exact solution has  been reached (considered only those algorithms whose the exact percentage is at least 5\% of all runs).}
+	\caption{Average runtime when exact solution is reached (considering only algorithms whose exact percentage is at least 5\% of all runs).}
 	\label{fig:time-avg-exact-noise}
@@
 
-In Figure~\ref{fig:time-avg-exact-noise}, average runtimes of the algorithms on those instance problems from the both ground-truth benchmark sets for which respective exact model has  been found, are compared.
-The algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant  and therefore included here, while others are just omitted.
-The runtimes of each algorithm  are averaged w.r.t\  different levels of noise, and presented by a bar plot.
-Algorithms are labeled on $x$-axis, while respective average runtimes (oer all runs) are shown on $y$-axis.
-Note that $y$-axis is logarithmically scaled.
-The following conclusions are drawn from here.
+Figure~\ref{fig:time-avg-exact-noise} compares the methods w.r.t.
+average runtimes (in seconds) when exact solution is reached.
+We do not consider methods whose exact percentage is too low, i.e., bellow 5\%.
+Methods are labeled on $x$-axis, while respective average runtimes are shown on $y$-axis.
+(Note that $y$-axis is logarithmically scaled.) The following conclusions are drawn from these results.
 
 \begin{itemize}
-	\item When considering the instance problems with no-noisy input data, the lowest average runtime  is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228$s$).
-A slightly worse runtime is obtained by \textsc{Dsr} algorithm (232$s$).
-However, note that the relative exact percentage produced by \textsc{RILS}--\textsc{ROLS} is far better from \textsc{Dsr} (60.62\% vs.
-19.71\%).
-	All remaining approaches deliver an order of magnitude larger average runtimes than that of the \textsc{RILS}--\textsc{ROLS} method in case of runs when the exact model has been reached.
-	\item  When considering the instance problems with the noise level of 0.001,    the lowest average runtime  to find the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108$s$).
-The second best average runtime is produced by \textsc{Dsr}, but this time significantly larger (622$s$) from the former algorithm.
-	\item When considering the instance problems with the noise level of 0.01, a similar conclusion may be drawn as that from above. 
+	\item When considering the instance problems with no-noise, the lowest average runtime is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228 sec.).
+A slightly worse runtime is obtained by \textsc{DSR} algorithm (232 sec.).
+Note that the relative exact percentage produced by \textsc{RILS}-\textsc{ROLS} is far better from \textsc{DSR} (60.62\% versu 19.71\%).
+All remaining approaches deliver an order of magnitude larger average runtimes than that of \textsc{RILS}-\textsc{ROLS} and \textsc{DSR} methods..
+	\item  When considering instances with the noise level of 0.001, the lowest average runtime to find the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108 sec.).
+The second best is produced by \textsc{DSR}, but this time significantly larger (622 sec.) compared to \textsc{RILS-ROLS}.
+	\item When considering the instance problems with the noise level of 0.01, the conclusion is similar to previous. 
 \end{itemize}
@@
 
-\section*{Appendix}
-\section{Overview of \textsc{RILS}-\textsc{ROLS} python package}\label{sec:appendix-1}
+\section*{Appendix -- \textsc{RILS}-\textsc{ROLS} Python package}\label{sec:appendix-1}
 

### 2022-12-01 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Round 2: up to Section 4.1

@@
 \usepackage{algpseudocode}
+
 \usepackage{url}
@@
 \subsubsection{Fitness function}\label{sec:fitness}
-\fxnote{Marko: Dosao dovde!}
 
@@
 This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
-The search process of \textsc{RILS}-\textsc{ROLS}  is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~\ref{eq:fitness}.
+The search process of \textsc{RILS}-\textsc{ROLS}  is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~(\ref{eq:fitness}).
 
@@
 	\label{eq:fitness}
-	fit(s) = (2-R^2(s)) \cdot (1+RMSE(s)) \cdot (1+penalty_{size} \cdot size(S))
+	fit(s) = (2-R^2(s)) \cdot (1+RMSE(s)) \cdot (1+penalty_{size} \cdot size(s))
 \end{equation}
@@
 \begin{algorithm}
-	\hspace*{\algorithmicindent} \textbf{Input}: solution $s$ \\
-	\hspace*{\algorithmicindent} \textbf{Output}: local perturbations (1-perturbations) of solution $s$ -- $s_{perturbations}$
+     \textbf{Input}: solution $s$ \\
+     \textbf{Output}: local perturbations (1-perturbations) of solution $s$ -- $s_{perturbations}$ \\
 	\begin{algorithmic}[1] 
@@
 
-The set of used 1-perturbations is increased in comparison to those used previously. Namely, in addition to those six possible types of node changes, the following four are added:
+The set of used 1-perturbations is expanded in comparison to those used previously. Namely, in addition to those six possible types of node changes, the following four are added:
 
@@
 
-Change under number 10 is very important -- it performs the general coefficient tuning, unlike OLS that considers only coefficients in linear combinations.
+Change under point 10 is very important -- it performs the general coefficient tuning, unlike OLS that considers only coefficients in linear combinations.
 
@@
 
-The following 13 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
-
-For the (13) competitors, the results are exported from \texttt{SRBench} \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
+The following 14 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
+
+For the (14) competitors, the results are exported from \texttt{SRBench} \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
 The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1 hour, while the maximal number of fitness function evaluations is set to 1 million.
@@
 
-\subsection{Datasets and \texttt{SRBench}}
+\subsection{Datasets and \texttt{SRBench}}\fxnote{Marko: Dosao dovde!}
 

### 2022-12-02 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Finished up to scalability section.

@@
 
-The following 14 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
+The following 14 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.
 
@@
 
-\begin{table}[!htb]
+\begin{table}[!h]
 	\caption{Comparison without noise}\label{tab:comp_noise0}
@@
 
-\begin{table}[!htb]
+\begin{table}[!h]
 	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
@@
 
-\begin{table}[!htb]
+\begin{table}[!h]
 	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 
@@
 
-In order to check the statistical significance of the results w.r.t.\ obtained exact models and their differences between the competitor approaches, we employed the statistical methodology comparing the results of \textsc{RILS}--\textsc{ROLS} to 13 other approaches over all algorithm runs on the problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
-Note that an indicator random variable is involved for each run of each algorithm.
-More precisely, the score that comes into the statistical observation is an indicator (0 or 1) indicating weather or not an algorithm was able to return the exact model at specific run.
-More precisely, we involved 1300 results into our statistical evaluation per each algorithm.
-Note that  results of some of the 13 competitors are not known from \texttt{SRBench} \url{https://cavalab.org/srbench/results/} due to   unknown reasons (most likely algorithm is terminated running out of memory or due to   chosen algorithm configuration settings).
-For these runs, we simply indicate a 0 as their score.
-
-Initially, Friedman’s test was separately executed for all competitor approaches.
-In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained results of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
+In order to check the statistical significance of the results w.r.t.\ competitor approaches, we employed the standard statistical methodology.
+To do so, we have compared the results of \textsc{RILS}-\textsc{ROLS} to 14 other approaches over all algorithm runs on the problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+The successful run means that the corresponding algorithm found the exact model.
+Having 1300 runs involved, this means that the maximal number of successful runs is 1300.
+
+\emph{Important note. Exact model accuracy of \textsc{RILS-ROLS} is calculated by dividing the number of successful runs with 1300, i.e., the maximal possible number of successful runs. 
+On the other hand, the exact model accuracy of methods revised in \texttt{SRBench} was calculated in a different way.
+First, the accuracy of each of 130 considered instances was calculated by dividing the number of successful runs with the number of runs that finished its execution.
+This means that, for example, if some instance was run 10 times, giving 4 successful models, but failing to finish 2 runs due to memory exhaustion or some other OS issue, the accuracy would be 50\% (4/8) instead of 40\% (4/10).
+Further, these individual accuracies were averaged.
+We do not believe this was the right way to calculate the accuracy, because, this allows one to have high-accuracy method with a low number of successful runs.
+For example, if method A finishes all of its runs, out of which 650 are successful, its total accuracy will be 50\%.
+On the other hand, one can have a method B that finishes instances execution in only 4 out of 10 runs, giving 2 successful models each time -- its per-instances accuracy will be 50\%, and after averaging across all instances it will be also 50\%.
+So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.}
+
+First, the omnibus rank-based Friedman’s test for all approaches was conducted. 
+The number of ranks is 1300, i.e., for each run of each method, the separate rank is calculated.
+Rank is based on the value of indicator variable, which takes 1 if the method delivers correct model in a given run, otherwise it takes value of 0, no matter if method finished and delivered incorrect model, or method did not finish at all.
+Further, the ranks are averaged and used to test the null hypothesis, which states that there is no statistical differences between the average ranks of all competitors.
+In the case in which the null hypothesis $H_0$ was rejected, pairwise comparisons were further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
 The outcome is represented by means of critical difference (CD) plots.
-In each CD plot, the (14) competitor approaches are placed on the horizontal axis according to their average ranking.
+In each CD plot, the 15 competitors are placed on the horizontal axis according to their average ranking.
 Thereafter, the CD score is computed for a significance level of 0.05.
 If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.
-Three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts} per each level of noise.
-The following conclusions may be drawn from there.
+This analysis is done for all three levels of noise, and the corresponding CD plots are shown in Figures~\ref{fig:CDplots-no-noise}-\ref{fig:CDplots-noise0.01}.
+
+\begin{figure}[!h]
+	\centering
+		\includegraphics[width=350pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
+		\caption{CD plots for no-noise scenario}
+		\label{fig:CDplots-no-noise}
+\end{figure}
+
+\begin{figure}[!h]
+
+	\includegraphics[width=350pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
+	\caption{CD plots for noise level 0.001}
+	\label{fig:CDplots-noise0.001}
+\end{figure}
+
+	\begin{figure}[!h]
+		\includegraphics[width=350pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
+		\caption{CD plots for noise level 0.01. }
+		\label{fig:CDplots-noise0.01}
+	\end{figure}
+
+The following conclusions may be drawn.
 
 \begin{itemize}
-	\item  Concerning the instance problems where no noise is included, \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models over all runs.
+	\item  Concerning the no-noise scenario, \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models over all runs.
 The second best average ranking is achieved by \textsc{AI-Feynman} algorithm.
-There is  statistically significant difference between these two approaches w.r.t.\ number of found exact solutions.
-The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{RILS}-\textsc{ROLS} w.r.t.\ delivered average ranking.
-	\item    Concerning the instance problems with the included  level of noise of 0.001, \textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking in terms of the found exact solutions.
+There is a statistically significant difference between these two approaches.
+The third best approach is \textsc{APF-FE},  which is far behind both \textsc{RILS}-\textsc{ROLS} and \textsc{AI-Feynman} w.r.t.\ delivered average ranking.
+	\item  For noise 0.001, the situation is similar.
+\textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking.
 The second best ranking is obtained by \textsc{AI-Feynman} algorithm.
-There is again a statistically significant difference between the results obtained by these two approaches.
-The third best approach is \textsc{Afp-Fe} which performs statistically worse than \textsc{AI-Feynman}.
-	\item  Concerning the instance problems with the included noise level of  0.01, again, \textsc{RILS-ROLS} method produces the best average ranking according to positively evaluated runs, i.e.
-those runs with found  exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \textsc{Dsr}, and \textsc{Afp}.
-The  latter three approaches perform statistically equal, but significantly worse than \text{RILS}-\textsc{ROLS} method.
-	The fourth best approach according to delivered average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}.
-Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data.
-Thus, despite being efficient when comes to the no-noisy data,  \textsc{AI-Feynman} shows to be very sensitive w.r.t.
-increase of the level of noise, which is not that dramatically conspicuous with our \textsc{RILS}-\textsc{ROLS} method.
+There is a statistically significant difference between the results obtained by these two approaches.
+The third best approach is \textsc{AFP-FE} which performs statistically worse than \textsc{AI-Feynman}.
+	\item  When noise level is 0.01, \textsc{RILS-ROLS} method is significantly better than other methods.
+The second best is \textsc{AFP-FE}, followed by \textsc{DSR}, and \textsc{AFTP}.
+The latter three approaches perform statistically equal.
+\textsc{AI-Feynman} is fourth, and on pair with \textsc{gplearn}.
+Note that the average ranking of \textsc{AI-Feynman} method declined significantly with high noise, which is not the case with \textsc{RILS}-\textsc{ROLS} method.
 
 \end{itemize}
-
-\begin{figure}[!ht]
-	\centering
-	\begin{subfigure}[b]{0.75\textwidth} 
-		\includegraphics[  width=300pt,height=180pt]{plots/Feynman_strogatz_noise_0_0-expanded.pdf}
-		\caption{No noise}
-		\label{fig:CDplots-no-noise}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.75\textwidth}
-
-		\includegraphics[  width=300pt,height=180pt]{plots/Feynman_strogatz_noise_0_001-expanded.pdf}
-		\caption{Level of noise equal to 0.001}
-		\label{fig:CDplots-noise0.001}
-	\end{subfigure}
-
-	\begin{subfigure}[b]{0.75\textwidth}
-		\includegraphics[  width=300pt,height=180pt]{plots/Feynman_strogatz_noise_0_01-expanded.pdf}
-		\caption{Level of noise equal to 0.01. }
-		\label{fig:CDplots-noise0.01}
-	\end{subfigure}
-	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.  }
-	\label{fig:cd-plots-exact-pcts}
-\end{figure}
 

### 2022-12-02 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Almost done polishing.

@@
 
-In this section we study the scalability of our method in terms of the size of  instance problems and  the presence of different noise levels in the input data.
-First, for the shake of simplicity of presenting,  we split the instances from \textsc{Random} benchmark sets into three parts as follows.
+In this section we study the scalability of \textsc{RILS-ROLS} w.r.t.
+size of instances problems under different levels of noise.
+For the sake of having simpler presentation, we split the instances from \textsc{Random} benchmark into three parts as follows.
 \begin{itemize}
-	\item \textit{Small--sized instances}: any instance  from \textsc{Random} benchmark whose   corresponding exact model  tree representation  has from 3 to 7 nodes belongs to this sub-set.
-	\item \textit{Medium--sized instances}:  any instance  from \textsc{Random} benchmark whose   corresponding exact model tree representation  has from 8 to 11 nodes belongs to this sub-set.
-	\item \textit{Large--sized instances}: any instances from \textsc{Random} benchmark whose   corresponding exact model  tree representation  has from 12 to 15 nodes belongs to this sub-set. 
+	\item \textit{Small-sized instances}: instances with solution size from 3 to 7.
+	\item \textit{Medium-sized instances}: those with size from 8 to 11.
+	\item \textit{Large-sized instances}: instances with size from 12 to 15. 
 \end{itemize}
 
-The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped with accordance to the above (three) formed sub-groups ($x$-axis); for each of them relative exact percentage rate   of \textsc{RILS}--\textsc{ROLS} algorithm is shown ($y$-axis).
-The following conclusions may be drawn from there.
-
-\begin{itemize}
-	\item   As expected, the exact percentage success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% (over all XXx runs) in case of no-noisy data.
-For the noisy data, the exact success rate is getting decreased as the level of noise increases.
-For example, on the small-sized problem instances with the noise level  of 0.0001, and 0.01, the exact percentage achieved by \textsc{RILS}--\textsc{ROLS} algorithm is still reasonably high, at about 55\%~ and 34 \%, respectively.
-	\item For the medium-sized instance problems where noise is not presented, the exact percentage rate of \textsc{RILS}-\textsc{ROLS} is slightly bellow 50\%.
-It also decreases by increasing the level of noise in the target data; for the highest level of noise (of 0.01), the success rate of \textsc{RILS}-\textsc{ROLS} method is just at about 6\%.
-	\item For the large-sized instance problems where no noise is utilized, the exact percentage rate of \textsc{RILS}--\textsc{ROLS} algorithm is at about 25\%, which means that the increase in the size of exact models affects the algorithm's performance, but not dramatically.
-
-	\item From the above, we can conclude that the size of exact models (solutions) and the increase of   level of noise both contribute to overall performance of our \textsc{RILS}--\textsc{ROLS} method.
-However, the exact percentage rate of the algorithm seems to decrease linearly  in the size of (exact) model, regardless of the noise level values.
-
-	\item Concerning  the percentage of  runs over all random instances for which \textsc{RILS-ROLS} terminates by producing an accurate model, that is a model with $R^2 > 0.999$, for the small--sized problem instances where no noise is included, \textsc{RILS}-\textsc{ROLS} delivers  the perfect score almost.
-In the presence of a low noise level (equals to 0.001), this percentage  is still holding high, at about 95\%.
-In case when the high level of noise (equals to 0.01) is presented in the input data, these percentages stagnate, but still are at a respectable 66\%.
-%small-sized instances it reaches a high--precision of $R^2=0.999$ upon termination.
-	As  pointed out already, for a half of these cases the respectable exact models were found by the algorithm.
-
-	\item Concerning  the medium-sized instance problems when the input data are free of the noise,   the final outcome reached the high precision in 65\% of all algorithm runs.
-The noisy the data are, these percentages, as expected, drop off; however, it is not so dramatically.
-For the level of noise of 0.01, the high--accuracy of the final solution is reported on $\approx$30\% of all runs.
-
-	\item Concerning  the large-sized instance problems with no noise, the  final solution reached the high precision in 60\% of all runs.
-Not so surprisingly, the hardest case to obtain the desired high--accuracy (that is, ensuring $R^2> 0.999$ for  the  outcome) is in the presence of a high level of noise (of 0.01), where the algorithm was successful on about 20\% of all runs concerning the large--sized instance problems.
-
-\end{itemize}
+The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped in accordance to above-mentioned parts ($x$-axis).
+The exact solution accuracy of \textsc{RILS}--\textsc{ROLS} is shown on $y$-axis.
 
@@
 
+The following conclusions may be drawn from there.
+
+\begin{itemize}
+	\item   As expected, the accuracy (exact percentage) is highest for the small-sized instances -- it is sightly bellow 90\% in no-noise scenario.
+For noisy data, the accuracy naturally decreases as the level of noise increases.
+For example, on the small-sized problem instances with the noise level of 0.001, and 0.01, the accuracy achieved by \textsc{RILS}-\textsc{ROLS} is still reasonably high, at about 55\%~ and 34 \%, respectively.
+	\item For the medium-sized instances, when there is no noise, the exact percentage rate is slightly bellow 50\%.
+It also decreases by as the level of noise increases -- for the highest level of noise (0.01), the accuracy of \textsc{RILS}-\textsc{ROLS} method is just about 6\%.
+	\item For the large-sized instance problems, where no noise is included, the exact percentage is about 25\%, which means that the increase in size affects the algorithm's performance, but not dramatically.
+
+	\item We can conclude that increased formula size and noise level jointly contribute to deterioration of overall \textsc{RILS-ROLS} accuracy, which is expected and natural.
+The diagram suggests that this deterioration behaves similar across different levels of noise when instance size changes from small to medium -- almost linearly, and with almost exact slope.
+On the other hand, the relative deterioration under no-noise level, when going from medium to large instance is higher than under noisy data.
+Possible explanation for this is that the exact solution accuracy of medium instances is already very deteriorated in noisy scenario, therefore, further increase in size does not have significant impact.
+\end{itemize}
+
+Results for the $R^2 > 0.999$ accuracy are presented in Figure~\ref{fig:compR2_noise_size}.
+
 \begin{center}
@@
 
-In the rest of the section,  we investigate scalability of our \textsc{RILS}--\textsc{ROLS} algorithm in terms of the number of variables and sizes of corresponding exact models of the problem instances varying levels of noise.
-There are three bar plots generated per each level of noise, shown by Figures~\ref{fig:compExact_noise_varcnt}--\ref{fig:compExact_noise_varsizes}.
-The instances are grouped according to the different variable count/size of respective exact models ($x$-axis) that correspond to them.
-For each group, the exact percentages obtained by \textsc{RILS}--\textsc{ROLS} algorithm group are shown on $y$-axis.
-
-The following conclusions can be drawn from Figure~\ref{fig:compExact_noise_varcnt}.
+The following conclusions may be drawn from these results.
 
 \begin{itemize}
-	\item For the no-noisy data, the exact percentage rate of \textsc{RILS}--\textsc{ROLS} algorithm  slightly decrease as the expected number of variables increases in the exact models. 
-	\item The exact percentages drop off with the presence of a larger noise level. As expected, the higher the noise level, the smaller the exact percentages are.
-	\item Interestingly, in the presence of noise in the data, the highest exact percentages are not obtained for the problem instances which have exact models consisted of a single variable, but two or three.
-We argue it by the fact that the early phase of the algorithm will more likely trying to include additional variables in current solution at the cost of increasing the model accuracy to ensure improving the fitness value over iterations.
-For the no--noisy data, OLS method will more likely find a small-sized high-accuracy model (in our experiments that happened on $\approx$ 50\% runs) that fits to the (no-noisy) input data than the case of noisy data.
-When the data is noisy, the decision of adding more variables at the beginning is likely to be forced than just dealing with short-size solutions.
-%By the progression of the algorithm, it gets harder improving the best fitness value by adding variables, and other operations are more frequently involved than in previous iterations.
-%This conclusion also correlates to the shape of fitness function given by Equation~(\ref{eq:fitness}) where the first two product terms there are already small (close to 1).
-\fxnote{TODO: need to be further expanded...}
-	%Obtaining an accurate model with a few variables in the presence of a high level of nose in the data 
+
+	\item For the small-sized instances, where no noise is included, \textsc{RILS}-\textsc{ROLS} delivers almost the perfect score.
+In the presence of a low noise (0.001), this percentage is still holding high, at about 95\%.
+In case when there is a lot of noise (0.01), these percentages deteriorate significantly, but still come at respectable 66\%.
+
+	\item Concerning  the medium-sized instances in no-noise scenario, accuracy is around 65\%.
+Having low noise does not affect the results too much.
+However, under high noise, the impact is significant, very similar to effect observable in small-sized instances -- it reduces accuracy to just $\approx$30\%.
+
+	\item For the large-sized instances without noise, the accuracy is around 60\%, which is very small relative deterioration in comparison to middle-sized instances.
+Not surprisingly, large instances under high noise are the most difficult to solve -- only 20\% reached $R^2 > 0.999$.
+
 \end{itemize}
 
-\begin{figure}[!ht]
+In the rest of the section, we investigate the sensitivity of \textsc{RILS}-\textsc{ROLS} to variable count under varying levels of noise.
+There are three bar plots generated per each level of noise, Figures~\ref{fig:compExact_noise_varcnt}.
+The instances are grouped according to different variable count ($x$-axis).
+For each group, the exact percentages are shown on $y$-axis.
+
+\begin{figure}[!h]
 
@@
 
-The  following conclusions may be drawn from Figure~\ref{fig:compExact_noise_varsizes}.
+The following conclusions can be drawn from these results.
+
 \begin{itemize}
-	\item The exact percentages are decreased with increase in  the size of exact models, in case of any level of noise utilized on the target values.  %within the input data.
-	\item The highest exact percentages, which are larger than 70\%, are noticed in case of the small-sized problem instances  (the size of models ranges from 3 to 7).
-However, for the same sizes, for noisy data, these percentages are significantly lower; for example, in case of the instances whose exact models are of size 7 when utilizing the level of noise of 0.001 and 0.01, the exact percentages obtained are 20\% and 10\%, respectively.
-
-	\item   For the problem instances with the largest size of (exact) models in case of the no noisy data, exact percentages are never lower than 20\%. The opposite holds for noisy data. 
+	\item For data without noise, the exact percentage of \textsc{RILS}-\textsc{ROLS} slightly decreases as the  number of variables increases. 
+	\item The exact percentages drop off with the presence of a larger noise level. As expected, higher noise means smaller exact percentage.
+	\item Interestingly, in the presence of noise in data, the highest exact percentages are not obtained for the instances with a single input variable, but for those with two or three.
+This is probably due to the expected level of \emph{non-linearity} in instances.
+Namely, when the size of instance is fixed, instances with less input variables will have to use more operations to compensate for the lack of input variables.
+(Note that expression size is calculated simply by counting all nodes in the expression tree, whether these nodes are operations, constants or variables.) Therefore, instances with less variables will more heavily use operations and their compositions, paving a way to more \emph{difficult} functional structure.
+	The reason this is not an issue for no-noisy data is because \textsc{RILS-ROLS} will have to wander less -- there will be no contradictory search directions as with noisy data.
 \end{itemize}
 
-\begin{figure}[!ht]
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_no_noise.eps}
-		\caption{No noise}
-		\label{fig:size-no-noise}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.45\textwidth}
-
-		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_noise0_001.eps}
-		\caption{Level of noise equal to 0.001}
-		\label{fig:size-noise0.001}
-	\end{subfigure}
-	\centering
-	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_exact_correct_noise0_01.eps}
-		\caption{Level of noise equal to 0.01.}
-		\label{fig:size-noise0.01}
-	\end{subfigure}
-	\caption{Exact solution percentages for varying levels of noise and exact model sizes.}
-	\label{fig:compExact_noise_varsizes}
-\end{figure}
+\fxnote{ACA: do ovde stigao}
 

### 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Finished polishing.

@@
 
+Training/test data splits were randomly performed in ratio 75\%:25\%, same as in \texttt{SRBench}.
+Moreover, the splits are structurally the same as in \texttt{SRBench}, because we used the same set of random generator seeds and the same Python splitting method (\texttt{train\_test\_split} from Scikit-Learn library~\cite{scikit-learn}).
+
 \subsection{Datasets and \texttt{SRBench}}\fxnote{Marko: Dosao dovde!}
@@
 \subsection{Comparison to other methods}
-In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to 13 other competitors from the literature.
+% ACA: ima 14 uporednih algoritama, ne 13
+In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to 14 other competitors from the literature.
 The numerical results are reported in Tables~\ref{tab:comp_noise0}-\ref{tab:comp_noise001}.
@@
 \begin{itemize}
-	\item When considering the instance problems with no-noise, the lowest average runtime is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228 sec.).
-A slightly worse runtime is obtained by \textsc{DSR} algorithm (232 sec.).
+	\item When considering the instance problems with no-noise, the lowest average runtime is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228 seconds).
+A slightly worse runtime is obtained by \textsc{DSR} algorithm (232 seconds).
 Note that the relative exact percentage produced by \textsc{RILS}-\textsc{ROLS} is far better from \textsc{DSR} (60.62\% versu 19.71\%).
 All remaining approaches deliver an order of magnitude larger average runtimes than that of \textsc{RILS}-\textsc{ROLS} and \textsc{DSR} methods..
-	\item  When considering instances with the noise level of 0.001, the lowest average runtime to find the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108 sec.).
-The second best is produced by \textsc{DSR}, but this time significantly larger (622 sec.) compared to \textsc{RILS-ROLS}.
+	\item  When considering instances with the noise level of 0.001, the lowest average runtime to find the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108 seconds).
+The second best is produced by \textsc{DSR}, but this time significantly larger (622 seconds) compared to \textsc{RILS-ROLS}.
 	\item When considering the instance problems with the noise level of 0.01, the conclusion is similar to previous. 
@@
 The outcome is represented by means of critical difference (CD) plots.
+% ACA: ima 15 ukupno algoritama, ne 14
 In each CD plot, the 15 competitors are placed on the horizontal axis according to their average ranking.
@@
 
-In this section we study the scalability of \textsc{RILS-ROLS} w.r.t.
-size of instances problems under different levels of noise.
+In this section we study the scalability of \textsc{RILS-ROLS} w.r.t. size of instances problems under different levels of noise.
+Since we do not compare \textsc{RILS-ROLS} to other competitors here, but just assess the method scalability and sensitivity to noise, the experimental setup is different.
+First, we run each instance only once -- note that are 5 randomly generated instances for each of 47 combinations of (size, variable count).
+Second, the exit criteria are different: 1) maximal running time is 300 seconds instead of 1 hour, and 2) maximal number of fitness evaluations is 100 thousands instead of 1 million.
+As before, test set takes 25\% of total data. 
 For the sake of having simpler presentation, we split the instances from \textsc{Random} benchmark into three parts as follows. 
@@
 
-\fxnote{ACA: do ovde stigao}
-
-When one concerns of the runtime analysis of \textsc{RILS}--\textsc{ROLS} algorithm on the \textsc{Random} benchmark set w.r.t\ number of variables, the results are displayed in Figure~\ref{fig:runtime_rils_rols}.
-The instances are grouped w.r.t.\ number of variables involved into corresponding exact models ($x$-axis).
-The following conclusions may be drawn from there.
-
-\begin{itemize}
-	\item As one could expect, average runtime is getting increased with the increase of the number of variables in exact models. 
-	\item Note that the average runtime in case of the instances whose exact models have the largest number of variables (5) is just about 200$s$.
-	\item The two above-mentioned points indicate efficacy of our method especially in case of the instances with small-to-medium sized exact models in the presence of small--to--middle noise levels included in the input data.
-In these cases, the algorithm is able to deliver a reasonable exact percentage rate, which are always larger than 50\%.
-Note that models which have more compact representations (thus, small in their size) are desirable in many areas of natural sciences as they are easy interpret-able than models represented by a more complex mathematical formula.
-\end{itemize}
-
-\begin{figure}[!ht]
+\textsc{RILS}-\textsc{ROLS} running times for \textsc{Random} benchmark are shown in Figure~\ref{fig:runtime_rils_rols}. Instances are grouped w.r.t.\ number of variables ($x$-axis). 
+As one could expect, average running time is getting increased with the increase of the number of variables. 
+\textsc{RILS-ROLS} usually terminates because the maximal number of fitness evaluation is reached (100 thousands), therefore average running times are bellow 300 seconds, which is time-based exit criterion.
+
+\begin{figure}[!h]
 	\begin{subfigure}[b]{0.45\textwidth}
@@
 
-In this paper, we dealt with solving the well--known Symbolic regression (SR)  problem.
-SR problem is a generalization of more interdisciplinary known problems such as linear and logistic regression.
-We proposed a meta-heuristic approach, called \textsc{RILS}-\textsc{ROLS}, which is built upon the Iterated local search (ILS) scheme.
-The first crucial concept within this scheme is utilizing the ordinary least square method to efficiently determine best-fitting internal coefficients to the candidate solution.
-% Thus, the search process is primarily focused on considering already promising solutions in the continuous part of the search space rather than applying enhanced heuristics to search for those coefficients.
-Another key aspect is the utilization of a carefully constructed fitness function in the search, which appeared as a combination of three important scores: RMSE, $R^2$  scores and the size of the model (solution).
-Last but not least, a carefully constructed local search is applied systematically exploring solutions obtained as 1--perturbations of the considered solution, represented as trees.
-1--perturbations of a solution are based on applying the six per-node change operations on the solution's tree representation.
-
-\textsc{RILS-ROLS} method is compared to the 14 other competitor algorithms from the literature on the two ground--truth benchmark sets from the literature, namely \textsc{Feynman} and \textsc{Strogatz}.
-Additionally, we introduced a non-biased benchmark set of randomly generated instances, labelled by \textsc{Random}.
-The experimental evaluation confirmed the efficiency of our method which produced the best average ranking results in terms of exact percentage when compared to all other competitors on the two ground-truth benchmarks in the presence of all three different levels of noise in the input data.
-In all cases, new best exact percentages are obtained by our \textsc{RILS-ROLS} method.
-More in details,
-our algorithm was able to obtain the right model on 60.62\%, 42.08\%, and 34.77\% runs over all considered problem instances in the presence of different noise levels: 0.0, 0.001, and 0.01, respectively.
-For the shake of comparisons, the second best approach \textsc{AI-Feynman}, when the noise level of 0.0 and 0.001 is included, obtains the exact percentages of 52.65\%, and 31.89\%, respectively.
-In case of the highest noise level, the second best approach was \textsc{Afp-Fe}, obtaining an exact percentage rate of 20\%.
-Additionally, the scalability and robustness of \textsc{RILS}-\textsc{ROLS} method are checked and confirmed on the unbiased \textsc{Random} benchmark set in terms of a few different criteria such as the size of the model, the number of variables included in exact models, and obtained average runtimes.
-
-In future work, one could think of constructing a hybrid of \textsc{RILS-ROLS} method with some other meta-heuristics to further boost the quality of the obtained results.
-For example, replacing ILS scheme of \textsc{RILS-RILS} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option to give it a try.
-VNS   utilizes a more stronger and systematic system of solutions diversification and thus escaping from local optima could be much easier and the convergence much faster.
-Additionally, as proof of the efficiency and usefulness of our algorithm, this tool could be applied to solving problems from various problem domains out of the area of computer science, for example from physics or chemistry, to help for setting up reasonable hypotheses or to obtain valuable insights on obtained experimental evaluations.
-
-\section*{Appendix -- \textsc{RILS}-\textsc{ROLS} Python package}\label{sec:appendix-1}
+In this paper, we dealt with solving the well-known symbolic regression (SR)  problem.  
+We proposed a meta-heuristic approach, called \textsc{RILS}-\textsc{ROLS}, built upon the iterated local search (ILS) scheme.
+The crucial element of this scheme is the ordinary least square method (OLS), used to efficiently determine best-fitting linear coefficients within solution equations.
+Another key aspect is the utilization of a carefully constructed fitness function. It combines three important measures of the solution: RMSE, $R^2$, and the solution size. 
+Further, we designed an efficient local search that systematically explores the solution space around candidate solution.
+
+\textsc{RILS-ROLS} method is compared to the 14 other competing methods from the literature on two ground-truth benchmark sets from the literature, named \textsc{Feynman} and \textsc{Strogatz}.
+The experimental evaluation confirmed the quality of our method -- \textsc{RILS-ROLS} produced the best average ranking results in terms of exact model accuracy under varying levels of noise in data.
+In details, our algorithm was able to find the right model in 60.62\%, 42.08\%, and 34.77\% under no-noise, low-level noise and high-level noise, respectively.
+The second best approach \textsc{AI-Feynman} obtains fairly worse percentages: 52.65\%, 31.89\% and 20\%.
+
+In addition to well-known benchmarks from literature, we introduced a new non-biased benchmark set of randomly generated instances, labeled by \textsc{Random}. 
+This benchmark was used to test \textsc{RILS}-\textsc{ROLS} scalability, by varying the size of the model and the number of variables.
+
+In the future work, one could think of constructing a hybrid of \textsc{RILS-ROLS} method with some other meta-heuristics to further boost the quality of the obtained results.
+For example, replacing ILS scheme of \textsc{RILS-RILS} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option.
+Also, \textsc{RILS-ROLS} could be used to solve practical problems from various domains.
+For example, it can be used in physics or chemistry to help setting-up reasonable hypotheses or to obtain valuable insights on obtained experimental evaluations.
+One more improvement direction is incorporating top-level constraints into the method.
+For example, if one knows that the modeled function needs to be monotonically decreasing or differentiable, or both, this knowledge could be used to alter the search -- eliminate inadequate parts of the search space (hard constraint) or more \emph{subtly} penalize this behavior through fitness function (soft constraint).
+
+\fxnote{ACA: PROVERITI REFERENCE, mislim da sam negde video da nedostaju volume ili stranice ili slicno...}
+
+\section*{Appendix - \textsc{RILS}-\textsc{ROLS} Python package}\label{sec:appendix-1}
 

### 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Final revisions almost done

@@
 
-\subsection{Datasets and \texttt{SRBench}}\fxnote{Marko: Dosao dovde!}
+\subsection{Datasets and \texttt{SRBench}}
 
@@
 
-Some \textsc{Random} instances are shown in Table~\ref{table:random}, while all instances can be found at \textsc{RILS-ROLS} GitHub repository: \url{https://github.com/kartelj/rils-rols}.
+Some random instances are shown in Table~\ref{table:random}, while all instances can be found at %\textsc{RILS-ROLS} GitHub 
+ the following repository: \url{https://github.com/kartelj/rils-rols}.
 
@@
 The numerical results are reported in Tables~\ref{tab:comp_noise0}-\ref{tab:comp_noise001}.
-The results for \textsc{Feynman} and \textsc{Storgatz} are given w.r.t.\  the following levels of noise: 0.0 (no-noisy data), 0.001 (low-level noise), and 0.01 (high-level noise).
+The results for \textsc{Feynman} and \textsc{Storgatz} benchmark are given w.r.t.\  the following levels of noise: 0.0 (no-noisy data), 0.001 (low-level noise), and 0.01 (high-level noise).
 More precisely, the white Gaussian noise is added to the target variable the same way as in~\cite{la2021contemporary}:
@@
 It found the exact solution in 57.84\% of runs for \textsc{Feynman} instances.
-It was even more impressive in solving \textsc{Strogatz} instances, being successful in 83.57\% runs.
+It is even more impressive in solving \textsc{Strogatz} instances, being successful in 83.57\% runs.
 The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\% runs for \textsc{Feynman} set, and 27.14\% runs for the problem instances from benchmark set \textsc{Strogatz}.
@@
 The overall results are in favor of \textsc{RILS-ROLS} with 60.62\%, while the second best is \textsc{AI-Feynman} with 52.65\%.
-	\item  Concerning the exact results in presence of the small noise (0.001), our \textsc{RILS-ROLS} is still performing very well, finding an exact model in 42.08\% of runs considering all problem instances.
+	\item  Concerning the exact results in presence of the small noise (0.001), our \textsc{RILS-ROLS} is still performing   well, finding an exact model in 42.08\% of runs considering all problem instances.
 The second best approach is again \textsc{AI-Feynman} being successful in 31.89\% runs.
@@
 
-	\item When comparing performances of the algorithms in terms of $R^2 > 0.999$ accuracy, in no-noise scenario, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (third place).
+	\item When comparing performances of the algorithms in terms of $R^2 > 0.999$ accuracy, in no-noise scenario, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (ranked on the third place).
 Better methods in terms of this accuracy are \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
@@
 A slightly worse runtime is obtained by \textsc{DSR} algorithm (232 seconds).
-Note that the relative exact percentage produced by \textsc{RILS}-\textsc{ROLS} is far better from \textsc{DSR} (60.62\% versu 19.71\%).
+Note that the relative exact percentage produced by \textsc{RILS}-\textsc{ROLS} is far better from \textsc{DSR} (60.62\% versus 19.71\%).
 All remaining approaches deliver an order of magnitude larger average runtimes than that of \textsc{RILS}-\textsc{ROLS} and \textsc{DSR} methods..
-	\item  When considering instances with the noise level of 0.001, the lowest average runtime to find the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108 seconds).
+	\item  When considering instances with the noise level of 0.001, the lowest average runtime to obtain the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108 seconds).
 The second best is produced by \textsc{DSR}, but this time significantly larger (622 seconds) compared to \textsc{RILS-ROLS}.
@@
 The number of ranks is 1300, i.e., for each run of each method, the separate rank is calculated.
-Rank is based on the value of indicator variable, which takes 1 if the method delivers correct model in a given run, otherwise it takes value of 0, no matter if method finished and delivered incorrect model, or method did not finish at all.
-Further, the ranks are averaged and used to test the null hypothesis, which states that there is no statistical differences between the average ranks of all competitors.
-In the case in which the null hypothesis $H_0$ was rejected, pairwise comparisons were further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
+Rank is based on the value of indicator variable, which takes 1 if the method delivers correct model in a given run, otherwise it takes value of 0, no matter if method finished and delivered incorrect model, or the method did not finish at all.
+Further, the ranks are averaged and used to test the null hypothesis, which states that there is   statistical differences between the average ranks of all competitors.
+In the case the null hypothesis $H_0$ was rejected, pairwise comparisons were further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
 The outcome is represented by means of critical difference (CD) plots.
-% ACA: ima 15 ukupno algoritama, ne 14
+
 In each CD plot, the 15 competitors are placed on the horizontal axis according to their average ranking.
@@
 Since we do not compare \textsc{RILS-ROLS} to other competitors here, but just assess the method scalability and sensitivity to noise, the experimental setup is different.
-First, we run each instance only once -- note that are 5 randomly generated instances for each of 47 combinations of (size, variable count).
+First, we run each instance only once -- note that there are 5 randomly generated instances for each of 47 combinations of (size, variable count).
 Second, the exit criteria are different: 1) maximal running time is 300 seconds instead of 1 hour, and 2) maximal number of fitness evaluations is 100 thousands instead of 1 million.
-As before, test set takes 25\% of total data. 
+As before, the test set takes 25\% of total data. 
 For the sake of having simpler presentation, we split the instances from \textsc{Random} benchmark into three parts as follows. 
@@
 The diagram suggests that this deterioration behaves similar across different levels of noise when instance size changes from small to medium -- almost linearly, and with almost exact slope.
-On the other hand, the relative deterioration under no-noise level, when going from medium to large instance is higher than under noisy data.
+On the other hand, the relative deterioration of accuracy under no-noise level, when going from medium to large instance is higher than under noisy data.
 Possible explanation for this is that the exact solution accuracy of medium instances is already very deteriorated in noisy scenario, therefore, further increase in size does not have significant impact.
@@
 
-The following conclusions may be drawn from these results.
+The following conclusions may be drawn from these results. \fxnote{Marko: dosao dovde!}
 

### 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Small sentence regarding our model accuracy calculation.

--- 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
@@
 On the other hand, one can have a method B that finishes instances execution in only 4 out of 10 runs, giving 2 successful models each time -- its per-instances accuracy will be 50\%, and after averaging across all instances it will be also 50\%.
-So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.}
+So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.
+Also, note that our calculation cannot overestimate \textsc{RILS-ROLS} exact model accuracy, since denominator is always maximal (1300) -- in essence, non-finished runs are counted as non-successful.}
 

### 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Abstract revision.

@@
 \begin{abstract} % abstract
-In this paper, we solve the well-known symbolic regression problem.
-This problem has been intensively studied in the literature and has a wide range of applications.
-The symbolic regression models could provide insights towards establishing physical theory behind experimentally observed data.
-Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modeling analytic representations of the exciton binding energy in energy science, finding models for band gaps of NaCl-type compounds
-in material science, just to name a few.
-
-We propose an efficient meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS} to solve this problem.
-\textsc{RILS}-\textsc{ROLS} is based on the following elements: ($i$) iterated local search is the method backbone, mainly solving combinatorial and some continuous aspects of the problem; ($ii$) ordinary least square method is focused on the continuous aspect of the search space -- it efficiently determines the best--fitting coefficients of linear combinations within solution equations;  ($iii$) a novel fitness function combines three important model quality measures: $R^2$ score, RMSE score, and the size of the model (or model complexity).
+In this paper, we solve the well-known symbolic regression problem that has been intensively studied in the literature and has a wide range of applications. 
+% ACA: ove recenice vise prilice uvodu, tamo svakako i postoji, da ne bude preglomazan abstrakt
+%The symbolic regression models could provide insights towards establishing physical theory behind experimentally observed data. 
+%Practical applications include revealing complex ecological dynamics in ecology, discovering mutations effects on protein stability in biology, modeling analytic representations of the exciton binding energy in energy science, finding models for band gaps of NaCl-type compounds in material science, just to name a few.
+
+We propose an efficient meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS} to solve it.
+\textsc{RILS}-\textsc{ROLS} is based on the following two parts: ($i$) iterated local search serving as the method backbone, mainly solving combinatorial and some continuous aspects of the problem; ($ii$) ordinary least square method is focused on the continuous aspect of the search space -- it efficiently determines the best--fitting coefficients of linear combinations within solution equations.
+Beside that, we introduce a novel fitness function that combines three important model quality measures: $R^2$ score, RMSE score, and the size of the model (or model complexity), and carefully designed local search, which allows systematic search in proximity to candidate solution.
 
@@
 \textsc{RILS}-\textsc{ROLS} was compared to 14 other competitors from the literature.
-Our method outperformed all 14 competitors with respect to the true symbolic model accuracy percentage under varying levels of noise.
+Our method outperformed all 14 competitors with respect to the true symbolic model accuracy under varying levels of noise.
 It also showed to be the most efficient considering the average running time of reaching the exact model.
 In addition to evaluation on known ground-truth datasets, a new randomly generated set of problem instances is introduced.
-The goal of \textsc{Random} dataset was to test the scalability of our method with respect to incremental equation sizes and different levels of noise.
-\textsc{RILS}-\textsc{ROLS} can be considered as a new state-of-the-art method for solving the problem of symbolic regression when ground-truth equations are known.
+The goal of \textsc{Random} dataset was to test the scalability of our method with respect to incremental equation sizes and number of variables, under different levels of noise.
+
+Statistical analysis of obtained experimental results confirmed that \textsc{RILS}-\textsc{ROLS} can be considered as a new state-of-the-art method for solving the problem of symbolic regression when ground-truth equations are known.
 \end{abstract}
@@
 \begin{keyword}
-\kwd{Symbolic regression}
-\kwd{Iterated local search}
-\kwd{Ordinary least square}
+\kwd{symbolic regression}
+\kwd{iterated local search}
+\kwd{ordinary least square}
 \end{keyword}

### 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Final polishing

--- 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
@@
 
-In this work we present a novel approach to solve \emph{ground-truth}-based SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2019iterated} with the ordinary least square method (OLS)~\cite{leng2007ordinary}.
+In this work we present a novel approach to solve \emph{ground-truth}-based SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2010iterated} with the ordinary least square method (OLS)~\cite{leng2007ordinary}.
 ILS mostly handles combinatorial (discrete) aspects of search space, while OLS helps in the process of a coefficient determination, so it handles some continuous parts of the search space.
@@
 		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
-		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+		Method &  \textsc{Feynman} & \textsc{Strogatz}& Total &  \textsc{Feynman} & \textsc{Strogatz} & Total \\ \hline
 		\textsc{RILS-ROLS}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
@@
 		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
-		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+		Method &  \textsc{Feynman} & \textsc{Strogatz} & Total &  \textsc{Feynman} & \textsc{Strogatz} & Total \\ \hline
 		\textsc{RILS-ROLS}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
@@
 		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
-		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
+		Method & \textsc{Feynman} & \textsc{Strogatz} & Total & \textsc{Feynman} & \textsc{Strogatz} & Total \\ \hline
 		\textsc{RILS-ROLS}&\bf{36.29}&\bf{22.14}&\bf{34.77}&64.91&46.43&62.92\\
@@
 On the other hand, one can have a method B that finishes instances execution in only 4 out of 10 runs, giving 2 successful models each time -- its per-instances accuracy will be 50\%, and after averaging across all instances it will be also 50\%.
-So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.
-Also, note that our calculation cannot overestimate \textsc{RILS-ROLS} exact model accuracy, since denominator is always maximal (1300) -- in essence, non-finished runs are counted as non-successful.}
+So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.}
 
@@
 
-The following conclusions may be drawn from these results. \fxnote{Marko: dosao dovde!}
+The following conclusions may be drawn from these results.
 
@@
 (Note that expression size is calculated simply by counting all nodes in the expression tree, whether these nodes are operations, constants or variables.) Therefore, instances with less variables will more heavily use operations and their compositions, paving a way to more \emph{difficult} functional structure.
-	The reason this is not an issue for no-noisy data is because \textsc{RILS-ROLS} will have to wander less -- there will be no contradictory search directions as with noisy data.
+	The reason this is not an issue for no-noisy data is because \textsc{RILS-ROLS} will have to wander less -- there will be no so many contradictory search directions as with noisy data.
 \end{itemize}
@@
 
-\section*{Acknowledgements}%% if any
-Text for this section\ldots
+ \section*{Acknowledgments}%% if any
+Not applicable.
 
  \section*{Funding}%% if any
-Text for this section\ldots
-
-\section*{Abbreviations}%% if any
-Text for this section\ldots
+Not applicable.
+
+%\section*{Abbreviations}%% if any
+%Text for this section\ldots
 
   \section*{Availability of data and materials}%% if any
-Text for this section\ldots
+ All accompanying resources regarding this paper can be found under the repository \url{https://github.com/kartelj/rils-rols}.
 
 \section*{Ethics approval and consent to participate}%% if any
-Text for this section\ldots
+Not applicable.
 
 \section*{Competing interests}
-The authors declare that they have no competing interests.
+The authors declare  no competing interests.
 
 \section*{Consent for publication}%% if any
-Text for this section\ldots
+Not applicable.
 
 \section*{Authors' contributions}
-Text for this section \ldots
-
-\section*{Authors' information}%% if any
-Text for this section\ldots
+A.K.
+and M.D.
+contributed to the conception of the work.
+A.K.
+worked on implementing the algorithm and the design of experiments.
+M.D.
+worked on analysis and discussion of the results.
+Both authors read and approved the final manuscript.
+
+%\section*{Authors' information}%% if any
+%Text for this section\ldots
 
@@
 
-\section*{Additional Files}
-  \subsection*{Additional file 1 --- Sample additional file title}
-    Additional file descriptions text (including details of how to
-    view the file, if it is in a non-standard format or the file extension).  This might
-    refer to a multi-page table or a figure...
+%\section*{Additional Files}
+%  \subsection*{Additional file 1 --- Sample additional file title}
+ %   Additional file descriptions text (including details of how to
+ %   view the file, if it is in a non-standard format or the file extension).  This might
+ %   refer to a multi-page table or a figure...
 

### 2022-12-04 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Converted docx for english proofreading.

@@
 
-		\includegraphics[  width=190pt,height=150pt]{plots/time-avg-noise0.001.eps}
+		\includegraphics[width=190pt,height=150pt]{plots/time-avg-noise0.001.eps}
 		\caption{Level of noise equal to 0.001}
@@
 	\begin{subfigure}[b]{0.47\textwidth}
-		\includegraphics[  width=190pt,height=150pt]{plots/time-avg-noise0.01.eps}
+		\includegraphics[width=190pt,height=150pt]{plots/time-avg-noise0.01.eps}
 		\caption{Level of noise equal to 0.01.}
@@
 	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_no_noise.eps}
+		\includegraphics[width=180pt,height=140pt]{plots/numvars_vs_exact_correct_no_noise.eps}
 		\caption{No noise}
@@
 
-		\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_noise0_001.eps}
+		\includegraphics[width=180pt,height=140pt]{plots/numvars_vs_exact_correct_noise0_001.eps}
 		\caption{Level of noise equal to 0.001}
@@
 	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/numvars_vs_exact_correct_noise0_01.eps}
+		\includegraphics[width=180pt,height=140pt]{plots/numvars_vs_exact_correct_noise0_01.eps}
 		\caption{Level of noise equal to 0.01.}
@@
 	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/numsize_vs_time_no_noise.eps}
+		\includegraphics[width=180pt,height=140pt]{plots/numsize_vs_time_no_noise.eps}
 		\caption{No noise}
@@
 
-		\includegraphics[  width=180pt,height=140pt]{plots/vars_vs_time_noise0_001.eps}
+		\includegraphics[width=180pt,height=140pt]{plots/vars_vs_time_noise0_001.eps}
 		\caption{Level of noise equal to 0.001}
@@
 	\begin{subfigure}[b]{0.40\textwidth}
-		\includegraphics[  width=180pt,height=140pt]{plots/vars_vs_time_noise0_01.eps}
+		\includegraphics[width=180pt,height=140pt]{plots/vars_vs_time_noise0_01.eps}
 		\caption{Level of noise equal to 0.01.}
@@
 
-\fxnote{ACA: PROVERITI REFERENCE, mislim da sam negde video da nedostaju volume ili stranice ili slicno...}
-
 \section*{Appendix - \textsc{RILS}-\textsc{ROLS} Python package}\label{sec:appendix-1}
@@
 
-Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found under the project GitHub page \url{https://github.com/kartelj/rils-rols}.
+Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found at the project GitHub page \url{https://github.com/kartelj/rils-rols}. 
+In addition, there is a
 
@@
 \section*{Authors' contributions}
-A.K.
-and M.D.
+Both A.K.
+and M.Dj.
 contributed to the conception of the work.
 A.K.
-worked on implementing the algorithm and the design of experiments.
-M.D.
-worked on analysis and discussion of the results.
-Both authors read and approved the final manuscript.
+worked on the implementation of method and the design of experiments.
+M.Dj.
+worked on analysis and discussion of the results, introduction and literature review.
 

### 2022-12-13 paper_resources/doc/bmc_jbd/bmc_jbd.tex
English revisions applied.

@@
 
-\title{ {RILS}-{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
+\title{ {RILS}-{ROLS}: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares}
 
@@
 \begin{abstract} % abstract
-In this paper, we solve the well-known symbolic regression problem that has been intensively studied in the literature and has a wide range of applications. 
+In this paper, we solve the well-known symbolic regression problem that has been intensively studied and has a wide range of applications. 
 % ACA: ove recenice vise prilice uvodu, tamo svakako i postoji, da ne bude preglomazan abstrakt
@@
 
-We propose an efficient meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS} to solve it.
-\textsc{RILS}-\textsc{ROLS} is based on the following two parts: ($i$) iterated local search serving as the method backbone, mainly solving combinatorial and some continuous aspects of the problem; ($ii$) ordinary least square method is focused on the continuous aspect of the search space -- it efficiently determines the best--fitting coefficients of linear combinations within solution equations.
-Beside that, we introduce a novel fitness function that combines three important model quality measures: $R^2$ score, RMSE score, and the size of the model (or model complexity), and carefully designed local search, which allows systematic search in proximity to candidate solution.
-
-The experiments are conducted on the two well-known ground-truth benchmark sets called \textsc{Feynman} and \textsc{Strogatz}.
+To solve it, we propose an efficient meta-heuristic-based approach, called \textsc{RILS}-\textsc{ROLS}.
+\textsc{RILS}-\textsc{ROLS} is based on the following two elements: ($i$) iterated local search, which is the method backbone, mainly solving combinatorial and some continuous aspects of the problem; ($ii$) ordinary least square method, which focuses on the continuous aspect of the search space -- it efficiently determines the best--fitting coefficients of linear combinations within solution equations.
+In addition, we introduce a novel fitness function that combines important model quality measures: $R^2$ score, RMSE score, size of the model (or model complexity), and carefully designed local search, which allows systematic search in proximity to candidate solution.
+
+Experiments are conducted on the two well-known ground-truth benchmark sets called \textsc{Feynman} and \textsc{Strogatz}.
 \textsc{RILS}-\textsc{ROLS} was compared to 14 other competitors from the literature.
 Our method outperformed all 14 competitors with respect to the true symbolic model accuracy under varying levels of noise.
-It also showed to be the most efficient considering the average running time of reaching the exact model.
-In addition to evaluation on known ground-truth datasets, a new randomly generated set of problem instances is introduced.
-The goal of \textsc{Random} dataset was to test the scalability of our method with respect to incremental equation sizes and number of variables, under different levels of noise.
-
-Statistical analysis of obtained experimental results confirmed that \textsc{RILS}-\textsc{ROLS} can be considered as a new state-of-the-art method for solving the problem of symbolic regression when ground-truth equations are known.
+It also proved to be the most efficient method considering the average running time of reaching the exact model.
+In addition to evaluation on known ground-truth datasets, we introduce a new randomly generated set of problem instances.
+The goal of the \textsc{Random} dataset was to test the scalability of our method with respect to incremental equation sizes and number of variables, under different levels of noise.
+
+The statistical analysis of obtained experimental results confirmed that \textsc{RILS}-\textsc{ROLS} can be considered as a new state-of-the-art method for solving the problem of symbolic regression when ground-truth equations are known.
 \end{abstract}
@@
 
-The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade.
-SR can be seen as a generalization of more specific variants of regression in which the functional form is fixed, e.g.
-the well-known linear regression, polynomial regression~\cite{stimson1978interpreting}, etc.
-All regression models have the same goal: given a set of $n$-dimensional input data and its corresponding continuous output target variable, the aim is to find a  mathematical expression (function) of $n$ (input) variables that   \emph{fits} best to the target variable.
+The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted a lot of research interest over the last decade.
+SR can be seen as a generalization of more specific variants of regression in which the functional form is fixed, e.g., the well-known linear regression, polynomial regression~\cite{stimson1978interpreting}, etc.
+All regression models have the same goal: given a set of $n$-dimensional input data and its corresponding continuous output target variable, the aim is to find a  mathematical expression (function) of $n$ (input) variables that best \emph{fits} the target variable.
 %This computationally intensive task is in general provenly NP--hard~\cite{virgolin2022symbolic}.
 In the case of linear regression, the model is always a linear combination of input variables.
-This is in general not good enough, since target variable might be dependent on some nonlinear function among input variables.
-Unlike linear regression, SR allows the search over much larger space of possible mathematical formulas to find the best-fitting ones, i.e.
-those able to predict the target variable from the input variables.
-The basis of constructing explicit formula is in elementary operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and others.
+This is in general not good enough, since the target variable might be dependent on a nonlinear function among input variables.
+Unlike linear regression, SR allows for the search over much larger space of possible mathematical formulas to find the best-fitting ones, i.e., those able to predict the target variable from input variables.
+The basis of constructing an explicit formula is in elementary operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other operations.
 %Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef
@@
 Moreover, relations among variables might be described in an elegant way.
-For example, the appearance of an exponential function can be associated with some physical phenomenon such as the intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}.
-Additionally, the SR models often have high generalization power unlike some models with fixed functional forms such as polynomial regression.
+For example, the appearance of an exponential function can be associated with a specific physical phenomenon such as the intensity of radiation or acceleration over time (see~\cite{udrescu2020ai}).
+Additionally, SR models often have high generalization power unlike some models with fixed functional forms such as polynomial regression.
 
 Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}.
-In particular, this paper describes the discovery of a series of new oxide perovskite catalysts with improved activities.
+This paper in particular describes the discovery of a series of new oxide perovskite catalysts with improved activities.
 The application of SR to discovering physical laws from a distorted video is studied in~\cite{udrescu2021symbolic}.
-Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}.
-Paper \cite{louis2021reviewing} provides the application of SR to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology.
-A recent study in \cite{liu2021machine} is concerned of auto-discovering conserved quantities using trajectory data from unknown dynamical systems.
-The application of SR to model analytic representations of the exciton binding energy is shown in~\cite{liang2019phillips}.
+The revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}.
+The paper \cite{louis2021reviewing} presents the application of the SR to model the effects of mutations on protein stability in the domain of fundamental and applied biology.
+A recent study in \cite{liu2021machine} is concerned with auto-discovering conserved quantities using trajectory data from unknown dynamical systems.
+The application of the SR to model analytic representations of exciton binding energy is shown in~\cite{liang2019phillips}.
 The use of SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}.
@@
 
-	There are many different ways to tackle the SR.
-Most of them are based on   machine learning techniques, genetic programming (GP) or some other meta-heuristics.
+There are many different ways to tackle SR.
+Most of them are based on   machine learning techniques, genetic programming (GP), or some other meta-heuristics.
 Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming.
-A differential evolution algorithm was proposed by Cerny et al.~\cite{cerny2008using}.
+A differential evolution algorithm is proposed by Cerny et al.~\cite{cerny2008using}.
 Age-fitness Pareto Optimization approach is proposed by Smidt and Lipson~\cite{schmidt2010age}.
@@
 Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
-A variable neighbourhood programming approach  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique is initially proposed in~\cite{elleuch2016variable}.
+A variable neighbourhood programming approach  is proposed by Elleurich et al.~\cite{elleuch2020variable}; this technique was initially proposed in~\cite{elleuch2016variable}.
 Kommenda et al.~\cite{kommenda2020parameter} proposed a method called \textsc{Operon} algorithm, which uses nonlinear least squares for parameter identification of SR models further integrated into a local search mechanism in tree-based GP.
 The C++ implementation of \textsc{Operon} is discussed in~\cite{burlacu2020operon}.
-The method that utilizes the Taylor polynomials to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
+The method that utilizes Taylor polynomials to approximate the symbolic equation that fits the dataset, called Taylor genetic programming, is proposed in~\cite{he2022taylor}.
 A GP approach that uses the idea of semantic back-propagation (SBP-GP) is proposed in~\cite{virgolin2019linear}.
-Empirical analysis of variance between many GP-based methods for SR is discussed in~\cite{kammerer2021empirical}.
+The empirical analysis of variance between many GP-based methods for SR is discussed in~\cite{kammerer2021empirical}.
 It is also worth to mention the GP-based Eurequa commercial solver~\cite{schmidt2009distilling, schmidt2011machine} that uses age-fitness pareto optimization with co-evolved fitness estimation.
@@
 
-	Method based on Bayesian symbolic regression (\textsc{BSR}) is proposed in~\cite{jin2019bayesian} -- this method belongs to a family of Markov Chain Monte Carlo algorithms (MCMC).
-Deep Symbolic Regression (\textsc{DSR}), an RNN approach, is proposed in~\cite{petersen2019deep} -- it utilizes the policy gradient search.
+The method based on Bayesian symbolic regression (\textsc{BSR}) is proposed in~\cite{jin2019bayesian} -- this method belongs to the family of Markov Chain Monte Carlo algorithms (MCMC).
+Deep Symbolic Regression (\textsc{DSR}), an RNN approach that utilizes the policy gradient search, is proposed in~\cite{petersen2019deep}.
 This mechanism of search is further investigated in~\cite{landajuela2021improving}.
-A fast neural network approach, called \textsc{OccamNet},  is proposed in~\cite{costa2020fast}.
+A fast neural network approach, called \textsc{OccamNet} is proposed in~\cite{costa2020fast}.
 A deep reinforcement learning approach enhanced with genetic programming is proposed in~\cite{mundhenk2021symbolic}.
 
-Powerful hybrid techniques to solve SR are also well studied; among them, we emphasize the \textsc{Eplex} solver from~\cite{la2019probabilistic,la2016epsilon} and \textsc{AI-Feynman} algorithm from~\cite{udrescu2020ai}, a physics-inspired divide-and-conquer method combined with the neural network fitting.
+Powerful hybrid techniques for solving SR are also well studied; among them, we emphasize the \textsc{Eplex} solver by~\cite{la2019probabilistic,la2016epsilon} and \textsc{AI-Feynman} algorithm by~\cite{udrescu2020ai}, based on a physics-inspired divide-and-conquer method combined with the neural network fitting.
 The latter is one of the most efficient methods for physically-inspired models.
-We also mention the Fast Function Extraction (\textsc{FFX}) algorithm developed by McConaghy~\cite{mcconaghy2011ffx}, which is a non-evolutionary method combined with a machine learning technique called path-wise-regularized learning, which quickly prunes a huge set of candidate basis functions down to compact models.
+We would also like to mention the Fast Function Extraction (\textsc{FFX}) algorithm developed by McConaghy~\cite{mcconaghy2011ffx}, which is a non-evolutionary method combined with a machine learning technique called path-wise-regularized learning, which quickly prunes a huge set of candidate basis functions down to compact models.
 
@@
 	\begin{table}[!h]
+		\caption{SR methods overview.}
+		\label{tab:gp-based}
 	\centering
@@
 			Algorithm          &   Paper/year &   Short details   \\ \hline
-			\textsc{GP}        &    \cite{koza1994genetic} (1994)    & Application of GP to SR \\ 
-			\textsc{Hybrid-GP}  &   \cite{raidl1998hybrid} (1998)   & GP-based method; solutions are locally optimized with OLS to find optimum coefficients for top-level terms \\ 
-			\textsc{DFE}        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
-			\textsc{APF-FE}                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness Pareto optimization approach using co-evolved fitness estimation   \\
-			APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness Pareto optimization approach                        \\
-			\textsc{FFX}  & \cite{mcconaghy2011ffx} (2011)  & The fast function extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning \\
-			\textsc{ABCP} &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach \\
-			\textsc{EPLEX}          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$-lexicase selection  \\ 
+			\textsc{GP}        &    \cite{koza1994genetic} (1994)    & Application of GP to SR. \\ 
+			\textsc{Hybrid-GP}  &   \cite{raidl1998hybrid} (1998)   & GP-based method; solutions are locally optimized with OLS to find optimal coefficients for top-level terms. \\ 
+			\textsc{DFE}        & \cite{cerny2008using} (2008)   & Differential evolution algorithm. \\
+			\textsc{APF-FE}                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness Pareto optimization approach using co-evolved fitness estimation.   \\
+			\textsc{APF}            &      \cite{schmidt2010age} (2010)        &  Age-fitness Pareto optimization approach.                        \\
+			\textsc{FFX}  & \cite{mcconaghy2011ffx} (2011)  & The fast function extraction algorithm --  non-evolutionary technique based on a machine learning technique called path-wise regularized learning.
+\\
+			\textsc{ABCP} &  \cite{karaboga2012artificial} (2012)  & Artificial bee colony programming  approach. \\
+			\textsc{EPLEX}          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$-lexicase selection.  \\ 
 			\textsc{MRGP} & \cite{arnaldo2014multiple} (2014) & It decouples and
-			linearly combines a program's subexpressions via multiple regression on the target variable  \\
-			Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants optimization in GP by nonlinear least squares \\
-			\textsc{FEAT} & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees comprised of activation functions; differentiable features are trained via gradient descent \\
-			\textsc{SBP-GP} &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP \\
-			\textsc{BSR} & \cite{jin2019bayesian} (2019) & ML-based approach; Bayesian symbolic regression  \\ 
-			\textsc{DSR}  & \cite{petersen2019deep} (2019) & Deep symbolic regression based on a RNN approach further utilizing the policy gradient search \\
-			\textsc{Operon} & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS \\
-			\textsc{VNP}    & \cite{elleuch2020variable} (2020) & VNS based GP approach \\
-			\textsc{OccamNet} & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation  based on cross-entropy matching in an EA strategy	 \\
-
-			\textsc{AI-Feynman} & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it also uses neural network fitting \\
+			linearly combines a program's subexpressions via multiple regression on the target variable.  \\
+			Local optimization NLS    & \cite{kommenda2018local} (2018)   & Constants optimization in GP by nonlinear least squares. \\
+			\textsc{FEAT} & \cite{la2018learning} (2018) & Features are represented as networks of multi-type expression trees comprised of activation functions; differentiable features are trained via gradient descent.
+\\
+			\textsc{SBP-GP} &  \cite{virgolin2019linear} (2019)  & The idea of semantic back-propagation utilized in GP. \\
+			\textsc{BSR} & \cite{jin2019bayesian} (2019) & ML-based approach; Bayesian symbolic regression. \\ 
+			\textsc{DSR}  & \cite{petersen2019deep} (2019) & Deep symbolic regression based on a RNN approach further utilizing the policy gradient search. \\
+			\textsc{Operon} & \cite{kommenda2020parameter} (2020) &  Utilizing nonlinear least squares for parameter identification of SR models with LS. \\
+			\textsc{VNP}    & \cite{elleuch2020variable} (2020) & VNS approach inspired by GP. \\
+			\textsc{OccamNet} & \cite{costa2020fast} (2020) &   A fast neural network approach; the model defines a probability distribution over a non-differentiable function space; it samples functions and updates the weights with back-propagation based on cross-entropy matching in an EA strategy.	 \\
+
+			\textsc{AI-Feynman} & \cite{udrescu2020ai} (2020) & A physics-inspired divide-and-conquer method; it also uses neural network fitting. \\
 			\textsc{GOMEA}  & \cite{virgolin2021improving} (2021)    & A model-based
-			EA framework called gene-pool optimal mixing evolutionary algorithm \\
-			\textsc{ITEA} & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA   \\
-			\textsc{SA} & \cite{kantor2021simulated} (2021) &  Simulated annealing approach \\
-
-			\textsc{DRLA} & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming \\
-			\textsc{Taylor-GP} &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations  \\ \hline
+			EA framework called gene-pool optimal mixing evolutionary algorithm. \\
+			\textsc{ITEA} & \cite{de2021interaction} (2021)   & EA based approach called the interaction-transformation EA.   \\
+			\textsc{SA} & \cite{kantor2021simulated} (2021) &  Simulated annealing approach. \\
+
+			\textsc{DRLA} & \cite{mundhenk2021symbolic} (2021)  &    A deep reinforcement learning approach enhanced with genetic programming. \\
+			\textsc{Taylor-GP} &  \cite{he2022taylor} (2022)  &  Taylor polynomials approximations.  \\ \hline
 
 	\end{tabularx} }
-	\caption{SR methods overview.}
-	\label{tab:gp-based}
 \end{table}
 
-The SR researches lack uniform, robust, and transparent
+SR research lacks uniform, robust, and transparent
 benchmarking standards. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
-open-source, reproducible benchmarking platform for SR, called \texttt{SRBench}.
+open-source, reproducible benchmarking platform for SR called \texttt{SRBench}.
 The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression problems, with 130 SR datasets for which exact (\emph{ground-truth}) models are known; see more in the aforementioned paper.
@@
 symbolic regression methods and 7 machine learning methods are compared on the set of 252 diverse regression problems.
-The remaining 122 SR datasets belong to a class of so-called \emph{black-box} problems for which the \emph{ground-truth} is unknown.
+The remaining 122 SR datasets belong to a class of so-called \emph{black-box} problems for which the ground-truth is unknown.
 One of the most interesting conclusions from La Cava et al.
-research is that algorithms specialize in either solving \emph{ground-truth} problems, or \emph{black-box} problems, but not both.
-
-In this work we present a novel approach to solve \emph{ground-truth}-based SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2010iterated} with the ordinary least square method (OLS)~\cite{leng2007ordinary}.
-ILS mostly handles combinatorial (discrete) aspects of search space, while OLS helps in the process of a coefficient determination, so it handles some continuous parts of the search space.
+research is that algorithms specialize in either solving ground-truth problems, or black-box problems, but not both.
+
+In this work we present a novel approach to solving ground-truth-based SR, which combines the popular iterated local search meta-heuristic (ILS)~\cite{lourencco2003iterated,lourencco2010iterated} with the ordinary least square method (OLS)~\cite{leng2007ordinary}.
+ILS mostly handles combinatorial (discrete) aspects of search space, while OLS helps in the process of coefficient determination, so it handles some continuous parts of the search space.
 As will be shown later, the proposed method has shown its robustness w.r.t.
-introduced noise, therefore we called the method \textsc{RILS}-\textsc{ROLS}  (with letters R corresponding to regression and robust).
-Additionally, in order to navigate the search toward exact model (and not only accurate one) the algorithm is equipped with a carefully constructed fitness function that combines three important model characteristics: RMSE and $R^2$ scores which participate into models accuracy, and a weighted solution size that penalizes too complex models.
+introduced noise, which is why we called the method \textsc{RILS}-\textsc{ROLS}  (with letters R for regression and robust).
+Additionally, to navigate the search toward the exact model (and not only the accurate one) the algorithm is equipped with a carefully constructed fitness function that combines three important model characteristics: RMSE and $R^2$ scores which participate int the model's accuracy, and a weighted solution size that penalizes too complex models.
 
@@
 \begin{enumerate}
-	\item The proposed method outperforms 14 comparison methods on two \emph{ground-truth} benchmark sets from literature -- these methods and benchmarks are used in \texttt{SRBench} platform.
-
-	\item The method shows its high robustness, which is proved by its comparison to the other algorithms in the presence of different levels of Gaussian white noise in the input data.
-
-	\item The method is very efficient, taking in average less than 4 minutes to reach the exact solution, on the problem instances where it was possible.
-
-	\item A new set of unbiased instances is introduced -- it consists of randomly generated formulae of various sizes and number of input variables.
-This set was employed to analyze the effect of the model size and the level of noise on the solving difficulty.
+	\item The proposed method outperforms 14 comparison methods on two ground-truth benchmark sets from the literature -- these methods and benchmarks are used in the \texttt{SRBench} platform.
+
+	\item The method demonstrates high robustness, which is proved by comparison to other algorithms in the presence of different levels of Gaussian white noise in data.
+
+	\item The method is very efficient, taking on average less than 4 minutes to reach the exact solution in the problem instances where it was possible.
+
+	\item A new set of unbiased instances is introduced -- it consists of randomly generated formulae of various sizes and a number of input variables.
+This set was employed to analyze the effect of model size, number of input variables and the level of noise on the solving difficulty.
 \end{enumerate}
@@
 \begin{definition}
-	Given is a dataset $D = \{(\mathbf{x_i}, y_i)\}_{i=1}^n$, where $\mathbf{x_i} \in \mathbb{R}^d$ represents i-th feature (input) vector while $y_i \in \mathbb{R}$ is its corresponding target (output) variable.
+	Given is a dataset $D = \{(\mathbf{x_i}, y_i)\}_{i=1}^n$, where $\mathbf{x_i} \in \mathbb{R}^d$ represents the i-th feature (input) vector while $y_i \in \mathbb{R}$ is its corresponding target (output) variable.
 Suppose that there exists an analytical model of the form $f(\mathbf{x})= g^*(\mathbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.
-	The goal of SR is to learn a mapping $\tilde{f}(\mathbf{x})=  \tilde{g}(\mathbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is observed white noise within the given input data.
+	The goal of SR is to learn the mapping $\tilde{f}(\mathbf{x})=  \tilde{g}(\mathbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the observed white noise within the given input data.
 
@@
 GP can be used to optimize nonlinear structures such as computer programs.
-In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants.
+In particular, programs are represented by syntax trees consisting of functions/operations over input features and constants.
 As an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example}.
 In essence, all valid syntax trees form the solution search space of SR.
-That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree.
-The solution accuracy can be computed on the basis of historical data $D$ and the chosen error measure such as $MSE$, $RMSE$, $R^2$, some combination of them, etc.
-Interestingly, the SR search space nature is twofold: discrete and continuous.
+That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by a respective syntax tree.
+The solution accuracy can be computed on the basis of historical data $D$ and the chosen error measure such as $MSE$, $RMSE$, $R^2$, their combination, etc.
+Interestingly, the nature of SR search space is twofold: discrete and continuous.
 It is primarily modeled as a problem of discrete (combinatorial) optimization, since the number of possible solution functional forms is countable.
@@
 Our method relies on the following operations: $+$, $-$, $\cdot$, $/$, $\sqrt{x}$, $x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $a^x$, where $a^x$ is only consequently used -- it is never explicitly introduced in the search space.
-Beside this, the following set of constants enters the search space explicitly: $-1$, $0$, $1$, $2$, $\pi$ and $10$.
-Before we give details on our   method for solving SR, we will explain two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least squares (OLS).
+Beside these, the following set of constants enters the search space explicitly: $-1$, $0$, $1$, $2$, $\pi$, and $10$.
+Before we provide details of our method for solving SR, we will explain the two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least squares (OLS).
 
 \subsection{Iterated local search}
-ILS~\cite{lourencco2003iterated} is an efficient meta-heuristics that iteratively generates a sequence of solutions produced by the (embedded) heuristic, such as local search (LS) or randomized greedy heuristics.
-When the search gets \emph{stuck} in local optimum, a \emph{perturbation} is performed -- this step is usually non-deterministic.
-This simple idea was proposed by Baxter~\cite{baxter1981local} in early 1980s, and, since then, has been  re-invented by many researches under different names.
-Some of the following names were used: iterated descent search~\cite{baum1998iterated}, large-step
-Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or, in some cases, combinations of previous~\cite{applegate2003chained}.
+ILS~\cite{lourencco2003iterated} is an efficient meta-heuristic that iteratively generates a sequence of solutions produced by the (embedded) heuristic, such as local search (LS) or randomized greedy heuristics.
+When the search gets \emph{stuck} in the local optimum, \emph{perturbation} is performed, which is usually a non-deterministic step.
+This simple idea was proposed by Baxter~\cite{baxter1981local} in the early 1980s, and has since then been re-invented by many researchers under different names.
+These are some of the names that were used: iterated descent search~\cite{baum1998iterated}, large-step
+Markov chains~\cite{martin1991large}, chained local optimization~\cite{martin1996combining}, or in some cases, combinations of those~\cite{applegate2003chained}.
 The most popular version of ILS is shown in Algorithm~\ref{alg:ils}.
@@
 
-An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by local search.
+An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards improved by local search.
 At each iteration, ILS applies three steps.
-First, the current incumbent solution $s$ is perturbed -- it is partially randomized, yielding new solution $s'$.
-Next, the solution $s'$ is potentially improved by a LS procedure.
-Thirdly, the newly obtained solution $s'$  possibly becomes new incumbent -- this is decided upon the acceptance criterion.
-Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back into already visited solutions.
+First, the current incumbent solution $s$ is perturbed, i.e., partially randomized, yielding a new solution $s'$.
+Next, the solution $s'$ is potentially improved by an LS procedure.
+Thirdly, the newly obtained solution $s'$  possibly becomes a new incumbent -- this is decided upon the acceptance criterion.
+Sometimes, ILS incorporates the mechanism of a tabu list, which prevents the search from getting back into already visited solutions.
 
 \subsection{Ordinary least square method}\label{sec:ols}
-Ordinary least square method (OLS) is a linear regression technique.
+The ordinary least square method (OLS) is a linear regression technique.
 It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model).
-More precisely, given   dataset $D$ of $n$ points $(\mathbf{x_i}, y_i)$ where each $\mathbf{x_i}$ is $d$-dimensional, the task is to determine linear mapping $\tilde{y} = \mathbf{k} \mathbf{x} + b$, that is coefficients (line slope) $\mathbf{k} = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i}^{n} (\tilde{y}_i - y_i)^2 $ is minimized.
-This sum is also know as the sum of squared errors (SSE).
+More precisely, given the   dataset $D$ of $n$ points $(\mathbf{x_i}, y_i)$ where each $\mathbf{x_i}$ is $d$-dimensional, the task is to determine linear mapping $\tilde{y} = \mathbf{k} \mathbf{x} + b$, that is coefficients (line slope) $\mathbf{k} = (k_1, \ldots, k_d)$ and $b$ (intercept), so that $ \sum_{i}^{n} (\tilde{y}_i - y_i)^2 $ is minimized.
+This sum is also known as the sum of squared errors (SSE).
 There are many methods to minimize SSE.
-One of the analytical approaches is the calculus-oriented -- it takes into account partial derivatives of SSE w.r.t.
+One of the analytical approaches is calculus-oriented so it takes into account the partial derivatives of SSE w.r.t.
 $k_j,\; j \in \{1, ..., d\}$:
@@
 %https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
-To solve this system one can use Cholesky  factorization or LU decomposition for matrix inversion, and Winograd or Strassen algorithm for matrix multiplication, depending on a solver of linear equations chosen as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}.
-For example, by using Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications.
+To solve this system, one can use Cholesky  factorization or LU decomposition for matrix inversion, and Winograd or Strassen algorithm for matrix multiplication, depending on a solver of linear equations chosen as well as the sparsity of the matrix associated with the linear system~\cite{krishnamoorthy2013matrix}.
+For example, by using Cholesky decomposition, solving the system requires matrix inversions and matrix multiplications.
 In that case the computation cost of $O(d^3)$ is required to find an inverse of the matrix associated to the linear system, which is the most consuming part of the algorithm.
-Thus, OLS using close-form matrix techniques performs in $O(d^3)$ time complexity.
+Thus, the OLS that use close-form matrix techniques perform in $O(d^3)$ time complexity.
 %, where $d$ stands for the number of input features.
@@
 \subsection{\textsc{RILS}-\textsc{ROLS}  method}
-Now we will explain the proposed \textsc{RILS}-\textsc{ROLS} method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
+We will now explain the proposed \textsc{RILS}-\textsc{ROLS} method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.
 
@@
 
-\textsc{RILS}-\textsc{ROLS}  algorithms receives training dataset $D_{tr}$ as input.
+The \textsc{RILS}-\textsc{ROLS} algorithm receives the training dataset $D_{tr}$ as input.
 In addition, it has two control parameters: $penalty_{size}$ and $tolerance_{error}$.
 The first one quantifies the importance of solution expression complexity in the overall solution quality measure (more on this in Section~\ref{sec:fitness}).
-The second parameter is related to the expected noise level in data -- higher noise means that tolerance to errors should be higher.
-$D_{tr}$ can have very large number of records, so the first step of \textsc{RILS}-\textsc{ROLS}  is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
-Initial the sample size is chosen as $\max(0.01 \cdot n_{tr}, 100)$.
-The size of sample is later dynamically adjusted through the algorithm's iterations -- when there are no solution improvements for some number of iterations, the sample size is doubled (lines~\ref{line:sampleAdj1}-\ref{line:sampleAdj2} of Algorithm~\ref{alg:rilsrols}).
+The second parameter is related to the expected noise level in data whereby higher noise means that tolerance to errors should be higher.
+$D_{tr}$ can have a very large number of records, so the first step of \textsc{RILS}-\textsc{ROLS}  is to choose a random sample $D_{tr}' \subseteq D_{tr}$ of size $sample_{size}$.
+Initially, sample size is chosen as $\max(0.01 \cdot n_{tr}, 100)$.
+The size of the sample is later dynamically adjusted through the algorithm's iterations -- when there are no solution improvements for a number of iterations, sample size is doubled (lines~\ref{line:sampleAdj1}-\ref{line:sampleAdj2} of Algorithm~\ref{alg:rilsrols}).
 
 As previously stated, solution is usually represented by means of a tree.
-We use a simple solution initialization -- tree root node is set to zero constant.
-We interchangeably use two solution variables: ($i$) $s$ denotes starting (or working) solution and ($ii$) $bs$ stands for the best solution so far, also known as the incumbent solution.
+We use a simple solution initialization where the tree root node is set to zero constant.
+We interchangeably use two solution variables: ($i$) $s$ denotes the starting (or working) solution and ($ii$) $bs$ stands for the best solution so far, also known as the incumbent solution.
 Solution quality is measured by evaluating the fitness function (more about it in the subsequent Section~\ref{sec:fitness}).
@@
 
-Main loop iterates as long as none of termination criteria is met: ($i$) maximal running time has been reached; ($ii$) maximal number of fitness calculations has been made; ($iii$) best solution is sufficiently good,
+The main loop iterates as long as none of the termination criteria are met: ($i$) the maximal running time has been reached; ($ii$) the maximal number of fitness calculations has been made; ($iii$) the best solution is sufficiently good
 w.r.t.
 its $R^2$ and $RMSE$ scores.
-More precisely, if $R^2$ is sufficiently close to 1 and, at the same time, $RMSE$ is sufficiently close to 0, the algorithm stops prematurely -- this significantly reduces the running times for the majority of tested instances.
-The sufficiency is controlled with parameter $tolerance_{error}$ --  smaller value means that $R^2$ and $RMSE$ should be closer to 1 and 0, respectively.
+More precisely, if $R^2$ is sufficiently close to 1 and, at the same time $RMSE$ is sufficiently close to 0, the algorithm stops prematurely, which significantly reduces the running times for the majority of tested instances.
+The sufficiency is controlled with parameter $tolerance_{error}$, whereby a smaller value means that $R^2$ and $RMSE$ should be closer to 1 and 0, respectively.
 
 One of the first steps in the main loop is to generate perturbations near the starting solution $s$ (line~\ref{line:sPert}). 
-As the name of this procedure (\texttt{All1Perturbations}) suggests, perturbation step is local -- meaning the closeness of starting solution $s$ and any of perturbations is 1 (we call it 1-perturbation sometimes).
-The precise way of generating perturbation is described separately, in Section~\ref{sec:pertGen}.
-
-Candidate perturbations are being improved by performing OLS coefficient fitting (procedure \texttt{FitOLS}).
-This means that coefficients in any of linear combinations of current solution are being set by applying  ordinary least square method, already described in Section~\ref{sec:ols}.
-After this step, perturbations are usually better suited to given sample data $D_{tr}'$. 
+As the name of this procedure (\texttt{All1Perturbations}) suggests, the perturbation step is local, meaning that the closeness of the starting solution $s$ and any of perturbations is 1 (we sometimes call it 1-perturbation).
+The precise way of generating perturbation is described separately in Section~\ref{sec:pertGen}.
+
+Candidate perturbations are improved by performing OLS coefficient fitting (procedure \texttt{FitOLS}).
+This means that the coefficients in any of the linear combinations of the current solution are being set by applying the ordinary least square method already described in Section~\ref{sec:ols}.
+After this step, perturbations are usually better suited to the given sample data $D_{tr}'$. 
 Further, these perturbations are sorted w.r.t. $R^2$ metric in the descending order (line~\ref{line:orderR2}).
 
-Now, the algorithm enters the internal loop -- it iterates over the ordered perturbations and aims to find the one which improves the best solution $bs$.
-But, before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}), after which the local search is performed (line~\ref{line:ls}).
-Solution simplification is done in a symbolical fashion by popular  Python package \texttt{SymPy}~\cite{sympy}.
-Local search tries to find local optima expressions close to the given $p$ -- explained in detail in Section~\ref{sec:ls}.  
+Now the algorithm enters the internal loop -- it iterates over the ordered perturbations and aims to find the one which improves the best solution $bs$.
+But before comparing candidate perturbation solution $p$ with $bs$, $p$ is first simplified (line~\ref{line:simp}), after which local search is performed (line~\ref{line:ls}).
+Solution simplification is done in a symbolic fashion by popular  Python package \texttt{SymPy}~\cite{sympy}.
+The local search tries to find local optima expressions close to the given $p$, explained in detail in Section~\ref{sec:ls}.  
 Finally, the fitness function value of $p$ is compared to the fitness function value of $bs$.
-If fitness of $p$ is better, $bs$ is updated correspondingly and the internal loop, that goes across ordered perturbations, is immediately terminated (it works in a  \emph{first-improvement} strategy).
+If fitness of $p$ is better, $bs$ is updated correspondingly and the internal loop, which goes across ordered perturbations, is immediately terminated (it works in a  \emph{first-improvement} strategy).
 Otherwise, the next perturbation is probed.
 Note that the probed perturbations are stored in a set denoted by $perturbations_{tried}$.
-The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}), i.e.
-$perturbations_{tried}$ serves as a kind of tabu list, which is known from the Tablu search meta-heuristic, see~\cite{glover1998tabu}.
-
-If some of $s_{perturbations}$ around starting solution $s$ yielded an improvement, $bs$ becomes the starting solution $s$ in the next iteration of the main loop (line~\ref{line:improved}). 
-Otherwise, it makes no sense to set starting solution to $bs$ -- the search is being  \emph{trapped} in a local optimum.
-Randomness is introduced in order to avoid this undesired situation.
+The goal is to avoid checking the same perturbation multiple times (lines \ref{line:avoid1}-\ref{line:avoid2}), i.e., $perturbations_{tried}$ serves as a kind of tabu list, which is known from the Tablu search meta-heuristic (see~\cite{glover1998tabu}).
+
+If some of $s_{perturbations}$ around the starting solution $s$ yielded an improvement, $bs$ becomes the starting solution $s$ in the next iteration of the main loop (line~\ref{line:improved}). 
+Otherwise, it makes no sense to set the starting solution to $bs$ as the search becomes  \emph{trapped} in a local optimum.
+Randomness is introduced in order to avoid this undesirable situation.
 First, a set of local perturbations around $bs$ is generated ($start_{candidates}$) in the same manner as before (procedure \texttt{All1Perturbations}).
@@
 
-Before returning the final symbolical model, \textsc{RILS}-\textsc{ROLS}  performs the final symbolical simplification and rounding of model coefficients.
-The latter is sensitive to control parameter $tolerance_{error}$ -- a smaller value means the information loss during rounding is smaller, i.e.
-a higher number of significant digits is preserved.
-Note that confidence in the symbolical model is reduced when expected noise in data is higher -- the rule of thumb is: for higher expected noise, $tolerance_{error}$ should be higher.
+Before returning the symbolic model, \textsc{RILS}-\textsc{ROLS}  performs the final symbolic simplification and rounding of model coefficients.
+The latter is sensitive to control parameter $tolerance_{error}$ -- a smaller value means that information loss during rounding is smaller, i.e., a higher number of significant digits is preserved.
+Note that confidence in the symbolic model is reduced when expected noise in data is higher; the rule of thumb is: for higher expected noise, $tolerance_{error}$ should be higher.
 
@@
 
-Symbolic regression objective is to determine the expression fitting available data.
-It is also allowed to obtain some equivalent expression, since there are multiple ways to express some symbolical equation.
-Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, because the goal expression is not known at that point -- only target values for some of the input data are known.
-Thus, various numerical metrics are being used in literature to guide the symbolic regression search process.
-The most popular are the coefficient of determination, also known as $R^2$, and the mean squared error (MSE) or root mean squared error (RMSE).
-Also, the important aspect of the solution quality is the solution expression complexity, which may correspond to the model size of its tree representation.
-This follows the Occam's razor principle~\cite{costa2020fast}~ that simpler solution  is more likely to be a correct one.
-The search process of \textsc{RILS}-\textsc{ROLS}  is guided by the non-linear combination of $R^2$, RMSE and solution expression size (complexity) presented in Equation~(\ref{eq:fitness}).
+The objective of symbolic regression is to determine the expression that fits available data.
+It is also allowed to obtain an equivalent expression, since there are multiple ways to express a symbolic equation.
+Although logically sound and intuitive, this objective is not quantifiable during the solution search/training phase, because the goal expression is not known at that point but only target values for some of the input data.
+Therefore there are various numerical metrics in the literature that guide the symbolic regression search process.
+The most popular ones are the coefficient of determination, also known as $R^2$, and the mean squared error (MSE) or root mean squared error (RMSE).
+The important aspect of solution quality is solution expression complexity, which may correspond to the model size of its tree representation.
+This follows the Occam's razor principle~\cite{costa2020fast} that a simpler solution  is more likely to be the correct one.
+The search process of \textsc{RILS}-\textsc{ROLS}  is guided by the non-linear combination of $R^2$, RMSE, and solution expression size (complexity) presented in Equation~(\ref{eq:fitness}).
 
@@
 \begin{itemize}
-	\item higher $R^2$ is preferred -- ideally, when $R^2(s)=1$, the effect of term $2-R^2(s)$ is neutralized; %since 1 is neutral for multiplication;
-	\item lower RMSE is preferred -- ideally, when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
+	\item higher $R^2$ is preferred, ideally when $R^2(s)=1$, the effect of term $2-R^2(s)$ is neutralized; %since 1 is neutral for multiplication;
+	\item lower RMSE is preferred, ideally when $RMSE(s)=0$, the whole term $(1+RMSE(s))$ becomes 1;
 	\item since $penalty_{size} > 0$, larger expressions tend to have higher fitness (which follows the Occam's razor principle); therefore, simpler solutions are favorable. 
@@
 
-In order to speed-up the fitness evaluation, we employ \emph{expression caching}.
-This means that values attached to expression trees or subtrees are persisted in key-value structure, such that the key is tree (subtree) textual representation, while the value is the $|D_{tr}'|$-size  vector of corresponding expression values on the sample training dataset $D_{tr}'$.
-(Of course, once the $D_{tr}'$ changes, which happens not that frequently, the whole cache is cleared.)
+In order to speed up fitness evaluation, we employ \emph{expression caching}.
+This means that values attached to expression trees or subtrees are stored in key-value structure, such that the key is tree (subtree) textual representation, while the value is the $|D_{tr}'|$-size  vector of corresponding expression values on the sample training dataset $D_{tr}'$.
+Of course, once the $D_{tr}'$ changes, which does not happen very frequently, the whole cache is cleared.
 Caching is performed in a partial way -- when determining the value of a given expression $T$, it is not required to find the exact \emph{hit} inside the cache.
-So, if some subexpression (subtree) of $T$ is present in the cache, its value will be reused and further combined to calculate the whole fitness function value.
-
-For example, let  $T = y^2 \cdot (x+y)/z - \sin(x+y)$ be an expression, and $D_{tr}'=\{([1, 2, 5], 7), ([3, 4, 3], 5), ([4, 5, 3], 6), ([6, 7, 4], 3), ([3, 3, 6], 2)\}$ be a sample training dataset (here, input feature vector is labeled by $[x, y, z]$); let expression cache consisting of the following key-value entries $cache=\{(x+y, [3, 7, 9, 13, 6]), (y^2, [4, 16, 25, 49, 9])\}$.
+So, if a subexpression (subtree) of $T$ is present in the cache, its value will be reused and further combined to calculate the whole fitness function value.
+
+For example, let  $T = y^2 \cdot (x+y)/z - \sin(x+y)$ be an expression, and $D_{tr}'=\{([1, 2, 5], 7), ([3, 4, 3], 5), ([4, 5, 3], 6), ([6, 7, 4], 3), ([3, 3, 6], 2)\}$ be a sample training dataset (here, input feature vector is labeled by $[x, y, z]$); let expression cache consist of the following key-value entries $cache=\{(x+y, [3, 7, 9, 13, 6]), (y^2, [4, 16, 25, 49, 9])\}$.
 Expression $T$ does not need to be fully evaluated since some of its parts are inside the cache: $y^2$ and $x+y$.
-(Note that single variables do not need to enter the cache, since they are already available as columns of  $D_{tr}'$.)
-Each newly evaluated (sub)expression (except constant or variable alone) enters the cache.
+Note that single variables do not need to enter the cache, since they are already available as columns of  $D_{tr}'$.
+Each newly evaluated (sub)expression (except for the constant or variable alone) enters the cache.
 In this example, the new entries will correspond to keys $(x+y)/z$, $y^2 \cdot (x+y)/z$, $\sin(x+y)$ and $y^2 \cdot (x+y)/z - \sin(x+y)$.
@@
 Perturbations allow the algorithm to escape from local optima.
-As previously described, perturbations are performed in two occasions: ($i$) during the exhaustive examination of neighboring solutions around the starting solution, ($ii$) during selection of the next starting solution, a non-exhaustive case.
+As previously described, perturbations are performed on two occasions: ($i$) during the exhaustive examination of neighboring solutions around the starting solution, ($ii$) during selection of the next starting solution, a non-exhaustive case.
 In both cases, the same Algorithm~\ref{alg:pert} is used.
@@
 
-This is followed by constant normalization during which coefficients that enter multiplication, division, addition or subtraction are set to 1, while those entering the power function are rounded to integer, with exception of square root, which is kept intact.
+This is followed by constant normalization during which coefficients that enter multiplication, division, addition or subtraction are set to 1, while those entering the power function are rounded to integer, with the exception of square root, which is kept intact.
 For example, for expression $3.3\cdot(x+45.1\cdot y^{3.2})\cdot 81\cdot x/\sqrt{y}$ the normalized version is $1\cdot (x+1\cdot y^3)\cdot 1\cdot x/\sqrt{y}$.
@@
 This reduction is reasonable, since normalization preserves the essential functional form.
-(Note that coefficients get tuned later: the linear coefficient during the OLS phase, and the remaining during local search.)
-
-After performing the normalization process, the expression is simplified -- getting compact expression is more likely after normalization than before.
-The previous expression will take form $(x+y^3)\cdot x/\sqrt{y}$.
+Note that coefficients get tuned later: the linear coefficient during the OLS phase, and the remaining ones during local search.
+
+After performing the normalization process, the expression is simplified -- getting the compact expression is more likely after normalization than before it.
+The previous expression will take the form $(x+y^3)\cdot x/\sqrt{y}$.
 In this particular case, the simplification will usually only remove unnecessary coefficients, but in general it can also perform some non-trivial symbolic simplification.
@@
 Perturbations are generated by making simple changes on the per-node level of $s$ expression tree.
-Depending on the structure of the expression tree (note that expression does not have to have unique tree representation), the set of subtrees of the previous expression $(x+y^3)\cdot x/\sqrt{y}$ might be $\{(x+y^3)\cdot x/\sqrt{y}, (x+y^3), x/\sqrt{y}, x, y^3, \sqrt{y}, y\}$.
+Depending on the structure of the expression tree (note that the expression does not need to have unique tree representation), the set of subtrees of the previous expression $(x+y^3)\cdot x/\sqrt{y}$ might be $\{(x+y^3)\cdot x/\sqrt{y}, (x+y^3), x/\sqrt{y}, x, y^3, \sqrt{y}, y\}$.
 %This set of subtrees is obtained if left subtree of the whole expression is $(x+y^3)$ while the right one is $x/\sqrt{y}$.
-Further, the set of perturbations around each subtree $n$ is generated (lines \ref{line:forSSStart}-\ref{line:forSSEnd} in Algorithm~\ref{alg:pert}).
-
-Algorithm~\ref{alg:pertNode} shows how perturbations around given subtree are generated.
+Further, the set of perturbations is generated around each subtree $n$ (lines \ref{line:forSSStart}-\ref{line:forSSEnd} in Algorithm~\ref{alg:pert}).
+
+Algorithm~\ref{alg:pertNode} shows how perturbations are generated around the given subtree.
 
@@
 \emph{Case 1}. 
-Observed node $n$ is the whole tree $s$ (see line ~\ref{alg:alg4-case-1} in Algorithm~\ref{alg:pertNode}).
-Following on  the previous exemplary expression tree, this means that multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
+The observed node $n$ is the whole tree $s$ (see line ~\ref{alg:alg4-case-1} in Algorithm~\ref{alg:pertNode}).
+Based on  the previous exemplary expression tree, this means that the multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
 For example, multiplication can be replaced by addition, which forms a 1-perturbation expression (tree) $(x+y^3)+ x/\sqrt{y}$.
@@
 \emph{Case 2}. 
-Node $n$ has arity of at least 1 (see line ~\ref{alg:alg4-case-2} in Algorithm~\ref{alg:pertNode}). This means that the left subtree exists, so the left subtree node is to be changed. 
+Node $n$ has the arity of at least 1 (see line ~\ref{alg:alg4-case-2} in Algorithm~\ref{alg:pertNode}). This means that the left subtree exists, so the left subtree node is to be changed. 
 For example, if $n=x+y^3$, the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
 Another example would be the case of unary operation, e.g., when $n=\sqrt{y}$.
-In that case, some of possible perturbations could be $(x+y^3)\cdot x/\sqrt{\ln{y}}$ (application of logarithm to left subtree $y$) or $(x+y^3)\cdot x/\sqrt{x}$ (changing variable $y$ to $x$), etc.
+In that case, some possible perturbations could be $(x+y^3)\cdot x/\sqrt{\ln{y}}$ (application of logarithm to the left subtree $y$) or $(x+y^3)\cdot x/\sqrt{x}$ (changing variable $y$ to $x$), etc.
 
 \emph{Case 3}. 
-Node $n$ is binary operation, meaning the right subtree must exist (Line ~\ref{alg:alg4-case-3} in Algorithm~\ref{alg:pertNode}). 
+Node $n$ is a binary operation, meaning that the right subtree must exist (Line ~\ref{alg:alg4-case-3} in Algorithm~\ref{alg:pertNode}). 
 The analogous idea is applied as in \emph{Case 2}.
 
-The algorithm allows the following set of carefully chosen per-node changes (method named \texttt{NodeChanges} in Algorithm~\ref{alg:pertNode}):
+The algorithm allows for the following set of carefully chosen per-node changes (method named \texttt{NodeChanges} in Algorithm~\ref{alg:pertNode}):
 
@@
 	\item Constant to variable. For example,  $(1+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sqrt{y}$.
-	\item Variable to unary operation applied to that variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot \ln{x}/\sqrt{y}$.
+	\item Variable to the unary operation applied to that variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot \ln{x}/\sqrt{y}$.
 	\item Unary operation to another unary operation. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sin{y}$.
 	\item Binary operation to another binary operation. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot (x + \sqrt{y})$. 
-	\item Variable or constant enter the binary operation with arbitrary variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+x/y^3)\cdot x/\sqrt{y}$. 
+	\item Variable or constant enter the binary operation with an arbitrary variable. For example,  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+x/y^3)\cdot x/\sqrt{y}$. 
 \end{enumerate}
 
-Method named \texttt{Replace}$(s, n, nc)$ inside Algorithm~\ref{alg:pertNode} is simply used to replace the node $n$ with node $nc$ inside the given expression tree $s$.
+The method named \texttt{Replace}$(s, n, nc)$ inside Algorithm~\ref{alg:pertNode} is simply used to replace the node $n$ with node $nc$ inside the given expression tree $s$.
 
@@
 
-Perturbations are further improved by means of local search procedure (Algorithm~\ref{alg:ls}).
+Perturbations are further improved by means of the local search procedure (Algorithm~\ref{alg:ls}).
 
@@
 
-For a given perturbation $p$, local search systematically explores extended set of 1-perturbations around $p$.
+For a given perturbation $p$, local search systematically explores the extended set of 1-perturbations around $p$.
 It relies on the \emph{best-improvement} strategy, meaning that all 1-perturbations (for all subtrees) are considered.
@@
 	\item Any node to any constant or variable. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow y \cdot x / \sqrt{y}$ or  $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+\pi) \cdot x / \sqrt{y}$.
-	\item Any node to unary operation applied to it. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\ln{\sqrt{y}}$.
-	\item Any node to binary operation applied to that node and some variable or constant. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sqrt{y} - x$.
-	\item Constant to its multiple, where possible multipliers are $\{$0.01, 0.1, 0.2, 0.5, 0.8, 0.9, 1.1, 1.2, 2, 5, 10, 20, 50, 100$\}$.
+	\item Any node to the unary operation applied to it. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\ln{\sqrt{y}}$.
+	\item Any node to the binary operation applied to that node and a variable or constant. For example, $(x+y^3)\cdot x/\sqrt{y} \rightarrow (x+y^3)\cdot x/\sqrt{y} - x$.
+	\item Constant to its multiple, whereby possible multipliers are $\{$0.01, 0.1, 0.2, 0.5, 0.8, 0.9, 1.1, 1.2, 2, 5, 10, 20, 50, 100$\}$.
 For example, $(1+y^3)\cdot x/\sqrt{y} \rightarrow (1.2+y^3)\cdot x/\sqrt{y}$.
@@
 
-Change under point 10 is very important -- it performs the general coefficient tuning, unlike OLS that considers only coefficients in linear combinations.
+Change under point 10 is very important as it performs general coefficient tuning, unlike OLS, which considers only coefficients in linear combinations.
 
@@
 All experiments concerning our method are conducted in the single-core mode, on a PC with Intel i9-9900KF CPU @3.6GHz, 64GB RAM, under Windows 10 Pro OS.
-The RAM consumption was very small (up to few hundred megabytes) -- beside memory space needed to load input dataset, the only considerable amount is reserved for expression cache.
+The RAM consumption was very small (up to a few hundred megabytes).
+Beside the memory space needed to load the input dataset, the only considerable amount is reserved for expression cache.
 
@@
 
-For the (14) competitors, the results are exported from \texttt{SRBench} \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
+For the 14 competitors, the results are exported from \texttt{SRBench} \url{https://cavalab.org/srbench/results/}, reported in~\cite{la2021contemporary}. 
 The maximum computation time allowed for each run of \textsc{RILS}-\textsc{ROLS} is set to 1 hour, while the maximal number of fitness function evaluations is set to 1 million.
-All other algorithms from \texttt{SRBench} used the time limit that was equal or bellow 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
+All other algorithms from \texttt{SRBench} used the time limit that was equal to or below 8 hours runtime and the same fitness evaluation limit of 1 million (see~\cite{la2021contemporary}).
 We did not use the full time limit of 8 hours because we empirically concluded that there were almost no improvements after 1 hour \textsc{RILS}-\textsc{ROLS} runtime.
 
-All non-deterministic algorithms (including \textsc{RILS}-\textsc{ROLS}) were run ten times per each problem instance, where each run used different setting of random number generator seed.
-
-Training/test data splits were randomly performed in ratio 75\%:25\%, same as in \texttt{SRBench}.
-Moreover, the splits are structurally the same as in \texttt{SRBench}, because we used the same set of random generator seeds and the same Python splitting method (\texttt{train\_test\_split} from Scikit-Learn library~\cite{scikit-learn}).
+All non-deterministic algorithms (including \textsc{RILS}-\textsc{ROLS}) were run ten times per each problem instance, where each run used a different setting of a random number generator seed.
+
+The training/test data splits were randomly performed in ratio 75\%:25\%, the same as in \texttt{SRBench}.
+Moreover, the splits are structurally the same as in \texttt{SRBench}, because we used the same set of random number generator seeds and the same Python splitting method (\texttt{train\_test\_split} from Scikit-Learn library~\cite{scikit-learn}).
 
@@
 
-\texttt{SRBench} (\url{https://cavalab.org/srbench/}) is an open-source benchmarking project which merges a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}.
-\texttt{SRBench} considers two types of symbolic regression problems: 1) \emph{ground-truth} problems, for which the exact model is known, and 2) \emph{black-box} problems, for which the exact model is not known.
-In our work, we consider only the former one, since \textsc{RILS-ROLS} was not designed to solve \emph{black-box} problems.
-There are two groups of instances in \texttt{SRBench} \emph{ground-truth} problem set:
+\texttt{SRBench} (\url{https://cavalab.org/srbench/}) is an open-source benchmarking project which merges a large set of diverse benchmark datasets, contemporary SR methods, as well as ML methods around shared model evaluation and an environment for analysis (see~\cite{la2021contemporary}).
+\texttt{SRBench} considers two types of symbolic regression problems: 1) ground-truth problems, for which the exact model is known, and 2) black-box problems, for which the exact model is not known.
+In our work, we consider only the former one, since \textsc{RILS-ROLS} was not designed to solve black-box problems.
+There are two groups of instances in the \texttt{SRBench} ground-truth problem set:
 \begin{itemize}
-	\item \textsc{Feynman} instances are inspired by physics and formulas/models that describes various natural laws.  
+	\item \textsc{Feynman} instances are inspired by physics and formulas/models that describe various natural laws.  
 	There are 116 instances, where each one consists of $10^5$  samples (see \cite{udrescu2020ai} for more details).
@@
 	\begin{table}[!ht]
+		\caption{Some \textsc{Feynman} instances.}
+		\label{tab:Feynamn-Eq}
 		\centering
@@
 		\end{tabular}
-		\caption{Some \textsc{Feynman} instances.}
-		\label{tab:Feynamn-Eq}
 	\end{table}
@@
 	The aim of each problem is to predict the rate of change of the subsequent state.
-These equations describe natural processes modeled by non-linear dynamics exhibiting chaos.
+These equations describe the natural processes modeled by non-linear dynamics exhibiting chaos.
 The equations for some of the datasets that belong \textsc{Strogatz} are shown in Table~\ref{table:strogatz-ODEs}.
-In overall, there are 14 \textsc{Strogatz} instances.
+There are 14 \textsc{Strogatz} instances in total.
 
@@
 	\begin{table}
+		\caption{Some \textsc{Strogatz} ODE instances.}
+		\label{table:strogatz-ODEs}
 		\centering
@@
 		\end{tabular}
-		\caption{Some \textsc{Strogatz} ODE instances.}
-		\label{table:strogatz-ODEs}
 	\end{table}
@@
 
-The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose   various symmetries, periodicity w.r.t.
-some variables, internal separability on some variables, etc.
+The above-mentioned benchmark sets may be biased since the models which describe physical laws usually impose various symmetries, periodicity, or internal separability on some variables, etc.
 In order to test \textsc{RILS-ROLS} robustness and scalability in unbiased setting, we generated a set of random SR problem instances called \textsc{Random}.
-These instances have a varying size (total number of expression nodes) and number of variables.
+These instances vary in size (total number of expression nodes) and number of variables.
 In total, there are 235 random instances, or 5 randomly generated instances for each of the following 47 (size, number of variables) combinations $\{(3, 1), \{4, 5\} \times \{1, 2\}, \{6\} \times \{1, 2, 3\}, \{7, 8, 9, 10, 11, 12\} \times \{1, 2, 3, 4\}, \{13, 14, 15\} \times \{1, 2, 3, 4, 5\}\}$.
-Each of \textsc{Random} instances has 10 thousands randomly generated samples.
-
-Some random instances are shown in Table~\ref{table:random}, while all instances can be found at %\textsc{RILS-ROLS} GitHub 
+Each of the \textsc{Random} instances has 10,000 randomly generated samples.
+
+Some random instances are shown in Table~\ref{table:random}, while all instances can be found in %\textsc{RILS-ROLS} GitHub 
  the following repository: \url{https://github.com/kartelj/rils-rols}.
@@
 \begin{table}
+	\caption{Some \textsc{Random} instances.}
+	\label{table:random}
 	\centering
@@
 	\end{tabular}
-	\caption{Some \textsc{Random} instances.}
-	\label{table:random}
 \end{table}
@@
 
-The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters, $penalty_{size}$ and $tolerance_{error}$.
-The first parameter is empirically tuned for considered benchmarks to 0.001 -- this is also used as a default value in the corresponding Python package (package is described in the Appendix).
-The second parameter is positively correlated with the expected level of noise in input data, i.e., for higher noise the $tolerance_{error}$ should take higher values and vice-versa.
+The \textsc{RILS}-\textsc{ROLS} algorithm employs two control parameters: $penalty_{size}$ and $tolerance_{error}$.
+The first parameter is empirically tuned to 0.001 for considered benchmarks -- this is also used as a default value in the corresponding Python package (package is described in the Appendix).
+The second parameter is positively correlated with the expected level of noise in input data, i.e., for higher noise $tolerance_{error}$ should take higher values and vice-versa.
 More precisely, in case there is no noise, we used the default setting $tolerance_{error}=10^{-16}$, while in noisy scenarios we set $tolerance_{error}$ to the corresponding noise level (0.001 or 0.01).
-For setting $penalty_{size}$ and $tolerance_{error}$ on new datasets one can either keep the default settings or use some wrapper tuning algorithm around \textsc{RILS-ROLS} regressor, e.g., grid-search w.r.t.
+For setting $penalty_{size}$ and $tolerance_{error}$ on new datasets, one can either keep the default settings or use a wrapper tuning algorithm around the \textsc{RILS-ROLS} regressor, e.g., grid-search w.r.t.
 training or validation accuracy.
@@
 % ACA: ima 14 uporednih algoritama, ne 13
-In this section, we evaluate our \textsc{RILS-ROLS} algorithm and compare it to 14 other competitors from the literature.
+In this section we evaluate our \textsc{RILS-ROLS} algorithm and compare it to 14 other competitors from the literature.
 The numerical results are reported in Tables~\ref{tab:comp_noise0}-\ref{tab:comp_noise001}.
@@
 $$ y_{noise} = y + \epsilon, \epsilon \sim \mathcal{N}\left(0, \alpha \sqrt{\frac{1}{n} \sum _{i=1}^n{y_i^2}}\right),$$
-where $n$ relates to the number of items in the input data.
-
-Each table consists of two blocks, where the first one gives the exact model accuracy, while the second is related to the less relevant statistical accuracy based on the $R^2$ metric.
-The exact model accuracy shows how often the method reaches true formula (ground-truth).
+where $n$ relates to the number of items in input data.
+
+Each table consists of two blocks, where the first one provides the exact model accuracy, while the second one is related to the less relevant statistical accuracy based on the $R^2$ metric.
+The exact model accuracy shows how often the method reaches the true formula (ground-truth).
 Regarding statistical accuracy, the solution is considered accurate if it produced an $R^2$ score larger than 0.999.
@@
 
-The following conclusions may be drawn from the numerical results:
+The following conclusions may also be drawn from the numerical results:
 
 \begin{itemize}
-	\item Concerning the exact percentages in case when no noise is utilized in the input data, the best performing algorithm is our \textsc{RILS-ROLS}.
+	\item Concerning the exact percentages in case when no noise is utilized in input data, the best performing algorithm is our \textsc{RILS-ROLS}.
 It found the exact solution in 57.84\% of runs for \textsc{Feynman} instances.
-It is even more impressive in solving \textsc{Strogatz} instances, being successful in 83.57\% runs.
-The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\% runs for \textsc{Feynman} set, and 27.14\% runs for the problem instances from benchmark set \textsc{Strogatz}.
-All other approaches perform significantly worse, and none of them is able to deliver the exact solution for more than 30\% runs over the instances of any of the two considered ground-truth benchmark sets.
+It is even more impressive in solving \textsc{Strogatz} instances, when it was successful in 83.57\% runs.
+The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\% runs for the \textsc{Feynman} set, and 27.14\% runs for the problem instances from the benchmark set \textsc{Strogatz}.
+All other approaches perform significantly worse, and none of them are able to deliver the exact solution in more than 30\% runs over the instances of any of the two considered ground-truth benchmark sets.
 The overall results are in favor of \textsc{RILS-ROLS} with 60.62\%, while the second best is \textsc{AI-Feynman} with 52.65\%.
-	\item  Concerning the exact results in presence of the small noise (0.001), our \textsc{RILS-ROLS} is still performing   well, finding an exact model in 42.08\% of runs considering all problem instances.
-The second best approach is again \textsc{AI-Feynman} being successful in 31.89\% runs.
-As in no-noise scenario, there is a significant difference in \textsc{AI-Feynman} performances among two sets of instances -- it performs much better on \textsc{Feynman} instances than on \textsc{Strogatz}.
+	\item  Concerning the exact results in the presence of small noise (0.001), our \textsc{RILS-ROLS} still performs well, finding the exact model in 42.08\% of runs considering all problem instances.
+The second best approach is again \textsc{AI-Feynman}, successful in 31.89\% runs.
+As in the no-noise scenario, there is a significant difference in \textsc{AI-Feynman} performances among two sets of instances -- it performs much better on \textsc{Feynman} instances than on \textsc{Strogatz}.
 It is also worth mentioning that \textsc{AFP-FE} shows to be robust w.r.t.
 noise so its performances only slightly deteriorate in comparison to the no-noise scenario.
-This puts it on the third place with overall accuracy of 21.23\%.
-Other approaches reach accuracy bellow 20\%.
-	\item  Concerning the scenario with high noise (level of 0.01), our \textsc{RILS-ROLS} is still performing quite well -- it finds and exact model in 34.77\% runs.
-The second best is \textsc{AFP-FE} reaching 20\% correct solutions.
-\textsc{AI-Feynman} performances degrade significantly under this level of noise, so it is ranked only 6th overall, reaching the accuracy of 12.61\%.
-
-	\item One more interesting method is \textsc{DSR}.
-It shows the perfect robustness to noise and agnosticism to benchmark dataset -- it has near 19\% exact model accuracy in all 6 combinations of benchmark dataset (\textsc{Feynman} or \textsc{Strogatz}) and noise level (0, 0.001 or 0.01).
-
-	\item When comparing performances of the algorithms in terms of $R^2 > 0.999$ accuracy, in no-noise scenario, our \textsc{RILS}-\textsc{ROLS} is successful with the rate of success of 83.38\% (ranked on the third place).
+This puts it on the third place with the overall accuracy of 21.23\%.
+The accuracy of other approaches is below 20\%.
+	\item  Concerning the scenario with high noise (level of 0.01), our \textsc{RILS-ROLS} still performs quite well -- it finds and exact model in 34.77\% runs.
+The second best is \textsc{AFP-FE}, reaching 20\% correct solutions.
+\textsc{AI-Feynman} performances degrade significantly under this level of noise, so it is the 6-th overall ranking, reaching the accuracy of only 12.61\%.
+
+	\item Another interesting method is \textsc{DSR}.
+It shows the perfect robustness to noise and agnosticism to the benchmark dataset -- it has almost 19\% exact model accuracy in all 6 combinations of the benchmark dataset (\textsc{Feynman} or \textsc{Strogatz}) and noise level (0, 0.001 or 0.01).
+
+	\item When comparing the performances of algorithms in terms of $R^2 > 0.999$ accuracy, in a no-noise scenario, our \textsc{RILS}-\textsc{ROLS} is successful with the success rate of 83.38\% (ranked third).
 Better methods in terms of this accuracy are \textsc{MRGP}, and \textsc{Operon}, with 92.69\%, and 86.92\%, respectively.
-On the other hand, the exact model percentages of these two approaches are rather low (0\% and 16\%, respectively).
-These two algorithms are therefore more appropriate in scenarios when the underlying (ground-truth) model is unknown, so-called \emph{black-box} regression.
-
-	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% of a success rate (ranked third, again).  As before, \textsc{MRGP} and \textsc{Operon} are best two here.
-
-	\item   When noise level is 0.01, the situation is almost the same, \textsc{MRGP} and \textsc{Operon} are the best and second best with 88.46\% and 86.54\% accuracy, respectively.
-\textsc{GP-GOMEA} now reaches third place with 73.46\%, while the proposed \textsc{RILS-ROLS} is fifth with 62.92\% $R^2$ accuracy.
+On the other hand, the exact model percentages of these two approaches are rather low: 0\% and 16\%, respectively.
+These two algorithms are therefore more appropriate for the so-called black-box regression, i.e., scenarios when the underlying (ground-truth) model is unknown.
+
+	\item  In the presence of the noise level of 0.001, our \textsc{RILS-ROLS} method has 78.62\% success rate (ranked third, again).  As before, \textsc{MRGP} and \textsc{Operon} are best two here.
+
+	\item   When the noise level is 0.01, the situation is almost the same.
+\textsc{MRGP} and \textsc{Operon} are the best and second best with 88.46\% and 86.54\% accuracy, respectively.
+\textsc{GP-GOMEA} now reaches the third place with 73.46\%, while the proposed \textsc{RILS-ROLS} is 5-th with 62.92\% $R^2$ accuracy.
 
@@
 It also shows high robustness to noise.
-Regarding statistical accuracy, which is not so relevant for the ground-truth problems, \textsc{RILS}-\textsc{ROLS} also performs quite well.
+Regarding statistical accuracy, which is not so relevant for ground-truth problems, \textsc{RILS}-\textsc{ROLS} also performs quite well.
 
@@
 Figure~\ref{fig:time-avg-exact-noise} compares the methods w.r.t.
-average runtimes (in seconds) when exact solution is reached.
-We do not consider methods whose exact percentage is too low, i.e., bellow 5\%.
-Methods are labeled on $x$-axis, while respective average runtimes are shown on $y$-axis.
+average runtimes (in seconds) when the exact solution is reached.
+We do not consider methods whose exact percentage is too low, i.e., below 5\%.
+Methods are labeled on the $x$-axis, while respective average runtimes are shown on the $y$-axis.
 (Note that $y$-axis is logarithmically scaled.) The following conclusions are drawn from these results.
@@
 \begin{itemize}
-	\item When considering the instance problems with no-noise, the lowest average runtime is reported for \textsc{RILS}-\textsc{ROLS} algorithm (228 seconds).
-A slightly worse runtime is obtained by \textsc{DSR} algorithm (232 seconds).
-Note that the relative exact percentage produced by \textsc{RILS}-\textsc{ROLS} is far better from \textsc{DSR} (60.62\% versus 19.71\%).
-All remaining approaches deliver an order of magnitude larger average runtimes than that of \textsc{RILS}-\textsc{ROLS} and \textsc{DSR} methods..
+	\item When considering instance problems without noise, the lowest average runtime is reported for the \textsc{RILS}-\textsc{ROLS} algorithm (228 seconds).
+A slightly worse runtime is obtained by the \textsc{DSR} algorithm (232 seconds).
+Note that the relative exact percentage produced by the \textsc{RILS}-\textsc{ROLS} is far better than \textsc{DSR} (60.62\% versus 19.71\%).
+All the remaining approaches deliver an order of magnitude larger average runtime than that of \textsc{RILS}-\textsc{ROLS} and \textsc{DSR} methods..
 	\item  When considering instances with the noise level of 0.001, the lowest average runtime to obtain the exact model is again delivered by \textsc{RILS}-\textsc{ROLS} algorithm (108 seconds).
-The second best is produced by \textsc{DSR}, but this time significantly larger (622 seconds) compared to \textsc{RILS-ROLS}.
-	\item When considering the instance problems with the noise level of 0.01, the conclusion is similar to previous. 
+The second best runtime is produced by \textsc{DSR}, but this time it is significantly longer (622 seconds) compared to \textsc{RILS-ROLS}.
+	\item When considering instance problems with the noise level of 0.01, the conclusion is similar to the previous one. 
 \end{itemize}
@@
 In order to check the statistical significance of the results w.r.t.\ competitor approaches, we employed the standard statistical methodology.
-To do so, we have compared the results of \textsc{RILS}-\textsc{ROLS} to 14 other approaches over all algorithm runs on the problem instances from the both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
+To do so, we have compared the results of \textsc{RILS}-\textsc{ROLS} to 14 other approaches over all algorithm runs on problem instances from both ground-truth benchmark sets, \textsc{Feynman} and \textsc{Strogatz}.
 The successful run means that the corresponding algorithm found the exact model.
@@
 On the other hand, the exact model accuracy of methods revised in \texttt{SRBench} was calculated in a different way.
-First, the accuracy of each of 130 considered instances was calculated by dividing the number of successful runs with the number of runs that finished its execution.
-This means that, for example, if some instance was run 10 times, giving 4 successful models, but failing to finish 2 runs due to memory exhaustion or some other OS issue, the accuracy would be 50\% (4/8) instead of 40\% (4/10).
+First, the accuracy of each of 130 considered instances was calculated by dividing the number of successful runs with the number of runs that finished their execution.
+This means that, for example, if an instance was run 10 times, giving 4 successful models, but failing to finish 2 runs due to memory exhaustion or an other OS issue, the accuracy would be 50\% (4/8) instead of 40\% (4/10).
 Further, these individual accuracies were averaged.
-We do not believe this was the right way to calculate the accuracy, because, this allows one to have high-accuracy method with a low number of successful runs.
+We do not believe this was the right way to calculate the accuracy because this allows one to have a high-accuracy method with a low number of successful runs.
 For example, if method A finishes all of its runs, out of which 650 are successful, its total accuracy will be 50\%.
-On the other hand, one can have a method B that finishes instances execution in only 4 out of 10 runs, giving 2 successful models each time -- its per-instances accuracy will be 50\%, and after averaging across all instances it will be also 50\%.
-So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.
-Also, note that our calculation cannot overestimate \textsc{RILS-ROLS} exact model accuracy, since denominator is always maximal (1300) -- in essence, non-finished runs are counted as non-successful.}
-
-First, the omnibus rank-based Friedman’s test for all approaches was conducted. 
-The number of ranks is 1300, i.e., for each run of each method, the separate rank is calculated.
-Rank is based on the value of indicator variable, which takes 1 if the method delivers correct model in a given run, otherwise it takes value of 0, no matter if method finished and delivered incorrect model, or the method did not finish at all.
-Further, the ranks are averaged and used to test the null hypothesis, which states that there is   statistical differences between the average ranks of all competitors.
+On the other hand, one can have method B that finishes instance execution in only 4 out of 10 runs, giving 2 successful models each time; its per-instances accuracy will be 50\%, and after averaging across all instances, it will also be 50\%.
+Methods A and B will therefore have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.
+Also note that our calculation cannot overestimate \textsc{RILS-ROLS} exact model accuracy, since the denominator is always maximal (1300).
+In essence, non-finished runs are counted as non-successful.}
+
+We first conducted the omnibus rank-based Friedman’s test for all approaches. 
+The number of ranks is 1300, i.e., a separate rank is calculated for each run of each method.
+The rank is based on the value of the indicator variable, which takes 1 if the method delivers the correct model in a given run; otherwise it takes value 0, no matter if the method has finished and delivered an incorrect model, or the method did not finish at all.
+The ranks are further averaged and used to test the null hypothesis, which states that there are statistical differences between the average ranks of all competitors.
 In the case the null hypothesis $H_0$ was rejected, pairwise comparisons were further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}.
@@
 
-In each CD plot, the 15 competitors are placed on the horizontal axis according to their average ranking.
-Thereafter, the CD score is computed for a significance level of 0.05.
-If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.
+In each CD plot, 15 competitors are placed on the horizontal axis according to their average ranking.
+Thereafter, the CD score is computed for the significance level of 0.05.
+If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar that links statistically equal approaches is drawn.
 This analysis is done for all three levels of noise, and the corresponding CD plots are shown in Figures~\ref{fig:CDplots-no-noise}-\ref{fig:CDplots-noise0.01}.
@@
 \begin{itemize}
-	\item  Concerning the no-noise scenario, \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models over all runs.
-The second best average ranking is achieved by \textsc{AI-Feynman} algorithm.
+	\item  Concerning the no-noise scenario, the \textsc{RILS}-\textsc{ROLS} method returns the best average ranking in terms of the number of obtained exact models over all runs.
+The second best average ranking is achieved by the \textsc{AI-Feynman} algorithm.
 There is a statistically significant difference between these two approaches.
@@
 	\item  For noise 0.001, the situation is similar.
-\textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking.
-The second best ranking is obtained by \textsc{AI-Feynman} algorithm.
+The \textsc{RILS}-\textsc{ROLS} method again obtains the best average ranking.
+The second best ranking is obtained by the \textsc{AI-Feynman} algorithm.
 There is a statistically significant difference between the results obtained by these two approaches.
-The third best approach is \textsc{AFP-FE} which performs statistically worse than \textsc{AI-Feynman}.
-	\item  When noise level is 0.01, \textsc{RILS-ROLS} method is significantly better than other methods.
+The third best approach is \textsc{AFP-FE}, which performs statistically worse than \textsc{AI-Feynman}.
+	\item  When the noise level is 0.01, the \textsc{RILS-ROLS} method is significantly better than other methods.
 The second best is \textsc{AFP-FE}, followed by \textsc{DSR}, and \textsc{AFTP}.
-The latter three approaches perform statistically equal.
-\textsc{AI-Feynman} is fourth, and on pair with \textsc{gplearn}.
-Note that the average ranking of \textsc{AI-Feynman} method declined significantly with high noise, which is not the case with \textsc{RILS}-\textsc{ROLS} method.
+The latter three approaches perform statistically equally.
+\textsc{AI-Feynman} is fourth, as is \textsc{gplearn}.
+Note that the average ranking of the \textsc{AI-Feynman} method declines significantly with high noise, which is not the case with the \textsc{RILS}-\textsc{ROLS} method.
 
@@
 
-In this section we study the scalability of \textsc{RILS-ROLS} w.r.t. size of instances problems under different levels of noise.
-Since we do not compare \textsc{RILS-ROLS} to other competitors here, but just assess the method scalability and sensitivity to noise, the experimental setup is different.
-First, we run each instance only once -- note that there are 5 randomly generated instances for each of 47 combinations of (size, variable count).
-Second, the exit criteria are different: 1) maximal running time is 300 seconds instead of 1 hour, and 2) maximal number of fitness evaluations is 100 thousands instead of 1 million.
+In this section we study the scalability of \textsc{RILS-ROLS} w.r.t. size of instance problems under different levels of noise.
+Since we do not compare \textsc{RILS-ROLS} to other competitors here, but just assess method scalability and sensitivity to noise, experimental setup is different.
+First, we run each instance only once -- note that there are 5 randomly generated instances for each of 47 combinations (size, variable count).
+Second, the exit criteria are different: 1) maximal running time is 300 seconds instead of 1 hour, and 2) maximal number of fitness evaluations is 100,000 instead of 1,000,000.
 As before, the test set takes 25\% of total data. 
-For the sake of having simpler presentation, we split the instances from \textsc{Random} benchmark into three parts as follows. 
+For the sake of having a simpler presentation, we split the instances from the \textsc{Random} benchmark into three parts as follows: 
 \begin{itemize}
@@
 
-The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped in accordance to above-mentioned parts ($x$-axis).
-The exact solution accuracy of \textsc{RILS}--\textsc{ROLS} is shown on $y$-axis.
+The results are displayed in Figure~\ref{fig:compExact_noise_size}, grouped in accordance to the above-mentioned parts ($x$-axis).
+The exact solution accuracy of \textsc{RILS}--\textsc{ROLS} is shown on the $y$-axis.
 
@@
 
-The following conclusions may be drawn from there.
+This leads to the following conclusions:
 
 \begin{itemize}
-	\item   As expected, the accuracy (exact percentage) is highest for the small-sized instances -- it is sightly bellow 90\% in no-noise scenario.
+	\item  As expected, the accuracy (exact percentage) is highest for small-sized instances -- it is sightly below 90\% in a no-noise scenario.
 For noisy data, the accuracy naturally decreases as the level of noise increases.
-For example, on the small-sized problem instances with the noise level of 0.001, and 0.01, the accuracy achieved by \textsc{RILS}-\textsc{ROLS} is still reasonably high, at about 55\%~ and 34 \%, respectively.
-	\item For the medium-sized instances, when there is no noise, the exact percentage rate is slightly bellow 50\%.
-It also decreases by as the level of noise increases -- for the highest level of noise (0.01), the accuracy of \textsc{RILS}-\textsc{ROLS} method is just about 6\%.
-	\item For the large-sized instance problems, where no noise is included, the exact percentage is about 25\%, which means that the increase in size affects the algorithm's performance, but not dramatically.
+For example, on the small-sized problem instances with the noise level of 0.001 and 0.01, the accuracy achieved by \textsc{RILS}-\textsc{ROLS} is still reasonably high, at about 55\%~ and 34\%, respectively.
+	\item For medium-sized instances when there is no noise, the exact percentage rate is slightly below 50\%.
+It also decreases as the level of noise increases -- for the highest level of noise (0.01), the accuracy of the \textsc{RILS}-\textsc{ROLS} method is just about 6\%.
+	\item For large-sized instance problems where no noise is included, the exact percentage is about 25\%, which means that the increase in size affects the algorithm's performance, but not dramatically.
 
 	\item We can conclude that increased formula size and noise level jointly contribute to deterioration of overall \textsc{RILS-ROLS} accuracy, which is expected and natural.
-The diagram suggests that this deterioration behaves similar across different levels of noise when instance size changes from small to medium -- almost linearly, and with almost exact slope.
-On the other hand, the relative deterioration of accuracy under no-noise level, when going from medium to large instance is higher than under noisy data.
-Possible explanation for this is that the exact solution accuracy of medium instances is already very deteriorated in noisy scenario, therefore, further increase in size does not have significant impact.
+The diagram suggests that this deterioration behaves similarly across different levels of noise when instance size changes from small to medium almost linearly, and with almost exact slope.
+On the other hand, the relative deterioration of accuracy under no-noise level, when going from a medium to a large instance, is higher than under noisy data.
+A possible explanation for this is that the exact solution accuracy of medium instances has already significantly deteriorated in a noisy scenario.
+A further increase in size therefore does not have a significant impact.
 \end{itemize}
 
-Results for the $R^2 > 0.999$ accuracy are presented in Figure~\ref{fig:compR2_noise_size}.
+Results for $R^2 > 0.999$ accuracy are presented in Figure~\ref{fig:compR2_noise_size}.
 
@@
 
-The following conclusions may be drawn from these results.
+The following conclusions may be drawn from these results:
 
@@
 
-	\item For the small-sized instances, where no noise is included, \textsc{RILS}-\textsc{ROLS} delivers almost the perfect score.
-In the presence of a low noise (0.001), this percentage is still holding high, at about 95\%.
+	\item For small-sized instances where no noise is included, \textsc{RILS}-\textsc{ROLS} delivers almost the perfect score.
+In the presence of low noise (0.001), this percentage is still holding high, at about 95\%.
 In case when there is a lot of noise (0.01), these percentages deteriorate significantly, but still come at respectable 66\%.
 
-	\item Concerning  the medium-sized instances in no-noise scenario, accuracy is around 65\%.
-Having low noise does not affect the results too much.
-However, under high noise, the impact is significant, very similar to effect observable in small-sized instances -- it reduces accuracy to just $\approx$30\%.
-
-	\item For the large-sized instances without noise, the accuracy is around 60\%, which is very small relative deterioration in comparison to middle-sized instances.
+	\item Concerning medium-sized instances in a no-noise scenario, accuracy is around 65\%.
+Having low noise does not affect the results considerably.
+However, under high noise, the impact is significant and very similar to the effect observable in small-sized instances -- it reduces accuracy to just $\approx$30\%.
+
+	\item In the case of large-sized instances without noise,  accuracy is around 60\%, which is very small relative deterioration in comparison to middle-sized instances.
 Not surprisingly, large instances under high noise are the most difficult to solve -- only 20\% reached $R^2 > 0.999$.
@@
 
-In the rest of the section, we investigate the sensitivity of \textsc{RILS}-\textsc{ROLS} to variable count under varying levels of noise.
-There are three bar plots generated per each level of noise, Figures~\ref{fig:compExact_noise_varcnt}.
-The instances are grouped according to different variable count ($x$-axis).
-For each group, the exact percentages are shown on $y$-axis.
+In the rest of the section, we investigate the sensitivity of \textsc{RILS}-\textsc{ROLS} to the variable count under varying levels of noise.
+There are three bar plots generated per each level of noise presented in Figures~\ref{fig:compExact_noise_varcnt}.
+The instances are grouped according to a different variable count ($x$-axis).
+Exact percentages for each group are shown on the $y$-axis.
 
@@
 
-The following conclusions can be drawn from these results.
+These results lead to the following conclusions:
 
@@
 	\item For data without noise, the exact percentage of \textsc{RILS}-\textsc{ROLS} slightly decreases as the  number of variables increases. 
-	\item The exact percentages drop off with the presence of a larger noise level. As expected, higher noise means smaller exact percentage.
-	\item Interestingly, in the presence of noise in data, the highest exact percentages are not obtained for the instances with a single input variable, but for those with two or three.
+	\item The exact percentage drops off in the presence of a higher level of noise. As expected, higher noise means smaller exact percentage.
+	\item Interestingly, in the presence of noise in data, the highest exact percentages are not obtained for instances with a single input variable, but for those with two or three.
 This is probably due to the expected level of \emph{non-linearity} in instances.
-Namely, when the size of instance is fixed, instances with less input variables will have to use more operations to compensate for the lack of input variables.
-(Note that expression size is calculated simply by counting all nodes in the expression tree, whether these nodes are operations, constants or variables.) Therefore, instances with less variables will more heavily use operations and their compositions, paving a way to more \emph{difficult} functional structure.
-	The reason this is not an issue for no-noisy data is because \textsc{RILS-ROLS} will have to wander less -- there will be no so many contradictory search directions as with noisy data.
+Namely, when the size of an instance is fixed, instances with fewer input variables will have to use more operations to compensate for the lack of input variables.
+Note that expression size is calculated simply by counting all nodes in the expression tree, whether these nodes are operations, constants or variables.
+Therefore, instances with fewer variables will use operations and their compositions more heavily, paving the way to a more \emph{difficult} functional structure.
+	The reason this is not an issue for no-noisy data is because \textsc{RILS-ROLS} will have to \emph{wander} less -- there will not be so many contradictory search directions as with noisy data.
 \end{itemize}
 
-\textsc{RILS}-\textsc{ROLS} running times for \textsc{Random} benchmark are shown in Figure~\ref{fig:runtime_rils_rols}. Instances are grouped w.r.t.\ number of variables ($x$-axis). 
-As one could expect, average running time is getting increased with the increase of the number of variables. 
-\textsc{RILS-ROLS} usually terminates because the maximal number of fitness evaluation is reached (100 thousands), therefore average running times are bellow 300 seconds, which is time-based exit criterion.
+\textsc{RILS}-\textsc{ROLS} running times for \textsc{Random} benchmark are shown in Figure~\ref{fig:runtime_rils_rols}. Instances are grouped w.r.t.\ the number of variables ($x$-axis). 
+As one could expect, the average running time increases with the increase in the number of variables. 
+\textsc{RILS-ROLS} usually terminates because the maximal number of fitness evaluation is reached (100,000) with average running times below 300 seconds, which is the time-based exit criterion.
 
@@
 
-In this paper, we dealt with solving the well-known symbolic regression (SR)  problem.  
-We proposed a meta-heuristic approach, called \textsc{RILS}-\textsc{ROLS}, built upon the iterated local search (ILS) scheme.
-The crucial element of this scheme is the ordinary least square method (OLS), used to efficiently determine best-fitting linear coefficients within solution equations.
-Another key aspect is the utilization of a carefully constructed fitness function. It combines three important measures of the solution: RMSE, $R^2$, and the solution size. 
-Further, we designed an efficient local search that systematically explores the solution space around candidate solution.
-
-\textsc{RILS-ROLS} method is compared to the 14 other competing methods from the literature on two ground-truth benchmark sets from the literature, named \textsc{Feynman} and \textsc{Strogatz}.
-The experimental evaluation confirmed the quality of our method -- \textsc{RILS-ROLS} produced the best average ranking results in terms of exact model accuracy under varying levels of noise in data.
-In details, our algorithm was able to find the right model in 60.62\%, 42.08\%, and 34.77\% under no-noise, low-level noise and high-level noise, respectively.
-The second best approach \textsc{AI-Feynman} obtains fairly worse percentages: 52.65\%, 31.89\% and 20\%.
-
-In addition to well-known benchmarks from literature, we introduced a new non-biased benchmark set of randomly generated instances, labeled by \textsc{Random}. 
+In this paper we dealt with solving the well-known symbolic regression (SR)  problem.  
+We proposed a meta-heuristic approach called \textsc{RILS}-\textsc{ROLS}, built upon the iterated local search (ILS) scheme.
+The crucial element of this scheme is the ordinary least square method (OLS), used to efficiently determine the best-fitting linear coefficients within solution equations.
+Another key aspect is the utilization of a carefully constructed fitness function which combines three important measures of the solution: RMSE, $R^2$, and solution size. 
+Further, we designed an efficient local search that systematically explores the solution space around the candidate solution.
+
+The \textsc{RILS-ROLS} method is compared to 14 other competing methods from the literature on two ground-truth benchmark sets from the literature: \textsc{Feynman} and \textsc{Strogatz}.
+Experimental evaluation confirmed the quality of our method -- \textsc{RILS-ROLS} produced the best average ranking results in terms of exact model accuracy under varying levels of noise in data.
+Our algorithm was able to find the right model with 60.62\%, 42.08\%, and 34.77\% accuracy under no-noise, low-level noise and high-level noise, respectively.
+The second best approach, \textsc{AI-Feynman}, obtains fairly worse percentages: 52.65\%, 31.89\%, and 20\%.
+
+In addition to well-known benchmarks from the literature, we introduced a new non-biased benchmark set of randomly generated instances, labeled by \textsc{Random}. 
 This benchmark was used to test \textsc{RILS}-\textsc{ROLS} scalability, by varying the size of the model and the number of variables.
 
-In the future work, one could think of constructing a hybrid of \textsc{RILS-ROLS} method with some other meta-heuristics to further boost the quality of the obtained results.
-For example, replacing ILS scheme of \textsc{RILS-RILS} with a more general Variable neighbourhood search (VNS) scheme is a reasonable option.
+In the future, one could think of constructing a hybrid of \textsc{RILS-ROLS} method with some other meta-heuristics to further boost the quality of the obtained results.
+For example, replacing the ILS scheme of \textsc{RILS-RILS} with a more general Variable neighborhood search (VNS) scheme is a reasonable option.
 Also, \textsc{RILS-ROLS} could be used to solve practical problems from various domains.
-For example, it can be used in physics or chemistry to help setting-up reasonable hypotheses or to obtain valuable insights on obtained experimental evaluations.
-One more improvement direction is incorporating top-level constraints into the method.
-For example, if one knows that the modeled function needs to be monotonically decreasing or differentiable, or both, this knowledge could be used to alter the search -- eliminate inadequate parts of the search space (hard constraint) or more \emph{subtly} penalize this behavior through fitness function (soft constraint).
+For example, it can be used in physics or chemistry to help set up reasonable hypotheses or obtain valuable insights into obtained experimental evaluations.
+Another improvement direction is incorporating top-level constraints into the method.
+For example, if one knows that the modeled function needs to be monotonically decreasing or differentiable, or both, this knowledge can be used to alter the search -- eliminate inadequate parts of the search space (hard constraint) or more subtly penalize this behavior through fitness function (soft constraint).
 
@@
 
-\textsc{RILS-ROLS} algorithm is available for install on the well-known Python package repository \url{https://pypi.org}, so it can be easily installed by typing commands:
+\textsc{RILS-ROLS} algorithm is available for installation in the well-known Python package repository \url{https://pypi.org}, so it can be easily installed by typing commands:
 \begin{python} 
@@
 \end{python}
-\textsc{RILS-ROLS} project page is at \url{https://pypi.org/project/rils-rols}. Here, one can find a minimal working example on how-to-use \textsc{RILS-ROLS}:
+\textsc{RILS-ROLS} PyPI project page is available at \url{https://pypi.org/project/rils-rols}. Here, one can find a minimal working example on how to use \textsc{RILS-ROLS}:
 
@@
 Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found at the project GitHub page \url{https://github.com/kartelj/rils-rols}.
-In addition, there is a
 
@@
   \section*{Availability of data and materials}%% if any
- All accompanying resources regarding this paper can be found under the repository \url{https://github.com/kartelj/rils-rols}.
+ All accompanying resources regarding this paper can be found in the GitHub repository \url{https://github.com/kartelj/rils-rols}.
 

### 2022-12-13 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Final proofread

@@
 Beside these, the following set of constants enters the search space explicitly: $-1$, $0$, $1$, $2$, $\pi$, and $10$.
-Before we provide details of our method for solving SR, we will explain the two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least squares (OLS).
+Before we provide details of our method for solving SR, we will explain the two building blocks of \textsc{RILS-ROLS}: 1) iterated local search (ILS) and 2) ordinary least square (OLS).
 
@@
 \begin{algorithm}
-     \textbf{Input}: solution $s$ \\
-     \textbf{Output}: local perturbations (1-perturbations) of solution $s$ -- $s_{perturbations}$ \\
+
 	\begin{algorithmic}[1] 
+		\Statex   \textbf{Input}: solution $s$ 
+		\Statex \textbf{Output}: local perturbations (1-perturbations) of solution $s$ -- $s_{perturbations}$
 		\Procedure{All1Perturbations}{$s$}
@@
 This reduction is reasonable, since normalization preserves the essential functional form.
-Note that coefficients get tuned later: the linear coefficient during the OLS phase, and the remaining ones during local search.
+Note that coefficients get tuned later: the linear coefficient during the OLS phase, and the remaining ones during local search, see Section~\ref{sec:ls}.
 
@@
 \begin{algorithm}
-	\hspace*{\algorithmicindent} \textbf{Input}: solution $s$, node $n$\\
-	\hspace*{\algorithmicindent} \textbf{Output}: 1-perturbations of solution $s$ around node $n$
+
 	\begin{algorithmic}[1]
+		\Statex  \textbf{Input}: solution $s$, node $n$ 
+		\Statex  \textbf{Output}: 1-perturbations of solution $s$ around node $n$
 		\Procedure{All1PerturbationsAroundNode}{$s$, $n$}
@@
 \emph{Case 1}. 
-The observed node $n$ is the whole tree $s$ (see line ~\ref{alg:alg4-case-1} in Algorithm~\ref{alg:pertNode}).
+The observed node $n$ is the whole tree $s$ (see line~\ref{alg:alg4-case-1} in Algorithm~\ref{alg:pertNode}).
 Based on  the previous exemplary expression tree, this means that the multiplication node that connects $(x+y^3)$ and $x/\sqrt{y}$ is to be changed.
@@
 \emph{Case 2}. 
-Node $n$ has the arity of at least 1 (see line ~\ref{alg:alg4-case-2} in Algorithm~\ref{alg:pertNode}). This means that the left subtree exists, so the left subtree node is to be changed. 
+Node $n$ has the arity of at least 1 (see line~\ref{alg:alg4-case-2} in Algorithm~\ref{alg:pertNode}). This means that the left subtree exists, so the left subtree node is to be changed. 
 For example, if $n=x+y^3$, the overall perturbation might be $(x/y^3)+x/\sqrt{y}$ (addition is replaced by division). 
@@
 \begin{algorithm}
-	\hspace*{\algorithmicindent} \textbf{Input}: perturbation $p$, sample training dataset $D_{tr}'$ \\
-	\hspace*{\algorithmicindent} \textbf{Output}: local optimum $bp$ in the vicinity of perturbation $p$
+
 	\begin{algorithmic}[1] 
+		\Statex \textbf{Input}: perturbation $p$, sample training dataset $D_{tr}'$   
+		\Statex \textbf{Output}: local optimum $bp$ in the vicinity of perturbation $p$
 		\Procedure{LocalSearch}{$p$, $D_{tr}'$}
@@
 It found the exact solution in 57.84\% of runs for \textsc{Feynman} instances.
-It is even more impressive in solving \textsc{Strogatz} instances, when it was successful in 83.57\% runs.
+It is even more impressive in solving \textsc{Strogatz} instances, as it was successful in 83.57\% runs.
 The second best performing  approach is \textsc{AI-Feynman}, successful in 55.78\% runs for the \textsc{Feynman} set, and 27.14\% runs for the problem instances from the benchmark set \textsc{Strogatz}.
@@
 
-In addition to well-known benchmarks from the literature, we introduced a new non-biased benchmark set of randomly generated instances, labeled by \textsc{Random}. 
+In addition to well-known benchmarks from the literature, we introduced a new non-biased benchmark set of randomly generated instances.  %, labeled by \textsc{Random}. 
 This benchmark was used to test \textsc{RILS}-\textsc{ROLS} scalability, by varying the size of the model and the number of variables.

### 2023-02-23 rils_rols/rils_rols.py
RILS-ROLS ensemble added.

@@ -148,7 +148,7 @@ class RILSROLSRegressor(BaseEstimator):
         self.model_simp = simplify(str(best_solution), ratio=1)
         self.model_simp = self.round_floats(self.model_simp)
         self.model = Solution([Solution.convert_to_my_nodes(self.model_simp)], self.complexity_penalty)
-        return (self.model, self.model_simp)
+        return (self.model, self.model_simp, Solution.fit_calls, self.main_it, self.ls_it)
     
     def round_floats(self, ex1):
         round_digits = int(math.log10(1/self.error_tolerance))

### 2023-02-23 rils_rols/rils_rols_ensemble.py

@@ -1,11 +1,11 @@
-import math
 from random import Random
 from sklearn.base import BaseEstimator
-import copy
 from sympy import *
 from .node import Node
 from .rils_rols import RILSROLSRegressor
 from joblib import Parallel, delayed
+from time import time
+from math import inf
 
 import warnings
 
@@ -25,14 +25,21 @@ class RILSROLSEnsembleRegressor(BaseEstimator):
         random_states = [rg.randint(10000, 99999) for i in range(self.parallelism)]
         self.base_regressors = [RILSROLSRegressor(max_fit_calls=max_fit_calls, max_seconds=max_seconds, complexity_penalty=complexity_penalty,
             error_tolerance=error_tolerance, random_perturbations_order=True, random_state=rgs) for rgs in random_states]
+        self.main_it = 0
+        self.ls_it = 0
+        self.fit_calls = 0
 
     def fit(self, X, y):
+        self.start = time()
         # now run each base regressor (RILSROLSRegressor) as a separate process
         results = Parallel(n_jobs=len(self.base_regressors))(delayed(reg.fit)(X, y) for reg in self.base_regressors)
         print("All regressors have finished now")
-        best_model, best_model_simp = results[0]
+        best_model, best_model_simp, _, _, _ = results[0]
         best_fit = best_model.fitness(X, y, False)
-        for model, model_simp in results:
+        for model, model_simp, fit_calls, main_it, ls_it in results:
+            self.fit_calls+=fit_calls
+            self.main_it+=main_it
+            self.ls_it+ls_it
             model_fit = model.fitness(X,y, False)
             if self.base_regressors[0].compare_fitness(model_fit, best_fit)<0:
                 best_fit = model_fit
@@ -42,6 +49,7 @@ class RILSROLSEnsembleRegressor(BaseEstimator):
         self.model = best_model
         self.model_simp = best_model_simp
         print('Best model is '+str(self.model) + ' with '+str(best_fit))
+        self.time_elapsed = time()-self.start
 
     def predict(self, X):
         Node.reset_node_value_cache()
@@ -50,7 +58,7 @@ class RILSROLSEnsembleRegressor(BaseEstimator):
     def size(self):
         if self.model is not None:
             return self.model.size()
-        return math.inf
+        return inf
 
     def modelString(self):
[…]

### 2023-02-23 testPMLB_ground_truth.py

@@ -1,16 +1,15 @@
 from pmlb import fetch_data
 from sklearn.model_selection import train_test_split
 from rils_rols.rils_rols import RILSROLSRegressor
-from rils_rols.node import Node
+from rils_rols.rils_rols_ensemble import RILSROLSEnsembleRegressor
 from rils_rols.utils import noisefy, R2, RMSE
-from os import listdir, stat
 import sys
-from sklearn.utils.estimator_checks import check_estimator
+#from sklearn.utils.estimator_checks import check_estimator
 import numpy as np
 
 #check_estimator(RILSROLSRegressor())
 
-if len(sys.argv)!=8:
+if len(sys.argv)<8:
     print("Usage: <working part or -1> <parts >=1> <random seed> <max time (s)> <max fit calls> <size penalty> <noise level>")
     print("Passed parameters were:")
     print(sys.argv[1:])
@@ -27,9 +26,14 @@ noise_level = float(sys.argv[7])
 test_size = 0.25
 label="target"
 
+parallelism = 1
+if len(sys.argv)>8:
+    parallelism = int(sys.argv[8])
+
 pmlb_cache = "../../../pmlb/datasets"
 
[…]
